\nopagenumbers 
\font\twelverm=cmbx12 at 12pt
\centerline{\bf\twelverm THE ABYSSINIAN PRINCE \#313}
\line{\hfil January 20, 2008}    
\smallskip                                                    
\settabs 3 \columns 
\beginsection

\medskip

Produced by Jim Burgess, 664 Smith Street, Providence, RI 02908-4327  USA,
(401)351-0287 
 
\noindent Accessible through Internet at burgess of world.std.com (all E-Mail
addresses are reported in this format, replace the `` of '' with ``@''; if you 
bounce try sending to me from another account. 
Some of you have been getting bounced messages from
my ISP's spam protection, if that happens to you, USE my backup E-Mail
at jfburgess of gmail.com!!!  Don't complain that my E-Mail keeps bouncing
without forwarding the bounced message to that address.
Then I can forward it to the ISP help to get it dealt with.
 
\noindent Web Page Address: /Postal/Zines/TAP/index.html

\bigskip

I expect ALL players to be signed up on the E-Mail notification list for the szine,
see below.
Some of you have been complaining about this, but it is up to you to get on this list,
it's easy, come ask me if you have trouble.
THIS IS A PROBLEM, sign up now if you're playing!!!

Yes, this is really, really late.  Work this year with my job switch has been
completely out of control.  I am using the szine as a sign of this, that my 
life will be back into some semblance of balance once I get this szine back
on track.  I mean that to happen now, but who knows, maybe I am not anticipating
well.  In any case, enough of that, you want to get this going again.
I have limited some of the really, really out of date stuff, but yes,
the Red Sox win the World Series again!!!
I knew it was done in I think it was Game 6 of the AL Championship Series
when J.~D.~Drew came up with the bases loaded early in the game. 
He has had a tough time with the Boston fans and his contract this year.
But I think it has been a year of adjustment for him and he is going to 
be a great Boston Red Sox player in the next few years.
He is very calm and has taken his troubles this year in stride in ways
that the impatient Boston fans just don't seem to appreciate.
Anyway, after ALL the difficulties, after all the comments, 
I turned to Charlotte and said, J.~D.~ is going to hit a home run
right here, and he needs to do it, to turn his season around.
On the next pitch, over the fence (and he's had almost no power all season),
and the grand slam was there.
Right there, I knew the World Series was won and had no serious tension in 
any game from there on out.
The poor Colorado Rockies had a great finishing stretch but they really 
were just completely outclassed.
I always think and say that we are all defined much more by how we deal
with adversity than how we deal with success.  
That's why I like baseball so much, since it's filled with adversity.
And J.~D.~is a good guy and was a good signing for the Red Sox.
As I write this back a month or two ago, we were trying to get the 
other really good guy we need to
sign for next year, Mike Lowell, into the fold.  If we didn't sign Lowell
then SOME people would have wanted to sign A-Rod and A-Rod does NOT handle adversity
well and I have zero desire to see him as a Red Sox player.  
This view is commonly held here in New England.....
anyway, updating more recently, of course the junior Steinbrenner stepped in
and around Scott Boras to sign A-Rod for the Yankees, which ensures the
Yankees won't win another World Series for another decade.
And, Lowell is resigned for Boston so that they basically return everyone,
with lots of the young players lobbying for more playing time.

Doug Kent is continuing to produce great issues of {\it Diplomacy World} on
schedule, and the most recent 130 page monster hit the Century Mark.
Think about contributing, most of you reading this have something to say.
Even if you just want to write a short note, do so, please.
You can send things for {\it DW} either to me or Doug.
The other big news is that the new Diplomacy National World Cup is 
ongoing, more on that below.
And, I've been having fun actually playing Dip again.
So I have been busy, just the szine hasn't gotten to the top of the list.

\bigskip
%Dave Partridge's unlisted phone number 603-672-2879 -- probably corrected!!!
%Tinamou players: Schwarzschild:  Graham Wilson (NO 
%but E-mails: grahamaw of home.com (or gwilson of dvnet.com)),
%Berry Renken, Heath Gardner
%Copernicus:  Warren Goesle, Heath Gardner, Art Schleinkofer, Bruce Reiff,
%Eric Brosius, Bob Dowrey
%Tour De Farce:  Jim Burgess, Eric Brosius, Warren Goesle, Sara Reichert,
%Phil Reynolds, Rick Desper
%Milk and Cookies: Jim Burgess, Warren Goesle, Sara Reichert, Phil Reynolds,
%Rick Desper, Richard Weiss, John Schultz
%Who's Your Buddy:  Sara Reichert, Phil Reynolds, Art Schleinkofer, 
%Brad Wilson, Rick Copeland, Karl Muller

The postal sub price is still
\$1.50 per issue in the US and Canada,
with double that for other foreign subbers(or \$3.00 per
issue sent airmail).
Players in current games and standbys will
continue to get the issues for free, and future game starts 
(except for Nuclear Yuppie Evil Empire Diplomacy, which is free) cost 
\$20.00 (\$15.00 for a life of the
game subscription and \$5 for the NMR Insurance.
Anyone may play in subszines 
for free and just jack up the issue page count.
Since I have to get caught up this issue with all sorts of subszines, 
I'm going to be fairly limited with other items this issue.  
See the revised game start announcements below!

Check out the connections in the Diplomatic Pouch with all of
the information you need to play Diplomacy on the Internet at:
/

I also have taken over the Postal port/DipPouch/Postal

\noindent and {\it TAP} on the web is there at:
/Postal/Zines/TAP/index.html

where the szine resides in html format. 
Presently, issues from \#190 to the current issue
are there, and I will be updating the back issues gradually someday. 
 
Peter Sullivan's subszine is out of stasis, and all the
back issues can be accessed via :

http://www.burdonvale.co.uk/octopus/index.html.

Peter is now back at least sometimes.
Rip Gooch is probably permanently missing.
Dave Partridge had been picking up the choo-choo
game slack.
Contact Dave
at rebhuhn of rocketmail.com for more info on getting into choo-choo games
and other sorts of different games.
And Andy York has been my most frequent subszine guest lately!!!
He's been in every issue, thanks, Andy!!!
And so has Doug Kent, so we have a full stable of subszines.
And Michael Lowrey gets his in every few issues too!

The {\it TAP} mailing list has moved!
It now is even BETTER protected than it was.
I even have a bit of trouble posting to it.
To post to this list, send your email to: tap of diplom.org.
But this is completely moderated, it won't go out to the list unless
I approve it.
In general, I intend to keep traffic down to just the szine, as we've
been doing and I'll put your LOCs in here.
I {\bf EXPECT} all players to be on this list, especially those of you who
are from foreign countries!!! 
You need this to find out when the szine is up on the web to check in on results.

General information about the mailing list is at:
/mailman/listinfo/tap

You can sign up from there, or send E-Mails to:
Tap-request of diplom.org;
with the word `help' in the subject or body (don't include the
quotes), and you will get back a message with instructions.
You must know your password to change your options (including changing
the password, itself) or to unsubscribe.  
Normally, Mailman will remind you of your diplom.org mailing list
passwords once every month, although you can disable this if you
prefer.  This reminder will also include instructions on how to
unsubscribe or change your account options.  There is also a button on
your options page that will email your current password to you.
A big, big thank you for Millis Miller for setting this all up!!

\bigskip

\centerline{\bf THE SEARCH FOR JERRY JONES}

\smallskip

With the 100th issue of {\it Diplomacy World} upcoming, the ONLY
former publisher who has not definitively been located is Jerry
Jones.  Doug Kent and I have some idea where he is, but we've not
succeeded in getting him to respond to us.  Find him and win
a fifty dollar prize.

\bigskip

Feel free to spend the time looking for some of the backlog.
Let's get Margaret, Derek, Sylvain, Steve, Ed, Tom, Gregory, and 
ESPECIALLY Kevin found too!!!
This is a regular continuing feature of the szine
and I will be introducing a new ``search for'' every five issues.
Moreover, you can win a \$25 prize for finding some previous
target who went unfound in the original \$50 period.
That means that if Margaret Gemignani or 
Steve Heinowski or Ed Henry or Tom Hurst or 
Gregory Stewart or Derek Nelson or Sylvain LaRose or John Smythe
is ``found'' from now on it is worth \$25.

\bigskip

Winners will receive credit for Dip hobby activities
that I will pay out as requested by the winner.
Subscribe to szines here or abroad, run your
own contests, publish a szine, finance a web page, 
GO TO A DIPLOMACY CONVENTION or whatever.
Spend it all right away or use me as a bank to cover hobby activities
for years.
What must you do to win?
Get me a letter to the editor for {\it TAP} from the person we're
searching for.

This is very important, just finding them doesn't do it.
They have to write me a letter.     
The final judge as to the winner of any contest will be the target 
himself and I reserve the right to investigate the winning entry.
When you find someone I'm looking for, you should ask him to send me a 
letter for print that includes a verification of who ``found'' him.
%Michael Swift, Mike Stewart, and 
%Jason Yarbrough , Tim Stabosz, 
%Eric Ozog has $25
%Leslie Obata is owed $25
%Derek Nelson, winner of the first postal game in Graustark.  I last saw him
%at the '76 DipCon in Baltimore.
%Charles Wells, former publisher
%John McCallum, former publisher (Brobdignag, SerenDip, etc.)
%Dan/Charles Brannan, former publisher (Wild 'n Wooly)

\bigskip


\bigskip

\centerline{\bf INTERNATIONAL SUBSCRIPTION EXCHANGE NEWS}

\smallskip

John Harrington and I have agreed to close the ISE.
In this age of PayPal, the traffic on the ISE had fallen almost to zero,
and what was left almost entirely was me facilitating orders of 
Breaking Away and John's other Fiendish Games.
So, I'm still going to help John out with that, but there will be no
ISE.
If anyone still needs assistance with this, though, since I'm helping
John out, like if you're in a foreign country and need to send dollars
for dipping things to someone in the US, I may be able to help you out.

\bigskip  

\centerline{\bf WORLDMASTERS04 SECTION}

\smallskip

See the Yahoo Group wm04-results for more information and 
for details on progress on the WORLDMASTERS04, the Finals are now 
into 1903.  
You can join the Yahoogroup too!

In the finals are Mike Tombu as Austria, Mike ``Smacko" McMillie as
England, Jerry ``JT" Fest as France, Georg ``Shef" Kotschy as Germany,
Randolph Ruff as Italy, Michael Weinzimer as Russia, and Tim Sweeney
as Turkey.  If you had asked me before the game started, I would have
been very worried about the central powers and seeing a collapse toward
the center of the board.  At the end of 1903 Georg made an error in trying
to remove a non-existent unit, so his Fleet Sweden was removed by default.
This leaves him with only three units left, and Smacko will easily be able
to take Sweden in 1904, already having Denmark.  
Anyway, my advance musings (you'll have to take
my word for it that I made them before knowing any results) came to pass
in the West, but not really in the East.  Smacko and JT are running away
with the game so far, with Smacko having six centers and JT seven.
Shef has only Kiel and Munich to go with the abandoned Sweden, as JT
already has Berlin and Shef is pretty well surrounded.
The key question (as Smacko built fleet Edinburgh, but JT built fleet
Brest) is whether EF stays together now.  Michael only has the four
home plus Rumania, Turkey has only Bulgaria, Italy is now up to five
having taken Greece and built another fleet Naples.  Otherwise, the
Eastern powers (especially Mike Tombu in Austria) seem pretty moribund
with not much going on.  Not a stellar WorldMasters final so far, but
we can hope it picks up.
The very latest, as I write today, is that Smacko and JT are still 
sweeping the board with no serious ``stop the leaders" coalition forming.
Expect Smacko and JT to stick together until near the end and then
you will see some top-flight maneuvering to see who might get the solo.

The new Tournament rankings for FTF also are out there that supercede the
ones that were on 18centres.
Go check out:

http://eurodip.nuxit.net/php/ranking/index.php?lang=Ang

There are all sorts of rankings there. Doug Moore leads the 
DipPouch rankings as done by Matt Shields, but Cyrille Sevin
is still WAY ahead in the C-Diplo based rankings that Edi Birsan
has been organizing with the French.  And Cyrille also leads
in Lei Saarlainen's World Performance Evaluation ratings. 
You can lose many hours poring through all these records and
stats.

\bigskip

\centerline{\bf DIPDOM NEWS SECTION (with letters)}

\smallskip
 
Obscure and not-so-obscure ramblings on the state of the hobby
and its publications, custodians, events, and individuals with
no guarantee of relevance from the fertile keyboard of Jim-Bob,
the E-Mail Dip world, and the rest of the postal hobby.
My comments are in {\it italics} and {\it ((double 
quotation marks))} like this.
{\bf Bold face} is used to set off each individual speaker.
I should also make a note that I do edit for syntax and spelling
on occasion.

%A VERY light discussion is taking place that will address what 
%stance we (the hobby) should take (proactive in some way for sure) 
%toward Hasbro, the new owners of the rights to Diplomacy.
%More on this will be forthcoming, but it looks like Hasbro might
%have its version of Diplomacy on the market for the Christmas
%season and they actually will be employing ``play-testers''.
%No word on precisely what this means yet, could it mean that
%they will offer a series of ``official'' variants?
%Stay tuned....
%If you want to be part of the discussion, send the MESSAGE:
%
%subscribe hasbro
%
%to majordomo of diplom.org, it works just like the tap mailing list
%described below.  Sending messages to hasbro of www.diplom.org
%sends the mail to the whole list.
%The big news this time is the beginning of the breakout of
%Hasbro into official contact with the hobby.

The game Diplomacy is a copyrighted product owned by Hasbro and all
reproductions or other use of that material in this szine is intended to
be personal use and not infringe on those rights in any way.
All reproductions are done at a heavy financial loss to the editor
and thus are without the remotest possibility of commercial intent,
except to promote THE game, the Game of Diplomacy, which you all 
should purchase from Hasbro or other duly licensed distributors.
 
Stephen Agar has matched the Hasbro rule lists 
and more with some of the even older
rulebooks.
Check these out if you like:

http://www.hasbro.com/default.asp?xcc\_gameandtoyinstructions

http://www.hasbro.com/instruct/Diplomacy.PDF

http://www.hasbro.com/instruct/Diplomacy(OlderVers).PDF

Nice of them to make BOTH of these available.
And all seven different US rulebooks for Diplomacy can now be found here
courtesy of Stephen Agar (relatively new address for this):

http://www.diplomacy-archive.com/diplomacy\_rules.htm

%1: The Reformer, who seeks perfection (crusading type).
%2: The Helper, who seeks love (altruistic type).
%3: The Performer, who seeks status (competitive type).
%4: The Individualist, who seeks an identity (imaginative type).
%5: The Investigator, who seeks knowledge (analytical type).
%6: The Loyalist, who seeks security (ambivalent type).
%7: The Enthusiast, who seeks gratification (thrill-seeking type).
%8: The Leader, who seeks self-sufficiency (dominant type).
%9: The Peacemaker, who seeks contentment (accommodating type).
%See http://graphics.lcs.mit.edu/~becca/enneagram/
%new test at: http://www.9types.com
%My scores in order were: 9, 13, 15, 7, 15, 6, 17, 18, 14.
%Robert Lesco's Marco Poll, the defacto poll of the
%North American hobby since the Runestone is pretty much
%officially dead, continues to collect votes.
%This is an official {\it TAP} approved poll.
%Here are the particulars on the Marco Poll:
%Vote for your top five in each category and you can't vote (or at least
%it won't be tabulated) for Robert Lesco or his szine, which I don't see.
%I will send this to Robert and offer him a trade.
%The deadline is September 1st and either send your ballot to marcopoll of yahoo.com
%or mail to Robert Lesco, 49 Parkside Drive, Brampton, Ontario, CANADA  L6Y 2H1.
%For identification purposes, Robert would like you to identify yourself both
%by name and by affiliation (a game you play in or a szine you sub to).
%Here are the categories this year (I like some of the new ones!!):
%1) Favourite {\it ((Hey, what, he's Canadian, yeah.))} Zine  {\it ((What's a zine,
%shouldn't that be Szine???))}
%Backstabbers United Monthly, Costaguana, The Diplomatic Pouch, Absolute, Vertigo
%2) All Time Favourite Zine {\it ((Szine))}
%Magus, Europa Express, Thirty Miles of Bad Road, Perelandra, North Sealth West George
%3) Best Diplomacy Player
%John Quarto von Tivadar, Edi Birsan, Mark Fassio, Chris Martin, David Partridge
%4) All Time Best Diplomacy Player
%Edi Birsan, Mark Fassio, Kathy Caruso, Rod Walker, Hohn Cho
%5) Best GM
%Malcolm Cornelius, Tim Miller, Tim Richardson, Conrad von Metzke, Doug Massey
%6) Player Who Writes the Best Letters/E-Mails
%Don Williams, Richard Weiss, Mark Fassio, Toby Harris, Cal White 
%7) Folded Zine {\it ((Szine))} You Miss the Most
%Magus, Diplomacy by Moonlight, Le Front du Liberation de Diplomacy, Kathy's Korner
%8) Favourite Variant
%Modern, Nuclear Yuppie Evil Empire Diplomacy, Woolworth, Spy Diplomacy, Colonia

\bigskip
 
{\bf Bruce Linsey (Nov. 10, 2007 4:37 PM)}   

Hi Jim,

You're probably tired of this question, but will we be seeing another issue 
of {\it TAP} soon?  It's been a few months, I think, since I got one.
{\it ((Yes, yes, obviously here we are.
I've avoided publishing the other kind notes I received on this.
Thanks for everyone's concern.))}

Anyhow, here's a brief letter I'd like to ask you to publish, unless you can 
tell me the best person (people) to ask privately.

``I am looking for a copy of an article I wrote long ago, called {\it The 
Astonishingly Arrogant Ankaran Assault}. It was published, I believe, in Allen Wells' 
zine {\it DOT HAPPY} in the early or mid 1980s.  
If someone can help me get a copy of 
this article, please contact me at GonzoHQ of aol.com. 
Thank you, Bruce Linsey" 

\centerline{Much obliged if you can help me out! Bruce, GonzoHQ of aol.com}
 
\bigskip

\centerline{Check out current and back issues of {\it Diplomacy World} -- Yahoogroup diplomacyworld}
and at Doug Kent's new {\it Diplomacy World} web site at:

\noindent http://www.diplomacyworld.net/

\bigskip

Also, I need any Hobby Award Nominations NOW (!!!) for the :

\noindent The 2005 and 2006 and 2007 Don Miller Award for Meritorious Service;

\noindent The 2005 and 2006 and 2007 Rod Walker Award for Literature;

\noindent The 2005 and 2006 and 2007 John Koning Award for Player Performance;

\noindent The 2005 and 2006 and 2007 Fred Hyatt Award for GM Performance;

or

\noindent A 2005 and 2006 and 2007 Kathy Byrne Caruso Award for Lifetime Achievement (if warranted).

The Hobby Awards Committee is Jim Burgess (Chair and Treasurer),
Fred Davis, Jr., Melinda Holley, Gary Behnen, Jamie Dreier,
Paul Kenny, Mark Stretch, and Robert Lesco.
I was going to publish the award ballot for this year 
in this issue, but I realized that I really just had to get this out first and
then do that.... and then, well, REAL SOON NOW!!!
And when I do, I'm going to give out three sets of awards and get caught up for the 
missed years, that seems to make the most sense.  
Committee.... you will be hearing from me soon!
This also fell apart with my move, but I think I can get it together for next
issue when all the games are in Winter.

\bigskip

{\it Diplomacy World} Issue Deadline is now:

\noindent Deadline Spring 2008, Issue \#101: beginning of April

I'm really pleased that former editor Doug Kent has agreed to come 
back and get this back on track and get us to \#100.
Thanks, Doug!
We're putting things together for the
next issue and it looks good too, but if any of you want to write anything
there's always more room,
contact Doug!
Most every old fart getting this szine sent something in for \#100,
so if you missed out, send something now for \#101!!!
We're looking for all sorts of kinds of articles, come talk to us if you
want some ideas.

See http://www.diplomacyworld.net/ for some exciting back issue material being
posted as well as the new Issues, including the monstrous Issue \#100.  
Highlights of \#100 include Walt Buchanan's ex-wife Carol showing us who REALLY
was in charge of the hobby back in the Hoosier Archives days, Eric Ozog augmenting
the oft-heard, but never get enough of, love story between Eric and Cathy,
and the start of the new Diplomacy World Demo Game.
In addition to the first two issues, we have 
every issue back to issue number 53 posted.  Eventually they all will be up.

%\noindent Final Hobby Awards Ballot for 2004, nominations now to:
%burgess of world.std.com
%
%The qualifications for the Kathy Byrne Caruso Lifetime Achievement 
%Award are that the awardee must have been: (1) Active in the 
%Diplomacy Hobby in at least Three Separate Decades; 
%(2) Multidimensional in their Contributions to the Hobby 
%(e.g. writing, playing, publishing); (3) Taking Retirement or 
%Semi-Retirement from the Diplomacy Hobby; and (4) One of the 
%Hobby’s Unique Personalities Worthy of Being Remembered as Long 
%as THE Game Continues to be Played.  This award need not be awarded
%each year, but only as worthy candidates are identified.  The only
%past honoree is the late Richard Sharp.
%
%The other award categories are self-explanatory:
%
%\noindent Nominees for the 2004 Don Miller Award for Meritorious Service
%
%\noindent Nominees for the 2004 Rod Walker Award for Literary Achievement
%
%\noindent Nominees for the 2004 John Koning Award for Player Performance
%
%\noindent Nominees for the 2004 Fred Hyatt Award for GM Performance
%
%--- --- --- --- --- --- ---

Editorial Board for {\it Diplomacy World}:

\noindent  Doug Kent, NEW Lead Executive Editor!, 11111 Woodmeadow Pkwy 
\#2327, Dallas, TX  75228, dougray30 of yahoo.com 

\noindent Tim Haffey, 810 53rd Ave., Oakland, CA 94601 USA; trhaffey of
aol.com -- Ex-Lead Editor and Archives Editor

\noindent Jim Burgess, 664 Smith Street, Providence, RI 02908-4327, USA;
burgess of world.std.com -- Co-Editor and Publisher

\noindent Rick Desper, 5440 Marinelli Road, \#204, Rockville, MD  20852, USA;
rick\_desper of yahoo.com -- Demo Games

\noindent Dave Partridge, 15 Woodland Drive, Brookline, NH  03033, USA;
rebhuhn of rocketmail.com -- US Postal

\bigskip

\centerline{\bf MUSIC AND MOVIES SECTION (WITH COMMENTS ON OTHER ARTS AND SOCIETY)}
     
\smallskip

We were running a ``23 tunes'' contest here
(stolen blatantly from Mark Wightman and the late lamented {\bf The Sprouts of Wrath}.
If anyone would like to send me a tape or CD of their 23 (which was the original point)
that would be great, but I don't intend to require that.  I will be playing in the
sense that I'll be putting 23 tunes in, and you have to guess me, but I obviously
won't score points.
Send commentary with your choices, and we'll see if people can
guess who you are!!!
And already there is a LOT of diversity in defining tunes and styles, so 
BE CREATIVE!!!
This kind of died, mostly because of me.  I don't want to take this last issue
getting it back together, but might next issue.
Feel free to send along general music comments any time.
It's always great to talk about the Mekons, as Eric Ozog does below.
 
%To encourage voting early, I picked five voters at random to receive five US
%dollars from me (either in cash or paid to someone for Dip stuff or to get
%a free tape).
%Tony Dickinson won the Round 5 prize, so we had three of the six Round 1 voters
%won and one of the three Round 2 postal voters who also got five chances to win.
%That showed the value of getting in early!!
%Voters in Round 1 were Mike Barno(\$5), Rick Desper (\$5), Tony Dickinson (\$5),
%Drew James, Heath Gardner, and John Harrington.
%Round 2 postal voters were John Schultz (\$5) Ian Moore, and Stan Johnson.
%Round 2 E-Mail voters were Scott Morris, 
%Warren Goesle, Peter Sullivan, and Michael Lowrey.
%Round 3 voters were Dick Martin, Richard Weiss, and Rip Gooch.
%Round 4 voters were Roland Sasseville, Jr. (\$5),
%Don Williams, Brent McKee, and Andy York.
%Round 5 voters were Mark Larzelere, Al Tabor, Jody McCullough, and that's it.
%We'll end up with a monster party tape at the end of it that I plan
%to segue and sequence and copy for distribution.
%The result will be a great New Millenium party tape -- we're going for 90 minutes.
%I've also been thinking that I should put this out on CD
%as truly emblematic of the new millenium.  
%I don't have the capability to do that quite yet, but I think
%I might by then.
%Any suggestions (or especially volunteers) on this front will
%be cheerfully accepted and could receive monetary payments!
%The CD way may still occur if someone steps forward and actually does it for me.
%So far, we have ``I Melt With You'' by Modern English; George Gershwin's
%``I got Plenty O' Nuttin' '' from {\it Porgy and Bess} in the 1957 concert
%recording with Ella Fitzgerald finishing off the vocals after Louis
%Armstrong blows and sings through the tune; Duke Ellington performing
%Billy Strayhorn's ``Take the A Train''; Frank Sinatra's ``New York,
%New York''; something from the B-52's;
%the original Van Morrison and Them version of ``Gloria'';
%The (English) Beat's 12 inch version of ``Save It for Later'' 
%ratchets things up to the next level (wherever you put it!);
%Buster Poindexter's ``Hot, Hot, Hot'' keeps you there;
%``Atomic Dog'' by George Clinton blows the doors off,
%and Koko Taylor cleans up singing Willie Dixon's ``Wang Dang Doodle''.
%After I get timings down, I'll choose exactly which songs below make the list.
%
%EXTRA SPECIAL B-52'S BULLPEN: (7) ``Love Shack'';
%``Rock Lobster". {\it ((A tie, a tie!!!!))}
%
%BULLPEN: (9) Nirvana -- ``Smells Like Teen Spirit";
%``Cumberland Blues'' -- the Grateful Dead.
%(8) ``Twistin the Night Away" -- Sam Cooke; ``In Between Days'' -- The Cure;
%``Mannish Boy" -- Muddy Waters; ``Shake, Rattle, \& Roll" -- Big Joe Turner; 
%``Proud Mary'' -- Ike and Tina Turner.
%(7)  ``I Wanna Be Sedated" -- Ramones; ``Twist \& Shout" -- Beatles.
%(6) ``Magic Carpet Ride" -- Steppenwolf;
%``Crossroads'' -- Eric Clapton; ``Play That Funky Music'' -- Wild Cherry;
%``I Fel Good" -- James Brown;
%``Radar Love'' -- Golden Earring; 
%Devo -- ``Whip It"; ``Echo Beach'' -- Martha and The Muffins.
%(5) ``Sing Sing Sing'' -- Benny Goodman; ``Rocking the Casbah'' -- The Clash; 
%Squeeze -- ``If I Didn't Love You"; ``Roadrunner'' -- 
%Jonathan Richman and the Modern Lovers.
%
%SPECIAL ROLLING STONES BULLPEN: (6) ``Paint It Black''. 
%
%SPECIAL TALKING HEADS BULLPEN: (9) ``Take me to the River".
%(4) the entire {\it Speaking in Tongues} record
%(special call for ``Road to Nowhere'').
%
%SPECIAL ALPHABET SONG BULLPEN: (6) ``YMCA" -- Village People. 
%
%SPECIAL DRUG MUSIC BULLPEN: 
%(8) ``Rd, Red Wine'' -- UB40.
%(6) ``Don't Bogart that Joint'' 
%-- Fraternity of Man; ``The Old Dope Peddler'' -- Tom Lehrer.
%(5) ``Cocaine'' -- Eric Clapton's version; ``Casey Jones'' -- the Grateful Dead.
%(4) ``White Rabbit'' -- Jefferson Airplane; ``Love Is the Drug'' -- Roxy Music.

\bigskip

\centerline{\bf {\it 23 Tunes Game}}

\smallskip

Here are the rules for 23 TUNES.  You send me three tunes for the first turn,
and then two tunes in each of the last ten turns for a total of 23.
If you missed the first turn, you can still catch up by sending five tunes next
issue, and guess on submitters to this issue.
I am also submitting my tunes.
After we're done, I'd like to exchange CD's/Tapes for as many of the tunes players
as possible, but this is not required.
I'll be sending the winner both my LAST 23 tune list and my NEW 23 tune list.
The winner is determined by having you guess each issue who submitted what list
(I will tell you who the submitters are).  For each list you get right, you get
a point, you also can win bonus points from me for really cool tune selections.
%That's it, not complicated.
%I hope by starting this up, we'll get more to join, five songs required to enter
%late.
%Playing this issue (guess who is whom by number, scores are in parentheses) 
%is, in alphabetical order, 
%Jim-Bob Burgess, Rick Desper (1), %Steve Emmert, Doug Kent, 
%Dick Martin, %Jim Reader,
%Richard Smith (3), Joakim Spangberg, %Brendan Whyte, 
%and Brad Wilson (4).
%The linking theme thing didn't seem to go over too well.
%No one really figured out the true linking theme.  
%Rick Desper was using Underground tube stops and songs with that as the title,
%they were things like that.  
%I'll let you guys talk a bit to each other on that with your guesses.
%I have added some kind of comment on each tune.

WHAT I NEED: 
Quite a number of you SAID you would join but haven't yet, so we'll get started and
put the pressure on you.
This part is still a MESS and I'm getting this issue out and then will catch up next time.
I think I'm going to simplify the rules to get it back on track.
%Rick Desper: Anyway, my tunes this time are "Set the Controls for the Heart of Sun" by Pink %Floyd, 
%in honor of the film Sunshine, and "Afternoon Delight" by the Starland Vocal Band, 
%that Will Hunting just sang a snippet from, and Ron Burgundy covered in "Anchorman".  
%The latter is really becoming an anthem of the Goofy 70s.
%I have no idea what this game is supposed to mean, but we can't go wrong with "Afternoon %Delight".

\bigskip

{\bf Eric M. Ozog (Dec. 2, 2007 11:57 PM)} 

\smallskip

\centerline{A ``Quiet" Night with The Mekons --
Seattle Town Hall -- October 10, 2007}

\centerline{By Eric Ozog}

\smallskip

I was thrilled to hear on KEXP (local independent radio) that 
The Mekons would be in Seattle in October.  
The last missed opportunity for me to see the band was sometime around 2000, 
when they played on Labor Day at the Bumbershoot music festival, 
but I was trapped filling in for a coworker on that day.  
``I could have been in downtown Seattle seeing The Mekons," I grieved to myself, 
``Instead I'm raking the compost" (of a public restroom--what's wrong 
with this picture?).  I guess that's the dedication of a Ranger, 
performing the ultimate in public service.  
But that was the last time: I am thankfully in a different job--pushing 
paper instead of pushing the poop around.  
I've been a fan of the Mekons--this eccentric, irreverent, 
rock/punk/folk/c\&w/reggae band--since 1989, 
when I bought {\it The Mekons -- Rock 'N' Roll}.  
I think what really turned me on the most was Sally Timms' 
vocals and Susie Honeyman's fiddle.  

As the date of the show got closer, I was debating 
whether to make the 50 mile drive, on a weeknight, 
with work the next day.  Then I came to my senses: 
``don't be an Old Man, go see the Mekons for Godssake!"  
So I bought and printed my own ticket from Ticketmaster 
and raced down the I-5 freeway in my '78 Mercury Cougar.  
After parking in the Seattle Convention Center garage, 
I walked around the blocks a couple times in a downtown 
disorientation haze until coming upon the venue, the Seattle Town Hall, 
a Greek-Romanesque building that looks like a mini version of 
Chicago's Union Station.  I made it in time.  
Inside the hall are arches and wooden church pews for the audience, 
and seven empty chairs on the stage. 

I had been thinking about ordering the new Mekons album, {\it Natural,} 
from Amazon.com but decided, ``Hey, what am I thinking--I'll 
buy it straight from the band!"  
So I walked up to the table and bought {\it Natural} from 
Sally Timms herself.  Jon Langford, Lu Headmonds 
(he just drew a smiley face), and Sally autographed the lyrics liner, 
writing, ``To Eric, Love Sally." 
Now Amazon doesn't hold a candle to that level of customer service!  
I said to Sally that I was a long time fan, and she replied that 
``most of our fans are, and that is part of the problem."  
I guess there aren't as many younger Mekons converts, 
but the audience had quite a few 20-somethings in it, 
as well as middle aged and older baby-boomers.  
The church pews were about half-occupied by their adoring fans.

I really didn't know what to expect when The Mekons first 
walked out on stage, as they billed the concert 
``A Quiet Night with the Mekons."  
I thought this might be a ``Mekons Unplugged" show with only 
2-3 of the band members.  I looked for the drums with fear--there 
were none!  But I was thrilled and relieved when seven 
Mekons entered the stage and promptly sat down in chairs, 
opening with ``Give Me Wine or Money," from their new album {\it Natural}; 
a song that sounds like a tin can on the CD but has the 
Big Sound when played live!  Besides Jon (who sang in his usual 
gruff voice, played the guitar and thumb piano) and 
Sally (vocals), Rico Bell played the accordian, Sarah Corina on bass, 
Steve Goulding on a drum kit that he sat on and played 
(surprisingly it produced a lot of sound), 
and Lu played some kind of a sitar-looking guitar.  
Alas, though, Tom Greenhalgh wasn't there (his wife was 
having their fourth child--he had text-messaged Jon 
announcing the birth), and Susie Honeyman was absent 
(no explanation given), with someone named Jessica 
playing the violin instead.  She played well, but the 
fiddle tended to get drowned out by the rest of the band--Susie 
would have insisted on cranking it up! 

{\it Natural} isn't the strongest album by the Mekons, 
and some of the songs sound rather tinny when compared to 
{\it Oooh! Out of Our Heads} and {\it Journey to the End of the Night}'s 
production, but these songs came alive when the 
Mekons played them in concert: ``Dickie Chalkie \& Nobby," 
``Burning in the Desert Burning," and ``Zeros and Ones."  
I particularly liked the moody ``Dark Dark Dark," from 
an English poem ``The trees stare back and we burn in smoke, 
reflecting in the water like ghosts," and they closed with 
the achingly haunting ``Perfect Mirror," ``The black mountain, 
above the lake, the trees are dead, a cold rolls off the water."   
This is the first time I heard the new album's songs--live--the 
way they are meant to be.  The Mekons also played ``Diamonds," the pretty 
``Hope and the Anchor" (solo by Sally), and ``Cockermouth" from 
{\it Natural}, with its reggae twist about the 
end of the world, as Jon Langford asked the audience to sing along, 
``You don't have to believe in the end, you have to believe 
this is the end."  The Mekons always had a sense for the sardonic 
about life, death, and our way of life in their songs: 
``Take it home right away, you've got three years to pay, but Satan 
is waiting his turn" (from ``Sin City" on {\it Honky Tonkin'}).

About half of the songs the Mekons played were from {\it Natural}, 
and the other half were songs from other albums: 
``Tina" (from {\it Journey...}. ``It looks like an accident, 
caused by the government"); 
``Thee Olde Trip to Jerusalem" (from {\it Oooh, Out of Our Heads}...
not a song I particularly like, but it sounded great live, 
with all the band members singing together); 
``Wild \& Blue" (from {\it Curse of the Mekons}); 
``Millionaire" (from {\it I Love Mekons}); 
the country \& western rocker ``Hole in the Ground" 
(from {\it Honky Tonkin'}, where Jon invited the audience 
to whistle along at the end (I can imagine Jake and Elwood Blues 
singing this song at Bob's cowboy bar).  The final encore song was 
``Ghosts of American Astronauts" (from the album {\it So Good It Hurts}, 
which I own on vinyl: ``A Flag flying free in a vacuum, 
Nixon sucks a dry martini, Ghosts of American astronauts, 
Stay with us in our dreams.").  
The only thing that would have made the show complete for 
me is if the Mekons had played my all time favorite song: 
``Only You and Your Ghost Would Know."  

Probably the best part of the show was Sally and Jon's 
banter between songs, which started by Sally announcing that 
Jon would turn 50 years old ``at midnight tonight" and making 
wisecracks about his age and not being able to ``get it up" anymore.  
Jon replied that he was going to launch his sputnik, 
``that will really scare the Americans," a dual meaning to 
the 50 year anniversary of the Russian spacecraft.  
Jon also warned the audience to stay away from chicken 
pot pies, that ``they've been broadcasting it on CNN all day."  
Jon also did a cartwheel on stage, and Sally said with concern, 
``I think you should do that no more than once."  
At the close of the show, the Mekons invited everyone 
over to the Tractor tavern for celebrating Jon's birthday, 
but being a family man I had to get home (and in one piece).  
Back the at the merchandise table I thanked the Mekons for coming back to Seattle.

\centerline{elferic of juno.com}

{\it ((Thanks much, Eric, it reminds me of all the many Mekons concerts
I've been to.
They really are more of a ``band of the people" than about any 
other band I know of.
My fiftieth birthday, of course, was on Sept. 29th.
And I've long known that I'm exactly two weeks older than Jon Langford,
his birthday really is October 12th, 1957 (Tom Greenhalgh and Susie
Honeyman are a bit older and Sally Timms is a bit younger).
He's always been my favorite band member, he really is a painter
these days, recall that he and Tom first met when they were in
art school together..... like how the Talking Heads met here in
Providence at the Rhode Island School of Design.))

((In recent years, they've not been playing the really old songs,
like the {\bf Fear and Whiskey} songs so much, and they love to
play ``Millionaire" and ``Ghosts of American Astronauts" in 
concert for some reason, I'm not entirely sure why.
Thanks for a great review, and made me drag out all my old 
Mekons songs and listen.
I just got a USB Turntable for Christmas from my stepson, so
I can put lots of my old vinyl onto music CDs for the highway.
The Mekons and Jonathan Richman are my two favorite ``traveling
artists."))}
%
%\bigskip
%
%\centerline{\bf SPY DIPLOMACY (Variant, revised Dec. 1986)}
%
%by Jim Burgess
%
%Rules:
%
%1) Unless otherwise specified, the standard rules of Diplomacy apply.
%
%2) Players receive adjudications for their own armies and fleets, but not
%the armies and fleets of other powers.  Similarly, each player sees only
%his or her own section of the supply center chart.
%
%3) In addition to the standard units, an unit called a "spy" is added.
%
%     A) Each of the seven powers begins with a spy in each home supply center.
%
%     B) Spies are supplied only by home supply centers (i.e. Russia may have
%as many as four spies at a time while other powers are limited to a maximum
%of three).
%
%     C) Spies are "built" and "disbanded" in Winter seasons at the same time
%as other units.
%
%     D) There is no limit to the number of spies that may be present in any
%province and spies may be ``stacked" with armies or fleets (exceptions are
%listed in Rule 6).
%
%4) Spy Reports
%
%     A) Spies report the location and nationality of armies and fleets in
%the province they occupy and all adjacent provinces immediately following
%the standard Winter, Spring, Summer, and Fall seasons (i.e. just prior to
%the spy movement seasons).  Spies can differentiate between units in retreat
%and successful attackers when two units "occupy" a province.
%
%     B) Spies also report the nationality of spies in the province they occupy
%and the presence (but not nationality) of spies in adjacent provinces at the
%same time.
%
%5) Movement of Spies
%
%     A) Spy movement follows the collection of spy reports, so orders to spies
%may be made conditional on any information gathered by spies on opposing troop
%movements or the adjudication of one's own units.
%
%     B) Spies move after each of the following standard seasons: Winter,
%Spring, Summer, and Fall (note that all spy movements PRECEDE Autumn
%retreats), beginning with Winter 1900.
%
%     C) Spies move as armies do with the following exceptions:
%
%          a) Spy movements cannot be stood off by movements of any other unit.
%
%          b) Spies may be convoyed by fleets of any power during any of the
%four movement seasons for spies.  The convoy orders for fleets in these
%seasons must be ordered by their owner in the usual fashion or else the spy
%convoy movement fails of execution.  Fleet convoy orders for spies may be made
%in addition to regular Spring and Fall moves (note, however, that the fleets
%themselves never move during spy movement seasons).
%
%          c) Spies may also be "picked up" and carried by fleets of any
%power. Embarkation and debarkation are moves that must be made during a
%spy movement season and "permission to board" is not required.  Embarkation
%consists of a movement from a land province to an adjacent sea province
%containing a fleet.  Debarkation consists of a movement from a sea province
%containing a fleet to an adjacent land province.  A spy may not "switch
%fleets in midstream".  Once boarded, a spy may only get off by debarking.
%After boarding a fleet, the spy moves with the fleet during regular movement.
%A spy may not debark from a fleet awaiting retreat (e.g. if a fleet carrying
%a spy is dislodged in Spring, the spy may not debark until the spy movement
%season following the standard Summer retreat season).
%
%6) Spy Mortality
%
%     A) This rule will outline the circumstances under which spies may be
%captured or killed.  Spies may be disbanded in Winter seasons at the same
%time as other units to meet the requirement that a power may not have more
%spies than the number of currently held home supply centers and spies are
%annihilated when they are on board a fleet that retreats off the board.
%Otherwise, spies may only be removed from the board (there is no difference
%in the game between capturing and killing a spy, but players should feel
%free to delineate between the two states in writing press) immediately
%following the four spy movement seasons.
%
%     B) Spies killed or captured in a given season do not submit written
%spy reports for that season, though their final movement may have been
%made conditional on that spy report.  Players may never know for sure how
%a spy was lost, just as in real life.
%
%     C) Spies are "killed" by being assassinated by other spies.  When a
%spy moves, he or she may attempt an assassination, specifying the nationality
%of spies to be executed if discovered.  Each spy may hunt for only one
%nationality in each of the four seasons.  The following rules and examples
%will govern the adjudication of assassinations:
%
%          a) A spy may attempt an assassination without moving (for instance
%if the target is in the same province).  In this case, any spies of the target
%nationality that end the spy movement phase in that province are assassinated
%with one exception.  If the spy attempting the stationary assassination is
%himself or herself assassinated by a moving assassin then that spy
%assassinates no one in that season (not even a potential target other than the
%one that assassinates that spy).
%
%          b) A spy attempting a moving assassination (may include a move of
%embarkation or debarkation from a fleet) is always successful in assassinating
%spies of the target nationality that finish the spy movement phase in the
%province that the spy moves to.  This makes "mutual assassinations" possible.
%
%          c) Example: French spy is on board a French fleet in the Channel.
%An English spy is in London.  Both powers specify assassination attempts
%against the spies of the other.  If the English spy embarks on the French
%fleet in the channel (remember that embarkation does not require the
%permission of the fleet being boarded) and the French spy doesn't move, the
%French spy is killed, but the English spy isn't (he may be immediateIy
%captured, however, see part D).  If a German spy is also on board and the
%French spy tried to assassinate the German spy, that operation would fail
%as well. If the French spy debarks to London at the same time, the two spies
%"pass in the night" and neither is killed.
%
%     D) Spies are "captured" by opposing armies and fleets.  Players may
%attempt to capture spies, specifying the nationality of spies to be captured
%if discovered.  Each army and fleet on the board may search for spies of one
%nationality in each of the four seasons.  The following rules and examples
%will govern the adjudication of attempts to capture spies:
%
%          a) Players may specify a nationality to be hunted separately for
%each unit or they may issue blanket searches to be applied to all units.
%
%          b) At the end of the spy movement phase, any spies of the
%nationality specified in the same province are captured (for example, if
%the French player specifies a hunt for English spies on their Channel fleet
%in the above example, then the English spy is captured).
%
%          c) Players are informed when they successfully capture an opposing
%spy.  Note that the "owner" of the spy, however, is not informed of the
%capture.  Communication just is cut.  This rule is the only exception to the
%generaI rule that armies and fleets are blind.  It is possible to play the
%game without allowing capture of spies by armies and fleets if one wishes
%to allow freer movement of spies (i.e. RuIe D may be ignored).
%
%7) It is suggested that the game be adjudicated in four separate seasons
%in the following order:
%
%     A) Spring: (for Spring 1901 this sequence is preceded by a spy movement
%phase (no spy reports are necessary) followed by assassinations or captures)
%
%          a) Standard movement by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     B) Summer:
%
%          a) Standard retreats by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     C) Fall:
%
%          a) Standard movement by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     D) Winter:
%
%          a) Standard Autumn retreats by fleets and armies, adjudication
%reported only for one's own units
%
%          b) Standard Winter builds and removals, also applies to spies
%
%          c) Spy report phase, spies collect information
%
%          d) Spy movement phase, spies move according to Rule 4
%
%          e) Spy assassination and capture phase
%
%\medskip
%
%These rules have been produced by Jim Burgess (with helpful comments from
%Bernie Oaklyn and Dick Martin).  Permission is granted to reproduce and use
%these rules without restrictions.  The author would be interested to hear
%any comments and criticisms regarding any aspect of the play of this variant.
%The rules have been deposited with the North American Variant Bank.  They are
%also available from the author for the cost of postage or free by E-Mail.
%
%\bigskip
%
%\centerline{Wing Rules} 
%
%1.A wing unit can move over both land and water spaces. 
%  
%2.A wing unit can support actions in any space adjacent to the one it occupies. 
%   
%3.A wing can give, receive and cut support in the same way as armies and fleets. 
%   
%4.A wing unit cannot convoy or be convoyed. 
%
%5.A wing unit cannot capture an SC, but instead blockades it: 
%        
%\indent\indent 5.1.A blockade occurs when a wing unit occupies the SC of 
%another player in a fall season. 
%        
%\indent\indent 5.2.The player who owns a blockaded SC does not count 
%it when counting his total number of SCs. 
%        
%\indent\indent 5.3.A blockade ends as soon as the wing unit no longer occupies the SC. 
%        
%\indent\indent 5.4.Builds only take place in the winter phase, just as in games without wings. 


\vfill\eject

\centerline{\bf {\it THE ABYSSINIAN PRINCE} GAMES SECTION}

\smallskip

``So I called up George and he called up Jim, I said let's make a deal.

He said he'd talk to him.  Gonna start a church where you can save yourself,

You can make some noise, When you've got no choice...

You told me useful things, what people think of me, I guess I should thank you.

It's true, then I agree... I'm all alone, I've got no choice,

I'm all alone, I've got no choice."

From ``Got No Choice" by the incomparable Mark Cutler, from the CD
{\it Mark Cutler and Useful Things}.

\smallskip

\indent If you want to submit orders, press, or letters by E-Mail,
you can find me through the Internet system at
``burgess of world.std.com''.
If anyone has an interest in having an E-Mail address listed so people
can negotiate with you by computer, just let me know.

I am continuing to note cut or failed support orders with a 
small ``s'' instead of a capital ``S''.
This will make it easier on the E-Mailed version of the szine to see
what happened, since the italics don't show there.
The italics DO show on the web page just fine.

\indent Standby lists:

Mike Barno, Dick Martin, Brad Wilson, Jack McHugh, Glenn
Petroski, Steve Emmert, Mark Kinney, Vince Lutterbie, Eric Brosius,
Paul Rauterberg, Bob Osuch, Doug Kent, Sean O'Donnell, Vern Parker,
Heath Gardner, Paul Kenny, and Jeff O'Donnell
stand by for regular Diplomacy.
%I am willing to take over for NMR or start new-Diplomacy.
%Vern Parker
%337 Winter Hill Pl.
%Powell, OH 43065
%VSParker of aol.com
%614-402-5139

Let me know if you want on or off these lists, especially OFF.
Standbies get the szine for free and receive my personal thanks.

\bigskip

\centerline{GAME OPENING INFORMATION} 

\smallskip

We've got lots of openings in the subszines, check them out!!!
Contact Rip Gooch directly at xyropedes of canada.com and try to entice him to return.
Rip has been a bit missing in action lately, but I am assured that he
SHALL return.
Can we get back to these game openings below?  
We just need a few more people for a couple of these.

I am willing to open another new game of REGULAR Diplomacy if there is enough interest!!!
Doug Kent, Fred Wiedemeyer, %e,f,r,i,g,t,a
Brad Wilson, and Shaun Thompson start the list, who would like to join them???

Also, is there any interest in another game of Nuclear Yuppie Evil Empire 
7x7 Dip?
I know it may be getting tired, but I really like it.
We have Karl Schmit on the list, let's get seven!!
It's FREE!!!
I may drop this one shortly if we still have no interest.

I also am starting a game of the variant I designed, Spy Diplomacy.
Signups for that are now open.
Bruce Edwards and Eric Ozog are signed up.
The rules were published recently, ask to see them if you missed them!!!

And since Colonia is over, Harold Reynolds is looking to start something else.
Harold has been updating the Diplomacy A to Z, go check it out at:
http://www.badpets.net/Diplomacy/AtoZ/index.html 

Also, I am going to design some postal rules for Devil Take the Hindmost,
and we have an opening here:
Bruce Edwards, Mike Barno, and Eoghan Barry are signed up.
Postal rules from me will be forthcoming shortly, on my never ending to-do list.
I will get them in SOON!
I'm more likely to get these things started if I see some interest.....
I've GOT to do this now,
Eoghan is getting tired of waiting....

Right now, the other thing going is the Modern
Diplomacy game with Wings.
Sean O'Donnell, Jeff O'Donnell, Steve Koehler, Art Schleinkofer,
Bob Holt, Rick Desper, Alexander Woo, and Dave Partridge are signed up for that.
I will start it when I get a full complement of players, we only need TWO more!
Only two, just TWO more...... come on.
%Sean's list: Britain, Spain, Germany, France, Egypt, Turkey, Russia, Ukraine, Italy, and Poland.

\bigskip

\centerline{\bf TAKING OVER ISHKIBIBBLE'S REGULAR DIPLOMACY GAMES ((NOT))}

\smallskip

Last chance for anyone who was a subber to {\it Ishkibibble} to join any new
game for free, but this is a ONE TIME only offer, get your request in now.
It is going to expire VERY shortly.
Marc Ellinger and Fred Wiedemeyer already have taken us up on this request.
Come on, let me call by name who qualifies
for this deal..... Karl Schmit, John Power, Tim Snyder,
Dave Partridge, Graham Wilson, and Kevin Wilson.
I especially would like to fill the Modern Diplomacy game that Dave Partridge
already is in.
As soon as one more game fills (I'm not counting the new Breaking Away game), 
I'm going to pull this offer.

\bigskip

\centerline{\bf THE PHIL REYNOLDS MEMORIAL: 2006B, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR WINTER 1902 IS FEBRUARY 16TH, 2008}

\smallskip

\noindent {\bf THE DUE DATE FOR SPRING 1903 IS MARCH 8TH, 2008}

\smallskip

\indent {\it Fall 1902}

\noindent AUSTRIA (Burgess): a TRI h, f alb-GRE, a gre-BUL, 
a SER S a gre-bul, 

{\it f AEG-con}, {\it a vie-tri} (nsu). 

\noindent ENGLAND (James): f ENG C a bre-bel, f NAO S f iri-mid, 
a bre-BEL, 

f iri-MID, f NTH S a bre-bel.

\noindent FRANCE (Williams): a par-BRE, 
{\it f mid-eng} (d r:spa(nc),spa(sc),por,naf,otb), 

a bur-PIC, a GAS S par-bre.

\noindent GERMANY (Ellinger): a KIE S a ber-mun, {\it a BER-mun}, 
f HOL S ENGLISH a bre-bel, {\it a DEN-swe}.

\noindent ITALY (Crow): a TYO S a mun, f tyh-WES, a MUN h, a apu-VEN, 
f ion-TYH.

\noindent RUSSIA (O'Donnell): f sev-BLA, a LVN h, a UKR S a mos-sev, 
f RUM S f sev-bla, 

a mos-SEV, {\it f GOB-swe}.

\noindent TURKEY (Wiedemeyer): {\it f bul(ec)-con} (d ann), 
a con-ANK, a arm-SMY.

\bigskip

\indent {\it Supply Center Chart}

\+ AUSTRIA (Burgess):&TRI,VIE,BUD,ser,gre,bul&(has 5, bld 1)\cr
\+ ENGLAND (James):&EDI,LVP,LON,nwy,bel&(has 5, even)\cr
\+ FRANCE (Williams):&PAR,MAR,BRE,spa,por&(has 3 or 4, bld 2(r:otb) or 1)\cr
\+ GERMANY (Ellinger):&KIE,BER,den,hol&(has 4, even)\cr
\+ ITALY (Crow):&ROM,NAP,VEN,tun,mun&(has 5, even)\cr
\+ RUSSIA (O'Donnell):&WAR,STP,SEV,MOS,swe,rum&(has 6, even)\cr
\+ TURKEY (Wiedemeyer):&ANK,SMY,CON&(has 2, bld 1)\cr
\+ Neutral:&none&(Total=34)\cr

%\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: David Burgess, 101 Laurel Lane, Queensbury, NY  12804

(518) 761-6687, burgesscd of roadrunner.com or dburgess of glensfallshosp.org

\noindent ENGLAND: Drew James, 3644 Whispering Woods Terrace,
Baldwinsville, NY  13027

(315) 652-1956, kjames01 of twcny.rr.com 

\noindent FRANCE: Don Williams, 27505 Artine Drive, Saugus, CA 91350, 
(661) 297-3947, 

wllmsfmly of earthlink.net or dwilliams of fontana.org (\$5)

\noindent GERMANY: Marc Ellinger, 751 Turnberry Drive,
Jefferson City, MO 65109

ellingermc of aol.com

\noindent ITALY: John Crow, 824 Kinwest Parkway \#101,
Irving, TX  75063, 

(214) 532-1418, johnny.crow of hotmail.com

\noindent RUSSIA: Jeff O'Donnell, 1345 Simpson Drive, Hurst, TX  76053
%402 Middle Ave., Elyria, OH  44035-5728,

(440) 322-2920 or (440) 225-9203 (cell, as late as midnight Eastern),
unclestaush of yahoo.com

\noindent TURKEY: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  

CANADA  T6T 1N1, (780) 465-6432, wiedem of planet.eon.net 
%cell 780-497-8283; fax 780-468-6432

\bigskip

{\it Game Notes:}

1) 

\bigskip
 
{\it Press:}

(BERLINER ZEITUNG): Kaiser Marc announced the newest social rehabilitation 
plan for the errant Bavarians. 
``We're going to send some good Prussians south to sober you up and get 
rid of the Italian wino's," stated the Kaiser.
``If we can't beat the olive eating, chianti swilling Italians, with some 
stout Prussians, the world is indeed a sad place."

(GERMANY to ENGLAND): Schedules shift, schedules change, but orders live on forever.

(GERMANY to FRANCE): Rumor has it that a certain Italian is casting 
dispersions upon Bordeaux, saying that French wine is swill and that 
only Italians can make a decent red. Surely you can't stand for that!!!

(GERMANY to RUSSIA): Good pickens down south...nice weather too. 
It's cold and stormy up north, you don't want to visit...do you???

(JEFF to JIM): I want Manny and Coco back...

(GERMANY to AUSTRIA): The mother tongue makes for good neighbors.

(GERMANY to TURKEY): Keep in touch!

(GERMANY to ITALY): In the words of Rodney King, 
``Can't we all just get along?"? In the words of the LA Cops, 
``I guess not....THWACK!!!"

(BOOB to GERMANY): Thwack, indeed!
And that brings us back to....

(RED KINGS 3 –- THE DIRT, THE SKIRT AND THE BEER):
So much for McGillicutty's.  
I had to hit the streets, dig up the dirt.  
I needed mullah, mad skrilla, money to pay for the 
broads and the beers and the cigars...oh yeah, and the rent.  
The Hobby's a dirty place, always someone doing someone in.  
A very dirty place, and I just needed a little dirt.  
Just a little, and I knew exactly where I could get it.
I headed downstairs and out the front door of {\it The Abyssinian Prince}; 
cool air drafted out of McGillicutty's bringing with it the 
tones of Bruno's humming to himself and the odor of stale 
cigarettes and warm beer...or was that warm cigarettes and stale beer?  
Either way, it was tempting, but I was on a mission, it would have to wait. 
I hung a left past {\it Houdini Blues} and headed downtown, 
past the boarded up {\it Sprouts of Wrath}, past {\it Cheesecake}, 
{\it The Boob Report, Magus, Coat of Arms, Perelandra}.  
I hung a right at {\it Fiat Bellum}, passed {\it Graustark, Flick of the Wrist} 
and {\it Europa Express}. 
I could no longer tell if I was in the good part of town, or the bad.  
Not that you could tell, the Hobby is painted in a Technicolor 
of sepia and grayscale, the sorta place you could have a 
Harlem sunset anywhere you were.
It wasn't long before I heard the music.  
I heard the music before I saw the lights, 
and I saw the lights from three szines away.  
Club Copasetic, the hottest club in the Hobby, and it showed, 
the place was buzzing.  There were broads and dames galore, 
attracted to the glitz by the money.  
And there was the money: high rollers and hardspenders, 
top-hats and pennypackers, attracted to the glitz by the broads.  
God, what a racket, it just had to make you smile.  
It was one of those John Wayne moments when you wanted to 
thank God for pussy and capitalism and the Great American Way.
 
The place was so busy that the bouncer, well here it's a doorman...
hoity toity, like I said, didn't have time to do a good job frisking me.  
Like a blind man on a first date he didn't know where to 
put his hands and I got in with my rod...both of 'em. 
``Move along. Don' be lettin' out the bought air," he muttered.  
Yeah, this place was class.  I walked in and had to pause, 
let my eyes adjust to the lighting.  
Apparently I had gotten there just as the headliner started to sing...
timing, it's all about the timing...and it didn't hurt that 
I was writing this bit either.
	
Barry had just taken the stage and lit into his trademark song: 

\smallskip

\noindent His name was WeedFred, he thought he was dead

\noindent With orders flying through the air, and fleets afloatin' here to there

\noindent He would meringue and do the cha-cha

\noindent Sidestep a frontal attack and support his own assault

\noindent And while he tried to save his life, the Russian sharpened up a knife.

\noindent Across a crowded board, they worked toward Fall oh-four

\noindent They had hate and they had each other

\noindent Who could ask for more?

\smallskip

\noindent At the Copa, Copasetic

\noindent The calmest spot in the North Atlantic

\noindent At the Copa, Copasetic

\noindent Worries and problems were never the fashion

\noindent Stabs in the back were always the passion,

\noindent Where everything’s okay...at the Copa

\smallskip

\noindent His name was David, he was a diamond 

\noindent Began with Austria as his lair, moving southward down from there

\noindent And when he finished -- when it was over --

\noindent He would have Turkey to himself like a trophy on a shelf.

\noindent But David went too far, he provoked the Czar

\noindent Then the punches flew and armies were split in two

\noindent There was blood and a sudden move

\noindent But just who stabbed who?

\smallskip

\noindent At the Copa, Copasetic

\noindent Always calm, never frenetic...

\noindent At the Copa, Copasetic

\noindent Worries and problems were never the fashion

\noindent Where everything's okay...at the Copa

\smallskip
	
\noindent His name was WeedFred and now he is dead

\noindent But that was thirty moves ago, when they used...

\smallskip

The rest blended into the background noise as I headed past 
the orchestra for the back of the room.  
I passed by the cigarette girl walking the aisles, 
smacking her gum and sashaying her pins like she had the only one.

``Cigars, cigarettes...say, honey, ya wanna try some Red Kings?  They's on special."

I picked up a pack from the box she had hiked on her hip, ``They any good?"
	
Her hand paused on mine for those seconds needed for our eyes to lock, 
you could almost hear the click, ``If they's were good, 
they wouldn't be on special."
	
I gave her the half smile with just the end of one lip curling up 
and looked back deep into her ice blue peepers.  ``What makes 'em so special?"
	
Her other hand came up to her neck, the glossy red nails 
just barely tracing the smooth alabaster skin, and she leaned forward 
to huskily whisper, ``I hear they've got their own Turkish 
tobacco to make 'em with.  
They gets it so cheap cause they don’t have to pay for it."
	
``Do the Turks know about this?"
	
She gave me a 150 watt smile, you know like the one you 
get when the bulb is new. I almost needed to pull down my fedora.  
``If they don't know already, they will when they read this."
	
I scratched the scruff on my chin, ``Cheap, huh?"

``Yeah," she breathed and I smelled honeysuckle, ``and I know cheap." 
	
``A woman after my own heart..."
	
``Oh, it wasn't your heart I was after."   
Yeah, it didn't hurt that I was writing this bit either.
  
I looked over at the next page and saw the guy I needed to talk to, I had to cut this short.
	
``Look babe, I gotta blow.  Meet me at my place in an hour,"  
I slipped her a fin and took a pack of Red Kings, 
``it's in {\it The Abyssinian Prince}, the walkup above 
Macgillicutty's...not the third floor, that's the games section."
	
``I like games," she said, pouting her red glossy lips. 
They reflected the house lights like the brake lights 
of a delivery truck on rain slicked streets at night.  
Like a Tuesday night, when it wasn't really heavy traffic, 
just the light sort of traffic that made you feel alone in a large Hobby.  
The soft patter of the rain, the dampness of the air 
itself muffling the noise and the light...
the long off sound of a horn blowing in off the harbor, 
or maybe the crackling snap of a radio, heard through an open window 
above your head, being tuned past stations that could only be heard at night...
	
``Errr, errr, er," she cleared her throat, ``I said, I like games..."
	
``Oh, yeah,"  I was back, ``not these sorts of games you wouldn't."
	
She smiled, ``see you in an hour."
	
``Great, hey, pick up a bottle of Cheater's on the way, wouldja doll?"
	
``Sure," she grinned, ``a lot can happen with a full bottle of whiskey."
	
I was liking this kitten more and more.  
I invested a couple of seconds on her gams as she walked away, 
I could practically feel myself falling for her. 
Back to business. The fall was over.
	
There was the guy I needed to see, someone who kept his thumb on the 
pulse of the Hobby, especially when that pulse was in your neck.  
I needed dirt, and this was the guy who had it, or knew where to get it...
or knew who was napping under it. 
He sat in his regular booth; the light bulb had been unscrewed so 
that he was in deep shadow. 
As I walked toward him a big palooka on a stool stood up in front of me, 
but a wave of a hand from the booth sat him back down.
	
``Nice, ya got him housebroken too?"
	
There was a lessening of the darkness that I took for a smile, 
``I thought you might show up."
	
``Flat, we gotta talk..."

(MALICE IN CENTERLAND -- PART FOUR:  FALLING DOWN):
Straight down the hole Malice fell in the darkness.  
As his eyes adjusted, however, he realized he could 
see the sides of the hole as well as the pulsing red lights 
of the Mutant Butler's eyes below him.  
They were falling through space.  
The concepts of `sides' and `below' soon lost meaning 
though as Malice and the Mutant Butler continued to fall and fall and fall.  
And fall.  
(Keep falling.  Really.)  
Either the hole was very deep or he fell very slowly, 
but he fell for some great time and eventually lost sense of how 
far he'd dropped and who he might be.  
After a time, he noted various maps stuck to the sides of the hole 
and, some time later still, he saw shelves with stacks of 
piled papers covered with strange names like {\it Cheesecake, 
The Boob Report, Magus, Coat of Arms, Hare of the Dog, 
Kathy's Korner, Fiat Bellum, Whitestonia, NorthSealthWestGeorge, 
Off-the-Shelf, Ter-Ran, Graustark, Flick of the Wrist, 
Bersaglieri, Perelandra, Mos Eisley Spacesport, Whiteflame, 
Ishkibibble, Europa Express} and many, many more besides.  
Eventually, Malice's simple-yet-mediocre mind began to 
wander and he found himself tunelessly mumbling a timeworn ditty of unknown origin:

\smallskip

\noindent ``Just sit right there and you'll hear a tale

\noindent A tale of an endless drop

\noindent That started when I jumped into

\noindent The North Atlantic Dot.'

\smallskip

\noindent `This Butler is a curious guide

\noindent His coat and eyes quite red

\noindent I sure hope that he knows this hole

\noindent Or when he hit we're dead!

\noindent (Unless we hit a bed...)"

\smallskip

Abruptly, Malice stopped mumbling as new words flowed into his 
thoughts from a source within him that he neither recognized nor understood.  
Moments later, though, he found himself mumbling again 
another odd verse as tunelessly as before:

\smallskip

\noindent ``This quest for the Diplonomicon

\noindent Is not for me alone

\noindent Six other souls will quest with me

\noindent To join the board and stones --

\noindent Join the board and stones!'

\smallskip

\noindent `Sure, Centerland will get quite rough --

\noindent Through chaos we'll be tossed

\noindent If not for the courage of the Hero-Fool

\noindent The Dipcon will be lost

\noindent And ancient myth exhaust!'

\smallskip

\noindent `The tale's about to start with this

\noindent Unartful story line --

\noindent With Hero-Fool, The Red King, too

\noindent Kings Yellow, Green, and White,

\noindent A King Dark Blue

\noindent The Black King and all Centerland --

\noindent Here's to ma-li-cious guile!"

\smallskip

Malice finished the tune and, pleased with himself, 
was about to launch into a second little number, this one from the 
Nickelodeon cartoon hit Spongebob Squarepants, 
when his fall was abruptly terminated by the sudden 
arrival of an unyielding floor-like substance.  
KERSHPLAT!!! went the unyielding floor-like substance as Malice landed on it.  
``OOOOF!!!" went Malice as he slammed heavily into the huge stack of 
musty old szines at the bottom of the hole.  The fall was over.

(RED KINGS 4 -- A SHOT IN THE DARK): ``Flat, we gotta talk..."

So there I was, in the Copasetic, sitting across from Flat Evil, 
the button on the belly of the dark underside of the Hobby.  
What little light was left in the already darkened booth seemed to 
suck into his persona.  
Sinking into the deep upholstery of the booth quelled the surrounding noise; 
the orchestra springing into a Henry Mancini number just became 
so much background music...muzak for mobsters.   
A big palooka, Flat's erstwhile bodyguard, sat vigilantly on his barstool 
across the aisle, sipping vigilantly at his beer, and keeping one vigilant eye on me.  
The guy oozed vigilance...I assume that ranks high on attributes for a button man.
	
The fingers that had killed a thousand people, or at least pointed out 
to underlings which ones to kill, pushed an empty shot glass toward me.   
In the middle of the table was a bottle of the high dollar stuff, 
Hardsloggin, aged 20 years. Real years, not game years, I told you...the good stuff.
	
``Stoke up," said Flat in that dead voice. 
A voice where echoes went to die.
I picked up the bottle, popped the cork.  
Instant aroma; it played well against the backdrop of smoke, 
good food, and the palooka's bad aftershave.  
I poured a generous dose into the shot glass, hell, it'd been hours 
since my last drink... at least one, and Hardsloggin was the good stuff.  
I settled in to take my shot in the dark.
 	
I drank it down, and poured another. 
	
``Didn't know you could do single malt in a bath-tub," I said to Flat.
	
``Youse were always the cute one," he muttered back.
	
``Yeah, but mom always liked you best."  
I'm known for my razor like repartee. Had to keep up appearances. 
	
``I was born an orphan," replied Flat and puffed on his cigar.  
Yeah, he was born an orphan the way the guy was that killed both his parents 
and threw himself on the mercy of the court because he was all alone in the world.	
	
``Youse gonna keep crackin' wise, or we gonna talk?"

``Jim Bob doesn't charge for dialog."
	
``Even at dat rate, youse cheatin' him."
	
``Good one," I smiled.
	
``I keeps my hand in."
	
I decided to play him, which is probably as dangerous as it sounds, 
but I'm not known for the blinding wattage of my intellect. 
I'm kinda of a gut instinct, fly by the seat of my pants, 
get my favorite face beat in kind of guy. 
A Chertoff meets Rockford kinda guy. 
Besides, I could tell he already knew something.
	
``You said you were expecting me."
	
``Someone takes a shit," says Flat, ``you expect the smell to show up."
	
``How eloquent.  So who took the shit?"
	
Wrong answer.  One of Flat's eyes narrowed and he leaned 
forward in the booth to better fillet me with the squint.
	
``Youse here about the missing Hierophant...right?"
	
``I didn't even know the Hobby had a zoo.  If an elephant's missing, 
you'd think he’d be pretty easy to find…being big and all.  
I'd look for a lot of grey, should stand out in a black and white world.  
Since when do I take a lost dog case?"
	
Flat chuckled and eased back in the booth.  
The palooka, who had half gotten up, settled back on his stool.  
Like I said, vigilant.
	
``Youse kill me.  Always crackin' wise."
	
I gave a mental sigh of relief.  I'd gotten away with it.  
I had no idea what he was talking about, ``I'm known for my razor like repartee." 

``Yeah, I read that somewheres a few lines back."
	
``So let's say that I was looking for the Hero-phant."
	
Flat nodded, ``youse and a buncha udders."
	
``Otters?"
	
``Don' push it."
	
``Who else is looking?"
	
``Let's say...interested parties."
	
``Why is everyone so...interested?"
	
``It ain't so much the Hierophant, he could be a yutz for all I care...
it's what he's after.  Real Lost Ark stuff."
	
``So he's like the Clockmaker in the Matrix?"
	
Flat grimaced, and pointed the blazing end of his cigar at me. 
``Dat is so cross genre!  Youse sposed to be a flat foot, not a nerd.  
Ya keep breakin' character and we'll get the Continuity Fuzz raiding dis place."   
The palooka looked nervously around at that remark, nervous about the cops. 
But still vigilant.
``I don need to buy more grief than I got already."
	
``So you're one of the interested parties."
	
Flat shrugged, ``I got some stacks o' pennies that could be upset 
by a, howdayasay...unfavorable outcome. But, who don't?  
Dis is a big deal, big as da Hobby."	

``So, if the elephant's not the big deal.  What is?"

``Dat Diplonomicon thingy."
	
I was leaving the Copasetic more confused than when I got there.  
Apparently there was a missing elephant, being chased by otters, 
because what he was after was very important.  
Important enough that the kingpin of the Hobby underworld was interested, 
if not a little worried.  
It almost sounded like an elephant joke, except for the Flat Evil part...
and I didn't know the punchline.

I hate it when I don't know the punchline.

I had faked my way through the meeting with Flat, he thought I was on to something.  
He thought I had a lead, and if I found out something, or someone, for him, 
he would be very grateful.  
Grateful in a couple of bucks sort of way and a 
Get Out of Scrape Without Broken Ribs card the next time 
we crossed paths in a less genial circumstance.  
It wouldn't hurt to have Flat owe me a favor.
I stood there at the front door of the Copasetic on my way out.  
Let my eyes adjust to the outside light as I shook a Red King out of the pack, 
and watched the doorman continue with his frisking of the ingoing patrons.  
I may not be the smartest flatfoot in the Hobby, but...nope, that was all I had.  
I wasn't the smartest flatfoot in the Hobby.  
Elephants, otters...I turned to the doorman.

``Hey, does the Hobby have a zoo?"

He stopped frisking, apparently multi-tasking wasn't a required skill.  
I could see the squint, almost hear the cogs rotate in his huge noggin.  
Seconds ticked by.  ``Nah, no zoo."

``Of course not, couldn't be that easy."   So much for a shot in the dark.

(BOOB to THE BRILLIANT PRESS WRITERS): I tried to perform what I thought was the 
intent of each writer. 
Many may recall (go back in the archives if you like) that both the Red Kings and
Malice in Centerland have previous incarnations in the press.
I didn't print any press in the last two issues, so I just want to remind 
people of this.
The current printing exhausts the list of ``Malice in Centerland"'s that I have
in hand; while I do have more ``Red Kings"'s to print.
I was following what I understood to be the intent of the writers.
If I failed, well, why do you think they call me ``Boob"?
If I succeeded, well, write more!!!
You can't cheat me!!!

\bigskip

\centerline{\bf SPIRALS OF PARANOIA: 2005A, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR WINTER 1906 IS FEBRUARY 16, 2008}

\smallskip

\noindent {\bf THE DUE DATE FOR SPRING 1907 IS MARCH 8, 2008}

\smallskip

\indent {\it Fall 1906}

\noindent AUSTRIA (Rauterberg): {\it a rum-bud} (d ann), 
{\it a SER s a rum-bud}, 

a NAP h, {\it a ALB-tri}, f tyh-GOL.

\noindent ENGLAND (Wiedemeyer): {\it f POR-spa(sc)}.

\noindent FRANCE (Tretick): f BRE S GERMAN f eng-mid, {\it a GAS-spa}, 
f spa(sc)-MAR,
 
f lon-ENG, a mar-BUR, f IRI S GERMAN f eng-mid.

\noindent GERMANY (Ozog for Tallman): a mun-BOH, 
a GAL S ITALIAN a ven-bud, a boh-VIE, 

a RUH h, a TYO S ITALIAN a ven-tri, f SKA h, 
a pie-TUS, a bur-PIC, f eng-MID.

\noindent ITALY (O'Donnell): a vie-BUD, a ven-TRI.

\noindent RUSSIA (Sundstrom): a UKR S a sev-rum, a sev-RUM, 
{\it a ARM-smy, 

a tri-ser} (d ann), a MOS h.

\noindent TURKEY (Biehl): {\it a ANK-arm}, f SMY h, 
f bul(ec)-BLA, {\it f TUN-wes}, 

f ion-TYH, {\it f WES s ENGLISH f por-mid} (nso).

\bigskip

\indent {\it Supply Center Chart}

\+ AUSTRIA (Rauterberg):&ser,nap,rom&(has 4, rem 1)\cr
\+ ENGLAND (Wiedemeyer):&por&(has 1, even)\cr
\+ FRANCE (Tretick):&PAR,BRE,MAR,spa,lvp,edi,lon&(has 6, bld 1)\cr
\+ GERMANY (Ozog/Tallman):&KIE,BER,MUN,hol,den,bel,swe,&(has 9, even)\cr
\+ &\enskip nwy,vie \cr
\+ ITALY (O'Donnell):&VEN,tri,bud&(has 2, bld 1)\cr
\+ RUSSIA (Sundstrom):&WAR,STP,SEV,MOS,bud,rum&(has 4, bld 2)\cr
\+ TURKEY (Biehl):&ANK,SMY,CON,gre,tun,bul&(has 6, even)\cr
\+ Neutral:&none&(Total=34)\cr

\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Paul Rauterberg, 3116 W.~American Dr., 
Greenfield, WI  53221, 

(414) 281-2339 (E-Mail)  trauterberg of wi.rr.com

\noindent ENGLAND: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  CANADA  T6T 1N1, 

(780) 465-6432, wiedem of planet.eon.net 
%cell 780-497-8283; fax 780-468-6432

\noindent FRANCE: Buddy Tretick, 5023 Sewell's Pointe Way,
Fredericksburg, VA  22407, (540) 898-3386

cell (540) 226-5571 (E-Mail) berniebuddy32 of aol.com

\noindent GERMANY: Terry Tallman, PO Box 782, Clinton, WA  98236,
(360) 331-5698 (\$2) 

terryt of whidbey.net

\noindent GERMANY: Temporary Standby is Eric Ozog, PO Box 1138, Granite Falls, WA  
98252-1138,

(360) 691-4264, ElfEric of Juno.com

\noindent ITALY: Jeff O'Donnell, 1345 Simpson Drive, Hurst, TX  76053
%402 Middle Ave., Elyria, OH  44035-5728,

(440) 322-2920 or (440) 225-9203 (cell, as late as midnight Eastern),
unclestaush of yahoo.com

\noindent RUSSIA: Matt Sundstrom, 1760 Robincrest Lane South, Glenview, IL  60025, 
(847) 729-1882, 

Matt.Sundstrom of bbdoch.com or mattandzoe of earthlink.net

\noindent TURKEY: John Biehl, \#8 -- 11530 84th Avenue, Delta, BRITISH COLUMBIA,
V4C 2M1  CANADA, 

(604) 816-0460 (cell) (\$7); jrb of dccnet.com

\bigskip

{\it Game Notes:}

1) Terry is still having some medical problems, 
Eric Ozog is continuing to
negotiate and submit orders for Terry.
Eric originally brought Terry into the Diplomacy hobby all those many
years ago, and so I'm glad he's agreed to do this.

2) The GIRF draw proposal is rejected and reproposed.
Please vote with your Winter orders, if you fail to vote, it cannot pass.
We also have a number of other proposals to vote on with your Winter orders.
As with all proposals, failure to vote vetoes the proposal and they must be 
unanimous.
So, we have I) GIRF draw, II) GT draw, III) FAIRT draw, IV) Recalling 
Terry Tallman to play Germany.
On the last one, I don't have a note from Terry volunteering to return,
but since any one vote, or failure to vote, will veto the proposal, I will
presume that at least one person will check with Terry before voting yes
for this.
If everyone (including Eric, obviously) votes to have Eric leave and
Terry doesn't want to take back over, I will find another standby.
I don't see how that will happen, but thought I should be explicit and 
complete. 
Again, votes are due with the Winter orders. 

\bigskip
 
{\it Press:}

(STAR TREK THE NEXT GENERATION PRESS -- ABOARD THE SCOUTSHIP `ODYSSEUS' -- 
SHIP'S LOG ENTRY): Current Situation Report -- a Borg Entity has been
detected with flank Ferengi and Klingon forces. Sensors indicate a
vestigal Breen presence (likely being assimilated). Our extreme range
sensors report a (vile) Klingon war bird attack on a Romulan trader.
Cardassian spaceship wreakage is also being encountered over a large
area of this quadrant. Furthermore, communications emanating from the
Vulcan home worlds sector report a (slimy) Ferengi sneak attack on
Vulcan, itself. Our only recourse is to power up the experimental Vulcan
designed deep space sensors. We might be able to analyze and break the
Borg signal codes thereby freeing the (misguided) Ferengi and Klingons
from further enslavement. Standby for emergency transmissions. Out.

\bigskip

\centerline{\bf FLIP FLOP: 2003G, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR WINTER 1909 IS FEBRUARY 16, 2008}

\smallskip

\noindent {\bf THE DUE DATE FOR SPRING 1910 IS MARCH 8, 2008}

\smallskip

\indent {\it Fall 1909}

\noindent AUSTRIA (Wiedemeyer): {\it a BUD s a vie}, a GAL S a bud,  
a ukr-WAR, 

{\it a MOS-sev}, a VIE S a bud.

\noindent ENGLAND (Schmit): NMR, DOUG KENT CALLED AS STANDBY; 
a DEN h, {\it a hol h} (d ann), 

a RUH h, f NTH h, f NWG h, f HEL h.

\noindent FRANCE (Jeff O'Donnell): a bel-HOL, a pic-BEL, 
f mid-ENG, a SPA h.

\noindent GERMANY (Sundstrom): f BER S a kie, a KIE S FRENCH a bel-hol, 
{\it f SWE-den},

a stp-NWY, {\it a MUN-ruh}, f SKA S a stp-nwy.

\noindent TURKEY (Levinson): f smy-AEG, {\it a SEV s a rum}, f tun-WES, 
a BUL S a rum, 

f VEN S a tri, f tyh-GOL, a TRI S a ser-bud, f adr-ION, 
f BLA S a sev, 

a RUM S a ser-bud, {\it a SER-bud}.
%Builds: A Con A Smy A Ank

\bigskip

\indent {\it Supply Center Chart}

\+ AUSTRIA (Wiedemeyer):&VIE,BUD,mos,war&(has 5, rem 1)\cr 
\+ ENGLAND (Schmit):&EDI,LVP,LON,por,den&(has 5, even)\cr
\+ FRANCE (Jeff O'Donnell):&PAR,MAR,BRE,spa,bel,hol&(has 4, bld 2)\cr
\+ GERMANY (Sundstrom):&KIE,BER,MUN,swe,stp,nwy&(has 6, even)\cr
\+ TURKEY (Levinson):&ANK,SMY,CON,bul,sev,ser,gre,&(has 11, bld 2)\cr
\+ &\enskip tun,rom,rum,nap,ven,tri \cr
\+ Neutral:&none&(Total=34)\cr

\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  CANADA  T6T 1N1, 

(780) 465-6432, wiedem of planet.eon.net 
%cell 780-497-8283; fax 780-468-6432

\noindent ENGLAND: Karl Schmit, 1509 O'Keefe Road, DePere, WI  54115, (920) 338-8402, 

diplomacy of new.rr.com (\$2)

\noindent ENGLAND: Standby is Doug Kent, 11111 Woodmeadow Pkwy \#2327, Dallas, TX  75228

dougray30 of yahoo.com 

\noindent FRANCE: Jeff O'Donnell, 1345 Simpson Drive, Hurst, TX  76053
%402 Middle Ave., Elyria, OH  44035-5728,

(440) 322-2920 or (440) 225-9203 (cell, as late as midnight Eastern),
unclestaush of yahoo.com

\noindent GERMANY: Matt Sundstrom, 1760 Robincrest Lane South, Glenview, IL  60025, 
(847) 729-1882, 

Matt.Sundstrom of bbdoch.com or mattandzoe of earthlink.net

\noindent ITALY: Don Williams, 27505 Artine Drive, Saugus, CA 91350, 
(661) 297-3947, 

wllmsfmly of earthlink.net or dwilliams of fontana.org

\noindent RUSSIA: Sean O'Donnell, 1044 Wellfleet Drive, Grafton, OH  44044,
(440) 926-0230, 

sean\_o\_donnell of hotmail.com

\noindent TURKEY: Alexandre Levinson, Beeklaan 504, 2562BP Den Haag
THE NETHERLANDS, don't need phone, 

levinson7 of hotmail.com (\$5)

\bigskip

{\it Game Notes:}

1) I have been trying to get Karl to submit orders for a while now.
So, I can't hold up this issue any more, so we go with the NMR.
I'm calling Doug Kent as a standby, but hope Karl returns.
Karl needs to get me draft Spring orders by the Winter deadline
to keep the position.  
Other players may make their Winter adjustments conditional on
who gets the position, which will be announced with Winter.

\bigskip

{\it Press:}

(JEFF O'DONNELL, THE REF SPEAKS): I have an idea on how to solve the N.B.A's 
problem with gambling and referees.

1. Do not give the ref's a long term schedule so the gamblers can't know 
where the ref's are going to be in advance. All the ref's need to know is 
that they will be somewhere. 

2. Hire six ref's for each game and have each one prepare to work with pay.  

3. Do not let ANYONE know which three of the six will be officiating  
the game until tip off.

4. Have the selection of which three ref's will work the game done by the 
same lottery machine that the N.B.A. uses to determine the draft. 

5.Do not let the refs use the phone, any phone at halftime. They basically
need to be sequestered.  With this system there would be no way the 
gamblers would know which ref to approach. It would also ensure that 
the officials are rested and will create a competitive spirit among 
the ref's as they sit on the bench and watch there counter parts work. 

p.s. I used to be a high school j.v. basketball ref before I started having 
physical problems.  it was always funny to me to watch how SOME of 
my fellow refs at the varsity,college and pro level can be so arrogant 
and often made the same type of mistakes that myself and my fellow j.v. 
refs would occasionaly make. like federal judges elected for life 
the apsolute authority that a ref gets even though it's only for 
a couple of hours causes some of them to cop an attitude.  
I think that was the mentality of the guy who threw out Tim Duncan.  
I don't see any real difference between the quality of refs from the 
college to the pro level. 
Adding another 76 refs would not lower the quality of the refs and I
think it would improve with the competition.

\bigskip

\centerline{\bf I CAN'T FIND MY MONEY!: 2001F, Regular Diplomacy}

\smallskip

\noindent {\bf TWO WAY DRAW BETWEEN AUSTRIA AND GERMANY WAS DECLARED!}

This one is done now, except I need to do the endgame chart for Tom Howell,
as he knows, I'm usually really slow with these, but I'll try to do it
next issue.

\bigskip

\centerline{\bf SECRETS: 1999D, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR WINTER 1923 IS FEBRUARY 16, 2008}

\smallskip

\noindent {\bf THE DUE DATE FOR SPRING 1924 IS MARCH 8, 2008}

\smallskip

\indent {\it Fall 1923}

\noindent ENGLAND (Kent): {\it f ENG-lon}, a GAS S FRENCH f mar, 
{\it a PIC-eng} (imp), 

f MID S FRENCH f spa(sc), f POR S FRENCH f spa(sc).

\noindent FRANCE (Sasseville): f MAR S f spa(sc), f SPA(SC) S f mar, 
{\it a BUR s f mar}.     
%standing orders, yes to ANY draw
                                             
\noindent GERMANY (Barno): a ser-BUL.
%votes yes to FREGT, no to EFRT 
%vote YES to FREGT draw

\noindent RUSSIA (Parker): f nwy-NWG, a stp-NWY, f nwg-EDI, 
f cly-LVP, a WAR h, 

{\it a DEN-lon}, a KIE S a pru-ber, f NTH C a den-lon, 
a HOL S TURKISH a bel h, a pru-BER.

\noindent TURKEY (Linsey): a arm-SEV, a bul-RUM, f TYH S f wes-gol, 
a rum-SER, {\it a MUN-bur}, 

a SIL S a boh-mun, {\it f WES-gol, a BOH-mun, f GOL-mar}, 
a BEL S a ruh, a tri-TYO, 

{\it f NAF s FRENCH f spa(sc)-wes} (nso), a VEN h, 
f PIE S f gol-mar, a RUH S a bel.

\bigskip

\indent {\it Supply Center Chart}

\+ ENGLAND (Kent):&LON,bre,por&(has 5, rem 2)\cr
\+ FRANCE (Sasseville):&PAR,MAR,spa&(has 3, even)\cr
\+ GERMANY (Barno):&bul&(has 1, even)\cr
\+ RUSSIA (Parker):&MOS,STP,nwy,swe,den,ber,WAR,&(has 10, bld 1)\cr
\+ &\enskip kie,edi,hol,lvp   \cr
\+ TURKEY (Linsey):&CON,ANK,SMY,rum,gre,ser,bud,&(has 15, bld 1)\cr
\+ &\enskip nap,ven,tun,sev,rom,tri,vie,mun,bel \cr
\+ Neutral:&none&(Total=34)\cr

\bigskip

\indent {\it Addresses of the Participants}

\noindent ENGLAND: Doug Kent, 11111 Woodmeadow Pkwy \#2327, Dallas, TX  75228

dougray30 of yahoo.com 

\noindent FRANCE: Roland Sasseville, Jr., 38 Bucklin Street, Pawtucket,
RI 02861, (401) 481-4280 (\$0)

roland6 of cox.net  

\noindent GERMANY: Mike Barno, 634 Dawson Hill Road, 
Spencer, NY 14883, (607) 589-4906 

mpbarno of lightlink.com 

\noindent RUSSIA: Vern Parker, 337 Winter Hill Place, Powell, OH 43065,
(614) 402-5139

VernDip of aol.com is preferred

\noindent TURKEY: Bruce Linsey, PO Box 234, Kinderhook, NY
12106

GonzoHQ of aol.com

\bigskip

{\it Game Notes:}

1) The RT Juggernaut draw and the concession to Turkey are rejected.

\bigskip

{\it Press:}
 

\bigskip

\centerline{\bf CAST NO SHADOWS: Breaking Away, Designer's Rules}

\smallskip

Rules are at:

\noindent http://devel.diplom.org/DipPouch/Postal/Zines/TAP/Tinamou/rules/BreakingAway.htm

\noindent Note the special rules for replenishments on the first turn, and I'm glad the 
math was double checked, we did have a card error, which is now corrected and we have
the first turn below.

\smallskip

\noindent {\bf DUE DATE FOR TURN 4 IS FEBRUARY 16, 2008}

\smallskip

%--F--I--N--A--L-- --F--I--N--I--S--H-- --L--I--N--E--
%--S--P--R--I--N--T-- --F--I--N--I--S--H-- --L--I--N--E--
%
\centerline{\it Turn 3}

\smallskip 

\+ 19 (replenish with a 3) &Sanctus   \cr
\+ 18 (no replenishment)   &Empty  \cr
\+ 17 (no replenishment)   &Empty  \cr 
\+ 16 (replenish with a 3) &Bonham, Granny   \cr
\+ 15 (replenish with a 5) &Water  \cr
\+ 14 (no replenishment)   &Empty  \cr 
\+ 13 (replenish with a 3) &Bowie, Travis, Crockett   \cr
\+ 12 (replenish with a 6) &Mideast  \cr
\+ 11 (replenish with a 7) &Kyrie, Xavier, Yorick, Gavrancic, Dragutinovic, Wally \cr 
\+ 10 (replenish with a 13)&Vidic, Krstajic, Kyoto, Drugs \cr
\+ 9 (no replenishment)    &Empty  \cr
\+ 8 (replenish with a 3)  &Zorro, Carrot  \cr
\+ 7 (replenish with a 5)  &Gloria, Rincewind   \cr
\+ 6 (replenish with a 7)  &Agnus, Death   \cr

\bigskip
%Sprint Points at 40, 80: 10,8,6,5,4,3,2,1 (final are just double these)
%Movement Order: A/B/C/D; highest card played that turn; highest card in hand

\indent {\it Addresses of the Participants -- Their Team and Their Cards}

\smallskip

\noindent TEAM 1 (Rick Desper): rick\_desper of yahoo.com (0 points)

Team Name: The Turtle Moves; Captained by Cut-My-Own-Throat Dibbler

\+ A: Rincewind the Wizzard &&14 12 16 5 (3) \cr
\+ B: Granny Weatherwax     &&12 11 3  (11) \cr
\+ C: Captain Carrot        &&15 11 3  (3) \cr
\+ D: Death                 &&13 20 7 (3) \cr

(note, Rincewind is accompanied by the Luggage, Granny is on Her Broom, 
Carrot is of the City Watch, and Death is just DEATH!)

Total Replenishments: $12+58+18 = 88$
                
\smallskip

\noindent TEAM 2 (Tom Howell): off-the-shelf of olympus.net (0 points)

Team Name: Never Ending Worry Source; Manager: Rumour; Team Captain: Ye Olde Manager

\+ A: Water    &&15 3 16 5 (11) \cr
\+ B: Kyoto    &&14 7 13 (3) \cr
\+ C: Mideast  &&11 5 6 (6) \cr
\+ D: Drugs    &&9 11 13 (5) \cr

Total Replenishments: $12+35+37 = 84$        
   
\smallskip

\noindent TEAM 3 ((David Partridge): rebhuhn of rocketmail.com (0 points)
%360-928-9698

Team Name: Famous Four  

\+ A: Krstajic      &&8 15 16 13 (6) \cr
\+ B: Vidic         &&8 13 13   (3) \cr
\+ C: Gavrancic     &&8 9 7   (5) \cr
\+ D: Dragutinovic  &&8 11 7 (6) \cr

Total Replenishments: $12+35+40 = 87$   
               
\smallskip

\noindent TEAM 4 (Brendan Whyte): obiwonfive of hotmail.com (0 points)

Team Name: The Reverse Alphabeticists

\+ A: Zorro    && 10 15 11 3 (3) \cr
\+ B: Yorick  && 10 12 7 (5) \cr
\+ C: Xavier   && 7 10 7  (5) \cr
\+ D: Wally    && 10 3 7 (5) \cr

Total Replenishments: $12+26+24 = 62$

\smallskip

\noindent TEAM 5 (Alexander Woo): aswoo of yahoo.com (0 points) %awoo@math.ucdavis.edu

Team Name: Just Ordinary; Manager: Credo

\+ A: Agnus     && 15 12 20 7 (3) \cr
\+ B: Sanctus   && 8 4 3  (3)   \cr
\+ C: Kyrie     && 10 7 7  (5)    \cr  
\+ D: Gloria    && 12 16 5 (3)    \cr
           
Total Replenishments: $12+44+22 = 88$ 

\smallskip 

\noindent TEAM 6 (Andy York): wandrew of compuserve.com (0 points)

Team Name: Alamo

\+ A: Crockett      && 15 5 3 3 (3) \cr
\+ B: Travis        && 15 3 3 (3)\cr
\+ C: Bowie         && 10 3 3 (3) \cr
\+ D: Bonham        && 3 3 3 (3) \cr

Total Replenishments: $12+12+12 = 36$

\bigskip

{\it Game Notes:}

1) The rules are on the {\it TAP} website in the {\it Tinamou} section.
Ask if you have any questions.
Up above in parentheses is the card you played to get to where you are
in the field.  The replenishment card is the last card in your list.
Be careful to note that the card you played (the one in parentheses) is
not available for you, for next turn.
Just for fun, I'm going to keep track of total replenishment, by turn, which is a 
rough measure of how the teams are doing.
Of course, it is lining up to get across the sprint and final lines in the
right places that really counts.
We can calculate an ``efficiency score" later, which will be the ratio
of scoring points per replenishment.
If I'm predicting how the future of this will come out, a 10\% score will
be really tremendous for this measure.

2) I didn't have orders from many of you, and didn't want to hold up this
already egregiously late issue for this game, so for those of you I didn't
have orders from, everyone played lowest card.
In the end, of course, ALMOST everyone played lowest card, just almost enough 
to break up the middle of the pack -- note the slick move by Wally...

\bigskip

{\it Press:}


\bigskip

{\it Personal Note to You:}

\vfill\eject
\end
