\nopagenumbers 
\font\twelverm=cmbx12 at 12pt
\centerline{\bf\twelverm THE ABYSSINIAN PRINCE \#315}
\line{\hfil March 26, 2008}    
\smallskip                                                    
\settabs 3 \columns 
\beginsection

\medskip

Produced by Jim Burgess, 664 Smith Street, Providence, RI 02908-4327  USA,
(401)351-0287 
 
\noindent Accessible through Internet at burgess of world.std.com (all E-Mail
addresses are reported in this format, replace the `` of '' with ``@''; if you 
bounce try sending to me from another account. 
Some of you have been getting bounced messages from
my ISP's spam protection, if that happens to you, USE my backup E-Mail
at jfburgess of gmail.com!!!  Don't complain that my E-Mail keeps bouncing
without forwarding the bounced message to that address.
Then I can forward it to the ISP help to get it dealt with.
 
\noindent Web Page Address: /Postal/Zines/TAP/index.html

\bigskip

I expect ALL players to be signed up on the E-Mail notification list for the szine,
see below.
Some of you have been complaining about this, but it is up to you to get on this list,
it's easy, come ask me if you have trouble.
THIS IS A PROBLEM, sign up now if you're playing!!!

I include the ManorCon announcement (my favorite European Dip Event) as Mark
Stretch requested.
It is in a new location from when I last attended, but from all accounts last
year was great despite poor weather, it should be better this year!!!
At the time of ManorCon, this year as usual on the last weekend in July, 
I plan to be at North American DipCon 
in Bangor, Maine, we hope details on that will be forthcoming shortly.
I think Doug Kent might get some more details for {\it Diplomacy World} \#101.
DipCon is supposed to be starting on the Thursday night and going through Sunday.
I was going to get this out a few days earlier, but with ``April 15th" coming up
I had already intended to take the deadline out an extra week, so we were all set.
I've got a host of subszines in here, and I think I'm back on track now.
Also, think about writing press for games, whether you're in them or not.
Let's show people what postal szines are SUPPOSED to be.
Thanks for the born-again press writers, you know who you are, we love you.

\bigskip
%Dave Partridge's unlisted phone number 603-672-2879 -- probably corrected!!!
%Tinamou players: Schwarzschild:  Graham Wilson (NO 
%but E-mails: grahamaw of home.com (or gwilson of dvnet.com)),
%Berry Renken, Heath Gardner
%Copernicus:  Warren Goesle, Heath Gardner, Art Schleinkofer, Bruce Reiff,
%Eric Brosius, Bob Dowrey
%Tour De Farce:  Jim Burgess, Eric Brosius, Warren Goesle, Sara Reichert,
%Phil Reynolds, Rick Desper
%Milk and Cookies: Jim Burgess, Warren Goesle, Sara Reichert, Phil Reynolds,
%Rick Desper, Richard Weiss, John Schultz
%Who's Your Buddy:  Sara Reichert, Phil Reynolds, Art Schleinkofer, 
%Brad Wilson, Rick Copeland, Karl Muller

The postal sub price is still
\$1.50 per issue in the US and Canada,
with double that for other foreign subbers(or \$3.00 per
issue sent airmail).
Players in current games and standbys will
continue to get the issues for free, and future game starts 
(except for Nuclear Yuppie Evil Empire Diplomacy, which is free) cost 
\$20.00 (\$15.00 for a life of the
game subscription and \$5 for the NMR Insurance.
Anyone may play in subszines 
for free and just jack up the issue page count.
Since I have to get caught up this issue with all sorts of subszines, 
I'm going to be fairly limited with other items this issue.  
See the revised game start announcements below!

Check out the connections in the Diplomatic Pouch with all of
the information you need to play Diplomacy on the Internet at:
/

I also have taken over the Postal port/DipPouch/Postal

\noindent and {\it TAP} on the web is there at:
/Postal/Zines/TAP/index.html

where the szine resides in html format. 
Presently, issues from \#190 to the current issue
are there, and I will be updating the back issues gradually someday. 
 
Peter Sullivan's subszine is out of stasis, and all the
back issues can be accessed via :

http://www.burdonvale.co.uk/octopus/index.html.

Peter is now back at least sometimes.
Rip Gooch is probably permanently missing.
Dave Partridge had been picking up the choo-choo
game slack.
Contact Dave
at rebhuhn of rocketmail.com for more info on getting into choo-choo games
and other sorts of different games.
And Andy York and Doug Kent have been my most frequent subszine guests lately!!!
Andy has been in every issue, thanks, Andy!!!
And Doug Kent has been coming out faster than {\it TAP} lately, so
many issues have been having multiple {\it Eternal Sunshine}'s. 
And Michael Lowrey gets his in every few issues too!
So, we have a full set of subszines at the moment.

The {\it TAP} mailing list has moved!
It now is even BETTER protected than it was.
I even have a bit of trouble posting to it.
To post to this list, send your email to: tap of diplom.org.
But this is completely moderated, it won't go out to the list unless
I approve it.
In general, I intend to keep traffic down to just the szine, as we've
been doing and I'll put your LOCs in here.
I {\bf EXPECT} all players to be on this list, especially those of you who
are from foreign countries!!! 
You need this to find out when the szine is up on the web to check in on results.

General information about the mailing list is at:
/mailman/listinfo/tap

You can sign up from there, or send E-Mails to:
Tap-request of diplom.org;
with the word `help' in the subject or body (don't include the
quotes), and you will get back a message with instructions.
You must know your password to change your options (including changing
the password, itself) or to unsubscribe.  
Normally, Mailman will remind you of your diplom.org mailing list
passwords once every month, although you can disable this if you
prefer.  This reminder will also include instructions on how to
unsubscribe or change your account options.  There is also a button on
your options page that will email your current password to you.
A big, big thank you for Millis Miller for setting this all up!!

\bigskip

\centerline{\bf THE SEARCH FOR MICHEL FERON}

\smallskip

Jerry Jones gets added to the list of failures, next up the former
editor of {\it Moeshoeshoe}, along with Michel Liesnard one of the 
founders of the Belgian Diplomacy hobby.
If you read the forthcoming {\it Diplomacy World} \#101 you will 
quickly figure out why I chose Michel Feron to search for next.
There are a host of clues on the Internet that I found, so he 
could be very easy to find. 
Go for it, you have until Issue \#320.

I am running out of people on MY list of who to search for, so
I am looking for ideas, who would you like to find?
Send me some names.
I may go into Jim Meinel's Encyclopedia of North American Diplomacy
szines and find some more szine editors to search for, that's
what I usually do, but I'd like to find people that some of you
will search for or want to find!!!
Come on, help me out.

\bigskip

Feel free to spend the time looking for some of the backlog.
Let's get Jerry, Margaret, Derek, Sylvain, Steve, Ed, Tom, Gregory, and 
ESPECIALLY Kevin found too!!!
This is a regular continuing feature of the szine
and I will be introducing a new ``search for'' every five issues.
Moreover, you can win a \$25 prize for finding some previous
target who went unfound in the original \$50 period.
That means that if Jerry Jones or Margaret Gemignani or 
Steve Heinowski or Ed Henry or Tom Hurst or 
Gregory Stewart or Derek Nelson or Sylvain LaRose or John Smythe
is ``found'' from now on it is worth \$25.

\bigskip

Winners will receive credit for Dip hobby activities
that I will pay out as requested by the winner.
Subscribe to szines here or abroad, run your
own contests, publish a szine, finance a web page, 
GO TO A DIPLOMACY CONVENTION or whatever.
Spend it all right away or use me as a bank to cover hobby activities
for years.
What must you do to win?
Get me a letter to the editor for {\it TAP} from the person we're
searching for.

This is very important, just finding them doesn't do it.
They have to write me a letter.     
The final judge as to the winner of any contest will be the target 
himself and I reserve the right to investigate the winning entry.
When you find someone I'm looking for, you should ask him to send me a 
letter for print that includes a verification of who ``found'' him.
%Michael Swift, Mike Stewart, and 
%Jason Yarbrough , Tim Stabosz, 
%Eric Ozog has $25
%Leslie Obata is owed $25
%Derek Nelson, winner of the first postal game in Graustark.  I last saw him
%at the '76 DipCon in Baltimore.
%Charles Wells, former publisher
%John McCallum, former publisher (Brobdignag, SerenDip, etc.)
%Dan/Charles Brannan, former publisher (Wild 'n Wooly)

\bigskip

\centerline{\bf INTERNATIONAL SUBSCRIPTION EXCHANGE NEWS}

\smallskip

John Harrington and I have agreed to close the ISE.
In this age of PayPal, the traffic on the ISE had fallen almost to zero,
and what was left almost entirely was me facilitating orders of 
Breaking Away and John's other Fiendish Games.
So, I'm still going to help John out with that, but there will be no
ISE.
If anyone still needs assistance with this, though, since I'm helping
John out, like if you're in a foreign country and need to send dollars
for dipping things to someone in the US, I may be able to help you out.

\bigskip

\centerline{\bf DIPDOM NEWS SECTION (with letters)}

\smallskip
 
Obscure and not-so-obscure ramblings on the state of the hobby
and its publications, custodians, events, and individuals with
no guarantee of relevance from the fertile keyboard of Jim-Bob,
the E-Mail Dip world, and the rest of the postal hobby.
My comments are in {\it italics} and {\it ((double 
quotation marks))} like this.
{\bf Bold face} is used to set off each individual speaker.
I should also make a note that I do edit for syntax and spelling
on occasion.

%A VERY light discussion is taking place that will address what 
%stance we (the hobby) should take (proactive in some way for sure) 
%toward Hasbro, the new owners of the rights to Diplomacy.
%More on this will be forthcoming, but it looks like Hasbro might
%have its version of Diplomacy on the market for the Christmas
%season and they actually will be employing ``play-testers''.
%No word on precisely what this means yet, could it mean that
%they will offer a series of ``official'' variants?
%Stay tuned....
%If you want to be part of the discussion, send the MESSAGE:
%
%subscribe hasbro
%
%to majordomo of diplom.org, it works just like the tap mailing list
%described below.  Sending messages to hasbro of www.diplom.org
%sends the mail to the whole list.
%The big news this time is the beginning of the breakout of
%Hasbro into official contact with the hobby.

The game Diplomacy is a copyrighted product owned by Hasbro and all
reproductions or other use of that material in this szine is intended to
be personal use and not infringe on those rights in any way.
All reproductions are done at a heavy financial loss to the editor
and thus are without the remotest possibility of commercial intent,
except to promote THE game, the Game of Diplomacy, which you all 
should purchase from Hasbro or other duly licensed distributors.
 
Stephen Agar has matched the Hasbro rule lists 
and more with some of the even older
rulebooks.
Check these out if you like:

http://www.hasbro.com/default.asp?xcc\_gameandtoyinstructions

http://www.hasbro.com/instruct/Diplomacy.PDF

http://www.hasbro.com/instruct/Diplomacy(OlderVers).PDF

Nice of them to make BOTH of these available.
And all seven different US rulebooks for Diplomacy can now be found here
courtesy of Stephen Agar (relatively new address for this):

http://www.diplomacy-archive.com/diplomacy\_rules.htm

%1: The Reformer, who seeks perfection (crusading type).
%2: The Helper, who seeks love (altruistic type).
%3: The Performer, who seeks status (competitive type).
%4: The Individualist, who seeks an identity (imaginative type).
%5: The Investigator, who seeks knowledge (analytical type).
%6: The Loyalist, who seeks security (ambivalent type).
%7: The Enthusiast, who seeks gratification (thrill-seeking type).
%8: The Leader, who seeks self-sufficiency (dominant type).
%9: The Peacemaker, who seeks contentment (accommodating type).
%See http://graphics.lcs.mit.edu/~becca/enneagram/
%new test at: http://www.9types.com
%My scores in order were: 9, 13, 15, 7, 15, 6, 17, 18, 14.
%Robert Lesco's Marco Poll, the defacto poll of the
%North American hobby since the Runestone is pretty much
%officially dead, continues to collect votes.
%This is an official {\it TAP} approved poll.
%Here are the particulars on the Marco Poll:
%Vote for your top five in each category and you can't vote (or at least
%it won't be tabulated) for Robert Lesco or his szine, which I don't see.
%I will send this to Robert and offer him a trade.
%The deadline is September 1st and either send your ballot to marcopoll of yahoo.com
%or mail to Robert Lesco, 49 Parkside Drive, Brampton, Ontario, CANADA  L6Y 2H1.
%For identification purposes, Robert would like you to identify yourself both
%by name and by affiliation (a game you play in or a szine you sub to).
%Here are the categories this year (I like some of the new ones!!):
%1) Favourite {\it ((Hey, what, he's Canadian, yeah.))} Zine  {\it ((What's a zine,
%shouldn't that be Szine???))}
%Backstabbers United Monthly, Costaguana, The Diplomatic Pouch, Absolute, Vertigo
%2) All Time Favourite Zine {\it ((Szine))}
%Magus, Europa Express, Thirty Miles of Bad Road, Perelandra, North Sealth West George
%3) Best Diplomacy Player
%John Quarto von Tivadar, Edi Birsan, Mark Fassio, Chris Martin, David Partridge
%4) All Time Best Diplomacy Player
%Edi Birsan, Mark Fassio, Kathy Caruso, Rod Walker, Hohn Cho
%5) Best GM
%Malcolm Cornelius, Tim Miller, Tim Richardson, Conrad von Metzke, Doug Massey
%6) Player Who Writes the Best Letters/E-Mails
%Don Williams, Richard Weiss, Mark Fassio, Toby Harris, Cal White 
%7) Folded Zine {\it ((Szine))} You Miss the Most
%Magus, Diplomacy by Moonlight, Le Front du Liberation de Diplomacy, Kathy's Korner
%8) Favourite Variant
%Modern, Nuclear Yuppie Evil Empire Diplomacy, Woolworth, Spy Diplomacy, Colonia

\bigskip 

{\bf Chris Babcock (Sat, 29 Mar 2008 13:03:20 -0700)}

At the instigation of Dorian Love, I've just set up ZAED - Zuid-Afrika
Educational Diplomacy. Dorian and I will co-JK this Diplomacy judge for
students, educators, homeschoolers and youth workers. If you are a
teacher, homeschooling parent or a leader in a youth association and
you would like to enroll children up to 18 years old in the program,
please contact me for details. There is infrastructure for intramural
and international competition at 3 levels of educational development.
The maps will be available on floc.net and openings published on the
Openings List on diplom.org, but registrations will need to be
pre-approved.

\centerline{Chris, cbabcock of kolonelpanic.org}

{\it ((Great idea, Chris (and Dorian).  Let us know how it goes, we
have a number of subbers here who might be interested in this, so 
I thought I would publicize it here.
Contact me or Chris directly.))}

\bigskip

\centerline{Check out current and back issues of {\it Diplomacy World} -- Yahoogroup diplomacyworld}
and at Doug Kent's new {\it Diplomacy World} web site at:

\noindent http://www.diplomacyworld.net/

\bigskip

Also, I need any Hobby Award Nominations NOW (!!!) for the :

\noindent The 2005 and 2006 and 2007 Don Miller Award for Meritorious Service;

\noindent The 2005 and 2006 and 2007 Rod Walker Award for Literature;

\noindent The 2005 and 2006 and 2007 John Koning Award for Player Performance;

\noindent The 2005 and 2006 and 2007 Fred Hyatt Award for GM Performance;

or

\noindent A 2005 and 2006 and 2007 Kathy Byrne Caruso Award for Lifetime Achievement (if warranted).

The Hobby Awards Committee is Jim Burgess (Chair and Treasurer),
Fred Davis, Jr., Melinda Holley, Gary Behnen, Jamie Dreier,
Paul Kenny, Mark Stretch, and Robert Lesco.
I was going to publish the award ballot for this year 
in this issue, but I realized that I really just had to get this out first and
then do that.... and then, well, REAL SOON NOW!!!
And when I do, I'm going to give out three sets of awards and get caught up for the 
missed years, that seems to make the most sense.  
Committee.... you will be hearing from me soon!
This also fell apart with my move, but I think I can get it together for next
issue when all the games are in Winter.

\bigskip

{\it Diplomacy World} Issue Deadline is now:

\noindent Deadline Spring 2008, Issue \#101: beginning of April

I'm really pleased that former editor Doug Kent has agreed to come 
back and get this back on track and get us to \#100.
Thanks, Doug!
We're putting things together for the
next issue and it looks good too, but if any of you want to write anything
there's always more room,
contact Doug!
Most every old fart getting this szine sent something in for \#100,
so if you missed out, send something now for \#101!!!
We're looking for all sorts of kinds of articles, come talk to us if you
want some ideas.

See http://www.diplomacyworld.net/ for some exciting back issue material being
posted as well as the new Issues, including the monstrous Issue \#100.  
Highlights of \#100 include Walt Buchanan's ex-wife Carol showing us who REALLY
was in charge of the hobby back in the Hoosier Archives days, Eric Ozog augmenting
the oft-heard, but never get enough of, love story between Eric and Cathy,
and the start of the new Diplomacy World Demo Game.
In addition to the first two issues, we have 
every issue back to issue number 53 posted.  Eventually they all will be up.

%\noindent Final Hobby Awards Ballot for 2004, nominations now to:
%burgess of world.std.com
%
%The qualifications for the Kathy Byrne Caruso Lifetime Achievement 
%Award are that the awardee must have been: (1) Active in the 
%Diplomacy Hobby in at least Three Separate Decades; 
%(2) Multidimensional in their Contributions to the Hobby 
%(e.g. writing, playing, publishing); (3) Taking Retirement or 
%Semi-Retirement from the Diplomacy Hobby; and (4) One of the 
%Hobby’s Unique Personalities Worthy of Being Remembered as Long 
%as THE Game Continues to be Played.  This award need not be awarded
%each year, but only as worthy candidates are identified.  The only
%past honoree is the late Richard Sharp.
%
%The other award categories are self-explanatory:
%
%\noindent Nominees for the 2004 Don Miller Award for Meritorious Service
%
%\noindent Nominees for the 2004 Rod Walker Award for Literary Achievement
%
%\noindent Nominees for the 2004 John Koning Award for Player Performance
%
%\noindent Nominees for the 2004 Fred Hyatt Award for GM Performance
%
%--- --- --- --- --- --- ---

Editorial Board for {\it Diplomacy World}:

\noindent  Doug Kent, NEW Lead Executive Editor!, 11111 Woodmeadow Pkwy 
\#2327, Dallas, TX  75228, dougray30 of yahoo.com 

\noindent Tim Haffey, 810 53rd Ave., Oakland, CA 94601 USA; trhaffey of
aol.com -- Ex-Lead Editor and Archives Editor

\noindent Jim Burgess, 664 Smith Street, Providence, RI 02908-4327, USA;
burgess of world.std.com -- Co-Editor and Interview Editor

\noindent Rick Desper, 5440 Marinelli Road, \#204, Rockville, MD  20852, USA;
rick\_desper of yahoo.com -- Demo Games

\noindent Jim O'Kelley, 4224 N. Hamlin Avenue, Chicago, IL 60618,
jimthegrey1013 of yahoo.com -- Club and Tournament Editor

\noindent Jack McHugh, 810 School Lane, Folcroft, PA  19032,
jwmchughjr of gmail.com -- Variant Editor

\bigskip

OK, and then we have FTF tournaments.
See the Pouch FTF tournament page at:

\smallskip

\noindent http://devel.diplom.org/Face/cons/index.php

\smallskip

\noindent and one that is not there yet is this year's DipCon.
DipCon will be held on the campus of the University of Maine at Orono, just
outside Bangor, Maine.
It is set for the last weekend in July, starting Thursday, July 24th and running
through Sunday, July 27th.
We hope to have more details soon, but I am planning to go and hope
many of you may be coming as well.
Talk to me if you're thinking about it.
I haven't been to DipCon in a few years now, so this year I'm planning it way
in advance.
I hope we get this going soon with the publicity so a lot of you come and make it.
Jim O'Kelley also has been coordinating a number of Chicago events etc.
that are on the web page, go to a FTF tournament near you soon.

\bigskip

\centerline{\bf MUSIC AND MOVIES SECTION (WITH COMMENTS ON OTHER ARTS AND SOCIETY)}
     
\smallskip

We were running a ``23 tunes'' contest here
(stolen blatantly from Mark Wightman and the late lamented {\bf The Sprouts of Wrath}.
If anyone would like to send me a tape or CD of their 23 (which was the original point)
that would be great, but I don't intend to require that.  I will be playing in the
sense that I'll be putting 23 tunes in, and you have to guess me, but I obviously
won't score points.
Send commentary with your choices, and we'll see if people can
guess who you are!!!
And already there is a LOT of diversity in defining tunes and styles, so 
BE CREATIVE!!!
This kind of died, mostly because of me.  I don't want to take this last issue
getting it back together, but might next issue.
Feel free to send along general music comments any time.
 
%To encourage voting early, I picked five voters at random to receive five US
%dollars from me (either in cash or paid to someone for Dip stuff or to get
%a free tape).
%Tony Dickinson won the Round 5 prize, so we had three of the six Round 1 voters
%won and one of the three Round 2 postal voters who also got five chances to win.
%That showed the value of getting in early!!
%Voters in Round 1 were Mike Barno(\$5), Rick Desper (\$5), Tony Dickinson (\$5),
%Drew James, Heath Gardner, and John Harrington.
%Round 2 postal voters were John Schultz (\$5) Ian Moore, and Stan Johnson.
%Round 2 E-Mail voters were Scott Morris, 
%Warren Goesle, Peter Sullivan, and Michael Lowrey.
%Round 3 voters were Dick Martin, Richard Weiss, and Rip Gooch.
%Round 4 voters were Roland Sasseville, Jr. (\$5),
%Don Williams, Brent McKee, and Andy York.
%Round 5 voters were Mark Larzelere, Al Tabor, Jody McCullough, and that's it.
%We'll end up with a monster party tape at the end of it that I plan
%to segue and sequence and copy for distribution.
%The result will be a great New Millenium party tape -- we're going for 90 minutes.
%I've also been thinking that I should put this out on CD
%as truly emblematic of the new millenium.  
%I don't have the capability to do that quite yet, but I think
%I might by then.
%Any suggestions (or especially volunteers) on this front will
%be cheerfully accepted and could receive monetary payments!
%The CD way may still occur if someone steps forward and actually does it for me.
%So far, we have ``I Melt With You'' by Modern English; George Gershwin's
%``I got Plenty O' Nuttin' '' from {\it Porgy and Bess} in the 1957 concert
%recording with Ella Fitzgerald finishing off the vocals after Louis
%Armstrong blows and sings through the tune; Duke Ellington performing
%Billy Strayhorn's ``Take the A Train''; Frank Sinatra's ``New York,
%New York''; something from the B-52's;
%the original Van Morrison and Them version of ``Gloria'';
%The (English) Beat's 12 inch version of ``Save It for Later'' 
%ratchets things up to the next level (wherever you put it!);
%Buster Poindexter's ``Hot, Hot, Hot'' keeps you there;
%``Atomic Dog'' by George Clinton blows the doors off,
%and Koko Taylor cleans up singing Willie Dixon's ``Wang Dang Doodle''.
%After I get timings down, I'll choose exactly which songs below make the list.
%
%EXTRA SPECIAL B-52'S BULLPEN: (7) ``Love Shack'';
%``Rock Lobster". {\it ((A tie, a tie!!!!))}
%
%BULLPEN: (9) Nirvana -- ``Smells Like Teen Spirit";
%``Cumberland Blues'' -- the Grateful Dead.
%(8) ``Twistin the Night Away" -- Sam Cooke; ``In Between Days'' -- The Cure;
%``Mannish Boy" -- Muddy Waters; ``Shake, Rattle, \& Roll" -- Big Joe Turner; 
%``Proud Mary'' -- Ike and Tina Turner.
%(7)  ``I Wanna Be Sedated" -- Ramones; ``Twist \& Shout" -- Beatles.
%(6) ``Magic Carpet Ride" -- Steppenwolf;
%``Crossroads'' -- Eric Clapton; ``Play That Funky Music'' -- Wild Cherry;
%``I Fel Good" -- James Brown;
%``Radar Love'' -- Golden Earring; 
%Devo -- ``Whip It"; ``Echo Beach'' -- Martha and The Muffins.
%(5) ``Sing Sing Sing'' -- Benny Goodman; ``Rocking the Casbah'' -- The Clash; 
%Squeeze -- ``If I Didn't Love You"; ``Roadrunner'' -- 
%Jonathan Richman and the Modern Lovers.
%
%SPECIAL ROLLING STONES BULLPEN: (6) ``Paint It Black''. 
%
%SPECIAL TALKING HEADS BULLPEN: (9) ``Take me to the River".
%(4) the entire {\it Speaking in Tongues} record
%(special call for ``Road to Nowhere'').
%
%SPECIAL ALPHABET SONG BULLPEN: (6) ``YMCA" -- Village People. 
%
%SPECIAL DRUG MUSIC BULLPEN: 
%(8) ``Rd, Red Wine'' -- UB40.
%(6) ``Don't Bogart that Joint'' 
%-- Fraternity of Man; ``The Old Dope Peddler'' -- Tom Lehrer.
%(5) ``Cocaine'' -- Eric Clapton's version; ``Casey Jones'' -- the Grateful Dead.
%(4) ``White Rabbit'' -- Jefferson Airplane; ``Love Is the Drug'' -- Roxy Music.

\bigskip

\centerline{\bf {\it 23 Tunes Game}}

\smallskip

Here are the rules for 23 TUNES.  You send me three tunes for the first turn,
and then two tunes in each of the last ten turns for a total of 23.
If you missed the first turn, you can still catch up by sending five tunes next
issue, and guess on submitters to this issue.
I am also submitting my tunes.
After we're done, I'd like to exchange CD's/Tapes for as many of the tunes players
as possible, but this is not required.
I'll be sending the winner both my LAST 23 tune list and my NEW 23 tune list.
The winner is determined by having you guess each issue who submitted what list
(I will tell you who the submitters are).  For each list you get right, you get
a point, you also can win bonus points from me for really cool tune selections.
%That's it, not complicated.
%I hope by starting this up, we'll get more to join, five songs required to enter
%late.
%Playing this issue (guess who is whom by number, scores are in parentheses) 
%is, in alphabetical order, 
%Jim-Bob Burgess, Rick Desper (1), %Steve Emmert, Doug Kent, 
%Dick Martin, %Jim Reader,
%Richard Smith (3), Joakim Spangberg, %Brendan Whyte, 
%and Brad Wilson (4).
%The linking theme thing didn't seem to go over too well.
%No one really figured out the true linking theme.  
%Rick Desper was using Underground tube stops and songs with that as the title,
%they were things like that.  
%I'll let you guys talk a bit to each other on that with your guesses.
%I have added some kind of comment on each tune.

WHAT I NEED: 
Quite a number of you SAID you would join but haven't yet, so we'll get started and
put the pressure on you.  
This part is still a MESS and I'm getting this issue out and then will catch up next time.
I think I'm going to simplify the rules to get it back on track.
%Rick Desper: Anyway, my tunes this time are "Set the Controls for the Heart of Sun" by Pink %Floyd, 
%in honor of the film Sunshine, and "Afternoon Delight" by the Starland Vocal Band, 
%that Will Hunting just sang a snippet from, and Ron Burgundy covered in "Anchorman".  
%The latter is really becoming an anthem of the Goofy 70s.
%I have no idea what this game is supposed to mean, but we can't go wrong with "Afternoon %Delight".

\bigskip

{\bf Mike Barno (Thu, 27 Mar 2008 09:57:16 -0500)}

Jim, I'm glad you liked the Parlor Cats CD.  Almost all of the Brian
Swan guitar work you enjoyed is performed on a big-bodied Gretsch with a
whammy bar.  Most of the more obvious note-bending is done with the
whammy bar, but there's some slide on a few songs.  I didn't know you
had live Eddie Vinson in your background.  What other old-time bluesmen
have you heard in person?  I guess the closest I come are Carey Bell and
Muddy Waters' son, but those were at an outdoor festival, which feels
different than hearing the same music in a little bar.

\centerline{Mike Barno}

{\it ((Sure, I spent a LOT of time in blues bars in the 1980's.
Cleanhead Eddie Vinson was only one of many.
I saw some of the ``popular" blues guys like Robert Cray, but saw
and enjoyed Gatemouth Brown the most. 
Gatemouth was loads of fun and even when he was completely stoned
he was fun to talk to wandering through the crowd.
The big locals at the time were Duke Robillard, Ken Lyon, and
Roomful of Blues.
There also were lots of solo blues artists I used to see all the
time back then, but I can't even remember some of their names now.
They were local guys from the generation older than Duke Robillard
and his crowd.))}

\bigskip 

{\bf Rick Desper (Sunday, March 20, 2008 11:03:53 PM)}

Did these quickly the other day, and gave them a re-look today and only 
made one major change.  I had originally knocked Carolina out in the Elite Eight,
but on reflection, I'm giving them a pass to the Final Four.
{\it ((I really thought Tennessee would beat Louisville and then North Carolina,
but UNC might go ahead and just win it all, they would be my choice if UCLA 
falters.))}

A lot of my picks are according to seed, so I'll only mention digressions and
interesting games.

East:
Apparently 10 seed S. Alabama gets to play their sub-regional in Alabama.  
I'll give them a first-round upset over Butler, but Tennessee will be too much for
them.  They'll be joined in the Sweet Sixteen by Louisville, Notre Dame, and UNC.   
My initial pick was for Tennessee to make the championship game, but I've 
soured on them and now have Louisville in the upset.  
UNC going to the Final Four.
{\it ((I should have rethought this like you did, Butler had a good team.))}

Midwest:
I watched Clemson look dismal for most of the game against Maryland and then,
inexplicably, Maryland collapsed and let them come back from 20 points down.  
(Probably not a good idea to mention this around Andy Marshall.)  
So I have Villanova beating them in the first round, and then, for good measure, 
they take out Vanderbilt to make the Sweet Sixteen along with Kansas, Wisconsin 
and Georgetown.
I have a minor upset in the first round with K-State over USC, 
but that's just to set up a K-State/Wisconsin match-up for my brother.  
He got his Ph.D. from Wisconsin and works at K-State these days.
{\it ((Still, you  did nail that one, K-State didn't give Wisconsin
a real battle though.))}
In the regional final, the safe thing to do would be to take Kansas over 
Georgetown, but in close games I'll be a homer and take the 
Hoyas in a minor upset to make the Final Four.
{\it ((Just what I had predicted.... go Davidson...))}

South:
I'm really boring in this bracket.  I don't pick a single upset before the 
Regional Finals, where I take Texas over Memphis.  
My bias in favor of large conference play is playing a role here.
{\it ((You nearly nailed that precisely, except for Michigan State's 
upset of Pitt, who left it all on the floor of the BEast Championship game.
And of course Texas didn't even come close against Memphis.))}

West:
I take A\&M over BYU in the 8-9 game, but either team is fodder for UCLA.  
UConn will make it back to the Sweet Sixteen, and if they play 
at their best they can give UCLA a game, but that should be about it for them.  
On the other side of the bracket, 
I have West Virginia taking out Duke in the second round, only to lose to Xavier.  
{\it ((Good picks!!!))}
Picking Duke to lose early is one of my favorite habits, and oddly, 
it has worked out well for me in recent years.  
The safe thing would be to pick Duke to at least make the Sweet Sixteen.  
In any case, I think UCLA is much
better than any of the other teams in this regional, and they should cruise 
to the Final Four.

Final Four:
At this point, I'll notice that the games are being played in Texas, and not a
neutral site.  On a neutral site, I would have UCLA winning.  Since it's in 
Texas, I've got the Longhorns winning.  And I pick Georgetown over UNC 
in the other semi, going again with the conscious bias to pick 
Georgetown in what should be a close game.  Oh, and Texas wins the championship.

I'm a bit concerned that I'm going too far with Georgetown.  But they really 
are a good team as long as they keep Hibbert out of stupid foul trouble like they
had against Pitt in the Big East Championship.  And in a weird twist, they 
actually have shooters that can shoot from outside.

Of the teams I knock out before the Final Four, Kansas is the most dangerous,
and certainly could win it all.  I'm a bit down on the Tennessee teams (Memphis,
the Vols, and, FWIW, Vandy) since I think the SEC is weak this year and C-USA 
is weak every year.  I think Memphis {\it could} make the Final Four over Texas, but
don't really feel the same about Tennessee.

There are a lot of teams that {\it could} win it all.  
I think UCLA should be the biggest favorite, even though UNC is \#1, 
since UNC doesn't seem very deep to me.
Also, Roy Williams is notorious for losing games in the tourney that he 
shouldn't.  I don't think he's completely shaken that.

My other concern is that I'm too negative about Duke.
But I really don't see a complete team there.
Also, aside from UNC, there were not a lot of
very good teams in the ACC this season.
The deep conferences are the Big 12 and the Big East.
THe ACC is still basking in the glow from the '90's, but
it's just not that good right now.
Miami was their \#4 team: in the Big East, they would not
have been in the top 8.

Texas is {\it not} the best team in the country.
Heck, they're not even the best team in the Big 12.

\centerline{Rick, rick\_desper of yahoo.com}

{\it ((Yeah, boy we could have said almost the same 
things for most of this.  I thought those BEast teams
were going to do well, but I think (in the end) they
just beat each other up too much.  My
bracket was wiped out by Georgetown and Pitt.
I went for the ``Two's plus UCLA", Georgetown, Tennessee,
Texas and UCLA and had Pitt beating Memphis.
Now we COULD have all four \#1 seeds go to the finals,
which has NEVER happened.
I did especially poorly this season by missing Davidson,
even though I even watched a game or two from them this year,
just thinking Curry wouldn't be THAT good, and didn't get
ANY of the Sweet Sixteen upsets (very poor year for me on
that).  
I got Davidson for their first round upset, along with Siena,
Villanova, Arkansas, and Texas A\&M, but that's really a 
pretty pathetic record.
Go UCLA!!!))}

\bigskip 
 
{\bf Rick Desper (Mon, 24 Mar 2008 09:10:55 -0700 (PDT))}

Yeah, I was really quite upset with Georgetown since they had a classic choke 
against Davidson.  After proving they could run up a huge lead, they just stopped
playing either offense or defense.  Guys were standing around with confused 
looks on their faces.  
They didn't use their advantage in the low post and Hibbert repeatedly 
drew stupid fouls.  Hibbert is maddening because he does this all the time.

I can still win the PTKS pool if Texas wins it all, but since I had Georgetown 
going to the championship game I'm likely screwed.

\centerline{Rick, rick\_desper of yahoo.com}

{\it ((Wow, some people in the PTKS pool must have REALLY nailed some picks
since your picks look pretty good except for that Georgetown pick.))}

\bigskip

{\bf Drew James (Sat, 22 Mar 2008 08:59:28 -0400)}

Jim,

So glad that you are back and {\it TAP} is still going strong!  

My Orange are in the NIT.  A lot of folks in Orange Nation are upset that
Kentucky got in the NCAAs while we are back in the NIT for a second straight
year (the sun did come up Monday morning, but we were very concerned).  I
agree that Kentucky didn't deserve to make the field, but I don't think that
Syracuse deserved it either.  We are playing for next year when we will have
more than 7 available players.  Look for SU to be a top 10 team next year.
I see that PC has fired Welsh.

\centerline{Drew, kjames01 of twcny.rr.com}

{\it ((Hey, sorry you ended up losing to UMass AGAIN....
I thought Syracuse would kick some NIT butt.
My bro' David was QUITE upset about that loss and how it happened after 
Syracuse being up by 20 points.
Yes, PC did fire Tim Welsh, I was not in favor of this move, but 
understand how it goes.
I now worry that they aren't cranking it up and getting the coach
that they need, since if they were going to disrupt everything it 
seems to me that they should get someone good.
Welsh leaves them loaded in relative PC terms, PC should be solidly
in the middle of the BEast next year.
Watch Brown's coach Craig Robinson, and brother-in-law of Barack
Obama.
He is really hot, if he stays at Brown it won't be long before 
Brown nabs the Ivy's NCAA slot.
Many people here think PC should hire him....))}

\bigskip 

{\bf Warren Goesle (Tue, 25 Mar 2008 12:48:12 -0500)}

Hmmm, apparently it's THAT time of year again.  Time to get the ball
rolling slowly down the line and see whose 3rd baseman can come up with
it.
{\it ((The popular curse to be discussing is the one that reaches its
100th anniversary this year.
Which 3rd baseman would that be??))}

Hopefully the Red Sox fans out there that wanted to could catch the
game...er...today.  
{\it ((It was sorta fun to watch the game over breakfast and listen to it
driving in rather than driving home, like I usually do.))}
Those of us that cheer mostly for the Cubs will have
to wait until the 31st to get our opening day, and until around 2040 to
hoist a WS banner.  Nevertheless, here are the fearless predictions from
the almost-no-longer-snowed-in heartland...

American League:  It looks a lot more cut-and-dried here in terms of who
challenges for playoff spots this year.  I see 6 teams challenging for
the 4 spots:  EE1, EE2, EE3 and Detroit, Cleveland and Seattle.  Toronto
is one Scott Rolen injury away from being under .500.  The Twins, A's
and Rangers are rebuilding.  The White Sox are probably better than a
lot of people think, but that only gets them to .500.  Tampa Bay is
improved enough to get to 70 wins and challenge Baltimore for 4th in the
AL East, and Kansas City is still Kansas City.

West:  A quandary here.  The Angles are so beat up in the pitching staff
that even their money may not get them enough replacements and depth to
out-do the M's.  It's a lack of supply, not a lack of resources.  I'll
take Mariners, Angles, Rangers and A's.  Seattle gets to 89 wins.

Central:  A second quandary here.  Does Detroit have enough pitching to
go with their monstrous hitting?  I think that some of their young arms
come back from last year, but counting on Willis is not going to pan
out.  I'll go with Cleveland, Detroit, Chicago, Minnesota, and
what's-their-names.

East:  More monstrous hitting, more questions in the pitching.  Can the
Red Sox get enough healthy arms to last the season?  See Angles above.
Can the Yankees recover in their starting rotation?  More questions than
answers.  I'll take New York, Boston, Toronto, Baltimore, Tampa Bay.

WC:  It comes down to Detroit and Boston.  I'll pick the Red Sox,
although there will be an investigation led by former Sen. Mitchell into
whether there was a conspiracy by ESPN to let them win it.  No one will
report on the possible conflict-of-interest.

National League:  Considerably cloudier than the AL.  Any time I think
of the Mets a loud voice screams in my head: ``Paper Tiger!!!".  I think
the Twins knew something dealing Santana.  I want to believe in them,
but I've never seen Omar Minaya and Gregory Potemkin pictured together.
I think the Phillies are down, the Rockies won't roll 7's all September,
and the Brewers have no depth or money to get it.

West:  A 4-team battle, and maybe even 5 with the Giants no longer
carrying Bonds' posse on the payroll.  More pitching than hitting in
this division, so who does it best?  I'll go with Arizona, San Diego,
Los Angeles, Colorado and San Francisco.  The Rockies are only 10 out at
the end of the season in the most competitive division.

Central:  The Cubs are spending their way up to EE status.  Not that it
will be easy for them, or that they'll be a lot over .500, but I think
they get the division.  Call it Chicago, St. Louis, Milwaukee, Houston,
Cincinnati, and Pittsburgh.  Cubs go 88-74.

East:  By contrast, this division seems back to normal, or at least back
to looking like it did 10 years ago.  Atlanta, New York, Philadelphia,
Florida, Washington.

WC:  Somehow the Mets find a way to choke, this time with 2 games left,
and San Diego gets the Wild Card.

\smallskip 

Playoffs:

ALDS:  Indians over Red Sox; Yankees over Mariners.

ALCS:  Indians over Yankees.  Note that Cleveland fans would celebrate
this more than a revenge ALCS win against Boston.

NLDS:  Braves over Padres; Diamondbacks over Cubs.

NLCS:  Braves over Diamondbacks.

Politically Incorrect WS:  Indians over Braves.

Ok, take your best shots.

\centerline{Goz, wgoesle of comcast.net}

{\it ((I was going to comment through yours, but decided to keep it
separate so everyone can see......))

((American League East: I think the Yankees have the greater number
of questions and Tampa Bay really could finish third.  I'll predict
it Boston, New York, Toronto, Tampa Bay, and Baltimore, but remember
that Tampa Bay is my ``sleeper pick.
The Red Sox will be better because guys like J.~D.~Drew and Julio Lugo
are going to be much better offensively this year and Bartolo Colon
is going to be NEEDED and turn out to be a steal.
The Yankees will have a mess getting a bunch of old guys playing time
when they're all healthy and then have holes when their injuries 
coincide.))

((American League Central: Everyone always forgets the ``don't predict
this season off last season", each one is different.
That's going to be the Indians' problem this year, just as it was
Detroit's last year.
Detroit wins it this time going away, Chicago and Cleveland battle for
second, but with no Wild Card chances.
The Twins go straight to the bottom and the Royals, YES, the Royals, are
the surprise team.
Brian Bannister will be better and Gil Meche is good.
Greinke and Bale are better than most teams have in 3/4 slots.
And Mark Teahen and Billy Butler will hit more than everyone expected.
That's the ``out on the limb" prediction this year.
Detroit, Chicago, Cleveland, KC, Minnesota.))

((American League West: I don't see why people think Oakland is going to be
THAT bad, I think they will be better than everyone expects, my sleeper
pick for this division.
Of course, that won't get them in the playoffs either, just like KC,
but they won't fall out by the All Star Break.
Texas is the TRULY bad team here, Kason Gabbard who Boston jettisoned
will end up being their top starter after the other injuries, if he
isn't injured again himself.
Angels, Seattle, Oakland, Texas.))

((The wild card will be between Seattle and New York, possibly with Chicago
as a surprise, but won't matter, the Red Sox blow out everyone in the playoffs
to go back to the World Series.))

((National League East: Goz beat me to it.
I think Atlanta will win this easier than most others believe.
The predictions I see show the Mets, Braves and Phillies really,
really close.
This REALLY means that Atlanta runs away with it as the Mets and
Phillies are each deeply flawed, so they are my sleeper, if a team
with as much payroll and history as them can sleep through anything.
Flip a coin at the bottom.
Washington needs Shawn Hill to get healthy, but I think he will.
Atlanta, Philly, New York, Washington, Florida.))

((National League Central: There are just TOO many teams in this division,
how can Pittsburgh get over .500 when they have so many teams to compete
against???
They won't do it again this year.
The Cardinals are also a disaster, but won't be as bad as Pittsburgh.
Any of the other four COULD win it, especially given this division's 
history.
Sleeper to win it, Cincinnati, really!
Like Boston picked up Bartolo Colon, Cinci stole Josh Fogg, he'll be solid,
and they have Francisco Cordero for the bullpen.
I love Scott Hatteberg as a super sub and pinch hitter, and Griffey Junior
will have a great season, I'll bet.
I'm not alone in this one, but also Edwin Encarnacion is likely to break out.
Sorry, Goz, the Cubs can make the playoffs as the Wild Card, but they
won't take the division.
Don't they have a new Japanese player, if he turns into Ichiro, maybe.
But otherwise, they are short.
Cincinnati, Chicago, Milwaukee, Houston, St. Louis, Pittsburgh.))

((National League West: I like Barry Bonds.  Really.
Someone should pick him up and I think someone will.
And he will be a positive offensive force.
You all think I'm insane, I don't care.
I've said enough, always happy to recount the issues.
The rules are the rules, and you have to judge each
era on what was done.
Just as Steroids were once claimed to be irrelevant in baseball
(remember that??), they now are claimed to be the ONLY reason why
people succeeded or failed.  Both views are 100\% wrong, of course,
and you ALL know that if you really think about it.  
The ``one reason" issue that our human brains seem to triangulate
in on to answer any question remains the most fascinating human
behavior to me.
Anyway, the only prediction, sorry as I am to make it as Giants
fan, I am sure about is that the Giants will finish last.
OK, so who is my ``sleeper", I've seen some people predict the
Dodgers will win, so it's not that much of a sleeper, but Arizona and
Colorado were the big winners last year, so LA it is.
I am NOT a Dodger fan, and I'm not a Joe Torre fan, but he IS the
right manager for this team.
Flip a coin for the rest, LA, Colorado, Arizona, San Diego, and SF.))

((The West beats itself up and the Wild Card does not come from there.
I think it will be Chicago, but could be Philly.
Can the Cubs win it all?
Tempting, they will win their first round game against LA.
Atlanta will beat Cincinnati.
I know how Goz loves Cubs/Atlanta games.
Atlanta goes to the World Series and loses to the Red Sox.
Another sweep.))

((Lastly, I feel I need to say something about the other basketball
issue going on.
I finally made the leap from rabbit ears and no cable all the way to
Verizon FIOS, this is a switch I've heard that lots of us Luddites
have been doing.
This is being driven, if you live in a cave, that our new digital 
broadcast TV system was going to cause people like me problems.
We get lots of stations with fuzz and snow.
Fuzz and snow in the digital world would have been unwatchable.
Anyway, I like sports on the radio, which is why I like basketball,
hockey and baseball, but not football.
Football is pretty worthless on radio.
But I like watching the Celtics on TV and I couldn't before.
All of you probably are aware of the historic turn-around, soon
the Celtics will set the record as they win about 35 games 
more than they did a year ago.
You're aware of Kevin Garnett, Paul Pierce, and Ray Allen.
What you are likely not aware of is what a TEAM they have.
Celtics fans have been wondering for years why Rick Pitino
drafted Chauncey Billups and then gave up on him before he
became a top-five in the NBA point guard.
Rick convinced ME that he would be that at the time.
Ever since the Celtics have struggled at point guard.
But Rajon Rondo is the real thing, and eventually he is 
going to be better than Billups.
Maybe as soon as the playoffs this year.
The Celtics are amazingly fun to watch, even if you think
NBA basketball is boring.
You heard it here first if you're not from around here.))}

%
%\bigskip
%
%\centerline{\bf SPY DIPLOMACY (Variant, revised Dec. 1986)}
%
%by Jim Burgess
%
%Rules:
%
%1) Unless otherwise specified, the standard rules of Diplomacy apply.
%
%2) Players receive adjudications for their own armies and fleets, but not
%the armies and fleets of other powers.  Similarly, each player sees only
%his or her own section of the supply center chart.
%
%3) In addition to the standard units, an unit called a "spy" is added.
%
%     A) Each of the seven powers begins with a spy in each home supply center.
%
%     B) Spies are supplied only by home supply centers (i.e. Russia may have
%as many as four spies at a time while other powers are limited to a maximum
%of three).
%
%     C) Spies are "built" and "disbanded" in Winter seasons at the same time
%as other units.
%
%     D) There is no limit to the number of spies that may be present in any
%province and spies may be ``stacked" with armies or fleets (exceptions are
%listed in Rule 6).
%
%4) Spy Reports
%
%     A) Spies report the location and nationality of armies and fleets in
%the province they occupy and all adjacent provinces immediately following
%the standard Winter, Spring, Summer, and Fall seasons (i.e. just prior to
%the spy movement seasons).  Spies can differentiate between units in retreat
%and successful attackers when two units "occupy" a province.
%
%     B) Spies also report the nationality of spies in the province they occupy
%and the presence (but not nationality) of spies in adjacent provinces at the
%same time.
%
%5) Movement of Spies
%
%     A) Spy movement follows the collection of spy reports, so orders to spies
%may be made conditional on any information gathered by spies on opposing troop
%movements or the adjudication of one's own units.
%
%     B) Spies move after each of the following standard seasons: Winter,
%Spring, Summer, and Fall (note that all spy movements PRECEDE Autumn
%retreats), beginning with Winter 1900.
%
%     C) Spies move as armies do with the following exceptions:
%
%          a) Spy movements cannot be stood off by movements of any other unit.
%
%          b) Spies may be convoyed by fleets of any power during any of the
%four movement seasons for spies.  The convoy orders for fleets in these
%seasons must be ordered by their owner in the usual fashion or else the spy
%convoy movement fails of execution.  Fleet convoy orders for spies may be made
%in addition to regular Spring and Fall moves (note, however, that the fleets
%themselves never move during spy movement seasons).
%
%          c) Spies may also be "picked up" and carried by fleets of any
%power. Embarkation and debarkation are moves that must be made during a
%spy movement season and "permission to board" is not required.  Embarkation
%consists of a movement from a land province to an adjacent sea province
%containing a fleet.  Debarkation consists of a movement from a sea province
%containing a fleet to an adjacent land province.  A spy may not "switch
%fleets in midstream".  Once boarded, a spy may only get off by debarking.
%After boarding a fleet, the spy moves with the fleet during regular movement.
%A spy may not debark from a fleet awaiting retreat (e.g. if a fleet carrying
%a spy is dislodged in Spring, the spy may not debark until the spy movement
%season following the standard Summer retreat season).
%
%6) Spy Mortality
%
%     A) This rule will outline the circumstances under which spies may be
%captured or killed.  Spies may be disbanded in Winter seasons at the same
%time as other units to meet the requirement that a power may not have more
%spies than the number of currently held home supply centers and spies are
%annihilated when they are on board a fleet that retreats off the board.
%Otherwise, spies may only be removed from the board (there is no difference
%in the game between capturing and killing a spy, but players should feel
%free to delineate between the two states in writing press) immediately
%following the four spy movement seasons.
%
%     B) Spies killed or captured in a given season do not submit written
%spy reports for that season, though their final movement may have been
%made conditional on that spy report.  Players may never know for sure how
%a spy was lost, just as in real life.
%
%     C) Spies are "killed" by being assassinated by other spies.  When a
%spy moves, he or she may attempt an assassination, specifying the nationality
%of spies to be executed if discovered.  Each spy may hunt for only one
%nationality in each of the four seasons.  The following rules and examples
%will govern the adjudication of assassinations:
%
%          a) A spy may attempt an assassination without moving (for instance
%if the target is in the same province).  In this case, any spies of the target
%nationality that end the spy movement phase in that province are assassinated
%with one exception.  If the spy attempting the stationary assassination is
%himself or herself assassinated by a moving assassin then that spy
%assassinates no one in that season (not even a potential target other than the
%one that assassinates that spy).
%
%          b) A spy attempting a moving assassination (may include a move of
%embarkation or debarkation from a fleet) is always successful in assassinating
%spies of the target nationality that finish the spy movement phase in the
%province that the spy moves to.  This makes "mutual assassinations" possible.
%
%          c) Example: French spy is on board a French fleet in the Channel.
%An English spy is in London.  Both powers specify assassination attempts
%against the spies of the other.  If the English spy embarks on the French
%fleet in the channel (remember that embarkation does not require the
%permission of the fleet being boarded) and the French spy doesn't move, the
%French spy is killed, but the English spy isn't (he may be immediateIy
%captured, however, see part D).  If a German spy is also on board and the
%French spy tried to assassinate the German spy, that operation would fail
%as well. If the French spy debarks to London at the same time, the two spies
%"pass in the night" and neither is killed.
%
%     D) Spies are "captured" by opposing armies and fleets.  Players may
%attempt to capture spies, specifying the nationality of spies to be captured
%if discovered.  Each army and fleet on the board may search for spies of one
%nationality in each of the four seasons.  The following rules and examples
%will govern the adjudication of attempts to capture spies:
%
%          a) Players may specify a nationality to be hunted separately for
%each unit or they may issue blanket searches to be applied to all units.
%
%          b) At the end of the spy movement phase, any spies of the
%nationality specified in the same province are captured (for example, if
%the French player specifies a hunt for English spies on their Channel fleet
%in the above example, then the English spy is captured).
%
%          c) Players are informed when they successfully capture an opposing
%spy.  Note that the "owner" of the spy, however, is not informed of the
%capture.  Communication just is cut.  This rule is the only exception to the
%generaI rule that armies and fleets are blind.  It is possible to play the
%game without allowing capture of spies by armies and fleets if one wishes
%to allow freer movement of spies (i.e. RuIe D may be ignored).
%
%7) It is suggested that the game be adjudicated in four separate seasons
%in the following order:
%
%     A) Spring: (for Spring 1901 this sequence is preceded by a spy movement
%phase (no spy reports are necessary) followed by assassinations or captures)
%
%          a) Standard movement by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     B) Summer:
%
%          a) Standard retreats by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     C) Fall:
%
%          a) Standard movement by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     D) Winter:
%
%          a) Standard Autumn retreats by fleets and armies, adjudication
%reported only for one's own units
%
%          b) Standard Winter builds and removals, also applies to spies
%
%          c) Spy report phase, spies collect information
%
%          d) Spy movement phase, spies move according to Rule 4
%
%          e) Spy assassination and capture phase
%
%\medskip
%
%These rules have been produced by Jim Burgess (with helpful comments from
%Bernie Oaklyn and Dick Martin).  Permission is granted to reproduce and use
%these rules without restrictions.  The author would be interested to hear
%any comments and criticisms regarding any aspect of the play of this variant.
%The rules have been deposited with the North American Variant Bank.  They are
%also available from the author for the cost of postage or free by E-Mail.
%
%\bigskip
%
%\centerline{Wing Rules} 
%
%1.A wing unit can move over both land and water spaces. 
%  
%2.A wing unit can support actions in any space adjacent to the one it occupies. 
%   
%3.A wing can give, receive and cut support in the same way as armies and fleets. 
%   
%4.A wing unit cannot convoy or be convoyed. 
%
%5.A wing unit cannot capture an SC, but instead blockades it: 
%        
%\indent\indent 5.1.A blockade occurs when a wing unit occupies the SC of 
%another player in a fall season. 
%        
%\indent\indent 5.2.The player who owns a blockaded SC does not count 
%it when counting his total number of SCs. 
%        
%\indent\indent 5.3.A blockade ends as soon as the wing unit no longer occupies the SC. 
%        
%\indent\indent 5.4.Builds only take place in the winter phase, just as in games without wings. 


\vfill\eject

\centerline{\bf {\it THE ABYSSINIAN PRINCE} GAMES SECTION}

\smallskip

``So I called up George and he called up Jim, I said let's make a deal.

He said he'd talk to him.  Gonna start a church where you can save yourself,

You can make some noise, When you've got no choice...

You told me useful things, what people think of me, I guess I should thank you.

It's true, then I agree... I'm all alone, I've got no choice,

I'm all alone, I've got no choice."

From ``Got No Choice" by the incomparable Mark Cutler, from the CD
{\it Mark Cutler and Useful Things}.

\smallskip

\indent If you want to submit orders, press, or letters by E-Mail,
you can find me through the Internet system at
``burgess of world.std.com''.
If anyone has an interest in having an E-Mail address listed so people
can negotiate with you by computer, just let me know.

I am continuing to note cut or failed support orders with a 
small ``s'' instead of a capital ``S''.
This will make it easier on the E-Mailed version of the szine to see
what happened, since the italics don't show there.
The italics DO show on the web page just fine.

\indent Standby lists:

Mike Barno, Dick Martin, Brad Wilson, Jack McHugh, Glenn
Petroski, Steve Emmert, Mark Kinney, Vince Lutterbie, Eric Brosius,
Paul Rauterberg, Bob Osuch, Doug Kent, Sean O'Donnell, Vern Parker,
Heath Gardner, Paul Kenny, and Jeff O'Donnell
stand by for regular Diplomacy.
%I am willing to take over for NMR or start new-Diplomacy.
%Vern Parker
%337 Winter Hill Pl.
%Powell, OH 43065
%VSParker of aol.com
%614-402-5139

Let me know if you want on or off these lists, especially OFF.
Standbies get the szine for free and receive my personal thanks.

\bigskip

\centerline{GAME OPENING INFORMATION} 

\smallskip

We've got lots of openings in the subszines, check them out!!!
Contact Rip Gooch directly at xyropedes of canada.com and try to entice him to return.
Rip has been a bit missing in action lately, but I am assured that he
SHALL return.
Can we get back to these game openings below?  
We just need a few more people for a couple of these.

I am willing to open another new game of REGULAR Diplomacy if there is enough interest!!!
Doug Kent, Fred Wiedemeyer, %e,f,r,i,g,t,a
Brad Wilson, and Shaun Thompson start the list, who would like to join them???

Also, is there any interest in another game of Nuclear Yuppie Evil Empire 
7x7 Dip?
I know it may be getting tired, but I really like it.
We have Karl Schmit on the list, let's get seven!!
It's FREE!!!
I may drop this one shortly if we still have no interest.

I also am starting a game of the variant I designed, Spy Diplomacy.
Signups for that are now open.
Bruce Edwards and Eric Ozog are signed up.
The rules were published recently, ask to see them if you missed them!!!

And since Colonia is over, Harold Reynolds is looking to start something else.
Harold has been updating the Diplomacy A to Z, go check it out at:
http://www.badpets.net/Diplomacy/AtoZ/index.html 

Also, I am going to design some postal rules for Devil Take the Hindmost,
and we have an opening here:
Bruce Edwards, Mike Barno, and Eoghan Barry are signed up.
Postal rules from me will be forthcoming shortly, on my never ending to-do list.
I will get them in SOON!
I'm more likely to get these things started if I see some interest.....
I've GOT to do this now,
Eoghan is getting tired of waiting....

Right now, the other thing going is the Modern
Diplomacy game with Wings.
Sean O'Donnell, Jeff O'Donnell, Steve Koehler, Art Schleinkofer,
Bob Holt, Rick Desper, Alexander Woo, and Dave Partridge are signed up for that.
I will start it when I get a full complement of players, we only need TWO more!
Only two, just TWO more...... come on.
%Sean's list: Britain, Spain, Germany, France, Egypt, Turkey, Russia, Ukraine, Italy, and Poland.

\bigskip

\centerline{\bf TAKING OVER ISHKIBIBBLE'S REGULAR DIPLOMACY GAMES ((NOT))}

\smallskip

Last chance for anyone who was a subber to {\it Ishkibibble} to join any new
game for free, but this is a ONE TIME only offer, get your request in now.
It is going to expire VERY shortly.
Marc Ellinger and Fred Wiedemeyer already have taken us up on this request.
Come on, let me call by name who qualifies
for this deal..... Karl Schmit, John Power, Tim Snyder,
Dave Partridge, Graham Wilson, and Kevin Wilson.
I especially would like to fill the Modern Diplomacy game that Dave Partridge
already is in.
As soon as one more game fills (I'm not counting the new Breaking Away game), 
I'm going to pull this offer.

\bigskip

\centerline{\bf THE PHIL REYNOLDS MEMORIAL: 2006B, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SUMMER 1903 IS APRIL 19TH, 2008}

\smallskip

\noindent {\bf THE DUE DATE FOR FALL 1903 IS MAY 10TH, 2008}

\smallskip

\indent {\it Spring 1903}

\noindent AUSTRIA (Burgess): a vie-GAL, a TRI h, {\it f GRE-aeg}, 
{\it a BUL-con},
 
{\it a SER-gre}, f aeg-EAS. 

\noindent ENGLAND (James): {\it f ENG-bre}, f NAO S f mid, a BEL h, 
f MID h, f nth-NWY.
 
\noindent FRANCE (Williams): f mar-SPA(SC), {\it a BRE s a pic, 
f POR-mid}, 

{\it a PIC s GERMAN f hol-bel} (nso), a gas-BUR.

\noindent GERMANY (Ellinger): a kie-MUN, a BER S a kie-mun, 
f HOL h, a den-SWE.

\noindent ITALY (Crow): {\it a TYO-mun}, f WES S FRENCH f mar-spa(sc), 
a mun-SIL, 

a ven-PIE, f tyh-TUN.

\noindent RUSSIA (Gordon): NMR, MIKE BARNO CALLED AS STANDBY; f BLA h, 
a LVN h, 

a UKR h, f RUM h, a SEV h, f GOB h.

\noindent TURKEY (Wiedemeyer): {\it f CON-aeg},  
a ank-ARM, {\it a SMY-con}.

%\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Burgess):&TRI,VIE,BUD,ser,gre,bul&(has 5, bld 1)\cr
%\+ ENGLAND (James):&EDI,LVP,LON,nwy,bel&(has 5, even)\cr
%\+ FRANCE (Williams):&PAR,MAR,BRE,spa,por&(has 3 or 4, bld 2(r:otb) or 1)\cr
%\+ GERMANY (Ellinger):&KIE,BER,den,hol&(has 4, even)\cr
%\+ ITALY (Crow):&ROM,NAP,VEN,tun,mun&(has 5, even)\cr
%\+ RUSSIA (Gordon):&WAR,STP,SEV,MOS,swe,rum&(has 6, even)\cr
%\+ TURKEY (Wiedemeyer):&ANK,SMY,CON&(has 2, bld 1)\cr
%\+ Neutral:&none&(Total=34)\cr
%
\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: David Burgess, 101 Laurel Lane, Queensbury, NY  12804

(518) 761-6687, burgesscd of roadrunner.com or dburgess of glensfallshosp.org

\noindent ENGLAND: Drew James, 3644 Whispering Woods Terrace,
Baldwinsville, NY  13027

(315) 652-1956, kjames01 of twcny.rr.com 

\noindent FRANCE: Don Williams, 27505 Artine Drive, Saugus, CA 91350, 
(661) 297-3947, 

wllmsfmly of earthlink.net or dwilliams of fontana.org (\$5)

\noindent GERMANY: Marc Ellinger, 751 Turnberry Drive,
Jefferson City, MO 65109

ellingermc of aol.com

\noindent ITALY: John Crow, 824 Kinwest Parkway \#101,
Irving, TX  75063, 

(214) 532-1418, johnny.crow of hotmail.com

\noindent RUSSIA: New Player still Heath Gordon?, 741 E. John Street, Appleton, WI
54911, (757) 710-0808,

angrydogproductions of gmail.com

\noindent RUSSIA: Standby is Mike Barno, 634 Dawson Hill Road, 
Spencer, NY 14883, (607) 589-4906 

mpbarno of lightlink.com 

\noindent TURKEY: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  

CANADA  T6T 1N1, (780) 465-6432, wiedem of telus.net or wiedem of shaw.ca
%cell 780-497-8283; fax 780-468-6432

\bigskip

{\it Game Notes:}

1) The proposal for an RA two way draw fails, we play on.

2) Well, that didn't work so well.  As Jeff O'Donnell had to leave
and I had to pull in multiple standbys, I had this E-Mail from this
guy Heath Gordon who wanted to join, we exchanged a whole series of 
E-Mails, but then..... he's gone.
Back to the first name on my standby list, I'm calling on Mike.
Heath has until the SUMMER deadline to get me draft Fall orders
if he actually wants to do this, otherwise Mike Barno will take
over.
Mike at present is having a problem with his Lightlink E-Mail account,
but he expects to have it corrected by the Summer deadline, so he
should be good to go, and most of you know Mike, I think?
This also will make it a bit of a ``New York flavored game 
as three players will be from there.

3) As a ``very last minute note" I heard from Heath (no orders, just 
heard from him) that he is in Germany on vacation.
If you notify me about these things in advance we can do something
about them....
in any case, things still stand that Heath has to get draft Fall orders
to me by the Summer deadline, or I'll have to replace him.
Thanks for understanding, everyone.

\bigskip
 
{\it Press:}

(OLD ENGLAND to NEW RUSSIA): It is hard to work things out without
talking.  Let's get talking!

(LONDON to BERLIN): Is the Kaiser still on vacation in Florida?  I hope he
provided orders to the Imperial Army before leaving.  It doesn't look good,
leaving the country in the middle of a war for survival.

(BOOB to THE BRITS): We got the orders from the Kaiser just fine.... the
Czar, not so good.
See above.

(BOOB SPEAKS OUT ON CLASSIC PRESS): I know we're seeing some of this in the 
{\it Eternal Sunshine} subszine too.
I just want to say how much I'm enjoying this press and want to encourage
everyone in the szine (players and non-players) to get more press.
This is one of the things that distinguishes the ``postal'' game from
the pure E-Mail game (attempts to add ``postal'' press to E-Mail games
generally have failed).
What I seem to be seeing in these recent efforts (both here and in {\it ES})
are similarities to press we used to read in Steve Langley's {\it Magus}
and the various subszines therein. 
If we could get to that level again, which we probably won't, but I can hope,
it would be truly tremendous.
I've always felt this pathetic effort never had a hope of holding a candle
to {\it Magus}.
Lastly, as you read below, you will see why I added these few lines of filler.... 

\smallskip

({\bf Red Kings 6} (Dark Press –- not for attribution)):

\smallskip 

\centerline{Nun too sure of herself}

\smallskip 

She said it solemnly, with weight.  Like it meant something.  

``I thought Hierophant reversed was Tnahporeih,'' I said.

``You'se a moron,'' the blonde said.  She punctuated the remark with the tommy gun. 
I'm assuming it was meant to be an exclamation point.

``Toots, that is the first thing you've said that I understand.'' 
I took off my fedora and spun it onto the hat rack across the room 
and propped my feet up   It looked like we were gonna be awhile. 

``So, this case you're working.  Whatcha got,'' asked the blonde.

``The case I got is a case of indigestion,'' I answered, 
``and not the garden variety.  We're talking a real hobo stew here.  
Nothing adds up, and there seem to be a lot of players.''

``At least seven,'' nodded the blond.  Her full head of hair 
swayed like an ocean wave as her head moved on her curvaceous neck.

Seven. I'd just learned something else.  
At this rate I'd be a genius in twenty issues.  
The trick is not to remember something important in the brain cell 
that you're gonna drink away that night.

``I was at the Copa to try and shake something loose,'' 
I gave her my best half-smile, ``looks like it worked.''

She hadn't come up with clothes since Chapter 5 so I was 
able to admire the way the blush worked its way over her alabaster skin.

``I been working dat joint for weeks, since \#307.  
I din't come up with nothing…till you came along.  
And I ain't dat loose,'' said the naked woman who had let herself into my home…

``Hey, a guy can only hope; you were definitely working it. 
Which begs the point, which player are you?''

I picked up the pack of Red Kings, 
tapped out two and put them both in my mouth.  
I started to reach into my pocket for my matches, 
but she raised the barrel of the tommy gun and arched an eyebrow.

``Two fingers.''

``Good idea,'' I muttered around the butts, ``I'll take a shot myself.''

She smiled those pouty lips of hers and took the hint.  
She pulled the cork on the bottle of the Cheater's she'd brought, 
using her pearly whites and poured two stiffs; 
that brought the count up to three all told.  
All the while, she kept the tommy gun barrel unwaveringly pointed 
in my direction.  This kitten could multi-task.

I used two fingers to fish out my matches, 
lit the cigs and then traded her a fag for the boiler.

She raised the shotglass, ``Bottoms up.''  I could only hope.

``May your allies be true and your enemies be few,'' I toasted back.

``Not in this game,'' she said, and downed the whiskey.
  
``So I figure you don't work for Flat.''  
She had the moxie that Flat could use, but he wouldn't 
had her set me up while he thought I was working on his dime.

``No,'' she smiled, ``someone higher up.''

``Higher up?'' I glanced at the header of the page -– {\it Red Kings}, 
``you really ${\underline{\bf are}}$ the cigarette girl?''

``Damn, you're thick.''

``Only in the good places.'' 

``I'm a nun.''
 
I had nothing... I looked back at the proceeding line to see if it was a typo.

``A nun?''  See, my reputation for snappy repartee is well deserved.  
I surveyed the situation from the comfort of my chair; 
yep, a naked blonde with a machine gun had the drop on me 
in my own place, she was drinking and smoking... and yep, she was hot.

``A nun?''

``Yes, I really am a nun.''

``That's a bad habit.''

``Well,'' she parted her lips with her tongue, ``bad habits are hard to break.''
 
``Can you do that.'' I asked, waving my cigarette 
vaguely back and forth to indicate... well everything.

``Do what?'' she cocked her pretty head to one side cascading the 
lustrous blonde hair down over one bare breast.  
Now I wasn't sure how I felt about that.

``Uh, y'know... flirt, be naked... you know the whole nun with a gun thing.  
I thought you had rules.''

``I'm not dat kind of nun,'' she answered back.

``Nuns got kinds?''

``Yeah, I'm a sister of the Order Magister.  A church dat's as old as time, 
founded by the followers of Archbale All-Man.''

``So you don’t have those regular nun type rules...''

She shook her head slowly back and forth.  

``I've got a Murphy bed.''

``Nice segue, but we're not done.  What did you learn at the Copa?''

I gave her my best smart-ass comeback,

``That the Hobby doesn’t have a zoo.''

``Well, no... at least, not anymore.''

``Damn!''  I could practically hear the click as the 
lightbulb came on, even the little skittering noise 
the chain makes when you let it go too quick and it bounces around.

``What is it?''

``I'd bet you dollars to donuts it's a clue.''

``What’s a clue?''

``The zoo.  The zoo is a clue.''  It was beginning to sound 
like Dr. Seuss again, I couldn't help but think about gnus... in canoes.  
But those weren't clues.

``What in the Hobby makes you think that the zoo has anything to do 
with the Tarot, the Diplonomicon, ancient powers, demons or the Hierophant,'' 
she exclaimed, again punctuating with the tommy gun.  
I hoped that thing had a safety.

``It's the elephant,'' I answered.  She looked at me blankly.  
``Look, the elephant was mentioned in Chapter 4, ``A Shot in the Dark.''  
And the doorman said the Hobby didn't have a zoo.  
It was mentioned in Chapter 5, ``The Lady Ratta-tat-tatted Lace'' 
along with the otters.  Now here we are in Chapter 6, 
``Nun Too Sure of Herself'' 
(I knew I should have paid more attention to that title when I walked by it!) 
and it turns out that there was, or had been, a zoo in the Hobby.  
That's significant.   
You don’t think they put all this stuff in here as filler and drivel, do you?''

``Yes, I do,'' answered the blonde.

``I'm telling you, it's a clue.''

``People pay you for this?''

``Well, not many people...'' I had to admit, 
``you got something against deductive reasoning.''

``We're looking for the Hierophant, not the elephant,'' 
she exasperated, which is cool to watch on a naked woman, 
``they just sound alike.  
That's not deductive reasoning, it's... it's... palindromic reasoning.''

``Actually a palindrome is a word that is spelled the same 
frontwards and backwards... like moron.''

She looked at me quizzically.  
Whatever reply she had was drowned out by the pounding on the door.  
As you know, I know my knocks, and this wasn't Burgess looking for rent, 
or even a potential client.  
This was gun-butt on wood breaking the door in knocking... not my favorite.

She sprayed the door with a sleet of lead from her gat, 
which brought a unique silence to the situation.

``They're onto us,'' she said, ``you got a back way outta here?''

We moved to the window behind my desk.  
I grabbed my fedora and trench coat off the hat rack as I passed by.  
Pushing up the window I looked down into the alley behind the Abyssinian Prince.

``Damn,'' I cursed, ``Burgess hasn't fixed the fire escape.  Chintzy landlord.''

The naked nun cast a quick glance out the window, 
still keeping her primary attention on the currently quiet front door.

``We'll have to jump,'' she surmised.

``Babe, we're at the top of the page.  
If we jump from here we’re liable to break something.  
Something we might want to use later.'' I gave her my best wink and raised eyebrow, but it ricocheted off her worried glance at the front door.

``What are we gonna do?''

``Tell me a story...''

``What.  Now?''  She looked at me incredulously. 

``Now's the best time, seeing as how there might not be a later. 
Like why did you become a nun?''

``It runs in the family...''

``Your mom was a nun,'' I asked.

``Actually, yes.''

``Your dad was a nun?''

Her response wasn't verbal.

``I'm liking your rules more and more,'' Nuns have kinds, whoda thunk it?  

``My family has been in the Order forever.  
We've been seeking the Diplonomicon longer than I've been alive.''

I was half paying attention to her, keeping one eye on the front door.  
Thought I heard some movement out there.  I was counting on my fingers.

``What are you counting?''

``Lines.  We're getting lower.  I figure a few more lines and we can jump.''

``Can't you just change the font size?''

I chuckled.  Amateurs.  I've been around the block.

``It doesn't work that way,'' I replied, 
``ya never know how the publisher's gonna handle it.  
You change the font size and he could change it back when he prints, 
go all Pica on ya'... then splat, you're pizza pie on the patio.  
Here, you're gonna need this.''  
I gave her the trench coat to put on, 
apparently we'd formed some sort of ad hoc alliance, 
as her heater was pointed more at the door than at me.

``So I guess we haven't been properly introduced,'' I said, ``what's your name?''

``Charlene St. Allman.  My friends call me Charly,'' she smiled, ``what's yours?''

Suddenly the front door splintered in on its hinges, 
and three plug uglies piled into the office throwing 
lead like molten mosquitoes in a summer swamp.

``Jump,'' I yelled, and grabbed Charly as I plunged through the window.  
She was a trooper rattling off return fire from the tommy as we went out and down.  
I hit the ground and tried my best to cushion her fall by banging 
my head on the asphalt, and bruising my elbows against the dumpster.  
She was all pillowy softness on top of me... under other circumstances...

I gasped for breath, ``keep talking.''

``What... why,'' we could see the gunsels charging the open window.  
She was trying to untangle the gat and bring it up.  
I grabbed her head in my hands and brought her lips to mine.  
At first she tried to pull away, then she felt the passion and plunged into it with fervor.  After a few moments we broke apart.

``Look,'' she said, ``they're back at the top of the page.''

``Yep, it's all about getting to the next page. Let's vamoose.''
	
So it was me and the nun with the gun on the run.  I couldn't wait for Chapter 7.


\bigskip

\centerline{\bf SPIRALS OF PARANOIA: 2005A, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SUMMER 1907 IS APRIL 19TH, 2008}

\smallskip

\noindent {\bf THE DUE DATE FOR FALL 1907 IS MAY 10TH, 2008}

\smallskip

\indent {\it Spring 1907}

\noindent AUSTRIA (Rauterberg): {\it a ser-bul} (d r:gre,alb,otb), 
a nap-ROM, 

{\it f GOL s TURKISH f wes-spa(sc)}.

\noindent ENGLAND (Wiedemeyer): f POR S TURKISH f wes-spa(sc).

\noindent FRANCE (Tretick): a par-BRE, f bre-MID, 
a GAS S GERMAN f mid-spa(sc), 

{\it f MAR-gol}, f ENG S f bre-mid, {\it a BUR-mar}, 
f IRI S f bre-mid.
 
\noindent GERMANY (Ozog for Tallman): a boh-TYO, a gal-BUD, 
a VIE S a gal-bud, a ruh-MUN, 

a tyo-VEN, f SKA h, a TUS S a tyo-ven, a pic-BEL, 

{\it f mid-spa(sc)} (d r:nao,otb).

\noindent ITALY (Kent): {\it a ven h} (d r:apu,pie,otb), 
a bud-SER, a TRI S a bud-ser.

\noindent RUSSIA (Sundstrom): {\it f SEV-bla, a UKR-rum, a RUM-bul, 
a ARM-smy, a MOS-sev}.

\noindent TURKEY (Biehl): {\it a ANK-arm}, f SMY h, 
{\it f BLA-bul(ec)}, f tun-NAF, 

f TYH S AUSTRIAN a nap-rom, {\it f WES-spa(sc)}.
                                                                                
%\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Rauterberg):&ser,nap,rom&(has 4, rem 1)\cr
%\+ ENGLAND (Wiedemeyer):&por&(has 1, even)\cr
%\+ FRANCE (Tretick):&PAR,BRE,MAR,spa,lvp,edi,lon&(has 6, bld 1)\cr
%\+ GERMANY (Ozog/Tallman):&KIE,BER,MUN,hol,den,bel,swe,&(has 9, even)\cr
%\+ &\enskip nwy,vie \cr
%\+ ITALY (O'Donnell):&VEN,tri,bud&(has 2, bld 1)\cr
%\+ RUSSIA (Sundstrom):&WAR,STP,SEV,MOS,rum&(has 4, bld 1)\cr
%\+ TURKEY (Biehl):&ANK,SMY,CON,gre,tun,bul&(has 6, even)\cr
%\+ Neutral:&none&(Total=34)\cr
%
\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Paul Rauterberg, 3116 W.~American Dr., 
Greenfield, WI  53221, 

(414) 281-2339 (E-Mail)  trauterberg of wi.rr.com

\noindent ENGLAND: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  CANADA  T6T 1N1, 

(780) 465-6432, wiedem of telus.net or wiedem of shaw.ca 
%cell 780-497-8283; fax 780-468-6432

\noindent FRANCE: Buddy Tretick, 5023 Sewell's Pointe Way,
Fredericksburg, VA  22407, (540) 898-3386

cell (540) 226-5571 (E-Mail) berniebuddy33 of aol.com

\noindent GERMANY: Terry Tallman, PO Box 782, Clinton, WA  98236,
(360) 331-5698 (\$2) 

terryt of whidbey.net

\noindent GERMANY: Temporary Standby is Eric Ozog, PO Box 1138, Granite Falls, WA  
98252-1138,

(360) 691-4264, ElfEric of Juno.com

\noindent ITALY: Doug Kent, 11111 Woodmeadow Pkwy \#2327, Dallas, TX  75228

dougray30 of yahoo.com 

\noindent RUSSIA: Matt Sundstrom, 1760 Robincrest Lane South, Glenview, IL  60025, 
(847) 729-1882, 

Matt.Sundstrom of bbdoch.com or mattandzoe of earthlink.net

\noindent TURKEY: John Biehl, \#8 -- 11530 84th Avenue, Delta, BRITISH COLUMBIA,
V4C 2M1  CANADA, 

(604) 816-0460 (cell) (\$7); jrb of dccnet.com

\bigskip

{\it Game Notes:}

1) Terry is still having some medical problems, 
Eric Ozog is continuing to
negotiate and submit orders for Terry.
Eric originally brought Terry into the Diplomacy hobby all those many
years ago, and so I'm glad he's agreed to do this.

2) So, we had I) GIRF draw, II) GT draw, III) FAIRT draw, IV) Recalling 
Terry Tallman to play Germany.
All were rejected.
New proposals are as follows.
We have I) Concession to Turkey; II) AEIT draw; and III) Expulsion of 
Ozog/Replacement player for Ger (Reason: Tallman is ambulatory and should 
have resumed play much earlier).
Please vote on each of these proposals with the Summer orders, 
failure to vote vetoes them all.

3) Note the slight adjustment in Bernie/Buddy's E-Mail address.

\bigskip
 
{\it Press:}

(ITALY -- TURKEY): Eric tells me you have a tendency to
get really cranky in this game.  I am waiting to see
how true that might be.

(CONSTANTINOPLE APR 1, 1907): Sultan Hatas I announced the 
cancellation of the projected Berlin -- Constantinople Railway. ``We 
cannot, alas, support this German scheme. We Ottomans must defend our 
realm unlike the cowardly Germans who scourge all weak nations yet have 
not the courage to oppose the strong."

(BERLIN): The Kaiser Interim scoffs at the proposal to bring the Kaiser
Emeritus back.
It is merely whining on the part of Austrians and Turks who desire for
the previous alliance structure which was more favorable to themselves
before I took over the reins of der Fatherland.
Heil Germany!

(BOOB RETORTS): Shouldn't that be der ToadFatherland?

(ITALY -- WORLD): If you don't care about this game, how
can you expect anybody else to?

(BUDDY): Welcome to Doug Kent as the replacement Italian Player.  
Long live R-G-F-I victory.

(ITALY -- GM): Make sure you and all who read this visit
http://www.helpfulkitty.com for the latest in Toby the
Helpful Kitty news, photos, and merchandise!

(BOOB to ITALY): Hey, why should I help you, I lose enough
money on this hobby too, why don't you let me share.
Oh, then I would have to run ads too.... never mind.

\bigskip

\centerline{\bf FLIP FLOP: 2003G, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SUMMER 1910 IS APRIL 19TH, 2008}

\smallskip

\noindent {\bf THE DUE DATE FOR FALL 1910 IS MAY 10TH, 2008}

\smallskip

\indent {\it Spring 1910}

\noindent AUSTRIA (Wiedemeyer): {\it a BUD-tri, a GAL-rum,  
a MOS-sev}, a VIE S a bud-tri.

\noindent ENGLAND (Kent): a den-SWE, a ruh-MUN, f nth-ENG, 
f nwg-BAR, f hel-NTH.

\noindent FRANCE (McHugh): f BRE S f eng-mid, f MAR S a spa,
a hol-RUH, a bel-BUR, 

f eng-MID, a SPA S f mar.

\noindent GERMANY (Sundstrom): f ber-BAL, a kie-BER, 
f swe-GOB,

a nwy-STP, a mun-BOH, f ska-DEN.

\noindent TURKEY (Levinson): {\it a CON-sev}, a smy-APU, 
f AEG C a smy-apu, a sev-UKR, 

{\it f WES-mid}, a BUL S a rum, f ven-ADR, f GOL h, a TRI h, 
f ION C a smy-apu, 

f BLA C a con-sev, {\it a RUM s a sev-ukr}, a SER S a tri.

%\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Wiedemeyer):&VIE,BUD,mos,war&(has 5, rem 1)\cr 
%\+ ENGLAND (Schmit):&EDI,LVP,LON,por,den&(has 5, even)\cr
%\+ FRANCE (Jeff O'Donnell):&PAR,MAR,BRE,spa,bel,hol&(has 4, bld 2)\cr
%\+ GERMANY (Sundstrom):&KIE,BER,MUN,swe,stp,nwy&(has 6, even)\cr
%\+ TURKEY (Levinson):&ANK,SMY,CON,bul,sev,ser,gre,&(has 11, bld 2)\cr
%\+ &\enskip tun,rom,rum,nap,ven,tri \cr
%\+ Neutral:&none&(Total=34)\cr
%
\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  CANADA  T6T 1N1, 

(780) 465-6432, wiedem of telus.net or wiedem of shaw.ca
%cell 780-497-8283; fax 780-468-6432

\noindent ENGLAND: Doug Kent, 11111 Woodmeadow Pkwy \#2327, Dallas, TX  75228

dougray30 of yahoo.com 

\noindent FRANCE: Jack McHugh, 810 School Lane, Folcroft, PA  19032,
(856) 456-5984,

jwmchughjr of gmail.com

\noindent GERMANY: Matt Sundstrom, 1760 Robincrest Lane South, Glenview, IL  60025, 
(847) 729-1882, 

Matt.Sundstrom of bbdoch.com or mattandzoe of earthlink.net

\noindent ITALY: Don Williams, 27505 Artine Drive, Saugus, CA 91350, 
(661) 297-3947, 

wllmsfmly of earthlink.net or dwilliams of fontana.org

\noindent RUSSIA: Sean O'Donnell, 1044 Wellfleet Drive, Grafton, OH  44044,
(440) 926-0230, 

sean\_o\_donnell of hotmail.com

\noindent TURKEY: Alexandre Levinson, Beeklaan 504, 2562BP Den Haag
THE NETHERLANDS, don't need phone, 

levinson7 of hotmail.com (\$5)

\bigskip

{\it Game Notes:}

1) The proposal for a concession to Turkey fails.

\bigskip

{\it Press:}

(JIM-BOOB to THE PLAYERS): How about if we start some cool press writing in this game?

\bigskip

\centerline{\bf I CAN'T FIND MY MONEY!: 2001F, Regular Diplomacy}

\smallskip

\noindent {\bf TWO WAY DRAW BETWEEN AUSTRIA AND GERMANY WAS DECLARED!}
\settabs 20 \columns

\medskip

G.M.: Jim Burgess

Date Started: November 2001

Date Completed: December 2006

Thanks to Boardman Number Custodian Tom Howell for compiling the statistics.
I think we can read this down below and I think I transcribed everything 
correctly.
Tom sent me it in UNIX format, finally I figured that out.
This is done unless we have any
last End-Game statements after seeing the SC Chart.

\smallskip

The Players:

\+ AUSTRIA:&&&Chris Lockheardt (res S07);&&&&&&Vern Parker (2-way Draw)  \cr
\+ ENGLAND:&&&Allan Heikkinen (drop F05);&&&&&&Mark Kinney (elim F11)    \cr
\+ FRANCE: &&&Adam Mitchell (drop S03);  &&&&&&Douglas Kent (surv)       \cr
\+ GERMANY:&&&Jim Sayers (res S05);      &&&&&&Kevin Wilson (2-way Draw) \cr
\+ ITALY:  &&&Dan Mehkeri (drop S05);    &&&&&&Heath Gardner (drop F09);  
&&&&&&Mike Barno (elim F10)  \cr
\+ RUSSIA: &&&CW Phillips (drop F01);    &&&&&&Rick Desper (elim F08)    \cr
\+ TURKEY: &&&Tim Miller (surv)                                          \cr

\medskip

\noindent SUPPLY CENTERS:

\smallskip

\+          &&&01 &02 &03 &04 &05 &06 &07 &08 &09 &10 &11 &12 &13  \cr
\+ AUSTRIA: &&&~5 &~8 &~7 &~8 &~8 &~8 &10 &10 &13 &14 &14 &15 &16  \cr
\+ ENGLAND: &&&~5 &~4 &~4 &*5 &~4 &~4 &~3 &~3 &~3 &~1 &~0          \cr
\+ FRANCE:  &&&~5 &~6 &~6 &~4 &~5 &~5 &~5 &~5 &~5 &~6 &~6 &~5 &~2  \cr 
\+ GERMANY: &&&~4 &~4 &~4 &*5 &*7 &~7 &~7 &~8 &~8 &10 &11 &12 &*15 \cr
\+ ITALY:   &&&~5 &~5 &~5 &~5 &~4 &~4 &~4 &~4 &~2 &~0              \cr 
\+ RUSSIA:  &&&~4 &~3 &~4 &~3 &~1 &~1 &~1 &~0                      \cr 
\+ TURKEY:  &&&~4 &~4 &~4 &~4 &~5 &~5 &~4 &~4 &~3 &~3 &~3 &~2 &~1  \cr

* $=$ Plays one short

\smallskip

{\bf NOTE:}
 Allan Heikkinen may have been a nom de guerre of Jim Sayers.

\settabs 3 \columns
\bigskip

\centerline{\bf SECRETS: 1999D, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SUMMER 1924 IS APRIL 19TH, 2008}

\smallskip

\noindent {\bf THE DUE DATE FOR FALL 1924 IS MAY 10TH, 2008}

\smallskip

\indent {\it Spring 1924}

\noindent ENGLAND (Kent): {\it a GAS s FRENCH f mar} (otm),  
{\it f MID s FRENCH f spa(sc)} (otm), 

{\it f POR s FRENCH f spa(sc)} (otm).

\noindent FRANCE (Sasseville): {\it f mar-gol} (d r:spa(sc),otb), 
f spa(sc)-WES, a bur-PAR.  
%standing orders, yes to ANY draw
                                             
\noindent GERMANY (Barno): a BUL h.
%votes yes to FREGT, no to EFRT 
%vote YES to FREGT draw

\noindent RUSSIA (Parker): NMR, BOB OSUCH CALLED AS STANDBY; 
f NWG h, a NWY h, f EDI h, 

f LVP h, a WAR h, a DEN h, a KIE h, f NTH h, a HOL h, a BER h.

\noindent TURKEY (Linsey): f con-AEG, a sev-RUM, a rum-GAL, 
f TYH S f wes-gol, a ser-GRE, 

a mun-BUR, a SIL S a boh-mun, f wes-GOL, a boh-MUN, f gol-MAR, 
a bel-PIC, a TYO S a boh-mun,
 
f NAF S FRENCH f spa(sc)-wes, a ven-TUS, f PIE S f gol-mar, 
a ruh-BEL.

%\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ ENGLAND (Kent):&LON,bre,por&(has 5, rem 2)\cr
%\+ FRANCE (Sasseville):&PAR,MAR,spa&(has 3, even)\cr
%\+ GERMANY (Barno):&bul&(has 1, even)\cr
%\+ RUSSIA (Parker):&MOS,STP,nwy,swe,den,ber,WAR,&(has 10, bld 1)\cr
%\+ &\enskip kie,edi,hol,lvp   \cr
%\+ TURKEY (Linsey):&CON,ANK,SMY,rum,gre,ser,bud,&(has 15, bld 1)\cr
%\+ &\enskip nap,ven,tun,sev,rom,tri,vie,mun,bel \cr
%\+ Neutral:&none&(Total=34)\cr
%
\bigskip

\indent {\it Addresses of the Participants}

\noindent ENGLAND: Doug Kent, 11111 Woodmeadow Pkwy \#2327, Dallas, TX  75228

dougray30 of yahoo.com 

\noindent FRANCE: Roland Sasseville, Jr., 38 Bucklin Street, Pawtucket,
RI 02861, (401) 481-4280 (\$0)

roland6 of cox.net  

\noindent GERMANY: Mike Barno, 634 Dawson Hill Road, 
Spencer, NY 14883, (607) 589-4906 

mpbarno of lightlink.com 

\noindent RUSSIA: Vern Parker, 337 Winter Hill Place, Powell, OH 43065,
(614) 402-5139

VernDip of aol.com is preferred

\noindent RUSSIA: Standby is Bob Osuch, 19137 Midland Avenue, Mokena, IL
60448, (708) 478-3885

ROsuch4082 of aol.com 

\noindent TURKEY: Bruce Linsey, PO Box 234, Kinderhook, NY
12106

GonzoHQ of aol.com

\bigskip

{\it Game Notes:}

1) There are no current proposals.

2) Vern Parker has NMRed, so I'm calling Bob Osuch as a standby.  
Bob hasn't played Diplomacy in a bit, and he reports he's been
playing Computer games lately, but he also says he recently was
perusing old {\it Voice of Doom}'s, so calling him to this position
(which I didn't know before asking him) seems appropriate.
Vern has to get me draft Fall orders by the Summer deadline to
retain the position, if he doesn't then Bob takes over and 
you'll all know that when you submit Fall orders.  As a warning
to everyone, Bruce Linsey is on vacation traveling much of this
month and will not have access to E-Mail, I don't believe, but
he will be back before Fall orders are due.

\bigskip

{\it Press:}
 
(JIM-BOOB to THE PLAYERS HERE TOO): It would be cool as this heads to
the end if someone thought about writing some press.
Think about it....

\bigskip

\centerline{\bf CAST NO SHADOWS: Breaking Away, Designer's Rules}

\smallskip

\noindent Rules at:
http://devel.diplom.org/DipPouch/Postal/Zines/TAP/Tinamou/rules/BreakingAway.htm

\smallskip

\noindent {\bf DUE DATE FOR TURN 6 IS APRIL 19TH, 2008}

\smallskip

%--F--I--N--A--L-- --F--I--N--I--S--H-- --L--I--N--E--
%--S--P--R--I--N--T-- --F--I--N--I--S--H-- --L--I--N--E--
%
\centerline{\it Turn 5}

\smallskip 

\+ 41 (replenish with a 6) &Agnus (BREAKING AWAY!!!)  \cr
--S--P--R--I--N--T-- --F--I--N--I--S--H-- --L--I--N--E--
\+ 40 (no replenishment)   &Empty  \cr
\+ 39 (no replenishment)   &Empty  \cr
\+ 38 (no replenishment)   &Empty  \cr
\+ 37 (no replenishment)   &Empty  \cr
\+ 36 (no replenishment)   &Empty  \cr
\+ 35 (replenish with a 3) &Bowie, Travis, Crockett  \cr
\+ 34 (no replenishment)   &Empty  \cr
\+ 33 (replenish with a 3) &Death  \cr
\+ 32 (no replenishment)   &Empty  \cr
\+ 31 (replenish with a 3) &Vidic, Krstajic  \cr
\+ 30 (replenish with a 5) &Kyoto, Yorick  \cr
\+ 29 (replenish with a 7) &Zorro  \cr
\+ 28 (replenish with a 8) &Xavier, Wally, \cr
\+ 27 (no replenishment)   &Empty  \cr
\+ 26 (replenish with a 3) &Gavrancic \cr
\+ 25 (replenish with a 4) &Water, Dragutinovic, Sanctus, Kyrie  \cr
\+ 24 (replenish with a 8) &Rincewind, Gloria  \cr
\+ 23 (replenish with a 10)&Mideast \cr
\+ 22 (replenish with a 11)&Granny, Carrot, Drugs, Bonham   \cr

\bigskip
%Sprint Points at 40, 80: 10,8,6,5,4,3,2,1 (final are just double these)
%Movement Order: A/B/C/D; highest card played that turn; highest card in hand

\indent {\it Addresses of the Participants -- Their Team and Their Cards}

\smallskip

\noindent TEAM 1 (Rick Desper): rick\_desper of yahoo.com (0 points)

Team Name: The Turtle Moves; Captained by Cut-My-Own-Throat Dibbler

\+ A: Rincewind the Wizzard &&14 16 4 8 (12) \cr
\+ B: Granny Weatherwax     &&12 11 11 (3) \cr
\+ C: Captain Carrot        &&15 5 11 (11) \cr
\+ D: Death                 &&13 3 3 (20) \cr

\noindent (Rincewind with the Luggage, Granny on Her Broom, 
Carrot of the City Watch, and Death is just DEATH!)

Total Replenishments: $12+58+18+15+33 = 136$
                
\smallskip

\noindent TEAM 2 (Tom Howell): off-the-shelf of olympus.net (0 points)

Team Name: Never Ending Worry Source; Manager: Rumour; Team Captain: Ye Olde Manager

\+ A: Water    &&15 16 5 4 (7) \cr
\+ B: Kyoto    &&14 17 5 (13) \cr
\+ C: Mideast  &&11 17 10 (6) \cr
\+ D: Drugs    &&11 13 11 (3) \cr

Total Replenishments: $12+35+37+44+30 = 158$        
   
\smallskip

\noindent TEAM 3 ((David Partridge): rebhuhn of rocketmail.com (0 points)
%360-928-9698

Team Name: Famous Four  

\+ A: Krstajic      &&15 16 7 3 (13) \cr
\+ B: Vidic         &&13 7 3 (13) \cr
\+ C: Gavrancic     &&9 7 3 (8) \cr
\+ D: Dragutinovic  &&8 11 4 (7) \cr

Total Replenishments: $12+35+40+28+13 = 128$   
               
\smallskip

\noindent TEAM 4 (Brendan Whyte): obiwonfive of hotmail.com (0 points)

Team Name: The Reverse Alphabeticists

\+ A: Zorro    && 15 3 7 7 (11) \cr
\+ B: Yorick  && 10 7 5 (12) \cr
\+ C: Xavier   && 7 7 8 (10) \cr
\+ D: Wally    && 3 7 8 (10) \cr

Total Replenishments: $12+26+24+28+28 = 118$

\smallskip

\noindent TEAM 5 (Alexander Woo): aswoo of yahoo.com (10 points) %awoo@math.ucdavis.edu

Team Name: Just Ordinary; Manager: Credo

\+ A: Agnus     && 12 7 4 6 (20) \cr
\+ B: Sanctus   && 8 4 4 (3)   \cr
\+ C: Kyrie     && 10 7 4 (7)    \cr  
\+ D: Gloria    && 16 3 8 (5)    \cr
 
Total Replenishments: $12+44+22+17+22 = 127$ 

\smallskip 

\noindent TEAM 6 (Andy York): wandrew88 of gmail.com (0 points)

Team Name: Alamo

\+ A: Crockett      && 15 5 3 3 (19) \cr
\+ B: Travis        && 15 3 3 (19)\cr
\+ C: Bowie         && 10 3 3 (19) \cr
\+ D: Bonham        && 3 3 11 (3) \cr

Total Replenishments: $12+12+12+60+20 = 116$

\bigskip

{\it Game Notes:}

1) The rules are on the {\it TAP} website in the {\it Tinamou} section.
Ask if you have any questions.
Up above in parentheses is the card you played to get to where you are
in the field.  The replenishment card is the last card in your list.
Be careful to note that the card you played (the one in parentheses) is
not available for you, for next turn.
Just for fun, I'm going to keep track of total replenishment, by turn, which is a 
rough measure of how the teams are doing.
Of course, it is lining up to get across the sprint and final lines in the
right places that really counts.
We can calculate an ``efficiency score" later, which will be the ratio
of scoring points per replenishment.
If I'm predicting how the future of this will come out, a 10\% score will
be really tremendous for this measure.

2) Note that Andy York's E-Mail address has been updated.

3) Alex Woo picks up the first points by winning the first Sprint!!!
Looks like the Three Alamos could follow close behind.... 
but they are trailed by Death....
(hey, I thought it was funny!!!!)

4) Dave replaces Rick as the ``low man on the replenishment totem pole".
I carved out some of your comments into press to keep the masses amused....
I'm sure you don't mind.

\bigskip

{\it Press:}

(CUT-MY-OWN-THROAT DIBBLER ROLLS): Let's see if I roll snake eyes three times in a row.

(BOOB to DIBBLER): Dave betters your feat for one round, at least.

(THE FAMOUS FOUR DRAFT): Hope being that I either land near the front to score some 
points this time, or Tom lines up his guys on 32-35 and I draft them.

(BOOB DABBLES): That would be no, and no....

(THE TURTLE GUESSES SOME MORE): I expect {\it some} riders to break 
for the sprint finish line.  
But the more experienced players like Dave and Tom may hang back.  
In any case, I have no hope for the first sprint, so I'll assume there 
will be a mob in the low 20s.  And hope that somebody is on 23.

(BOOB DING-DONG DANGLES): Ding, ding, ding, you hit the jackpot, choosing
correctly that Tom would play Mideast low.

(GRANNY): Waves from her broom as she slows down, she hopes somebody tucks in between 
her and Rincewind at 23.

(CAPTAIN CARROT OF THE CITY WATCH) Speeds up to have a chat with Granny, whom 
he hasn't seen in a while.

(DEATH): Notices that somebody's hourglass is running low on sand, so he dashes forward.

(BOOB CONCLUDES): The Alamos had better watch out, their time is nearly up!

\bigskip

{\it Personal Note to You:}

\vfill\eject
\end
