\nopagenumbers 
\font\twelverm=cmbx12 at 12pt
\centerline{\bf\twelverm THE ABYSSINIAN PRINCE \#308}
\line{\hfil December 15, 2006}    
\smallskip                                                    
\settabs 3 \columns 
\beginsection

\medskip

Produced by Jim Burgess, 664 Smith Street, Providence, RI 02908-4327  USA,
(401)351-0287 
 
\noindent Accessible through Internet at burgess of world.std.com (all E-Mail
addresses are reported in this format, replace the `` of '' with ``@''; if you 
bounce try sending to me from another account. 
Some of you have been getting bounced messages from
my ISP's spam protection, if that happens to you, USE my backup E-Mail
at jfburgess of gmail.com!!!  Don't complain that my E-Mail keeps bouncing
without forwarding the bounced message to that address.
Then I can forward it to the ISP help to get it dealt with.
 
\noindent Web Page Address: /Postal/Zines/TAP/index.html

\bigskip

I expect ALL players to be signed up on the E-Mail notification list for the szine,
see below.
Some of you have been complaining about this, but it is up to you to get on this list,
it's easy, come ask me if you have trouble.
We have yet more exciting issues of {\it By the Way}, {\it Houdini Blues}, {\it Tinamou} 
in this issue.
We're making progress on starting new games, help fill things up, see below for more.
BREAKING AWAY starts in this issue, send me your cards!!!
Since I was late, let's go straight into the Christmas break.
Have a Merry Christmas and a Happy New Year!!

\bigskip

%Dave Partridge's unlisted phone number 603-672-2879 -- probably corrected!!!
%Tinamou players: Schwarzschild:  Graham Wilson (NO 
%but E-mails: grahamaw of home.com (or gwilson of dvnet.com)),
%Berry Renken, Phil Reynolds, Heath Gardner
%Copernicus:  Warren Goesle, Heath Gardner, Art Schleinkofer, Bruce Reiff,
%Eric Brosius, Bob Dowrey
%Tour De Farce:  Jim Burgess, Eric Brosius, Warren Goesle, Sara Reichert,
%Phil Reynolds, Rick Desper
%Milk and Cookies: Jim Burgess, Warren Goesle, Sara Reichert, Phil Reynolds,
%Rick Desper, Richard Weiss, John Schultz
%Who's Your Buddy:  Sara Reichert, Phil Reynolds, Art Schleinkofer, 
%Brad Wilson, Rick Copeland, Karl Muller

The postal sub price is still
\$1.50 per issue in the US and Canada,
with double that for other foreign subbers(or \$3.00 per
issue sent airmail).
Players in current games and standbys will
continue to get the issues for free, and future game starts 
(except for Nuclear Yuppie Evil Empire Diplomacy, which is free) cost 
\$20.00 (\$15.00 for a life of the
game subscription and \$5 for the NMR Insurance.
Anyone may play in subszines 
for free and just jack up the issue page count. 
See the revised game start announcements below!

Check out the connections in the Diplomatic Pouch with all of
the information you need to play Diplomacy on the Internet at:
/

I also have taken over the Postal port/DipPouch/Postal

\noindent and {\it TAP} on the web is there at:
/Postal/Zines/TAP/index.html

where the szine resides in html format. 
Presently, issues from \#190 to the current issue
are there, and I will be updating the back issues gradually someday. 
Also, check out Stephen Agar's more extensive efforts at:
http://www.diplomacy-archive.com and http://www.diplomacy.co.uk
 
Peter Sullivan's subszine is out of stasis, and all the
back issues can be accessed via :

http://www.burdonvale.co.uk/octopus/index.html.

Peter now seems to be sliding back into stasis!
Rip Gooch and Dave Partridge had been picking up the choo-choo
game slack,
but Rip also has been missing in action completely for over a year now, 
I don't have an update but he
and Dave Partridge communicate. 
Contact Rip at xyropedes of canada.com or Dave
at rebhuhn of rocketmail.com for more info on getting into choo-choo games.
And Andy York has been my most frequent subszine guest lately!!!
He's been in every issue, thanks, Andy!!!

The {\it TAP} mailing list has moved!
It now is even BETTER protected than it was.
I even have a bit of trouble posting to it.
To post to this list, send your email to: tap of diplom.org.
But this is completely moderated, it won't go out to the list unless
I approve it.
In general, I intend to keep traffic down to just the szine, as we've
been doing and I'll put your LOCs in here.
I {\bf EXPECT} all players to be on this list, especially those of you who
are from foreign countries!!! 
You need this to find out when the szine is up on the web to check in on results.

General information about the mailing list is at:
/mailman/listinfo/tap

You can sign up from there, or send E-Mails to:
Tap-request of diplom.org;
with the word `help' in the subject or body (don't include the
quotes), and you will get back a message with instructions.
You must know your password to change your options (including changing
the password, itself) or to unsubscribe.  
Normally, Mailman will remind you of your diplom.org mailing list
passwords once every month, although you can disable this if you
prefer.  This reminder will also include instructions on how to
unsubscribe or change your account options.  There is also a button on
your options page that will email your current password to you.
A big, big thank you for Millis Miller for setting this all up!!

\bigskip

\centerline{\bf THE SEARCH FOR MARGARET GEMIGNANI}

\smallskip

OK, now, why Margaret?  Margaret, of course, is one of the most famous personalities in 
Dipdom, Science Fiction, Star Trek, Comic, etc. fandom.  
She was a nurse in the DC area, I believe, and then retired to Florida some years ago.
Many people had an address for her in Fort Lauderdale (including me), but that address
went missing around 1994.
If you do Google searching, as I have done off and on, there is a Margaret Gemignani
that contributes to the Baltimore and Ohio Historical Railroad Association, along with 
a husband, Gino (anyone know if that matches.... the B\&O matches where she used to live...
but don't tell me, use it as info to go looking yourself!!!)
Margaret has a couple of mentions in the Diplomacy AtoZ and I first encountered her
in the old Bernie Oaklyn {\it Le Front} szine.
I think it would be fun to find her.
You have until issue 310 and then we move on to someone else.

\bigskip

Feel free to spend the time looking for some of the backlog.
Let's get Jeff, Derek, Sylvain, Steve, Ed, Tom, Bill, Gregory, and 
ESPECIALLY Kevin found too!!!
This is a regular continuing feature of the szine
and I will be introducing a new ``search for'' every five issues.
Moreover, you can win a \$25 prize for finding some previous
target who went unfound in the original \$50 period.
That means that if Jeff Key or Steve Heinowski or Ed Henry or Tom Hurst or Bill Quinn or 
Gregory Stewart or Derek Nelson or Sylvain LaRose or John Smythe
is ``found'' from now on it is worth \$25.

\bigskip

Winners will receive credit for Dip hobby activities
that I will pay out as requested by the winner.
Subscribe to szines here or abroad, run your
own contests, publish a szine, finance a web page, 
GO TO A DIPLOMACY CONVENTION or whatever.
Spend it all right away or use me as a bank to cover hobby activities
for years.
What must you do to win?
Get me a letter to the editor for {\it TAP} from the person we're
searching for.

This is very important, just finding them doesn't do it.
They have to write me a letter.     
The final judge as to the winner of any contest will be the target 
himself and I reserve the right to investigate the winning entry.
When you find someone I'm looking for, you should ask him to send me a 
letter for print that includes a verification of who ``found'' him.
%Michael Swift, Mike Stewart, and 
%Jason Yarbrough , Tim Stabosz, 
%Eric Ozog has $25
%Leslie Obata is owed $25
%Derek Nelson, winner of the first postal game in Graustark.  I last saw him
%at the '76 DipCon in Baltimore.
%Charles Wells, former publisher
%John McCallum, former publisher (Brobdignag, SerenDip, etc.)
%Dan/Charles Brannan, former publisher (Wild 'n Wooly)
%Margaret Gemignani, former player and nurse living in Florida

\bigskip


\bigskip

\centerline{\bf INTERNATIONAL SUBSCRIPTION EXCHANGE NEWS}

\smallskip

The British representative is the editor of
{\it Mission From God}, John Harrington.
John may be contacted at 1 Churchbury Close, Enfield, Middlesex
EN1 3UW, UK.

E-Mail: fiendish of operamail.com, John.Harrington of tfeurope.com 

Please include the full name and address of the foreign publisher with
your order, if possible, as well as the szine title.
Make your check in US dollars out to me personally or in GBP to John
if you're doing things from that end.
I will conduct business for Canadians as well, if I can, but prefer
to deal in US dollars with them if possible, or Canadian dollars cash.
To subscribe to American szines, the system works in reverse.

We have closed the European continental branch, as I think most
of you had figured out.

And the ISE in Australia hadn't had much real action in recent
years, and Brendan Whyte has moved on to Jerusalem!!!
Brendan still produces what I find to be the most readable
small szine in the worldwide hobby.
Did you all realize that?
Write to Brendan at his new Jerusalem address and ask him
about subscribing, I'm not sure what the new deal will be.
Department of Geography, Faculty of Social Sciences,
The Hebrew University of Jerusalem, Mount Scopus, Jerusalem
91905, ISRAEL.
His travelogues are wonderful.

\bigskip  

\centerline{\bf WORLDMASTERS04 SECTION}

\smallskip

See http://www.worldmasters.net/wm04/
for details on progress on the WORLDMASTERS04, the Semifinals have now begun.  
Some semifinal notables include: Egg Ferreira, Buffalo Bartalone, Lee Simpson, 
Joe Janbu, Sebastian Beer, Doug Moore,
Jerry Fest, Twerg O'Donnchu, Tim Sweeney, Dave Partridge, Glenn Ledder,
Adam Silverman, Toby Harris, and Thomas Franke.
This is one of the deepest semifinal fields for this great tournament 
that I've seen, with representatives from nearly all of the world's
hobby communities.
Actually, the Semifinal games began in October.
I was wondering why I hadn't seen anything on progress in these games,
and that's why.
More on that next issue!!!
Thomas Franke and David Partridge are in a game together that seems
on first glance to be the weakest in the rest of the players.
So my first thought is that one of those two will have a slot in
the finals.
I am getting raked over the coals for it, but I just ended a game
in a three way draw between me, Thomas, and Ray Setzer that I might
have had a chance in ekeing out a win mostly because Thomas asked
for it to end so he could focus on this semi-final.
Sorry, David, but I had to do it.....
Of course, after saying that, David Partridge is in England getting beaten
on by Guy Thomas in France, who is allied with Thomas Franke in Italy.
But Italy has a Juggernaut bearing down on him from Mike Tombu and
Julio Cardoza.
And Toby Harris just got crunched in his game where he is Turkey, but
I don't count him out yet, he has more lives than a cat!!
But never mind, I don't know how ANY of this will turn out!!!
Doug Moore is doing pretty well as Russia in his game so far, but
Russia can always be crunched after doing well early.
Buffalo is doing pretty well in his game as France taking down Germany
and now attacking Adam Silverman's England, I think, that part is still
developing.

I've joined the Yahoogroup WM04-Chat where some of this
discussion is happening.
You can join too!
However, this forum has been very, very quiet, I hope it picks up with
semis, maybe I'll have to start some discussion.
I had to go the main Worldmasters site at www.worldmasters.net/wm04/ to
find some of these results.
The new Tournament rankings for FTF also are out there that supercede the
ones that were on 18centres.
Go check out:

http://eurodip.nuxit.net/php/ranking/affiche\_ranking.php?id\_ranking=3\&lang=Ang

It ranks 4788 FTF players and is the most complete known compilation of FTF play
ever in the hobby.
You really want to check it out.
Poor Eve Smith ends up 4788th, having been in 33 tournaments in the last ten years,
an achievement in itself!
And of course Don Del Grande is down near the bottom at 4784th, off of 13 tournaments,
two of them in Australia.
For having the Don Challenge Cup named after him, he didn't do THAT badly in his
tournaments Down Under, better than I'd been led to believe at 54/78 and 34/57
And Frank Johansen is a well deserved \#1.
And I'm amazingly in the top quarter with a ranking of 1171, accurately reflecting
the nine tournaments that I know I've been to (i.e. I don't see any missing).
Yann Clouet (if I counted right) has been to 95 tournaments, I'd be surprised if
someone surpasses him in number, and he ranks 9th.
Guaranteed to be a fun browse....

\bigskip

\centerline{\bf DIPDOM NEWS SECTION (with letters)}

\smallskip
 
Obscure and not-so-obscure ramblings on the state of the hobby
and its publications, custodians, events, and individuals with
no guarantee of relevance from the fertile keyboard of Jim-Bob,
the E-Mail Dip world, and the rest of the postal hobby.
My comments are in {\it italics} and {\it ((double 
quotation marks))} like this.
{\bf Bold face} is used to set off each individual speaker.
I should also make a note that I do edit for syntax and spelling
on occasion.

%A VERY light discussion is taking place that will address what 
%stance we (the hobby) should take (proactive in some way for sure) 
%toward Hasbro, the new owners of the rights to Diplomacy.
%More on this will be forthcoming, but it looks like Hasbro might
%have its version of Diplomacy on the market for the Christmas
%season and they actually will be employing ``play-testers''.
%No word on precisely what this means yet, could it mean that
%they will offer a series of ``official'' variants?
%Stay tuned....
%If you want to be part of the discussion, send the MESSAGE:
%
%subscribe hasbro
%
%to majordomo of diplom.org, it works just like the tap mailing list
%described below.  Sending messages to hasbro of www.diplom.org
%sends the mail to the whole list.
%The big news this time is the beginning of the breakout of
%Hasbro into official contact with the hobby.

The game Diplomacy is a copyrighted product owned by Hasbro and all
reproductions or other use of that material in this szine is intended to
be personal use and not infringe on those rights in any way.
All reproductions are done at a heavy financial loss to the editor
and thus are without the remotest possibility of commercial intent,
except to promote THE game, the Game of Diplomacy, which you all 
should purchase from Hasbro or other duly licensed distributors.
 
Stephen Agar has matched the Hasbro rule lists 
and more with some of the even older
rulebooks.
Check these out if you like:

http://www.hasbro.com/default.asp?xcc\_gameandtoyinstructions

http://www.hasbro.com/instruct/Diplomacy.PDF

http://www.hasbro.com/instruct/Diplomacy(OlderVers).PDF

Nice of them to make BOTH of these available.
And all seven different US rulebooks for Diplomacy can now be found here
courtesy of Stephen Agar (relatively new address for this):

http://www.diplomacy-archive.com/diplomacy\_rules.htm

%1: The Reformer, who seeks perfection (crusading type).
%2: The Helper, who seeks love (altruistic type).
%3: The Performer, who seeks status (competitive type).
%4: The Individualist, who seeks an identity (imaginative type).
%5: The Investigator, who seeks knowledge (analytical type).
%6: The Loyalist, who seeks security (ambivalent type).
%7: The Enthusiast, who seeks gratification (thrill-seeking type).
%8: The Leader, who seeks self-sufficiency (dominant type).
%9: The Peacemaker, who seeks contentment (accommodating type).
%See http://graphics.lcs.mit.edu/~becca/enneagram/
%new test at: http://www.9types.com
%My scores in order were: 9, 13, 15, 7, 15, 6, 17, 18, 14.
%Robert Lesco's Marco Poll, the defacto poll of the
%North American hobby since the Runestone is pretty much
%officially dead, continues to collect votes.
%This is an official {\it TAP} approved poll.
%Here are the particulars on the Marco Poll:
%Vote for your top five in each category and you can't vote (or at least
%it won't be tabulated) for Robert Lesco or his szine, which I don't see.
%I will send this to Robert and offer him a trade.
%The deadline is September 1st and either send your ballot to marcopoll of yahoo.com
%or mail to Robert Lesco, 49 Parkside Drive, Brampton, Ontario, CANADA  L6Y 2H1.
%For identification purposes, Robert would like you to identify yourself both
%by name and by affiliation (a game you play in or a szine you sub to).
%Here are the categories this year (I like some of the new ones!!):
%1) Favourite {\it ((Hey, what, he's Canadian, yeah.))} Zine  {\it ((What's a zine,
%shouldn't that be Szine???))}
%Backstabbers United Monthly, Costaguana, The Diplomatic Pouch, Absolute, Vertigo
%2) All Time Favourite Zine {\it ((Szine))}
%Magus, Europa Express, Thirty Miles of Bad Road, Perelandra, North Sealth West George
%3) Best Diplomacy Player
%John Quarto von Tivadar, Edi Birsan, Mark Fassio, Chris Martin, David Partridge
%4) All Time Best Diplomacy Player
%Edi Birsan, Mark Fassio, Kathy Caruso, Rod Walker, Hohn Cho
%5) Best GM
%Malcolm Cornelius, Tim Miller, Tim Richardson, Conrad von Metzke, Doug Massey
%6) Player Who Writes the Best Letters/E-Mails
%Don Williams, Richard Weiss, Mark Fassio, Toby Harris, Cal White 
%7) Folded Zine {\it ((Szine))} You Miss the Most
%Magus, Diplomacy by Moonlight, Le Front du Liberation de Diplomacy, Kathy's Korner
%8) Favourite Variant
%Modern, Nuclear Yuppie Evil Empire Diplomacy, Woolworth, Spy Diplomacy, Colonia

\bigskip

\centerline{Check out current and back issues of {\it Diplomacy World} -- Yahoogroup diplomacyworld}

Also, I need any Hobby Award Nominations NOW (!!!) for the :

\noindent The 2005 and 2006 Don Miller Award for Meritorious Service;

\noindent The 2005 and 2006 Rod Walker Award for Literature;

\noindent The 2005 and 2006 John Koning Award for Player Performance;

\noindent The 2005 and 2006 Fred Hyatt Award for GM Performance;

or

\noindent A 2005 and 2006 Kathy Byrne Caruso Award for Lifetime Achievement (if warranted).

The Hobby Awards Committee is Jim Burgess (Chair and Treasurer),
Fred Davis, Jr., Melinda Holley, Gary Behnen, Jamie Dreier,
Paul Kenny, Mark Stretch, and Robert Lesco.
I was going to publish the award ballot for this year 
in this issue, but I realized that I really just had to get this out first and
then do that.... and then, well, REAL SOON NOW!!!
And when I do, I'm going to give out two sets of awards and get caught up for the 
missed year, that seems to make the most sense.  
Committee.... you will be hearing from me soon!

\bigskip

{\it Diplomacy World} Issue Deadlines were:

\noindent Deadline Spring 2006, Issue \#97: March 1, 2006

\noindent Deadline Summer 2006, Issue \#98: June 1, 2006

Note that Andrew Neumann had taken 
over the lead editorship from Tim Haffey, but he clearly wasn't up to it.
So, I'm officially looking for a lead editor again.
As we have had for the last five years or so, the Pouch is back up and
running again, and Diplomacy World is dead in the water, it seems that is
the way it is.
One runs, and the other one stops.
This occurs even though there really is no direct connection.
If you'd like to do this, let me know, I make it pretty easy, but I
CANNOT be lead editor for two szines at once, I just can't.

%\noindent Final Hobby Awards Ballot for 2004, nominations now to:
%burgess of world.std.com
%
%The qualifications for the Kathy Byrne Caruso Lifetime Achievement 
%Award are that the awardee must have been: (1) Active in the 
%Diplomacy Hobby in at least Three Separate Decades; 
%(2) Multidimensional in their Contributions to the Hobby 
%(e.g. writing, playing, publishing); (3) Taking Retirement or 
%Semi-Retirement from the Diplomacy Hobby; and (4) One of the 
%Hobby’s Unique Personalities Worthy of Being Remembered as Long 
%as THE Game Continues to be Played.  This award need not be awarded
%each year, but only as worthy candidates are identified.  The only
%past honoree is the late Richard Sharp.
%
%The other award categories are self-explanatory:
%
%\noindent Nominees for the 2004 Don Miller Award for Meritorious Service
%
%\noindent Nominees for the 2004 Rod Walker Award for Literary Achievement
%
%\noindent Nominees for the 2004 John Koning Award for Player Performance
%
%\noindent Nominees for the 2004 Fred Hyatt Award for GM Performance
%
%--- --- --- --- --- --- ---

Editorial Board for Diplomacy World (need a Lead!!!):

\noindent Andrew Neumann, andrewneum of gmail.com -- Missing Lead Executive Editor!

\noindent Tim Haffey, 810 53rd Ave., Oakland, CA 94601 USA; trhaffey of
aol.com -- Ex-Lead Editor and Archives Editor

\noindent Jim Burgess, 664 Smith Street, Providence, RI 02908-4327, USA;
burgess of world.std.com -- Co-Editor and Publisher

\noindent Stephen Agar, 4 Cedars Gardens, Brighton, UNITED KINGDOM  BN1 6YD;
stephen of stephenagar.com -- Webmaster and Non-US Postal

\noindent Rick Desper, 5440 Marinelli Road, \#204, Rockville, MD  20852, USA;
rick\_desper of yahoo.com -- Demo Games

\noindent Dave Partridge, 15 Woodland Drive, Brookline, NH  03033, USA;
rebhuhn of rocketmail.com -- US Postal

\bigskip

ATTENTION: There is a new company that had been doing a new PC Diplomacy game:

http://www.paradoxplaza.com/news.asp?ArticleID=239\&Page$=$News

You all should read the interview in the Spring 2005 movement issue
of the {\it Diplomatic Pouch} (and I mean ALL!!!!!!! of you!!!!!)
that I think you can find at: 

\noindent /Zine/S2005M/

I'm not sure what is going to happen now, but basically everywhere 
except in Russia the game pretty much failed.
The AI was not good (not a huge surprise) and it just required too many
updates to get it to work.
Besides, it really was designed for ``real time'' play and everyone
doesn't want that.
To find out more general information on DIPLOMACY please visit
www.diplomacy-pcgame.com or contact pr of paradoxplaza.com
but I think it is about to wither away and die.
In sum, I think that is too bad.
But the hobby as a whole is going strong with thousands and thousands of
Diplomacy players worldwide.
REALLY!!!

The product that tried to do what you are talking about was designed by 
Paradox, released in Feb. 2005.  But by all accounts I've heard, it became 
very popular in Russia, but hasn't done very well in the English speaking 
world.  You can find out more at:

http://forum.paradoxplaza.com/forum/forumdisplay.php?f=295

The posts in there explain how Paradox tried and basically gave up to do 
what you're asking.  This is because Diplomacy is a deceptively complex 
game.  VERY deceptively complex because it appears to be so simple on a 
number of levels.  Perhaps this is what draws you to the game.  If so, I 
would urge you to dare to play with humans at a slower pace.  It really 
does reward the effort.

I think you can still purchase the Paradox game and play it, and if you 
read the posts above, you won't have overly high expectations to be 
dashed.  I think one can learn about the game via Paradox's product, but 
you will quickly become bored with it, especially playing against 6 
computer bots, and will come out to play the real thing.


\bigskip

\centerline{\bf MUSIC AND MOVIES SECTION (WITH COMMENTS ON OTHER ARTS AND SOCIETY)}
     
\smallskip

We're running a ``23 tunes'' contest here
(stolen blatantly from Mark Wightman and the late lamented {\bf The Sprouts of Wrath}.
If anyone would like to send me a tape or CD of their 23 (which was the original point)
that would be great, but I don't intend to require that.  I will be playing in the
sense that I'll be putting 23 tunes in, and you have to guess me, but I obviously
won't score points.
Send commentary with your choices, and we'll see if people can
guess who you are!!!
And already there is a LOT of diversity in defining tunes and styles, so 
BE CREATIVE!!!
 
%To encourage voting early, I picked five voters at random to receive five US
%dollars from me (either in cash or paid to someone for Dip stuff or to get
%a free tape).
%Tony Dickinson won the Round 5 prize, so we had three of the six Round 1 voters
%won and one of the three Round 2 postal voters who also got five chances to win.
%That showed the value of getting in early!!
%Voters in Round 1 were Mike Barno(\$5), Rick Desper (\$5), Tony Dickinson (\$5),
%Drew James, Heath Gardner, and John Harrington.
%Round 2 postal voters were John Schultz (\$5) Ian Moore, and Stan Johnson.
%Round 2 E-Mail voters were Scott Morris, 
%Warren Goesle, Peter Sullivan, and Michael Lowrey.
%Round 3 voters were Dick Martin, Richard Weiss, and Rip Gooch.
%Round 4 voters were Roland Sasseville, Jr. (\$5),
%Don Williams, Brent McKee, and Andy York.
%Round 5 voters were Mark Larzelere, Al Tabor, Jody McCullough, and that's it.
%We'll end up with a monster party tape at the end of it that I plan
%to segue and sequence and copy for distribution.
%The result will be a great New Millenium party tape -- we're going for 90 minutes.
%I've also been thinking that I should put this out on CD
%as truly emblematic of the new millenium.  
%I don't have the capability to do that quite yet, but I think
%I might by then.
%Any suggestions (or especially volunteers) on this front will
%be cheerfully accepted and could receive monetary payments!
%The CD way may still occur if someone steps forward and actually does it for me.
%So far, we have ``I Melt With You'' by Modern English; George Gershwin's
%``I got Plenty O' Nuttin' '' from {\it Porgy and Bess} in the 1957 concert
%recording with Ella Fitzgerald finishing off the vocals after Louis
%Armstrong blows and sings through the tune; Duke Ellington performing
%Billy Strayhorn's ``Take the A Train''; Frank Sinatra's ``New York,
%New York''; something from the B-52's;
%the original Van Morrison and Them version of ``Gloria'';
%The (English) Beat's 12 inch version of ``Save It for Later'' 
%ratchets things up to the next level (wherever you put it!);
%Buster Poindexter's ``Hot, Hot, Hot'' keeps you there;
%``Atomic Dog'' by George Clinton blows the doors off,
%and Koko Taylor cleans up singing Willie Dixon's ``Wang Dang Doodle''.
%After I get timings down, I'll choose exactly which songs below make the list.
%
%EXTRA SPECIAL B-52'S BULLPEN: (7) ``Love Shack'';
%``Rock Lobster". {\it ((A tie, a tie!!!!))}
%
%BULLPEN: (9) Nirvana -- ``Smells Like Teen Spirit";
%``Cumberland Blues'' -- the Grateful Dead.
%(8) ``Twistin the Night Away" -- Sam Cooke; ``In Between Days'' -- The Cure;
%``Mannish Boy" -- Muddy Waters; ``Shake, Rattle, \& Roll" -- Big Joe Turner; 
%``Proud Mary'' -- Ike and Tina Turner.
%(7)  ``I Wanna Be Sedated" -- Ramones; ``Twist \& Shout" -- Beatles.
%(6) ``Magic Carpet Ride" -- Steppenwolf;
%``Crossroads'' -- Eric Clapton; ``Play That Funky Music'' -- Wild Cherry;
%``I Fel Good" -- James Brown;
%``Radar Love'' -- Golden Earring; 
%Devo -- ``Whip It"; ``Echo Beach'' -- Martha and The Muffins.
%(5) ``Sing Sing Sing'' -- Benny Goodman; ``Rocking the Casbah'' -- The Clash; 
%Squeeze -- ``If I Didn't Love You"; ``Roadrunner'' -- 
%Jonathan Richman and the Modern Lovers.
%
%SPECIAL ROLLING STONES BULLPEN: (6) ``Paint It Black''. 
%
%SPECIAL TALKING HEADS BULLPEN: (9) ``Take me to the River".
%(4) the entire {\it Speaking in Tongues} record
%(special call for ``Road to Nowhere'').
%
%SPECIAL ALPHABET SONG BULLPEN: (6) ``YMCA" -- Village People. 
%
%SPECIAL DRUG MUSIC BULLPEN: 
%(8) ``Rd, Red Wine'' -- UB40.
%(6) ``Don't Bogart that Joint'' 
%-- Fraternity of Man; ``The Old Dope Peddler'' -- Tom Lehrer.
%(5) ``Cocaine'' -- Eric Clapton's version; ``Casey Jones'' -- the Grateful Dead.
%(4) ``White Rabbit'' -- Jefferson Airplane; ``Love Is the Drug'' -- Roxy Music.

\bigskip

\centerline{\bf {\it 23 Tunes Game}}

\smallskip

Here are the rules for 23 TUNES.  You send me three tunes for the first turn,
and then two tunes in each of the last ten turns for a total of 23.
If you missed the first turn, you can still catch up by sending five tunes next
issue, and guess on submitters to this issue.
I am also submitting my tunes.
After we're done, I'd like to exchange CD's/Tapes for as many of the tunes players
as possible, but this is not required.
I'll be sending the winner both my LAST 23 tune list and my NEW 23 tune list.
The winner is determined by having you guess each issue who submitted what list
(I will tell you who the submitters are).  For each list you get right, you get
a point, you also can win bonus points from me for really cool tune selections.
That's it, not complicated.
I hope by starting this up, we'll get more to join, five songs required to enter
late.
Playing this issue (guess who is whom by number, scores are in parentheses) 
is, in alphabetical order, 
Jim-Bob Burgess, Rick Desper (1), %Steve Emmert, Doug Kent, 
Dick Martin, %Jim Reader,
Richard Smith (3), Joakim Spangberg, %Brendan Whyte, 
and Brad Wilson (4).
The linking theme thing didn't seem to go over too well.
No one really figured out the true linking theme.  
Rick Desper was using Underground tube stops and songs with that as the title,
they were things like that.  
I'll let you guys talk a bit to each other on that with your guesses.
I have added some kind of comment on each tune.

WHAT I NEED: two more tunes (seven if you're joining up new, four if you NTRed (NO TUNES
RECEIVED!!) and want to get back in), your guesses as to who
submitted which lists, and guesses about people's themes if any.
Quite a number of you SAID you would join but haven't yet, so we'll get started and
put the pressure on you.

\noindent Here are your guesses and comments (also alphabetical order):

Rick Desper: Since you wrote comments for all the picks, 
that means you are faking comments?
{\it ((Yessiree, I did it really well the first time, didn't I?
This time I fell down a little.))}
Well, I have no freakin' idea who picked what.  Half the players I don't know at
all.  And by ``half" I mean ``everybody but you and Emmert".  
I'll say Emmert picked \#1 (NO) and you picked \#3 (YES).
{\it ((You score one point, as a mathematician like you should know, 
you CAN earn points here for guessing.))}
For an off-game bonus, do you know Ricky Gervais?
http://www.youtube.com/watch?v$=$EMEdQDUjZEk\&mode$=$related\&search$=$
It's for charity. :)
{\it ((Of course, but I am not a huge fan.
I think both the original and American versions are OK, and there
is something about the women playing the secretaries in both ``Offices"
that you can't take your eyes off, but no, I'm not a big fan.))}

Richard Smith: Guesses:
1. Brendan Whyte  (YES);
2. Brad Wilson (NO);
3. Jim-Bob Burgess (YES);
4. Rick Desper (NO);
5. Richard Smith (THAT'S YOU no pts.);
6. Doug Kent  (NO);
7. Steve Emmert (NO);
8. Dick Martin  (YES).
{\it ((That gives you three points. 
Not bad for joining the szine right now to play.))}

Brad Wilson: I must have missed the part about themes, because Lord
knows I didn't have one.
Anyway, my guesses (and theme guess if any):
1) Whyte - choral singing (YES, no real theme, though you're right they were choral);
2) Kent  (YES);
3) you   (YES);
4) Smith  (NO);
5) Desper  (NO);
6) Emmert  (NO);
8) Dick Martin  (YES).
I'll be damned if I get any other ``themes". I'm kinda
dense these days.
{\it ((You did hit four points, that's pretty good!
You're way ahead with NTR's.))}

\medskip

MYSTERY PERSON \#1 for TURN 2:
%Joakim Spangberg <joakim@konfliktspel.com>
%That's it, I've been lurking long enough... here's the 
%first batch of tunes for a game light enough and fitting 
%one of my&nbsp;major interests perefctly. My theme 
%this time is, obviously, Germany.<BR>

4) Das Ich -- Keimzeit:
Weirdest looking act I've ever seen. 
I've got mental picture of these guys fetching their children from daycare... 
I'd bet they would would have to go home empty handed most of times.
{\it ((OK, I knew it would happen, we would hit a song I just don't know.
So you know this isn't me.))}

5) Einst\"urzende Neubauten -- Seele Brennt:
Usually delivering interesting soundscapes though sometimes being more silly than challenging.
{\it ((I actually do know this song, I like it, a bit cutesy, but a bit more interesting
than you indicate, compares favorably to the masters of soundscape, Stereolab.))}

%Qntal - Vogelfluc<BR>
%German electronic medieval music anyone?<BR>
%<BR>
\medskip

%Richard Smith <richard of sholing.force9.co.uk>
%I've got 20-odd tracks in mind, mostly from this year though they won't fit
%on a single CD - will have to be a double :-) I've picked my first three
%from near the bottom of the list...
%MYSTERY PERSON \#5 for TURN 1
MYSTERY PERSON \#2 for TURN 2:
%1) Pure Reason Revolution -- The Bright Ambassadors of Morning:
%So, you're a promising new pop band with a (currently) trendy retro-rock
%stylee. You've just been signed to Sony-BMG, one of the biggest labels in
%the world. It's single time. You choose to go for a 12-minute epic
%masterpiece. Music biz suicide? No! Everyone loves it.
%{\it ((And worthy successors to Pink Floyd, Genesis, and other bands who did it
%before them.
%There's nothing wrong with 12 minutes.))}
%
%2) Mastodon -- Siberian Divide:
%One of America's up and coming metal bands, Mastodon have gone a bit arty
%with their ``Blood Mountain" album to great effect. It's hard to pick a best
%track, but this is my favorite.
%{\it ((Metal seems to be making a comeback, in new and interesting ``arty'' ways.))}
%
%3) Wolverine -- Liar on the Mount:
%This track is from the Swedish prog-mettalers' 2006 album ``Still". It
%features spoken passages from none other than Mr. George W. Bush. How dare
%they lambast the leader of the free world! Oh well why not, everyone else
%does and the track is really good. Oddly, the first time I heard this track,
%the tone of Dubya's voice reminded me of the guy on Mylo's ``Destroy Rock and
%Roll" who rattles off a list of musical artists that are ``evil", including
%David Boowie and Cindy Looper.
%{\it ((No, say it ain't so?
%W.??
%The real question about lies is the relationship between lies and propaganda.
%If no one calls you on it -- not really -- is it a lie or just spin?))}

4) Rammstein -- Links 234 (Live):
German heavy metal band Rammstein are without doubt one of the best live 
acts in the world. This track is from the Volkerball DVD which features 
them in all their glory -- pyrotechnics, costumes, blood, sado-masochism, 
and most of all arsch-kicking rock 'n' roll. They have been accused of 
many things including homoerotic symbolism and being Nazis. My chosen 
track is about their repudiation of the latter. The words contain ``we 
sound right but we think left" whilst the music (deliberately) sounds a 
bit ``zieg heil". Works for me, whenever I listen to it I have a strange 
urge to annex my next-door neighbors :-) 
{\it ((Ah, heck, everyone's going to know this isn't me either.
I really like the next song, but this one leaves me cold, maybe I do need
to hear it live.
I do find your note about the lyrics intriguing.))}

5) Porcupine Tree -- Hatesong (Live):
British art-rock quartet Porcupine Tree have been getting increasingly
popular in America following two successful albums ``In Absentia" and 
``Deadwing". This track is from the ``Arriving Somewhere" DVD filmed in 
Chicago last year. Wow, awesome gig! The track I've chosen is ``Hatesong" 
which is one of the highlights of the show with a total wig-out guitar 
solo and fantastic drumming. I can't get enough of these guys, they make 
other bands look like bumbling amateurs!
{\it ((Damned straight.
To me, much of the last five or six years has been low on invention and
sincere energy, but NOT from these guys, possibly the best band around
right now who is not the Mekons.... ;-)  ))}

\medskip

%"Wilson, Bradley" <BWilson of Phillyburbs.com>
%MYSTERY PERSON \#7 for Turn 1
MYSTERY PERSON \#3 for TURN 2:
%1) Mem Shannon, ``Taxicab Driver" (from ``A Cab Driver's Blues", Hannibal/Rykodisc, 
%1995): Blues is not necessarily a native New Orleans form of music: 
%the blues' roots in the Mississippi Delta took it north to Memphis, Kansas City 
%and (most of all) Chicago. But take gritty urban blues, the swampy, funky 
%second-line rhythm that fuels New Orleans music and a sharp wit typical of 
%New Orleans, and the result is a song like this: 
%funny, foot-tapping and utterly charming. Shannon's expressive voice 
%and distinctive guitar sound (Albert Collins meets Wes Montgomery) 
%make this one a treat.
%{\it ((Many people think that this sort of music all sounds the same, they're
%completely nuts.
%The range of potential emotions is immense and fundamentally isn't music about
%emotion.
%It's just emotion.... or is that the motion.
%Sorry, can't resist a Ghod reference.))}
%
%2) The Kinks, ``Catch Me Now I'm Falling" (from ``One from the Road", 
%recorded 1979, released 1980, Konk Records): I always thought the 
%Kinks rocked harder and wrote sharper lyrics than the (to me) 
%overrated Beatles, and here's the proof. This whole live album 
%glistens and sizzles with intensity and passion, and the band never 
%sounded tighter. The song is that rare bird, a political song from 
%the late 1970's still sadly relevant; its ferocious lyrics sum 
%up Jimmy Carter-malaise era U.S.A. well, and they are just as apt 
%today for the running disaster that is Bushism. 
%Dave Davies never sounded better on lead guitar than here.
%{\it ((I know there are Beatles fans of this generation -- resident {\it TAP}pites
%Keith Sherwood and Peter Sullivan most definitely included -- but a lot of people
%didn't remember that the Kinks were making relevant music in the Elvis Costello
%era.))}
%
%3) Eartha Kitt, ``Let's Do It" (from ``Eartha Kitt Purr-fect Greatest Hits, 
%7N Records, 1998; recorded 5 October 1953, with Henri Rene \& 
%His Orchestra): Cole Porter, that old sybarite and matchless wit, 
%must have loved this: the ever-slinky Miss Kitt turning a Porter 
%tune about falling in love into something else entirely -- let's 
%just say Kitt's throaty delivery and arch-seductive voice obviously take
%the ``it" of the title to mean somnething more, er, basic. 
%This snappy, hot little number is a textbook case of how to take a 
%standard and make it your own. Kitt -- now on Broadway in ``Mimi le Duck" -- 
%is a force of nature, a dazzling entertainer with an utterly 
%distinctive voice and great legs for a lady in her 70's.
%Her 50's recordings are as sexy and dangerous as anything Elvis ever did.
%{\it ((And she even played Catwoman on Batman, who can forget that???
%And I just noticed after checking that she shortly turns 79, so she's
%almost OUT of her 70's.
%Lastly, she once played Helen of Troy in the Orson Welles production of
%{\it Dr. Faust}, it was Welles who saw that her magnetic personality made
%her an actress, not just a singer/dancer.))}
%Brad Wilson <bwdolphin146@yahoo.com>

4) ``April in Paris", Count Basie and His Orchestra
(Verve, recorded 1955, released 1956): Like listening
to liquid chocolate, so velvety and creamy and rich.
The post-war Basie band at its absolute swinging,
so-tight-it's-loose peak. Thad Jones never sounded
better on trumpet. Sizzling arrangement. The best
dance music ever written.
{\it ((I honestly don't get why this music isn't 
heard more.
I like some headbanging as much as the next bloke, 
but sometimes you want to glide around the dance floor,
well at least dream about gliding around the dance floor
to the likes of this.))} 

5) ``The Goodbye Look", Donald Fagen (from ``The
Nightfly", Warner Brothers, 1982): A nasty little gem,
overshadowed on this LP by the title track and the
bouncy ``I.G.Y.", but still a classic piece of cynicism
and detachment from half of the grandly bitter duo
known as Steely Dan. Set in somewhere south of Key
West, Fagen's troubled resort is anything but
Margaritaville. Anyone who likes Steely Dan should
have Fagen's solo discs.
{\it ((Go listen to Steely Dan again, you might have pooh-poohed it
in 1978, pledging your allegiance to Elvis Costello and Joe Jackson, 
but you would be wrong.
It's interesting how this post-Steely Dan material garnered such
little attention.))}

\medskip

%From: Rick Desper <rick_desper of yahoo.com>
%MYSTERY PERSON \#6: in Turn 1
%It would be pretty easy to "play to win" by repeatedly picking completely obscure songs that have %no relationship to each other (or me), but that seems boring.  So here's my first trio:
%The connection is obvious to me.  Is it to you?
%Well, this is a hint:
%http://www.tfl.gov.uk/tube/
MYSTERY PERSON \#4 for TURN 2:
%1) ``Baker Street'' by Gerry Rafferty:
%I have always liked ``Baker Street", which has one of the most 
%famous sax riffs in pop music.  
%It was big on MTV in the early 80s when videos were young.
%{\it ((Yes, indeed, and I am a huge sax fan, at that time, I was much more of a Saxa
%fan with the English Beat, but this one is more famous than Saxa's on, say,
%``Mirror in the Bathroom".))}
%
%2) Waterloo by Abba:
%``Waterloo" is one of the ABBA songs that was {\it not} on my Dad's ABBA 
%8-track tape that he'd play in the car in the 70s.  
%His collection consisted of one 8-track apiece from ABBA, John Denver, The Beach 
%Boys, and Helen Reddy.  That was it, I think.  After having that beaten into 
%my head for about five years I developed a bit of an antipathy to the group, 
%but that's faded in recent years.  When I moved to {\it ((place name 
%censored since it might give away who this is))} I rediscovered 
%the group, since they were still big in the dance clubs in a retro way.  
%Of course ``Dancing Queen" was the big hit.  Didn't hear ``Waterloo" 
%until I saw ``Muriel's Wedding", the film that inspired the musical 
%``Mamma Mia".  Both are filled with ABBA tunes.  
%{\it ((My dad really did have this 8-track collection
%you'll have to figure out if that means this is my list
%or that my father and this person's father had the same 8-track tape taste.
%And ``Muriel's Wedding'' and ``Mamma Mia" are both worthy vehicles for this
%infectious music!!))}
%
%3) Angel by Sarah McLachlan:
%The Bakerloo tube line is named after the Baker Street and Waterloo stations.  
%My commute every day goes through the former station (I'm traveling from 
%that "Mornington Crescent" is also the name of a song.  
%``Angel" has been the title of a number of songs.  
%I picked the Sarah McLachlan song after listening to a few since it sounded nice.  
%{\it ((I also like the P.P. Arnold version of ``Angel of the Morning", but that's
%more than just Angel -- there is a theme in this one, in case you can't tell....
%and I think Sarah is just that ``nice''.
%I'll bet she's nice and down to earth in person too.))}

4) ``Mad World" performed by Gary Jules for the Donnie Darko sound
track, covering a Tears for Fears song.
Donnie Darko is a great film and this tune really captures 
its spirit of confusion and pain.  
Also, one of the more inventive SF films of recent years.
{\it ((I don't know why this film was so overlooked.
I pretty much watch EVERY SF film that comes down the pike, so I can't
easily tell, but this one seemed to be overlooked.))}

5) ``Praise you" by Fatboy Slim.  The video is priceless.
{\it ((Nuff said.
There is no more.
I still think in many ways the ``first video'' (``Video Killed the Radio Star"
by the Buggles is the best, but this really IS the best video ever.))} 

\medskip

%Dick Martin <phantom2 of speakeasy.net>
%MYSTERY PERSON \#8: in TURN 1
MYSTERY PERSON \#5 in TURN 2:

%1) ``Want-Ad Blues", John Lee Hooker: Sure, there are better-known 
%Hooker tunes, like ``Boom Boom" and the classic ``Boogie Chillun", but 
%this is the one I keep coming back to.  Maybe it's the slyly suggestive 
%lyrics sung in Hooker's gravelly voice that's always just around but 
%not quite on the beat that creates the magnetic tension.  Maybe it's the 
%groove so deep ``even a white person could get it".  Whatever.  It's easy 
%to listen to and hard to sit still for.
%{\it ((Yes, yes, yes, this music seems so simple, but is so complex....))}
%
%2) ``Sing, Sing, Sing", Benny Goodman:  I hadn't heard this tune for ages 
%til I heard Los Straitjackets play it in concert a couple years back. 
%they ripped into it as a surf guitar instrumental and I kept thinking 
%to myself, ``I know this song, I know this song...what is it???" then it 
%clicked and I was blown away.  It's still as amazingly hot today as it 
%was back in the big band days.  Gotta go back to the source and pick the 
%original for being so timeless, even though the live Los Straitjackets 
%version is about as good.
%{\it ((I think all of us were not actually alive when Benny Goodman
%originally recorded this, or if we were, we weren't really old enough
%to pay attention.
%It's scary how good and fresh some of that music sounds today in our
%world of retreads and recycles.
%Cab Calloway is another of the band leaders who made music that sounds
%wonderful and amazingly hot today.
%for Cab, I recommend the ``Are You Hep to the Jive?'' CD compilation that
%came out a decade ago or so.))}
%
%3) ``Blue on a Green Planet", Big Country:  Anthems...nobody does 
%anthemic guitar rock as well as Big Country.  Big, loud, wailing guitar 
%sounds.  Lyrics that sorta make sense if you don't think about them too 
%deeply.  Drench with heartfelt emotion.  Crank it up to 11.  Repeat.
%{\it ((No one has the big sound down better than these guys.
%If you've only heard their eponymous ``In a Big Country", the Country is
%big enough to hold some other great anthems as well.
%Big Country has a conscience too.))}

4) ``Instrumental Introduction/Don't Look Down", Lindsey Buckingham: The 
first time I heard this I just kinda shrugged and said, ``eh". Second 
time I thought it maybe wasn't such a weak song after all. Third 
time...I couldn't take it out of the CD player for a month. It's 
beautifully played pop music that is just off-center enough to stay 
fresh no matter how often it's played.
{\it ((I used to like skating to this song a huge amount.  I'm not
sure why, not sure if it ever has been used by a major figure skater,
but they should think about it.))}

5) ``Sweet Marie" (live), Hothouse Flowers:  This is about as close as it 
gets to putting pure emotion into song. It's a gospelly breakup song, 
sung to the girl that's just left him.  He's still in love, but knows 
that it's not going to work.  Mildly irrational, sweetly romantic, 
wishing the best for the woman he loves but can't have.  Time to just 
carry on and savor the feelings because they're all you have left.  I've 
been there.
{\it ((This is another band that is really cool live, and if you've
not heard this song live, go take a listen.))}

%6. "brand new cadillac", the clash. the second song on the greatest 
%album of all time, the only band that matters covers an old rockabilly 
%song and makes it all their own. propulsively danceable, rocking hard 
%from start to finish. yeah, his girl has left him and ain't never 
%coming back...but he still can't help but be impressed by the caddy.
%
%7. "in my life", the beatles. a whole lifetime's love song compressed 
%into less than two and a half minutes. sentimental without being sappy, 
%simple, earnest, honest, concise and with room to spare for a piano 
%solo. they don't make them like this anymore.
%
%8. "the real me", the who. for a band that spent a great deal of time 
%obsessing on identity issues, it doesn't get any more basic than this. 
%hmmm...is he daring us to consider him, or pleading? either way, it 
%looks bleak - just like the rest of the brilliant quadrophenia. and 
%with entwistle's agile bass, "the best keith moon style drummer on the 
%planet" and townsend's power chords playing against each other as much 
%as with each other, form matches content perfectly.
%
%9. "rev. jack and his roamin' cadillac church", by timbuk3. ok, so i'm 
%a sucker for the big guitar playing the big groove. add a dash of wry, 
%dry humor, a galloping drum machine, some wailing harp and barbara k's 
%sublime harmony vocals and it's a tasty treat. too bad nobody ever 
%heard this song because it's not on the cd with their "only" song. eden 
%alley is a very strong cd throughout, and well worth a listen if you 
%can still find a copy.

\medskip

%ME
%MYSTERY PERSON \#3 for TURN 1
MYSTERY PERSON \#6 in TURN 2:

%1) ``White Rhino Tea" by the Ozric Tentacles: Starting this off slow with
%an instrumental by this jazzy space rock band from 1991.  Six minutes of
%dreamy, haunting sonic tapestry, and the first cut off of what I think is their best
%album, {\it Strangeitude}.
%{\it ((Most of the progressive rock like this which I like is much earlier
%than this, Bob Olsen and I, for example, are huge Klaus Schulze fans, but
%the Tentacles fit well into this genre and are worthy successors.))}
%
%2) ``The Secret of Bethany's Mouth" by the Green Pajamas: This psych pop
%masterpiece is the latest from this veteran group, 
%from the 2005 release {\it 21st Century Seance} that naturally is about
%various kinds of ghost stories, following up on the theme.
%Green Pajamas remain possibly the best of the many bands continuing to plumb the 
%new psychedelia.
%This song has as its main inspiration the romantic mystery novel
%``Pale as the Dead'' by Fiona Mountain and as a folky feel to it.
%{\it ((Since Eric Ozog isn't in the game (at least so far) I can tell you
%that this is Eric's favorite band and they hail, naturally, from Seattle.))}
%
%3) ``The Pictures on My Wall'' by Echo and the Bunnymen: 1979 beginning of the 
%McCulloch boys is fresh and exciting when heard today.
%There is even a hint of Joy Division-ness in them on this cut.
%This first single was unavailable anywhere I knew about until the mid-1990's,
%since the early vinyl printing was small.
%{\it ((I was happy to see someone select this song, not many people have ever
%heard it, but to us Bunnymen fans this is an essential pickup.))}

4) ``Muddy Waters" from Pere Ubu: This is off the 1998 {\it Pennsylvania} CD.
The record as a whole is quite frankly still way ahead of its time, nearly ten
years after it was recorded.
There isn't anything quite yet like David Thomas and Pere Ubu even now.
This track is unlike the other tracks on the album, but heck you could say
that about almost every track.
I'd not listened to this in some time, and it was immensely rewarding to hear it
again.
As far as this track goes, well, it doesn't sound like Muddy, not really anyway,
but Muddy is part of the inspiration that underlies the work here.
Reminds me in many ways of Zappa as it salutes Muddy without imitating him.
{\it ((This tune is the middle point of the album (7th track), the best two other songs are ``Woolie
Bullie'' that leads off the CD and ``Wheelhouse" which ends the disc as the 15th
track. 
Great choice, this is a much overlooked CD, it was reissued last year as I believe
the original label for it folded.))}

5) ``Girls and Boys'' from Blur (pet shop boys mix): The two pet shop boys mixes
on the single are both much better than the base song (one of them is four minutes,
ther other over seven) of this classic 1994 anthem.
It anticipates the metrosexual movement (theme here is songs ahead of their times)
with the deliciously ambiguous ``Girls who are boys,
Who like boys to be girls, Who do boys like they're girls,
Who do girls like they're boys,
Always should be someone you really love!''
{\it (({\bf TAP} has always been a Blur over Oasis szine, and this was one
of the heights of the Blur movement.
If you have to ask who Blur and Oasis were, then of course this isn't going
to make any sense even were I to explain it to you.
Pop music debates are kinda like that, aren't they???))}


\medskip

%Brendan Whyte <bwhyte of mscc.huji.ac.il>
%MYSTERY PERSON \#1 from Turn 1 NTR for Turn 2
%
%1) The ``Hallelujah" Chorus from Handel's ``Messiah":
%The title tells you what the words are, and the middle few bars are 
%so famous, but how many people, apart from those that sing it, know 
%the whole movement? A great little number this, boppy and exciting to 
%sing, to sing along to, or just to tap ones fingers to on the 
%steering wheel while caught in traffic, though with the new bridge to 
%replace the Woodrow Wilson drawbridge in DC should ease the latter at least.
%{\it ((As I've said before, I most prefer the John Eliot Gardner version
%(Philips R 215049, 1983) with the light clarity of tone that I'm trying
%to develop right now in my own singing.
%John Eliot Gardner's recording with the Monteverdi Choir of the 
%Dixit Dominus by Handel (Erato, 1992) is even better to illustrate this point.))}
%
%2) ``Libera Me" from Andrew Lloyd Webber's ``Requiem":
%The final movement of this impressive modernist-classical piece 
%leaves the boy soprano on his own to hold pitch and rhythm singing 
%about eternal peace, when the organ comes crashing in over him with 
%dissonance and gusto trying to drown him out in chaos, but its waves 
%of noise break and underneath the sweet high ``perpertua" carries on. 
%It's a brave young lad who can maintain that, especially in any live 
%performance in front of an audience. But live or recorded, this is 
%great music and a fascinating musical analogy of peace and goodness 
%and light triumphing over noise and chaos.
%{\it ((I've heard about five attempts in recent years to compose a Requiem,
%quite a difficult task to do.
%Even as I quibble with A.L. Webber on many points in how he composes his
%other more popular music, this is easily the best of those Requiems.
%And no, I'm not even counting Paul McCartney's Ecce Com Meum composition.))}
%
%3) ``Mau Kamu Suka Kamu" by Rano Karno:
%An interesting delve into singing by TV presenter Karno comes up 
%trumps with this sugary but fun silly love song in a disco-dangdut 
%style (one could never call Karno himself `dangdut', he's too 
%respectable!). Mothers and daughters will sing along in the catchy 
%chorus. A difficult track to find outside Java, but worth the effort 
%of hunting down, especially to see the expression on the faces of 
%expat Indonesians when you play it!
%{\it ((I have a strange soft spot for silly love songs, you know.....))}
%
%\medskip
%
%Douglas Kent <dougray30 of yahoo.com>
%MYSTERY PERSON \#2 in Turn 1, NTR in Turn 2 
%
%1) ``Haunted'' by Poe: An honorable attempt to deal with her
%father's death.  Really the whole album is.
%{\it ((You all know how much I grew up on complex layers of sound and
%this 2000 release was the best of that genre in that year by far.))}
%
%2) ``Can You Do It'' by Grand Funk Railroad: Produced by
%Frank Zappa, from their final studio album of the
%original incarnation (1976's Good singing, Good Playing)
%{\it ((People forget how focused and talented a producer Frank Zappa was.
%This year's Zappa Plays Zappa led by Dweezil was one of the musical happenings
%of the year... of course I did NOT get to see it, but I hope some of you did.))}
%
%3) ``Tempus Fugit'' by Yes: Trevor Horn takes vocals on this
%album, Drama, instead of Jon Anderson, prior to his
%stint as opening act on MTV in The Buggles.  One of
%the ten best true rock songs of all time.
%{\it ((You probably all know how much I like the Buggles,
%and Yes was the very first rock concert I ever went to in person,
%before Trevor Horn joined the group, of course.))}
%
%\medskip
%
%From: <steve.emmert of cox.net>
%MYSTERY PERSON \#4:
%
%1) ``6 Underground" by Sneaker Pimps: If you know Sneaker Pimps, 
%then you're way too cool for me.  But ``6U" is a terrific tune.
%{\it ((Ah, lots of people are selecting psychedelic or electropop sorts of things.
%``6U'' is from their first and probably best album, I think it reached \#6 on
%the British pop charts, was less popular here in the States.
%Its various members are presently scattered around doing all sorts of side
%or separate projects.
%From what I know, none of that is producing anything terribly exciting, which
%is too bad.))}
%
%2) ``In Memory of Elizabeth Reed" by the Allman Brothers Band:
%``Liz Reed" is the tune that, in my mind, definitively proves that the 
%Allman Brothers were in reality jazz musicians.  It's their tribute to Miles Davis.
%{\it ((I haven't heard this since I was in college in the 1970's and had my 
%jazz show on the radio station.
%I never played this song on that, to my recollection, but I do remember it 
%being an extended drum solo by Trucks and being quite striking.))}
%
%3) ``Spanish Sky" by Chris Isaak:
%``Spanish Sky" is from {\it Heart Shaped World}, the album 
%(back then, they still called them albums) that made Isaak famous with the 
%single, ``Wicked Game."  I doubt I could ever get tired of that CD.
%{\it ((I don't think this is my thing, and I think everyone will know this list 
%isn't mine when
%I say that I think I remember ``Wicked Game" but I'm positive I've never heard the 
%whole CD.))}
%
%\bigskip
%
%\centerline{\bf SPY DIPLOMACY (Variant, revised Dec. 1986)}
%
%by Jim Burgess
%
%Rules:
%
%1) Unless otherwise specified, the standard rules of Diplomacy apply.
%
%2) Players receive adjudications for their own armies and fleets, but not
%the armies and fleets of other powers.  Similarly, each player sees only
%his or her own section of the supply center chart.
%
%3) In addition to the standard units, an unit called a "spy" is added.
%
%     A) Each of the seven powers begins with a spy in each home supply center.
%
%     B) Spies are supplied only by home supply centers (i.e. Russia may have
%as many as four spies at a time while other powers are limited to a maximum
%of three).
%
%     C) Spies are "built" and "disbanded" in Winter seasons at the same time
%as other units.
%
%     D) There is no limit to the number of spies that may be present in any
%province and spies may be ``stacked" with armies or fleets (exceptions are
%listed in Rule 6).
%
%4) Spy Reports
%
%     A) Spies report the location and nationality of armies and fleets in
%the province they occupy and all adjacent provinces immediately following
%the standard Winter, Spring, Summer, and Fall seasons (i.e. just prior to
%the spy movement seasons).  Spies can differentiate between units in retreat
%and successful attackers when two units "occupy" a province.
%
%     B) Spies also report the nationality of spies in the province they occupy
%and the presence (but not nationality) of spies in adjacent provinces at the
%same time.
%
%5) Movement of Spies
%
%     A) Spy movement follows the collection of spy reports, so orders to spies
%may be made conditional on any information gathered by spies on opposing troop
%movements or the adjudication of one's own units.
%
%     B) Spies move after each of the following standard seasons: Winter,
%Spring, Summer, and Fall (note that all spy movements PRECEDE Autumn
%retreats), beginning with Winter 1900.
%
%     C) Spies move as armies do with the following exceptions:
%
%          a) Spy movements cannot be stood off by movements of any other unit.
%
%          b) Spies may be convoyed by fleets of any power during any of the
%four movement seasons for spies.  The convoy orders for fleets in these
%seasons must be ordered by their owner in the usual fashion or else the spy
%convoy movement fails of execution.  Fleet convoy orders for spies may be made
%in addition to regular Spring and Fall moves (note, however, that the fleets
%themselves never move during spy movement seasons).
%
%          c) Spies may also be "picked up" and carried by fleets of any
%power. Embarkation and debarkation are moves that must be made during a
%spy movement season and "permission to board" is not required.  Embarkation
%consists of a movement from a land province to an adjacent sea province
%containing a fleet.  Debarkation consists of a movement from a sea province
%containing a fleet to an adjacent land province.  A spy may not "switch
%fleets in midstream".  Once boarded, a spy may only get off by debarking.
%After boarding a fleet, the spy moves with the fleet during regular movement.
%A spy may not debark from a fleet awaiting retreat (e.g. if a fleet carrying
%a spy is dislodged in Spring, the spy may not debark until the spy movement
%season following the standard Summer retreat season).
%
%6) Spy Mortality
%
%     A) This rule will outline the circumstances under which spies may be
%captured or killed.  Spies may be disbanded in Winter seasons at the same
%time as other units to meet the requirement that a power may not have more
%spies than the number of currently held home supply centers and spies are
%annihilated when they are on board a fleet that retreats off the board.
%Otherwise, spies may only be removed from the board (there is no difference
%in the game between capturing and killing a spy, but players should feel
%free to delineate between the two states in writing press) immediately
%following the four spy movement seasons.
%
%     B) Spies killed or captured in a given season do not submit written
%spy reports for that season, though their final movement may have been
%made conditional on that spy report.  Players may never know for sure how
%a spy was lost, just as in real life.
%
%     C) Spies are "killed" by being assassinated by other spies.  When a
%spy moves, he or she may attempt an assassination, specifying the nationality
%of spies to be executed if discovered.  Each spy may hunt for only one
%nationality in each of the four seasons.  The following rules and examples
%will govern the adjudication of assassinations:
%
%          a) A spy may attempt an assassination without moving (for instance
%if the target is in the same province).  In this case, any spies of the target
%nationality that end the spy movement phase in that province are assassinated
%with one exception.  If the spy attempting the stationary assassination is
%himself or herself assassinated by a moving assassin then that spy
%assassinates no one in that season (not even a potential target other than the
%one that assassinates that spy).
%
%          b) A spy attempting a moving assassination (may include a move of
%embarkation or debarkation from a fleet) is always successful in assassinating
%spies of the target nationality that finish the spy movement phase in the
%province that the spy moves to.  This makes "mutual assassinations" possible.
%
%          c) Example: French spy is on board a French fleet in the Channel.
%An English spy is in London.  Both powers specify assassination attempts
%against the spies of the other.  If the English spy embarks on the French
%fleet in the channel (remember that embarkation does not require the
%permission of the fleet being boarded) and the French spy doesn't move, the
%French spy is killed, but the English spy isn't (he may be immediateIy
%captured, however, see part D).  If a German spy is also on board and the
%French spy tried to assassinate the German spy, that operation would fail
%as well. If the French spy debarks to London at the same time, the two spies
%"pass in the night" and neither is killed.
%
%     D) Spies are "captured" by opposing armies and fleets.  Players may
%attempt to capture spies, specifying the nationality of spies to be captured
%if discovered.  Each army and fleet on the board may search for spies of one
%nationality in each of the four seasons.  The following rules and examples
%will govern the adjudication of attempts to capture spies:
%
%          a) Players may specify a nationality to be hunted separately for
%each unit or they may issue blanket searches to be applied to all units.
%
%          b) At the end of the spy movement phase, any spies of the
%nationality specified in the same province are captured (for example, if
%the French player specifies a hunt for English spies on their Channel fleet
%in the above example, then the English spy is captured).
%
%          c) Players are informed when they successfully capture an opposing
%spy.  Note that the "owner" of the spy, however, is not informed of the
%capture.  Communication just is cut.  This rule is the only exception to the
%generaI rule that armies and fleets are blind.  It is possible to play the
%game without allowing capture of spies by armies and fleets if one wishes
%to allow freer movement of spies (i.e. RuIe D may be ignored).
%
%7) It is suggested that the game be adjudicated in four separate seasons
%in the following order:
%
%     A) Spring: (for Spring 1901 this sequence is preceded by a spy movement
%phase (no spy reports are necessary) followed by assassinations or captures)
%
%          a) Standard movement by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     B) Summer:
%
%          a) Standard retreats by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     C) Fall:
%
%          a) Standard movement by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     D) Winter:
%
%          a) Standard Autumn retreats by fleets and armies, adjudication
%reported only for one's own units
%
%          b) Standard Winter builds and removals, also applies to spies
%
%          c) Spy report phase, spies collect information
%
%          d) Spy movement phase, spies move according to Rule 4
%
%          e) Spy assassination and capture phase
%
%\medskip
%
%These rules have been produced by Jim Burgess (with helpful comments from
%Bernie Oaklyn and Dick Martin).  Permission is granted to reproduce and use
%these rules without restrictions.  The author would be interested to hear
%any comments and criticisms regarding any aspect of the play of this variant.
%The rules have been deposited with the North American Variant Bank.  They are
%also available from the author for the cost of postage or free by E-Mail.
%
%\bigskip
%
%\centerline{Wing Rules} 
%
%1.A wing unit can move over both land and water spaces. 
%  
%2.A wing unit can support actions in any space adjacent to the one it occupies. 
%   
%3.A wing can give, receive and cut support in the same way as armies and fleets. 
%   
%4.A wing unit cannot convoy or be convoyed. 
%
%5.A wing unit cannot capture an SC, but instead blockades it: 
%        
%\indent\indent 5.1.A blockade occurs when a wing unit occupies the SC of 
%another player in a fall season. 
%        
%\indent\indent 5.2.The player who owns a blockaded SC does not count 
%it when counting his total number of SCs. 
%        
%\indent\indent 5.3.A blockade ends as soon as the wing unit no longer occupies the SC. 
%        
%\indent\indent 5.4.Builds only take place in the winter phase, just as in games without wings. 

\bigskip

\centerline{\bf Diplomacy at TempleCon}

\medskip

\centerline{\it Tournament Director: Jim Burgess}

\smallskip

Game: Diplomacy

Teaching Session: Friday night, 8 PM to 11PM, Regular Diplomacy and/or
Escalation Diplomacy depending on numbers.  Escalation Diplomacy II
can be found at:

\noindent http://www.variantbank.org/results/rules/e/escalation2.htm

We will use the ``five minute teaching guide" that I'll have to hand out as well:

\bigskip

\centerline{Teaching Diplomacy: A 5 minute teaching guide}

\medskip

\centerline{By Edi Birsan}

\smallskip

Players: there are 7 players in the game, one for each of the major
powers in Europe in 1901: England, France, Germany, Italy, Austria,
Russia and Turkey (E-F-G-I-A-R-T)

Turns are divided : Spring and Fall with the game starting in Spring 1901.

You are not bound by anything you say or do with another player.

Players secretly write down their orders for their pieces and then
they are revealed and adjudicated simultaneously.

Abbreviations in order writing are listed on the conference map with S
for Support and C for Convoy.

There is no discussion when players have to retreat or make
adjustments to their positions.

The map is divided into different named spaces. Click here to view a
Standard map.

Spaces can be all water, all land or coastal.

There are 34 supply centers on the map (stars/dots) scattered in 60+
named spaces.

To win you need 18 supply centers at the end of a Fall move.

Players start with 3 or 4 supply centers; these are your home centers
in one of 7 Great Powers.

Two piece types are: Army and Fleet.

For every supply center you own at the end of the Fall you may have
one piece on the board.

If you are short of pieces you build new ones in unoccupied home centers.

If you have more pieces than supply centers you must reduce your
pieces to equal the number of supply centers.

Each piece has equal strength so it moves with a force of 1 plus 1 for
each of its supports.

An Army may move or give support into an adjacent land or coastal province.

A Fleet may move or give support into an adjacent water or coastal province.

Only one piece may be in a space at any time.

Your piece may only do one thing in any turn:

MOVE to an adjacent space or be convoyed from a coastal province to a
coastal province. Fleets in split coasts may only move to adjacent
coastal or water spaces.

SUPPORT to defend another adjacent piece in place if you could have
moved there and it is not moving.

SUPPORT an attack on another piece's space that your unit could move
to; fleets in split coasts may only support moves into a space that
they could have moved on.

CONVOY if a fleet, you can assist in convoying an army.

HOLD (also called Stand) in place doing nothing.

A piece moves only one space at a time to an adjacent space unless you
are an Army being convoyed.

No switching. Units ordered to each other's space do NOT switch
positions unless one is being convoyed.

When giving support you are adding your force to the mover on, or the
holder of, a space.

You may support other peoples pieces.

Bounce: if units of equal support try to move to an unoccupied space
then they BOUNCE and no one gets in.

Supports are CUT by a piece moving on the supporter from other than
the space that the support is directed at.

To force someone out of a space requires that you have greater force
than the piece that is holding the space plus all of its supports to
Hold. A move with one support and a hold with one support bounce.

Cut supports do not count for the determination of who has the most force.

A convoy is a move of an army in a coastal province to another by a
fleet or a chain of fleets in adjacent water spaces.

A fleet in a coastal province may not convoy.

You can not dislodge or cut support of one of your own units. No
'friendly fire'.

Units forced out of their space are dislodged and must RETREAT to an
adjacent space.

You may not retreat to a space that was the site of a Bounce.

You may not retreat via a convoy.

If you can not retreat or decide not to retreat, the piece is disbanded.

A piece that is DISLODGED has no effect on the space from which the
mover came that dislodged it.

A convoying fleet that is dislodged disrupts the convoy and the convoy
does not take place.

Oddities: Kiel and Constantinople have a single coast due to their
waterways (Kiel Canal/Bosphorus). Denmark is a coastal province that
connects with Sweden so armies can go between them but does not divide
itself or the Swedish coast in two. As a coastal province you may not
convoy through Denmark, Kiel or Constantinople.

\bigskip

\centerline{\bf Tournament Schedule:}

\medskip

Round 1: Start 9AM on Saturday, no official stop time, but games
should end by about 4PM

Round 2: Start 6PM on Saturday, no official stop time, but games
should end by about 1AM

Round 3: Start Noon on Sunday, official Random Stop Time between 4 PM
and 5PM, only announced at last Fall turn

Board Assignments: Random to board and country in First Two Saturday
rounds, Top Board plus Random for Final Sunday round.  In third round,
cannot play same country as played in either of first two rounds.
Tournament Director will play if necessary to fill out a board and can
possibly play positions on two boards simultaneously to fill out
boards -- tournament director's scores do not count.  Otherwise first
come/first served, at most, one board may start late if players
assemble late.

{\bf GAME TURN SCHEDULE:} Run games on Central Clock with possible delayed
exception of ``final board" for each round.  20 minutes per Spring and
Fall season with builds and retreats taken out of negotiation time run
as quickly as possible.

Voting on Draws/Game Stop: Comes out of negotiation time, Tournament
Director discretion can be disallowed or delayed for repeated
requests.

Limit on Players: 28 players or four boards (but this could be raised
prior to the event if there is indication that more players are coming
from the advance Diplomacy hobby publicity)

\bigskip

{\bf Scoring System: Detour98f}

This is the scoring system used for most New Zealand tournaments and
New England tournaments.

-- If you survive to 1905 then you get a point (whether you're
eliminated later or not).

-- If you are in the draw at the end of the game then you get a point.

-- You get a point for every supply centre you own.

-- If you are in the outright lead then you get a bonus of the
difference between you and the next best player.

-- If you are first on the board you get 4 bonus points, if you are
second you get 3 bonus points, if you are third you get 2 bonus
points, if you're fourth you get 1 bonus point. (If there's a tie you
get the points for the lower position -ie equal 2nd both get 2 bonus
points)

-- You add each person's points to get a raw score. The next step is to
standardize the game. Divide each person's raw score with the sum of
all the raw scores and then multiply by 100. This generate a
percentage for everyone. So an entire game is worth 100 points and how
much of those points that each person gets is determined points 1-5.

-- If you solo you get 110 points and everyone else gets *nothing*.

-- Tournament Scoring: Total points across the three rounds will be
scored with the last round featuring a Top Board featuring the top
seven players playing the last round based on scores in the first two
rounds.  Scoring on the Top Board will be doubled for Tournament
Scoring purposes.

-- There also will be Best Country awards for each of the seven
countries which can be won by people who play only one round.  For
purposes of Best Country scoring, scores on the Top Board will not be
doubled.

{\it ((Yes, I decided to get off my butt and try to expand the FTF
offerings in New England.
I hope some of you will make it.
Let me know ASAP since the pre-registration deadline is January 17th.
The Convention Organizers will be providing a large Championship Trophy 
and we'll have Seven Best Country Plaques.
See more details at the web site www.templecon.org.
Also, check out the new Face to Face section of the Diplomatic Pouch where
you can put in other tournaments if you're a tournament director.
I haven't been able to negotiate pre-registration group discounts 
other than their standard deal, which is:))}

\medskip

\centerline{\it Welcome to TempleCon Group Pre-Registration!}

If you have a group of friends who you game with and want to take 
TempleCon by storm with them, then our group registration is
made for you. Pre-register with five or more people for the whole 
weekend to get a discount of each of your crew's memberships, 
at only \$25 per person. Group membership to TempleCon 2007 is 
by pre-reg only, so register before January 17th. 

Best of all, if you register as group, the name of your team/clan/store 
will appear on your badges to let people
know who they are going up against. 
You'll also be registered for the TempleCon group leaderboards, to see where you and your 
team stands in TempleCon events. 
We also have a pretty impressive trophy in the works for the team that stands above all others. 

\medskip

{\it ((I'm organizing everyone interested in going to enter as a group.  
Otherwise the cost is} \${\it 40 for the weekend.
So let me know if you're interested in coming.
Also, PrezCon is the next weekend in Virginia, so any long distance travelers should
plan a two-fer!
Any questions, comments, offers to help, let me know!
Tim Richardson is the Tournament Director for PrezCon, which is one of Buz Eddy's 
Grand Prix events and I'm thinking about making TempleCon a Grand Prix event.
See the North American Diplomacy Federation website out at 
/NADF/index.htm for more on the Grand Prix lineup.
You can contact Tim Richardson at timrich of diplom.org and Buz Eddy at 
buzeddy of aol.com.
Mel Nicholson (who is getting married on March 9th back in New Zealand, congrats
Mel!!!) brought us the Detour scoring system to us in New England from New Zealand,
where she originates obviously.
I really like the balance in Detour, it isn't as earthshatteringly stark as my
own scoring system which really demands play out to the bitter end, and it rewards
Supply Centers, but not TOO much.
Plus it's easy to figure.
I am doing it with a Top Board on the last day (which depending on attendance may
not be THAT much of a Top Board) to minimize the fact that people could easily 
figure out who was leading.  
This will put the leaders on the same board on Sunday.
So come on, some of you come and play, if you need crash space or the like, talk to me!!!))}

\vfill\eject

\centerline{\bf {\it THE ABYSSINIAN PRINCE} GAMES SECTION}

\smallskip

``So I called up George and he called up Jim, I said let's make a deal.

He said he'd talk to him.  Gonna start a church where you can save yourself,

You can make some noise, When you've got no choice...

You told me useful things, what people think of me, I guess I should thank you.

It's true, then I agree... I'm all alone, I've got no choice,

I'm all alone, I've got no choice."

From ``Got No Choice" by the incomparable Mark Cutler, from the CD
{\it Mark Cutler and Useful Things}.

\smallskip

\indent If you want to submit orders, press, or letters by E-Mail,
you can find me through the Internet system at
``burgess of world.std.com''.
If anyone has an interest in having an E-Mail address listed so people
can negotiate with you by computer, just let me know.
FAX orders to (401) 277-9904 if you let me know in advance to be sure
the fax machine is set up. 

I am continuing to note cut or failed support orders with a 
small ``s'' instead of a capital ``S''.
This will make it easier on the E-Mailed version of the szine to see
what happened, since the italics don't show there.
The italics DO show on the web page just fine.

\indent Standby lists:

Mike Barno, Dick Martin, Brad Wilson, Jack McHugh, Glenn
Petroski, Steve Emmert, Mark Kinney, Vince Lutterbie, Eric Brosius,
Paul Rauterberg, Bob Osuch, Doug Kent, Sean O'Donnell, Vern Parker,
Heath Gardner, Paul Kenny, and Jeff O'Donnell
stand by for regular Diplomacy.
%I am willing to take over for NMR or start new-Diplomacy.
%Vern Parker
%337 Winter Hill Pl.
%Powell, OH 43065
%VSParker of aol.com
%614-402-5139

Let me know if you want on or off these lists, especially OFF.
Standbies get the szine for free and receive my personal thanks.

\bigskip

\centerline{GAME OPENING INFORMATION} 

\smallskip

We've got lots of openings in the subszines, check them out!!!
Contact Rip Gooch directly at xyropedes of canada.com and try to entice him to return.
Rip has been a bit missing in action lately, but I am assured that he
SHALL return.

Breaking Away starts in this issue!!! 

I am willing to open another new game of REGULAR Diplomacy if there is enough interest!!!
Fred Wiedemeyer, %e,f,r,i,g,t,a
Brad Wilson, and Sean O'Donnell start the list, who would like to join them???

Also, is there any interest in another game of Nuclear Yuppie Evil Empire 
7x7 Dip?
I know it may be getting tired, but I really like it.
We have Karl Schmit and Sean O'Donnell on the list, let's get seven!!
It's FREE!!!

I also am starting a game of the variant I designed, Spy Diplomacy.
Signups for that are now open.
Bruce Edwards and Eric Ozog are signed up.
The rules were published recently, ask to see them if you missed them!!!

John Harrington is offering to guest GM a game of Office Politics.
Any interest in that??
Let me or John know!
Jody McCullough and Bruce Edwards are interested, anyone else?
I think I'm going to drop this one as having no interest.

And since Colonia is over, Harold Reynolds is looking to start something else.

Also, I am going to design some postal rules for Devil Take the Hindmost,
and we have an opening here:
Bruce Edwards, Mike Barno, and Eoghan Barry are signed up.
Postal rules from me will be forthcoming shortly, on my never ending to-do list.
I will get them in SOON!
I'm more likely to get these things started if I see some interest.....
I've GOT to do this now,
Eoghan is getting tired of waiting....

Right now, the other thing going is the Modern
Diplomacy game with Wings.
Sean O'Donnell, Jeff O'Donnell, Steve Koehler, Art Schleinkofer,
Bob Holt, Rick Desper, Alexander Woo, and Dave Partridge are signed up for that.
I will start it when I get a full complement of players, we only need TWO more!
%Sean's list: Britain, Spain, Germany, France, Egypt, Turkey, Russia, Ukraine, Italy, and Poland.

\bigskip

\centerline{\bf TAKING OVER ISHKIBIBBLE'S REGULAR DIPLOMACY GAMES ((NOT))}

\smallskip

Last chance for anyone who was a subber to {\it Ishkibibble} to join any new
game for free, but this is a ONE TIME only offer, get your request in now.
It is going to expire VERY shortly.
Marc Ellinger and Fred Wiedemeyer already have taken us up on this request.
Come on, let me call by name who qualifies
for this deal..... Karl Schmit, John Power, Tim Snyder,
Dave Partridge, Graham Wilson, and Kevin Wilson.
I especially would like to fill the Modern Diplomacy game that Dave Partridge
already is in.
As soon as one more game fills (I'm not counting the new Breaking Away game), 
I'm going to pull this offer.

\bigskip

\centerline{\bf THE PHIL REYNOLDS MEMORIAL: 2006B, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR WINTER 1901 IS JANUARY 13TH, 2007}

\smallskip

\indent {\it Fall 1901}

\noindent AUSTRIA (Burgess): a SER S RUSSIAN f rum-bul(ec), {\it a BUD-rum}, f alb-GRE. 

\noindent ENGLAND (James): a wal-BRE, f ENG C a wal-bre, f nth-NWY.

\noindent FRANCE (Williams): f mid-POR, a BUR S ITALIAN a tyo-mun, a mar-SPA.

\noindent GERMANY (Ellinger): {\it a mun-bur} (d r:boh,sil,ber,kie,ruh,otb), f hol-BEL, 
a kie-DEN.

\noindent ITALY (Crow): a tyo-MUN, a apu-TUN, f ION C a apu-tun.

\noindent RUSSIA (O'Donnell): {\it a UKR-sev}, f rum-BUL(EC), a lvn-MOS, f gob-SWE.

\noindent TURKEY (Wiedemeyer): {\it f BLA-rum, a bul S f bla-rum} (d r:con,otb), 
{\it a ARM-sev}.

\bigskip

\indent {\it Supply Center Chart}

\+ AUSTRIA (Burgess):&TRI,VIE,BUD,ser,gre&(has 3, bld 2)\cr
\+ ENGLAND (James):&EDI,LVP,LON,nwy,bre&(has 3, bld 2)\cr
\+ FRANCE (Williams):&PAR,MAR,spa,por&(has 3, bld 1)\cr
\+ GERMANY (Ellinger):&KIE,BER,den,bel,&(has 2 or 3, bld 2(r:otb) or 1)\cr
\+ ITALY (Crow):&ROM,NAP,VEN,tun,mun&(has 3, bld 2)\cr
\+ RUSSIA (O'Donnell):&WAR,STP,SEV,MOS,bul,swe&(has 4, bld 2)\cr
\+ TURKEY (Wiedemeyer):&ANK,SMY,CON&(has 2 or 3, bld 1(r:otb) or even)\cr
\+ Neutral:&hol,rum&(Total=34)\cr

\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: David Burgess, 101 Laurel Lane, Queensbury, NY  12804

(518) 761-6687, dburgess of glensfallshosp.org

\noindent ENGLAND: Drew James, 3644 Whispering Woods Terrace,
Baldwinsville, NY  13027

(315) 652-1956, kjames01 of twcny.rr.com 

\noindent FRANCE: Don Williams, 27505 Artine Drive, Saugus, CA 91350, 
(661) 297-3947, 

wllmsfmly of earthlink.net or dwilliams of fontana.org (\$5)

\noindent GERMANY: Marc Ellinger, 751 Turnberry Drive,
Jefferson City, MO 65109

ellingermc of aol.com

\noindent ITALY: John Crow, 824 Kinwest Parkway \#101,
Irving, TX  75063, (214) 532-1418

\noindent RUSSIA: Jeff O'Donnell, 1345 Simpson Drive, Hurst, TX  76053
%402 Middle Ave., Elyria, OH  44035-5728,

(440) 322-2920 or (440) 225-9203 (cell, as late as midnight Eastern)

\noindent TURKEY: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  

CANADA  T6T 1N1, (780) 465-6432, wiedem of planet.eon.net 
%cell 780-497-8283; fax 780-468-6432

\bigskip

{\it Game Notes:}

1) You now get the Christmas break to ponder your builds.
Lots more press this time.
Just a reminder, that press in this szine is ``Black", which means anything
can come from anywhere.
Your imagination is the limit, except that my strategy for stopping feuding
(not to say any is going on, as it doesn't seem to be) is that if you abuse
other players in the Black Press, you need to abuse ME as much or more than
anyone else, so I can join in on the FUN!
In other words, keep the abuse coming, we love it, we masochistic Boobishness
GMish Jim-Bobs of the world.

\bigskip
 
{\it Press:}

(FRANCE to GERMANY):  So you know, I will attempt with my friends 
(whoever they are and wherever they may appear from) to make you a 
more attempting target to London than I am.  
Given his knack for backstabbing, I'm sure it won't take long for him 
to come around to my way of thinking ... I'm guessing -- hoping? -- 
there'll be enough blood in the water this season to convince him 
to strike you next season with his shiny new units.

(ENGLAND to FRANCE):  The silence is deafening.  Sorry, but we had no choice.
I assume we will be bouncing this season.  

(FRANCE to ENGLAND):  Obviously, your spies were wrong and I did exactly 
as promised.  I would ask you to have them shot but your 
lack of correspondence or apology puts lie to comments; 
it appears you lie as much in the press as you do in your correspondence.  
En garde, Monsieur ... I'm yours!

(PARIS to ROME):  To the uttermost, mon ami!  I am yours in spirit and steel!

(PARIS to BREST):  Those dreadnaughts in the Channel are bluffing.  
Trust us -- we're from the central government and we're here to help.  
Now get those militia down to the beaches!  Quickly!  Quickly!  
And those bank security guards!  And don't forget the school hall pass monitors!

(F MID to F CHA):  You ARE bluffing, aren't you?

(SYRACUSE to WORLD):  College basketball season has started at last and
football is finally over (at least for bad teams like SU).  My last and only
comment on football is that Rutgers is now SU and SU is now Rutgers.

(LE REPUBLIQUE to SUBLIME PORTE):  Nothing against the Tsar, but nicely done.  
Haven't seen that attack come off so well in years ... or at least not 
since I did it to Burgess!

(BOOB to TAWNY PORT): Serve me up another, that last one was REAL smooth.
I am so smooth that I cannot be surprised like that.

(DON to BOOB):  Did too!  Did too!  Did too!

(DON to MS. CHARLOTTE):  When are you going to wise up and trade you-know-who in 
for a better model?

(BOOB to HANDSOMER MODEL): You know she doesn't read this dreck, ESPECIALLY your dreck.....

(FRANCE to TSAR):  Good luck, my friend.  For what it's worth, 
I appear to be about to keep England and Germany occupied for five or six years.  
You can thank me later.  (I'll be looking for you at the bar ... make mine a pale lager ... )

(BOOB to TSAR): I hope you can get something decent down in the wilds of Texas, do they
still drink that rattlesnake wine that the French send there?

(FIREBALL XL5 to STAR DRECK PRESS):  Oh, c'mon, O'Donnell, not this merde again.  
Keep it up and you'll outdo Boob for mirthless press, and that 
*would* be an accomplishment.  If you are going to take up space 
in this press column, make it amusing, interesting, informative, 
obscure, infamous, or -- failing all else -- scandalously libelous.  
Anything else is mindless Burgesspew.

(BOOB LAMENTS): I resemble that remark....

(BACKFIRE to BASE): Maneuvers Acceptable

(FIREBALL XL5 to ABYSSINIAN PRESS MERCHANT):  Uh, no offense intended.

(BOOB LIGHTS UP THE FIREBALL): Good, if you're not trying to offend me, then 
stop bugging my bud Jeff.
You know the {\it TAP} House Rules!
If you are, then let's have at it, FLAME ON!!!

(FIREBALL XL5 to NOSTROMO, BATTLESTAR GALLACTICA, RED FIVE, THUNDERBIRD 4 AND SERENITY):  
If the Star Dreck press doesn't improve immediately (or sooner) 
I say we phaser his ass right into the next universe.

(FRANCE to BURGESS the YOUNGER): ... and better looking and smarter.  
Stay the course.  We love you over here in Burgundy.  Let's ally and sweep the board!

(PARIS to BASQUE SEPARATISTS): Stay put for a few years, will you?  
We have a lovely bit of property we're willing to turn over to 
you in a couple years -- good for starting your own little country.  
(Be quiet and don't tell anyone, but it's that bit east of 
itain-bray known as ermany-gay.  Shhh!  Mum's the word!)

(BOOB to MALICEFILLED TAPPITES): What we saw last issue does not seem to be the
last we've heard of poor little Malice.
You will have to fill yourselves up yet further.
If anyone is in danger of exploding from too much Malice..... well, tough, here's
more.

(MALICE IN CENTERLAND -- Part Two:  A Simple Desultory Poem):

\noindent Malice eventually decided that being kept by a demon was not as bad 
as it sounded.  First, nothing in his life was different due 
to his new knowledge of his captivity.  
There were no chains, cages, bars, fetters, locked doors -– nothing.  
He still fed Don daily, and they now talked where they had not 
done so before, but that was the only change.  
And as the days went by Malice learned many things.

\noindent One fall day they followed the dirt road into the local woods to read.  
The demon brought a favored strategy article while Malice had the 
latest issue of {\it The Abyssinian Prince}.  
(It had arrived several months late as usual, but Malice didn't mind.)  
They walked for some time before entering a small clearing 
where the dappled sunlight and a tiny rippling stream made 
things pleasant in the waning warmth of the afternoon.  
Don stopped, noticing where the road split on the other 
side of the clearing.  
The demon without thinking began to mutter, as if to himself.

\indent ``Two roads diverged in a yellow wood and, 
sorry I could not travel both and be one traveler, 
long I stood and looked down the one as far as I could to 
where it bent in the undergrowth ... .''  
His voice trailed off.  
Malice, restless and distracted at the first whiff of anything 
literary or uplifting, started thumbing the pages of {\it TAP}.  
``I don't like where this is going,'' said the demon.  
``It's the wrong poem, Malice, but it surely bears witness.  
It has meaning... yes, it does.  
It's about choosing a road or a path or, more correctly, 
choosing one path over another and considering consequences later.  
I think this means it's time, Malice.''
	
\indent ``Time?  Time for what?  We just got here,'' said Malice, 
not looking up from the szine.  
But Don did not answer and, instead, stood in uffish 
thought for a few moments before he started intoning another poem:

\medskip

\centerline{`The time has come, the Demon sighed,}

\centerline{to speak of many things:}

\centerline{Of Dots –- and Blocks –- and Powers Great –-}

\centerline{Of Allies -– Foes -– and Kings –-}

\centerline{And whether you should trust at all}

\centerline{In tales a demon sings.'}

\smallskip

\centerline{`In ancient years across the sea}

\centerline{A foolish empire sought}

\centerline{To wield great power, quite arcane,}

\centerline{Against the foe they fought –-}

\centerline{They sent the Maltese Dipcon out}

\centerline{Not knowing what they'd wrought!'}

\smallskip

\centerline{`The galley sailed upon the sea}

\centerline{And in it in a trunk –-}

\centerline{A guardian demon with the bane –-}

\centerline{Unless the legend’s bunk –-}

\centerline{But tempest tossed the galley was}

\centerline{And all aboard were sunk.'}

\smallskip

\centerline{`Or so it's told' –- the Demon said –-}

\centerline{`And yet I surely know}

\centerline{That there, in fact, was one life spared}

\centerline{From a watery grave below.}

\centerline{For he arrived upon the shore}

\centerline{With demon -– me! –- in tow.'}

\smallskip

\centerline{`And Cabal Harem was his name –-}

\centerline{Magus of Malta old.}

\centerline{But other names he had as well –-}

\centerline{Though none of them are told –-}

\centerline{Except in nasty secret rites,}

\centerline{Where souls are bought and sold.'}

\smallskip

\centerline{` ``Remove the amulet you wear''}

\centerline{The Magus said to me}

\centerline{``Hand over what I'm asking for –-}

\centerline{And then I'll go –- you'll see.}

\centerline{I want the tablet and the blocks –-}

\centerline{That bane from you I'll free.'' '}

\smallskip

\centerline{`I guard this ancient artifact}

\centerline{And so I answered ``No!''}

\centerline{As quick as lightning did he strike –-}

\centerline{And landed the first blow –-}

\centerline{He stomped real hard with both his feet}

\centerline{And really crushed my toe!'}

\smallskip

\centerline{Our battle then was quickly joined –-}

\centerline{With Fists -– and Feet –- we hit}

\centerline{But Cabal Harem had to win –-}

\centerline{So ass with teeth he bit –-}

\centerline{And while I howled in agony}

\centerline{He snatched the amulet!'}

\smallskip

\centerline{`And then these words he spoke aloud –-}

\centerline{Quote -– ``Idiom clop non! –-}

\centerline{Domino cop nil!'' he said and}

\centerline{The amulet was gone* –-}

\centerline{And in it's place –- I kid thee not –-}

\centerline{The Diplonomicon!'}

\smallskip

\centerline{`He gazed in awe at the stone blocks}

\centerline{Then grabbed them for to hoard –-}

\centerline{And while he was distracted thus}

\centerline{I likewise grabbed the board!}

\centerline{Then beating hard my mighty wings –-}

\centerline{Above Cabal I soared.}

\smallskip

\centerline{`Enraged! –- Insane!  He screamed aloft –-}

\centerline{``I'll see you back in Hell!''}

\centerline{And summoning his fearful gifts}

\centerline{He cast an evil spell}

\centerline{Encasing me in walls of glass –-}

\centerline{A crystal prison cell!'}

\smallskip

\centerline{``And held there fast –- in glass entrapped –-}

\centerline{I plunged into the sea}

\centerline{We grew quite small -– bewitched and all –-}

\centerline{The amulet and me –-}

\centerline{The board remained within my grasp}

\centerline{A partial victory.'}

\smallskip

\centerline{`For reasons that the Author knows –-}

\centerline{Yet will not share his heart –-}

\centerline{Cabal Harem grabbed the stones}

\centerline{And with archaic art}

\centerline{He disappeared from this true Earth –-}

\centerline{The Blocks and Board -– apart!'}

\smallskip

\centerline{`Thus was the Diplonomicon}

\centerline{Ripped in twain -– Asunder! –-}

\centerline{Re-gathered only –- says the Myth –-}

\centerline{By fantastic blunder}

\centerline{Of Hero-Fool in Centerland –-}

\centerline{Who is that, I wonder?'}

\smallskip

\centerline{`So, Malice, there you have the Tale –-}

\centerline{Save one small fact you'll rue –-}

\centerline{Genetically you fall in line}

\centerline{To make the Myth come true –-}

\centerline{From Cabal Harem’s loins did all}

\centerline{Your DNA ensue!}


\centerline{`When first I spoke –- when first I spoke –-}

\centerline{A lie –- a demon’s story?}

\centerline{Or is it not a lie at all,}

\centerline{But just the truth grown hoary?}

\centerline{And will you be the Hero-Fool,}

\centerline{Stumbling into glory?}

\smallskip

\centerline{`Our metre's run –- this poem’s done –-}

\centerline{The Readers I do bore}

\centerline{(For if you listen carefully}

\centerline{I think you'll hear them snore)}

\centerline{But please don't go -– now you should know}

\centerline{It's just three stanzas more.'}

\smallskip

\centerline{`When while you read beneath a tree –-}

\centerline{Brain-dead from Burgess press}

\centerline{A Mutant Butler running by –-}

\centerline{In bright red waistcoat dressed –-}

\centerline{Will stop his run and say ``I'm late''}

\centerline{Then run on quite distressed.'}

\smallskip

\centerline{`That's when you'll know it's time to go –-}

\centerline{Awake or deep in dream –-}

\centerline{In either case you could give chase}

\centerline{Or just let seeming seem.}

\centerline{Restore the Diplonomicon –-}

\centerline{Or just read Jim-Boob's szine?'}

\smallskip

\centerline{`Your journey's start is near at hand –-}

\centerline{And it will take some thought}

\centerline{To not too deep or fast become}

\centerline{In paradoxy caught –-}

\centerline{The way to Centerland is down}

\centerline{The North Atlantic Dot.'}

\medskip

\noindent{\it (*  It didn't really disappear.  
It was stuck to the underside of the tablet and 
Monde the Demon found it later.  No, really ...trust us on this one ,eh?  The Author.)}

\noindent Don ended his lengthy recital and, pleased with himself, 
looked over to Malice whose eyes –- alas –- had rolled 
completely back into his head under the epic onslaught.  
The demon slapped Malice's cheeks a few times, and momentarily, he came around.

\indent ``Merde!  You ever do that again and –- demon or not –- I'll kick your horned ass.''

\indent ``Sorry, Malice,'' said Don, sheepishly, ``but you must understand 
what's at stake.  The Maltese Dipcon –- the Diplonomicon –- 
is a weapon of immense and catastrophic power.  
It was forged deep in the volcanic fire of ancient Malta by 
Archbale All-Man, a Grand Magus and Master of the Tarot.  
The tablet –- the board, that is –- and blocks are manifestations 
of the dark forces of the Tarot.  
They don't just augur the fate and doom of humanity but –- in the wrong hands -– 
they create it.  The 22 starting positions of the stones on the 
tablet represent the 22 cards of the Major Arcana.  
They portray by mythic symbol the virtues and defects of Humankind.  
The 112 stones, 56 of each in two shapes divided into seven colors, 
represent the 56 cards of the Minor Arcana.  
They play out man's unfolding doom.''
	
\indent ``You done yet?'' asked Alex, ``Because, apart from boring the 
piss out of me, you're getting more than a little weird with all this 
`major' and `minor' Arkansas crap.''
In response, the demon silently removed from his neck the amulet and, 
dropping it to the ground, began chanting:

\medskip

\centerline{``Imido clop non, lipid mono con}

\centerline{Monic idol plo, nomic nil do po}

\centerline{Domino con lip, omni colon dip!''}

\medskip

\noindent Alex felt rather than heard the low, slow thrum 
as the land beneath his feet began to writhe and change as 
the demon's chant trailed off.  The tiny stream widened to a brook.  
Inexplicably, he found himself nearly asleep under a nearby 
tree beside the brook, {\it TAP} in his lap, fluttering slightly 
in the cooling breeze.  The landscape had shape-shifted and 
warped in all directions at once and, suddenly, nothing was the same.
	
\indent ``The time for the Dipcon to be re-gathered is upon us, 
Malice,'' spoke Don lowly, almost to himself.  
``For better or worse, you are the Hero-Fool foretold in legend 
and this task falls to you, unbidden.  It is your quest, and yours alone.  
Sort of a major `oopsie' if you ask me, but there it is.  
Good luck, you’re gonna need.  We’re all gonna need it.''  
The breeze muffled his words, kept Malice from hearing the last of them.
	
\indent ``It's a good thing,'' said Don as he slowly vanished, 
his wings disappearing last.

\bigskip

\centerline{\bf SPIRALS OF PARANOIA: 2005A, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SUMMER 1905 IS JANUARY 13TH, 2007}

\smallskip

\noindent {\bf THE DUE DATE FOR FALL 1905 IS FEBRUARY 3RD, 2007}

\smallskip

\indent {\it Spring 1904}

\noindent AUSTRIA (Rauterberg): {\it a BUD-gal}, a VIE S a tri-tyo, 
{\it a SER-tri, a boh s a tri-tyo} (d ann), 

a nap-ROM, {\it a TRI-tyo}, f ion-TYH.

\noindent ENGLAND (Wiedemeyer): f mid-SPA(SC).

\noindent FRANCE (Tretick): a par-GAS, f bre-MID, f edi-YOR, a lvp-WAL, 
f IRI S f bre-mid.

\noindent GERMANY (Ozog for Tallman): a kie-BER, a ber-SIL, a sil-BOH, 

a HOL h, a MUN S a sil-boh, f NWY h, a mar-PIE, a pic-BUR, f NTH h.

\noindent ITALY (O'Donnell): {\it a TYO-tri}, a VEN S a tyo-tri, f adr-APU.

\noindent RUSSIA (Sundstrom): a ukr-RUM, a SEV S a ukr-rum, {\it a GAL-bud}, a LVN h.

\noindent TURKEY (Biehl): f con-BLA, f AEG S f gre, 
f GRE S f eas-ion, f eas-ION.

%\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Rauterberg):&TRI,VIE,BUD,ser,bul,rum,nap&(has 7, even)\cr
%\+ ENGLAND (Wiedemeyer):&LON&(has 4, rem 3)\cr
%\+ FRANCE (Tretick):&PAR,BRE,spa,por,lvp,edi&(has 4, bld 1, PLAYS ONE SHORT)\cr
%\+ GERMANY (Ozog/Tallman):&KIE,BER,MUN,hol,den,bel,swe,&(has 6 or 7, bld 3(r:otb) or 2)\cr
%\+ &\enskip mar,nwy \cr
%\+ ITALY (O'Donnell):&ROM,VEN,tun&(has 4, rem 1)\cr
%\+ RUSSIA (Sundstrom):&WAR,STP,SEV,MOS&(has 4, even)\cr
%\+ TURKEY (Biehl):&ANK,SMY,CON,gre&(has 3, bld 1)\cr
%\+ Neutral:&none&(Total=34)\cr
%
\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Paul Rauterberg, 3116 W.~American Dr., 
Greenfield, WI  53221, 

(414) 281-2339 (E-Mail)  trauterberg of wi.rr.com

\noindent ENGLAND: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  CANADA  T6T 1N1, 

(780) 465-6432, wiedem of planet.eon.net 
%cell 780-497-8283; fax 780-468-6432

\noindent FRANCE: Buddy Tretick, 5023 Sewell's Pointe Way,
Fredericksburg, VA  22407, (540) 898-3386

cell (540) 226-5571 (E-Mail) berniebuddy32 of aol.com

\noindent GERMANY: Terry Tallman, PO Box 782, Clinton, WA  98236,
(360) 331-5698 (\$2) 

terryt of whidbey.net

\noindent GERMANY: Temporary Standby is Eric Ozog, PO Box 1138, Granite Falls, WA  
98252-1138,

(360) 691-4264, ElfEric of Juno.com

\noindent ITALY: Jeff O'Donnell, 1345 Simpson Drive, Hurst, TX  76053
%402 Middle Ave., Elyria, OH  44035-5728,

(440) 322-2920 or (440) 225-9203 (cell, as late as midnight Eastern)

\noindent RUSSIA: Matt Sundstrom, 1760 Robincrest Lane South, Glenview, IL  60025, 
(847) 729-1882, 

Matt.Sundstrom of bbdoch.com or mattandzoe of earthlink.net

\noindent TURKEY: John Biehl, \#8 -- 11530 84th Avenue, Delta, BRITISH COLUMBIA,
V4C 2M1  CANADA, 

(604) 816-0460 (cell) (\$7); jrb of dccnet.com

\bigskip

{\it Game Notes:}

1) Terry is still having some medical problems, 
Eric Ozog is continuing to
negotiate and submit orders for Terry.
Eric originally brought Terry into the Diplomacy hobby all those many
years ago, and so I'm glad he's agreed to do this.

2) Note that Jeff O'Donnell has changed his postal address, at least temporarily.
And you should use his cell phone number above if you want to call him, I think.

3) Since we have the long Christmas break deadline coming up and there are
no Summer adjustments, if everyone would like to submit Fall orders by
January 13th, I can go ahead with that turn at that time.
Let me know.

\bigskip
 
{\it Press:}

(FRANCE to ENGLAND):  Okay, be a pest.  But you will not even slow down my 
advance.  That is the problem with starting the game insisting this and that.  I 
never could bend over for tyrants.

(BOOB SALUTES FRENCH TACTICAL PROWESS): The move for England indeed would have been to 
move to Gascony.  The way for England now is dire.

\bigskip

\centerline{\bf FLIP FLOP: 2003G, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR WINTER 1908 IS JANUARY 13TH, 2007}

\smallskip

\noindent {\bf THE DUE DATE FOR SPRING 1909 IS FEBRUARY 3RD, 2007}

\smallskip

\indent {\it Fall 1908}

\noindent AUSTRIA (Wiedemeyer): f adr-VEN, a BUD S a tri, a gal-WAR,  
a UKR S a sev, 

{\it a sev s a ukr} (d r:mos,otb), {\it a TRI s a bud}.

\noindent ENGLAND (Schmit): a BEL h, a kie-HOL, 
{\it f MID-spa(sc), a RUH-kie},

{\it f NTH s a bel}, f NWG S f nth, f HEL S a kie-hol.

\noindent FRANCE (Jeff O'Donnell): {\it a BUR-ruh, a PIC-bel, f SPA(SC)-mid, 
a GAS-spa}.

\noindent GERMANY (Sundstrom): a ber-KIE, {\it f hol s FRENCH a pic-bel} (d ann), 
f SWE S a den, a DEN S a ber-kie,
 
a NWY S f swe, a MUN S a ber-kie, {\it f SKA-nth}.

\noindent TURKEY (Levinson): a arm-SEV, f aeg-ION, a BUL S a rum, f APU S f ion-adr, 
f tyh-NAP, {\it a ALB-tri}, 

f ion-ADR, f BLA S a arm-sev, a RUM S a arm-sev, a SER S a alb-tri.
%builds: F Smy   A Con

\bigskip

\indent {\it Supply Center Chart}

\+ AUSTRIA (Wiedemeyer):&TRI,VIE,BUD,ven,mos,war&(has 5 or 6, bld 1(r:otb) or even)\cr 
\+ ENGLAND (Schmit):&EDI,LVP,LON,por,bel,hol&(has 7, rem 1)\cr
\+ FRANCE (Jeff O'Donnell):&PAR,MAR,BRE,spa&(has 4, even)\cr
\+ GERMANY (Sundstrom):&KIE,BER,MUN,den,swe,stp,nwy&(has 6, bld 1)\cr
\+ TURKEY (Levinson):&ANK,SMY,CON,bul,sev,ser,gre,&(has 10, bld 1)\cr
\+ &\enskip tun,rom,rum,nap \cr
\+ Neutral:&none&(Total=34)\cr

\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  CANADA  T6T 1N1, 

(780) 465-6432, wiedem of planet.eon.net 
%cell 780-497-8283; fax 780-468-6432

\noindent ENGLAND: Karl Schmit, 1509 O'Keefe Road, DePere, WI  54115, (920) 338-8402, 

diplomacy of new.rr.com (\$3)

\noindent FRANCE: Jeff O'Donnell, 1345 Simpson Drive, Hurst, TX  76053
%402 Middle Ave., Elyria, OH  44035-5728,

(440) 322-2920 or (440) 225-9203 (cell, as late as midnight Eastern)

\noindent GERMANY: Matt Sundstrom, 1760 Robincrest Lane South, Glenview, IL  60025, 
(847) 729-1882, 

Matt.Sundstrom of bbdoch.com or mattandzoe of earthlink.net

\noindent ITALY: Don Williams, 27505 Artine Drive, Saugus, CA 91350, 
(661) 297-3947, 

wllmsfmly of earthlink.net or dwilliams of fontana.org

\noindent RUSSIA: Sean O'Donnell, 1044 Wellfleet Drive, Grafton, OH  44044,
(440) 926-0230, 

sean\_o\_donnell of hotmail.com

\noindent TURKEY: Alexandre Levinson, Beeklaan 504, 2562BP Den Haag
THE NETHERLANDS, don't need phone, 

levinson7 of hotmail.com (\$5)

\bigskip

{\it Game Notes:}

1) Note Jeff's new temporary postal address above.
You also might want to use the cell phone number, as a result, if you 
want to call him.

\bigskip

{\it Press:}

(SEAN--JEFF): It's midgame for you while it's post game for me. That's right 
blame it on the country Stosh (as I stick my tongue at you). I thank you for 
your compliment, but I'd rather have been able to out survive you.

(GERMANY): A fine mess in and around the Bight.  I'm really intrigued as to how we guessed.

(SEAN--JEFF): You know Jeff. I would love to be able to get you into the 
Nucleur Madd Yuppie game or however it's spelled. It is free, and I think 
that you'd have a blast. ;)
{\it ((Thanks, Sean, I'd love to get it started as well.
It is free, and easy to play.
You don't even have to negotiate if you don't want to, that's what makes it a Yuppie game....))}

\bigskip

\centerline{\bf I CAN'T FIND MY MONEY!: 2001F, Regular Diplomacy}

\smallskip

\noindent {\bf TWO WAY DRAW BETWEEN AUSTRIA AND GERMANY IS DECLARED!}

%\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Parker):&TRI,BUD,VIE,ser,rum,nap,&(has 15, bld 1)\cr
%\+ &\enskip war,mos,sev,ven,rom,bul,gre,smy,con,tun\cr
%\+ FRANCE (Kent):&PAR,BRE&(has 4, rem 2)\cr
%\+ GERMANY (Wilson):&KIE,BER,hol,den,bel,MUN,swe,&(has 12, bld 2 (PLAYS ONE SHORT))\cr
%\+ &\enskip nwy,mar,edi,lon,spa,por,stp,lvp\cr
%\+ TURKEY (Miller):&ANK&(has 2, rem 1)\cr
%\+ Neutral:&none&(Total=34)\cr
% 
\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Vern Parker, 337 Winter Hill Place, Powell, OH 43065,
(614) 402-5139

VernDip of aol.com is preferred

\noindent ENGLAND: Mark Kinney, 4830 Westport Road, Apt D,
Louisville KY  40222

alberich of iglou.com

\noindent FRANCE: Doug Kent, 11111 Woodmeadow Pkwy \#2327, Dallas, TX  75228

dougray30 of yahoo.com 

\noindent GERMANY: Kevin Wilson, 18623 Santa Maria Drive, Baton Rouge, LA  70809,
225-751-3857,

ckevinw1 of cox.net

\noindent ITALY: Formerly was Heath Gardner, metaphorman of gmail.com

\noindent ITALY: Mike Barno, 634 Dawson Hill Road, 
Spencer, NY 14883 

mpbarno of lightlink.com 

\noindent RUSSIA: Rick Desper, 

rick\_desper of yahoo.com

\noindent TURKEY: Tim Miller, 258 New Mark Esplanade, Rockville, MD 20850,

tim of webjudge.net

\noindent GM: Jim-Bob Burgess, 664 Smith Street, Providence, RI  02908-4327,
$+$1 401-351-0287

burgess of world.std.com

\bigskip

{\it Game Notes:}

1) The GA-GA draw is now accepted by everyone, so the game is over with the two way draw.
I did have orders in hand from both Germany and Austria codifying the 17-17 split.
You can send endgame statements any time now.
I have some comments in hand from Kevin Wilson that he wrote three or four months ago
which I will use next issue.
Thanks to everyone who played!

\bigskip

{\it Press:}


\bigskip

\centerline{\bf SECRETS: 1999D, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR FALL 1922 IS JANUARY 13TH, 2007}

\smallskip

\indent {\it Summer 1922}

\noindent ENGLAND (Kent): R a ruh-BEL; has f ENG, a GAS, 
a BEL, f MID, f NTH, f HOL, f POR.

\noindent FRANCE (Sasseville): has f MAR, f SPA(SC), a BUR.     
%standing orders, yes to ANY draw
                                             
\noindent GERMANY (Barno): has a SER.
%votes yes to FREGT, no to EFRT 
%vote YES to FREGT draw

\noindent RUSSIA (Parker): has f NWY, f NWG, a WAR, a DEN, a BER, 
f HEL, a KIE, a LVN.
%F Nwy-Nth 
%F Nwg-Edi
%A War H
%A Den H
%A Ber-Kie
%A Kie-Hol
%F Hel Sup A Kie-Hol
%A Liv H

\noindent TURKEY (Linsey): has a SMY, f AEG, a BUL, 
a BOH, a SIL, 

f WES, a GAL, f GOL, a RUH, a TRI, f NAF, 
a TYO, f PIE, a MUN.
%F Wes S F Lyo
%F NAf S F Wes
%F Lyo S F Wes
%F Pie S F Lyo
%A Ruh S RUSSIAN A Kie-Hol
%A Mun S A Ruh
%A Tyo S A Mun
%A Sil S A Mun
%A Boh S A Mun
%A Tri H
%A Bul S GERMAN A Ser-Gre
%A Gal S A Sil
%F Aeg-Ion
%A Smy-Con
%Build A Ank
%Build F Smy (if I get a second build)

%\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ ENGLAND (Kent):&LON,LVP,EDI,bre,por,bel,hol&(has 7 or 8, even(r:otb) or rem 1)\cr
%\+ FRANCE (Sasseville):&PAR,MAR,spa&(has 3, even)\cr
%\+ GERMANY (Barno):&con,bul&(has 1, PLAYS ONE SHORT)\cr
%\+ RUSSIA (Parker):&MOS,STP,nwy,swe,den,ber,WAR,kie&(has 7, bld 1)\cr
%\+ TURKEY (Linsey):&ANK,SMY,rum,gre,&(has 15, rem 1)\cr
%\+ &\enskip bud,nap,ven,tun,sev,rom,tri,vie,ser,mun \cr
%\+ Neutral:&none&(Total=34)\cr
%
\bigskip

\indent {\it Addresses of the Participants}

\noindent ENGLAND: Doug Kent, 11111 Woodmeadow Pkwy \#2327, Dallas, TX  75228

dougray30 of yahoo.com 

\noindent FRANCE: Roland Sasseville, Jr., 38 Bucklin Street, Pawtucket,
RI 02861, (401) 481-4280 (\$0)

roland6 of cox.net  

\noindent GERMANY: Mike Barno, 634 Dawson Hill Road, 
Spencer, NY 14883, (607) 589-4906 

mpbarno of lightlink.com 

\noindent RUSSIA: Vern Parker, 337 Winter Hill Place, Powell, OH 43065,
(614) 402-5139

VernDip of aol.com is preferred

\noindent TURKEY: Bruce Linsey, PO Box 234, Kinderhook, NY
12106

GonzoHQ of aol.com

\bigskip

{\it Game Notes:}

1) The concession to Turkey fails.

\bigskip

{\it Press:}
 


\bigskip

\centerline{\bf CAST NO SHADOWS: Breaking Away, Designer's Rules}

\smallskip

\noindent {\bf NEW GAME START, GET ME YOUR RIDERS AND CARDS!!}

\smallskip

Players are: David Partridge, Brendan Whyte, Alexander Woo, Andy York (who is replacing
Eric Martin who had to drop), Rick Desper, and Tom Howell.
Rules are at:

\noindent http://devel.diplom.org/DipPouch/Postal/Zines/TAP/Tinamou/rules/BreakingAway.htm
%\smallskip
%
%\noindent {\bf GAME OVER -- DUE DATE FOR ENDGAME STATEMENTS IS SEPTEMBER 10TH, 2005}
%
%\smallskip
%
%--F--I--N--A--L-- --F--I--N--I--S--H-- --L--I--N--E--
%--S--P--R--I--N--T-- --F--I--N--I--S--H-- --L--I--N--E--
%
%\centerline{\it Turn 16}
%
%\smallskip
%
%\+ Finished:                &Pebble, Homer, Spades (12), Clay (10), El Vez (8),  \cr
%\+                          &\indent Carl Sagan (6), James (4), Paige (2)    \cr

%--F--I--N--A--L-- --F--I--N--I--S--H-- --L--I--N--E--

%\+ 120 (replenish with a 3) &Spades  \cr
%\+ 119 (no replenishment)   &Empty   \cr
%\+ 118 (replenish with a 3) &Clay, El Vez   \cr
%\+ 117 (replenish with a 5) &Carl Sagan, James   \cr
%\+ 116 (replenish with a 7) &Sand, Paige  \cr
%\+ 115 (replenish with a 9) &Hearts, Geri Lee Lewis, Johnny Peso   \cr
%\+ 114 (replenish with a 12)&Marge   \cr
%\+ 113 (replenish with a 13)&Franklin  \cr
%\+ 112 (replenish with a 14)&Wade, Diamonds   \cr
%\+ 111 (no replenishment)   &Empty     \cr
%\+ 110 (replenish with a 3) &Frederick, Clubs, Edmond   \cr

\bigskip
%Sprint Points: 10,8,6,5,4,3,2,1 (final are just double these)
%Movement Order: A/B/C/D; highest card played that turn; highest card in hand

%\indent {\it Addresses of the Participants -- Their Team and Their Cards}

%\smallskip

%\noindent TEAM 1 (Rick Desper): rick\_desper of yahoo.com (55 points, efficiency
%score 13.7\%)

%Team Name: Team Springfield

%\+ A: Homer Simpson &&Finished \cr
%\+ B: Marge Simpson &&(3) 3 3 12  \cr
%\+ C: Bart Simpson  &&Sulks \cr
%\+ D: Lisa Simpson  &&(4) 3 5 6 \cr

%Total Replenishments: $22+63+46+13+15+29+21+17+25+17+18+33+32+10+13+18 = 402$
                
%\smallskip

%\noindent TEAM 2 (Bruce Edwards): kactusjak of ntlworld.com (8 points, efficiency
%score 2.3\%)

%Team Name: Last Again

%\+ A: Zedd   &&(3) 3 3 3 \cr
%\+ B: Omega  &&(4) 3 3 3 \cr
%\+ C: Paige  &&(13) 5 10 7 \cr
%\+ D: James  &&(16) 3 6 5 \cr

%Total Replenishments: $16+37+29+25+12+13+26+24+21+18+16+15+30+23+32+18 = 355$        
   
%\smallskip

%\noindent TEAM 3 (Tom Howell): off-the-shelf of olympus.net (31 points, efficiency
%score 8.0\%)%360-928-9698

%Team Name:  The Soils; Manager:   Boulder

%\+ A:   Clay    &&(7) 3 5 3 \cr
%\+ B:   Silt    &&(4) 4 4 4  \cr
%\+ C:   Sand    &&(10) 3 3 7 \cr
%\+ D:   Pebble  &&Finished \cr

%Total Replenishments: $17+62+63+25+12+13+12+29+27+21+17+31+15+15+13+14 = 386$   
               
%\smallskip

%\noindent TEAM 4 (Dennis Menear): dmenear of wirefire.com (9 points, efficiency
%score 2.2\%)

%Team Name: The Firm

%\+ A: Edmond    &&(5) 3 3 3 3  \cr
%\+ B: Franklin  &&(10) 4 4 13 \cr
%\+ C: Frederick &&(4) 4 3 3 \cr
%\+ D: Wade      &&(8) 3 3 14 \cr

%Total Replenishments: $12+28+32+35+38+25+24+17+29+21+15+26+21+35+26+33 = 417$

%\smallskip

%\noindent TEAM 5 (David Partridge): rebhuhn of rocketmail.com (36 points, efficiency
%score 8.5\%)

%Team Name: It's In The Cards; Manager: The Joker

%\+ A: Spades   &&(7) 3 3 3 3 \cr
%\+ B: Hearts   &&(6) 2 3 9 \cr
%\+ C: Diamonds &&(8) 5 6 14 \cr  
%\+ D: Clubs    &&(5) 3 3 3 \cr
           
%Total Replenishments: $17+55+51+25+30+24+26+20+34+15+15+25+18+20+22+29 = 426$ 

%\smallskip 

%\noindent TEAM 6 (Karl Schmit): diplomacy of new.rr.com (17 points, efficiency
%score 3.6\%)

%Team Name: 25 Dollar Quartet

%\+ A: Carl Sagan      &&(15) 3 9 13 5 \cr
%\+ B: El Vez          &&(15) 13 10 3 \cr
%\+ C: Geri Lee Lewis  &&(13) 9 9 9 \cr
%\+ D: Johnny Peso     &&(13) 1 8 9 \cr

%Total Replenishments: $12+37+22+44+16+27+28+27+32+39+33+20+24+39+49+26 = 475$
%Team Name: Time Will Tell -- Tom Howell
%
%You need a manager?  I'll have to think on that one...  <g>
%
%Riders:
%
%Afteryule:   1, 5, 10, 14
%Blotmath:    4, 6, 15
%Overlithe:   3, 7, 10
%Winterfilth: 2, 8, 6

\bigskip

{\it Game Notes:}

1) The rules are on the {\it TAP} website in the {\it Tinamou} section.
Ask if you have any questions.
Send in your riders and their starting cards NOW!!!
Your A rider can have three or four cards that need to add up to 30,
your B rider three cards adding up to 25, your C rider three cards
adding up to 20, and your D rider three cards adding up to 16.
You also need to name your team, and can have a team captain if you want.

%Up above in parentheses is the card you played to get to where you are
%in the field.  The replenishment card is the last card in your list.
%Be careful to note that the card you played (the one in parentheses) is
%not available for you, for next turn.
%Just for fun, I'm going to keep track of total replenishment, by turn, which is a 
%rough measure of how the teams are doing.
%Of course, it is lining up to get across the sprint and final lines in the
%right places that really counts.
%We can calculate an ``efficiency score" later, which will be the ratio
%of scoring points per replenishment.
%If I'm predicting how the future of this will come out, a 10\% score will
%be really tremendous for this measure.

2) The name of this new game is CAST NO SHADOWS, a great name for a pelaton based
game.
But of course, this is a very excellent Mekons song. 

\bigskip

{\it Press:}


\bigskip

{\it Personal Note to You:}

\vfill\eject
\end
