\nopagenumbers 
\font\twelverm=cmbx12 at 12pt
\centerline{\bf\twelverm THE ABYSSINIAN PRINCE \#305}
\line{\hfil September 11, 2006}    
\smallskip                                                    
\settabs 3 \columns 
\beginsection

\medskip

Produced by Jim Burgess, 664 Smith Street, Providence, RI 02908-4327  USA,
(401)351-0287 
 
\noindent Accessible through Internet at burgess of world.std.com (all E-Mail
addresses are reported in this format, replace the `` of '' with ``@''; if you 
bounce try sending to me from another account. 
Some of you have been getting bounced messages from
my ISP's spam protection, if that happens to you, USE my backup E-Mail
at jfburgess of gmail.com!!!  Don't complain that my E-Mail keeps bouncing
without forwarding the bounced message to that address.
Then I can forward it to the ISP help to get it dealt with.
 
\noindent Web Page Address: http://www.diplom.org/DipPouch/Postal/Zines/TAP/index.html

\bigskip

Where were YOU five years ago on September 11th, as most of you remember, I was up
in a plane.... stuck in Chicago for the longest three days of my life, but nothing
like the experience of anyone at Ground Zero.  
Best wishes to everyone, and for true Peace on Earth.

The szine is late again, so I pushed deadlines back a week.
Lots of orders coming in for the new Phil Reynolds Memorial game, good start!!!
Let's get some of the other games started.
We have {\it Tinamou} and {\it By the WAY} issues in the postal version and on the web.
JOIN the 23 TUNES GAME!!!  SEND ME THREE TUNES AND COMMENTARY!!!

I expect ALL players to be signed up on the E-Mail notification list for the szine,
see below.
Some of you have been complaining about this, but it is up to you to get on this list,
it's easy, come ask me if you have trouble.
We have another exciting issue of {\it By the Way} in this issue if everything
is going as planned.
We're making progress on starting new games, help fill things up, see below for more.
The new regular Diplomacy game has started, Spring 1901 results in the next issue!!!

\bigskip

%Dave Partridge's unlisted phone number 603-672-2879 -- probably corrected!!!
%Tinamou players: Schwarzschild:  Graham Wilson (NO 
%but E-mails: grahamaw of home.com (or gwilson of dvnet.com)),
%Berry Renken, Phil Reynolds, Heath Gardner
%Copernicus:  Warren Goesle, Heath Gardner, Art Schleinkofer, Bruce Reiff,
%Eric Brosius, Bob Dowrey
%Tour De Farce:  Jim Burgess, Eric Brosius, Warren Goesle, Sara Reichert,
%Phil Reynolds, Rick Desper
%Milk and Cookies: Jim Burgess, Warren Goesle, Sara Reichert, Phil Reynolds,
%Rick Desper, Richard Weiss, John Schultz
%Who's Your Buddy:  Sara Reichert, Phil Reynolds, Art Schleinkofer, 
%Brad Wilson, Rick Copeland, Karl Muller

The postal sub price is still
\$1.50 per issue in the US and Canada,
with double that for other foreign subbers(or \$3.00 per
issue sent airmail).
Players in current games and standbys will
continue to get the issues for free, and future game starts 
(except for Nuclear Yuppie Evil Empire Diplomacy, which is free) cost 
\$20.00 (\$15.00 for a life of the
game subscription and \$5 for the NMR Insurance.
Anyone may play in subszines 
for free and just jack up the issue page count. 
See the revised game start announcements below!

Check out the connections in the Diplomatic Pouch with all of
the information you need to play Diplomacy on the Internet at:
http://www.diplom.org/DipPouch/

I also have taken over the Postal port/DipPouch/Postal

\noindent and {\it TAP} on the web is there at:
http://www.diplom.org/DipPouch/Postal/Zines/TAP/index.html

where the szine resides in html format. 
Presently, issues from \#190 to the current issue
are there, and I will be updating the back issues gradually someday. 
Also, check out Stephen Agar's more extensive efforts at:
http://www.diplomacy-archive.com and http://www.diplomacy.co.uk
 
Peter Sullivan's subszine is out of stasis, and all the
back issues can be accessed via :

http://www.burdonvale.co.uk/octopus/index.html.

Peter is now clearly back and appears in most issues!
Rip Gooch and Dave Partridge had been picking up the choo-choo
game slack,
but Rip also has been missing in action lately, I don't have an update but he
and Dave Partridge communicate. 
Contact Rip at xyropedes of canada.com or Dave
at rebhuhn of rocketmail.com for more info on getting into choo-choo games.
And Andy York has been my most frequent subszine guest lately!!!

The {\it TAP} mailing list has moved!
It now is even BETTER protected than it was.
I even have a bit of trouble posting to it.
To post to this list, send your email to: tap of diplom.org.
But this is completely moderated, it won't go out to the list unless
I approve it.
In general, I intend to keep traffic down to just the szine, as we've
been doing and I'll put your LOCs in here.
I {\bf EXPECT} all players to be on this list, especially those of you who
are from foreign countries!!! 
You need this to find out when the szine is up on the web to check in on results.

General information about the mailing list is at:
http://www.diplom.org/mailman/listinfo/tap

You can sign up from there, or send E-Mails to:
Tap-request of diplom.org;
with the word `help' in the subject or body (don't include the
quotes), and you will get back a message with instructions.
You must know your password to change your options (including changing
the password, itself) or to unsubscribe.  
Normally, Mailman will remind you of your diplom.org mailing list
passwords once every month, although you can disable this if you
prefer.  This reminder will also include instructions on how to
unsubscribe or change your account options.  There is also a button on
your options page that will email your current password to you.
A big, big thank you for Millis Miller for setting this all up!!

\bigskip

\centerline{\bf THE SEARCH FOR MARGARET GEMIGNANI}

\smallskip

OK, now, why Margaret?  Margaret, of course, is one of the most famous personalities in 
Dipdom, Science Fiction, Star Trek, Comic, etc. fandom.  
She was a nurse in the DC area, I believe, and then retired to Florida some years ago.
Many people had an address for her in Fort Lauderdale (including me), but that address
went missing around 1994.
If you do Google searching, as I have done off and on, there is a Margaret Gemignani
that contributes to the Baltimore and Ohio Historical Railroad Association, along with 
a husband, Gino (anyone know if that matches.... the B\&O matches where she used to live...
but don't tell me, use it as info to go looking yourself!!!)
Margaret has a couple of mentions in the Diplomacy AtoZ and I first encountered her
in the old Bernie Oaklyn {\it Le Front} szine.
I think it would be fun to find her.
We also have a leftover letter on Jeff Key from Mark Lew below.

\bigskip

Feel free to spend the time looking for some of the backlog.
Let's get Jeff, Derek, Sylvain, Steve, Ed, Tom, Bill, Gregory, and 
ESPECIALLY Kevin found too!!!
This is a regular continuing feature of the szine
and I will be introducing a new ``search for'' every five issues.
Moreover, you can win a \$25 prize for finding some previous
target who went unfound in the original \$50 period.
That means that if Jeff Key or Steve Heinowski or Ed Henry or Tom Hurst or Bill Quinn or 
Gregory Stewart or Derek Nelson or Sylvain LaRose or John Smythe
is ``found'' from now on it is worth \$25.

\bigskip

Winners will receive credit for Dip hobby activities
that I will pay out as requested by the winner.
Subscribe to szines here or abroad, run your
own contests, publish a szine, finance a web page, 
GO TO A DIPLOMACY CONVENTION or whatever.
Spend it all right away or use me as a bank to cover hobby activities
for years.
What must you do to win?
Get me a letter to the editor for {\it TAP} from the person we're
searching for.

This is very important, just finding them doesn't do it.
They have to write me a letter.     
The final judge as to the winner of any contest will be the target 
himself and I reserve the right to investigate the winning entry.
When you find someone I'm looking for, you should ask him to send me a 
letter for print that includes a verification of who ``found'' him.
%Michael Swift, Mike Stewart, and 
%Jason Yarbrough , Tim Stabosz, 
%Eric Ozog has $25
%Leslie Obata is owed $25
%Derek Nelson, winner of the first postal game in Graustark.  I last saw him
%at the '76 DipCon in Baltimore.
%Charles Wells, former publisher
%John McCallum, former publisher (Brobdignag, SerenDip, etc.)
%Dan/Charles Brannan, former publisher (Wild 'n Wooly)
%Margaret Gemignani, former player and nurse living in Florida

\bigskip

{\bf Mark Lew (Tue, 5 Sep 2006 19:46:38 -0700)}

Jim-Bob,

I confess, I never read {\it TAP} promptly and I rarely read it completely 
either.  Today I happened to see a paragraph about the search for Jeff 
Key from the Aug 10 issue.  The way you talk about the ``Key Lepanto" 
makes me wonder if you've got it wrong. (Or maybe I'm remembering it 
wrong.)

{\it ((No, I know, but I didn't say it very well..... so why don't you
explain more properly and then I'll quote from the Official Mark Berch
A to Z definitions.  Although, Mark Berch DOES say that Jeff originated
both the Key Opening and Key Lepanto.))}

As you no doubt know, plain old vanilla Lepanto is spring 01 A Rom-Apu, 
F Nap-Ion; fall 01 F Ion C A Apu-Tun; winter 01 build F Nap; spring 02 
F Nap-Ion, F Ion-Eas; and fall 02 F Ion \& F Eas C A Tun-Syr.  The idea 
was that in spring 02 Turkey doesn't see it coming so he doesn't leave 
anyone in Smy or Arm, and therefore in fall the convoy to Syria can't 
be bounced.

The generic label ``Lepanto" later came to be applied to any variation 
that tries to convoy an army from Tunis to somewhere in Turkey.  (And 
I'll resist the urge to point out all the reasons why the name isn't 
very apt historically....)

The ``Key Lepanto" was not invented directly, at least not the way I 
remember it.  The opening that Jeff invented was the plain old Key 
opening that originally had nothing to do with the Lepanto.  The 
essence of the Key opening is that in spring 01 Italy moves A Ven-Tri, 
and then in fall 01 A Tri moves on to Serbia.  The idea here is that 
the A-I alliance gets one more unit into the Balkans early.  Austria 
tries to get both Rum and Gre while Italy gets Tun and Ser.  Obviously, 
the illusion of an A-I war helps in the diplomacy for fall 01 to trick 
R and/or T into leaving something insufficiently defended.  Then if it 
works out they've got three in place to possibly pop Turkey out of 
Bulgaria in spring 02.

The generic label ``Key" later came to be applied to any variation where 
Italy sends an army through Trieste with Austria's blessing.

The ``Key Lepanto" is a later hybrid that tries to do both at once. 
Presumably the illusion of the A-I war is less effective since if Italy 
was really going after Austria he probably wouldn't send A Rom to Apu; 
but at the same time it has the common theme of getting Italy's units 
forward quicker in an A-I alliance, both the army in Serbia and the 
fleet still in Ion for the start of spring 02.

I don't know that Jeff invented the Key Lepanto.  I think he just 
invented the Key, and then the other variations came along later.  
(Somewhere in a box I've got Mark Berch's lexicon of Diplomacy, which 
probably details all the openings and their histories.)

\centerline{mdl, markdlew of earthlink.net}

{\it ((You can access the full Diplomacy AtoZ on the Internet through the 
TAP home page.  
Here are some of those original definitions as written by Mark Berch,
note the Key Lepanto entry was edited somewhat by others later, Mark
Berch himself is welcome to chime in:))}

KEY OPENING: Named by Jeff Key, the inventor, of an
Italian-Austrian opening with A(Ven)-Tri-Ser (usually with Austrian 
support to foil A(Bul)-Ser), A(Bud)-Ser-Gre (latter with support from 
F(Alb)).  Since Italy gets his build in Ser, he can do F(ION)-AEG/EAS. 
This opening is particularly valuable if Turkey opens F(Ank)-Con, 
since the traditional {Lepanto} is almost certain to be foiled.  If 
A(Bul)-Gre is believed unlikely, Austria can step up the naval pressure 
on Turkey with F(Alb)-ION.  Italy can readily stab Austria with 
A(Tri)-Vie, A(Ven)-Tri, or by gaining Turkish support for 
A(Apu)/F(ION)-Gre, plus A(Tri)-Alb to cut support. 

KEY LEPANTO: A specific variation of the
{Lepanto} series of Italian opening moves: A(Ven)-Tri, A(Rom)-Apu, F(Nap)-ION.
The intent is A(Tri)-Ser, a Key opening without the camouflage (and risk to
Austria) of A(Rom)-Ven. A(Apu) is presumably heading for Tun, thus passing up
one of the main values of the Key opening.
Unfortunately for agreeable Austrian players, most Italians allowed into
Trieste refuse to move out in Autumn, with horrific consequences for
beleaguered Austria.  Consequently, despite the overwhelming popularity of the
Lepanto as an opening, the Key Lepanto itself is rarely seen.  
If we considered the moves A(Ven)-Tri and F(Nap)-ION to be the stem
of the Key Lepanto then we have the following variations:
A(Rom)-Apu (Key Lepanto);
A(Rom) H, (Key Lepanto, Rome Variation);
A(Rom)-Nap (Key Lepanto, Naples Variation);
A(Rom)-Tus (Key Lepanto, Tuscany Variation).
Note that the A(Rom)-Ven move is known as the Stab Lepanto.
{\it ((this version was named by Richard Sharp.))}
Devised by American player Jeff Key.

\bigskip

\centerline{\bf INTERNATIONAL SUBSCRIPTION EXCHANGE NEWS}

\smallskip

The British representative is the editor of
{\it Mission From God}, John Harrington.
John may be contacted at 1 Churchbury Close, Enfield, Middlesex
EN1 3UW, UK.

E-Mail: fiendish of operamail.com, John.Harrington of tfeurope.com 

Please include the full name and address of the foreign publisher with
your order, if possible, as well as the szine title.
Make your check in US dollars out to me personally or in GBP to John
if you're doing things from that end.
I will conduct business for Canadians as well, if I can, but prefer
to deal in US dollars with them if possible, or Canadian dollars cash.
To subscribe to American szines, the system works in reverse.

We have closed the European continental branch, as I think most
of you had figured out.

And the ISE in Australia hadn't had much real action in recent
years, and Brendan Whyte has moved on to Jerusalem!!!
Brendan still produces what I find to be the most readable
small szine in the worldwide hobby.
Did you all realize that?
Write to Brendan at his new Jerusalem address and ask him
about subscribing, I'm not sure what the new deal will be.
Department of Geography, Faculty of Social Sciences,
The Hebrew University of Jerusalem, Mount Scopus, Jerusalem
91905, ISRAEL.
His travelogues are wonderful.

\bigskip  

\centerline{\bf WORLDMASTERS04 SECTION}

\smallskip

See http://www.worldmasters.net/wm04/
for details on progress on the WORLDMASTERS04, the Semifinals have now begun.  
Some semifinal notables include: Egg Ferreira, Buffalo Bartalone, Lee Simpson, 
Joe Janbu, Sebastian Beer,
Jerry Fest, Twerg O'Donnchu, Tim Sweeney, Dave Partridge, Glenn Ledder,
Adam Silverman, Toby Harris, and Thomas Franke.
This is one of the deepest semifinal fields for this great tournament 
that I've seen, with representatives from nearly all of the world's
hobby communities.
Actually, in an update, the Semifinal games will begin in Mid-September.
I was wondering why I hadn't seen anything on progress in these games,
and that's why.
But the pairings have just been announced.
More on that next issue!!!
Thomas Franke and David Partridge are in a game together that seems
on first glance to be the weakest in the rest of the players.
So my first thought is that one of those two will have a slot in
the finals.

It is helping now that I've joined the Yahoogroup WM04-Chat where this
discussion is happening.
You can join too!
However, this forum has been very, very quiet, I hope it picks up with
semis, maybe I'll have to start some discussion.
But most of the talk that there has been has about Yann Clouet and the French
Hobby's new ``World Palmares Evaluation" of FTF Diplomacy Play.
Of course, Yann Clouet comes out \#1, further backing up winning
the John Koning award, and I am 1442nd (in a tie with Mark Nelson
and Tony Dickinson, among others!).  
This uses lots of tournament results, more than 750 of them, and really
is quite comprehensive.
See those rankings at:
http://www.18centres.com/SPIP3/article.php3?id\_article=199 

\bigskip

\centerline{\bf DIPDOM NEWS SECTION (with letters)}

\smallskip
 
Obscure and not-so-obscure ramblings on the state of the hobby
and its publications, custodians, events, and individuals with
no guarantee of relevance from the fertile keyboard of Jim-Bob,
the E-Mail Dip world, and the rest of the postal hobby.
My comments are in {\it italics} and {\it ((double 
quotation marks))} like this.
{\bf Bold face} is used to set off each individual speaker.
I should also make a note that I do edit for syntax and spelling
on occasion.

%A VERY light discussion is taking place that will address what 
%stance we (the hobby) should take (proactive in some way for sure) 
%toward Hasbro, the new owners of the rights to Diplomacy.
%More on this will be forthcoming, but it looks like Hasbro might
%have its version of Diplomacy on the market for the Christmas
%season and they actually will be employing ``play-testers''.
%No word on precisely what this means yet, could it mean that
%they will offer a series of ``official'' variants?
%Stay tuned....
%If you want to be part of the discussion, send the MESSAGE:
%
%subscribe hasbro
%
%to majordomo of diplom.org, it works just like the tap mailing list
%described below.  Sending messages to hasbro of www.diplom.org
%sends the mail to the whole list.
%The big news this time is the beginning of the breakout of
%Hasbro into official contact with the hobby.

The game Diplomacy is a copyrighted product owned by Hasbro and all
reproductions or other use of that material in this szine is intended to
be personal use and not infringe on those rights in any way.
All reproductions are done at a heavy financial loss to the editor
and thus are without the remotest possibility of commercial intent,
except to promote THE game, the Game of Diplomacy, which you all 
should purchase from Hasbro or other duly licensed distributors.
 
Stephen Agar has matched the Hasbro rule lists 
and more with some of the even older
rulebooks.
Check these out if you like:

http://www.hasbro.com/default.asp?xcc\_gameandtoyinstructions

http://www.hasbro.com/instruct/Diplomacy.PDF

http://www.hasbro.com/instruct/Diplomacy(OlderVers).PDF

Nice of them to make BOTH of these available.
And all seven different US rulebooks for Diplomacy can now be found here
courtesy of Stephen Agar (relatively new address for this):

http://www.diplomacy-archive.com/diplomacy\_rules.htm

%1: The Reformer, who seeks perfection (crusading type).
%2: The Helper, who seeks love (altruistic type).
%3: The Performer, who seeks status (competitive type).
%4: The Individualist, who seeks an identity (imaginative type).
%5: The Investigator, who seeks knowledge (analytical type).
%6: The Loyalist, who seeks security (ambivalent type).
%7: The Enthusiast, who seeks gratification (thrill-seeking type).
%8: The Leader, who seeks self-sufficiency (dominant type).
%9: The Peacemaker, who seeks contentment (accommodating type).
%See http://graphics.lcs.mit.edu/~becca/enneagram/
%new test at: http://www.9types.com
%My scores in order were: 9, 13, 15, 7, 15, 6, 17, 18, 14.
%Robert Lesco's Marco Poll, the defacto poll of the
%North American hobby since the Runestone is pretty much
%officially dead, continues to collect votes.
%This is an official {\it TAP} approved poll.
%Here are the particulars on the Marco Poll:
%Vote for your top five in each category and you can't vote (or at least
%it won't be tabulated) for Robert Lesco or his szine, which I don't see.
%I will send this to Robert and offer him a trade.
%The deadline is September 1st and either send your ballot to marcopoll of yahoo.com
%or mail to Robert Lesco, 49 Parkside Drive, Brampton, Ontario, CANADA  L6Y 2H1.
%For identification purposes, Robert would like you to identify yourself both
%by name and by affiliation (a game you play in or a szine you sub to).
%Here are the categories this year (I like some of the new ones!!):
%1) Favourite {\it ((Hey, what, he's Canadian, yeah.))} Zine  {\it ((What's a zine,
%shouldn't that be Szine???))}
%Backstabbers United Monthly, Costaguana, The Diplomatic Pouch, Absolute, Vertigo
%2) All Time Favourite Zine {\it ((Szine))}
%Magus, Europa Express, Thirty Miles of Bad Road, Perelandra, North Sealth West George
%3) Best Diplomacy Player
%John Quarto von Tivadar, Edi Birsan, Mark Fassio, Chris Martin, David Partridge
%4) All Time Best Diplomacy Player
%Edi Birsan, Mark Fassio, Kathy Caruso, Rod Walker, Hohn Cho
%5) Best GM
%Malcolm Cornelius, Tim Miller, Tim Richardson, Conrad von Metzke, Doug Massey
%6) Player Who Writes the Best Letters/E-Mails
%Don Williams, Richard Weiss, Mark Fassio, Toby Harris, Cal White 
%7) Folded Zine {\it ((Szine))} You Miss the Most
%Magus, Diplomacy by Moonlight, Le Front du Liberation de Diplomacy, Kathy's Korner
%8) Favourite Variant
%Modern, Nuclear Yuppie Evil Empire Diplomacy, Woolworth, Spy Diplomacy, Colonia

\bigskip

\centerline{Check out current and back issues of {\it Diplomacy World} -- Yahoogroup diplomacyworld}

Also, I need any Hobby Award Nominations NOW (!!!) for:

\noindent The 2005 Don Miller Award for Meritorious Service;

\noindent The 2005 Rod Walker Award for Literature;

\noindent The 2005 John Koning Award for Player Performance;

\noindent The 2005 Fred Hyatt Award for GM Performance;

or

\noindent A 2005 Kathy Byrne Caruso Award for Lifetime Achievement (if warranted).

The Hobby Awards Committee is Jim Burgess (Chair and Treasurer),
Fred Davis, Jr., Melinda Holley, Gary Behnen, Jamie Dreier,
Paul Kenny, Mark Stretch, and Robert Lesco.
I was going to publish the award ballot for this year 
in this issue, but I realized that I really just had to get this out first and
then do that.... and then, well, REAL SOON NOW!!!

\bigskip

{\it Diplomacy World} Issue Deadlines:

\noindent Deadline Spring 2006, Issue \#97: March 1, 2006

\noindent Deadline Summer 2006, Issue \#98: June 1, 2006

Note that Andrew Neumann has taken 
over the lead editorship from Tim Haffey.
Get us articles NOW!!!
The March issue has been delayed but should be out shortly.
That probably means that Issue \#98 will be delayed until Fall.

%\noindent Final Hobby Awards Ballot for 2004, nominations now to:
%burgess of world.std.com
%
%The qualifications for the Kathy Byrne Caruso Lifetime Achievement 
%Award are that the awardee must have been: (1) Active in the 
%Diplomacy Hobby in at least Three Separate Decades; 
%(2) Multidimensional in their Contributions to the Hobby 
%(e.g. writing, playing, publishing); (3) Taking Retirement or 
%Semi-Retirement from the Diplomacy Hobby; and (4) One of the 
%Hobby’s Unique Personalities Worthy of Being Remembered as Long 
%as THE Game Continues to be Played.  This award need not be awarded
%each year, but only as worthy candidates are identified.  The only
%past honoree is the late Richard Sharp.
%
%The other award categories are self-explanatory:
%
%\noindent Nominees for the 2004 Don Miller Award for Meritorious Service
%
%\noindent Nominees for the 2004 Rod Walker Award for Literary Achievement
%
%\noindent Nominees for the 2004 John Koning Award for Player Performance
%
%\noindent Nominees for the 2004 Fred Hyatt Award for GM Performance
%
%--- --- --- --- --- --- ---

Editorial Board for Diplomacy World:

\noindent Andrew Neumann, andrewneum of gmail.com -- New Lead Executive Editor!

\noindent Tim Haffey, 810 53rd Ave., Oakland, CA 94601 USA; trhaffey of
aol.com -- Ex-Lead Editor and Archives Editor

\noindent Jim Burgess, 664 Smith Street, Providence, RI 02908-4327, USA;
burgess of world.std.com -- Co-Editor and Publisher

\noindent Stephen Agar, 4 Cedars Gardens, Brighton, UNITED KINGDOM  BN1 6YD;
stephen of stephenagar.com -- Webmaster and Non-US Postal

\noindent Rick Desper, 5440 Marinelli Road, \#204, Rockville, MD  20852, USA;
rick\_desper of yahoo.com -- Demo Games

\noindent Dave Partridge, 15 Woodland Drive, Brookline, NH  03033, USA;
rebhuhn of rocketmail.com -- US Postal

\bigskip

ATTENTION: There is a new company that had been doing a new PC Diplomacy game:

http://www.paradoxplaza.com/news.asp?ArticleID=239\&Page$=$News

You all should read the interview in the Spring 2005 movement issue
of the {\it Diplomatic Pouch} (and I mean ALL!!!!!!! of you!!!!!)
that I think you can find at: 

\noindent http://www.diplom.org/Zine/S2005M/

I'm not sure what is going to happen now, but basically everywhere 
except in Russia the game pretty much failed.
The AI was not good (not a huge surprise) and it just required too many
updates to get it to work.
Besides, it really was designed for ``real time'' play and everyone
doesn't want that.
To find out more general information on DIPLOMACY please visit
www.diplomacy-pcgame.com or contact pr of paradoxplaza.com
but I think it is about to wither away and die.
In sum, I think that is too bad.
But the hobby as a whole is going strong with thousands and thousands of
Diplomacy players worldwide.
REALLY!!!
Speaking of worldwide, there's been a resurgeance of the Australian/New
Zealand hobbies lately after three years of relative quiet.
Here's an update from my teddy bear cuddly pal, Sean Colman
of a statement by Phil Davies!!!
This is the good side by the way, they've also been feuding over
how/when to allow younger Dippers to play relative to having side
games of poker and drinking to go on.
As always, it is a shame when greater hobby energy translates
into rule mongering and feuding.
Here's to hoping that Sean and others come to their senses and 
focus on PLAYING and having FUN.
I choose here to focus on the good plans for the future....

\bigskip

{\bf Forwarded by Sean Colman (Wed, 30 Aug 2006 16:45:24)}

The inaugural Australian Games Expo (AGE), conducted in Albury on the
Queen's Birthday Weekend of 10th \& 11th June 2006, was an outstanding 
success.

There were in excess of 1000 attendees over the two days.
Exhibitors totaled 18, with one, Mary Couzin, owner of Discovergames.com 
and convenor of the Chicago International Toy \& Games Fair (CHiTAG) 
travelling from the USA.

Mike Hirtle, Vice President Research \& Development from Hasbro USA also 
traveled from the USA to support the event.
All exhibitors have indicated they will be returning next year, some 
requiring larger booths.

There were 95 entrants for the Sanctioned, Carcassonne \& Settlers of 
Catan Tournaments. Complying with Spielezentrum Herne requirements, the 
first prizes were return airfares to Essen to enable Australia to be 
represented in the World Championships in October 2006.
In addition, 5 nights accommodation was included for each player, in 
Essen.

The three Australian wholesalers, Funatical, Walrus \& Carpenter \& 
Ventura, who supplied the first prizes, have all agreed to be sponsors 
again in 2007.

The Diplomacy Association of Australia \& New Zealand ``DAANZ" 
(www.daanz.org.au) has decided to conduct the Annual Australian 
Sanctioned Championships at AGE in 2007 as well. As with Carcassonne \& 
``Settlers" the first prize will be a return airfare to the world 
championships.

The plan for AGE 2007 is to aim for 40 Exhibitors, with a target of 3000 
attendees.

To achieve this, advertising will be conducted in all Australian State 
Capitals.
Hasbro Australia has agreed to be lead sponsor to help achieve these 
targets.
Hasbro Australia and Mayfair Games have already indicated they intend to 
be Exhibitors.

I will be attending and exhibiting, at The Chicago International Toys \& 
Games Fair (www.chitag.com) in November 2006, in an effort to gain 
further International exhibitor support.
The Australian board game market, clearly has reached a maturity level, 
especially with the Euro style games, where an event such as this is 
justified and sustainable.

The 2007 Expo will encompass not only board \& card games, but games of 
all types, including Table Top Games, Role-playing Games and Collectible 
Trading Card Games.

I encourage you, to take the step of being an Exhibitor at the 
Australian Games Expo 2007.
Please take the time to visit the Expo website. www.austgamesexpo.com

I look forward to your response and discussing your involvement in the 
Australian Games Expo on 9th \& 10th June 2007.

\centerline{Convenor -- Phil Davies, phil of austgamesexpo.com,      
www.austgamesexpo.com}

\centerline{Sean, sean of seropeco.com.au}

{\it ((I'm probably going to get back to Australia somewhere around that time in 2008, 
so you can be sure I'm going to be watching for time of this event.
Joakim Spangberg answered this question about PBM zines in the UK....
that Jonathan Amery asked.))}

\bigskip

{\bf Joakim Spangberg (24 Aug 2006 21:24:39 -0700)}

Here are the ones I know is active but there are for sure several more:
Borealis;
Bloodstock;
Greatest Hits;
Hopscotch;
For Whom the Die Rolls;
Jamais n'est-ce pas la gare?;
Minstrel;
Ode;
Save Your xxs For Me;
To Win Just Once;
The Tangerine Terror;
Variable Pig;
Where Is My Mind.

These might only be available by e-mail and/or on the web:
Dane's Games;
Devolution;
The Blue Nose Special;
Will It Lead to Trouble!?

\centerline{Joakim, joakim of konfliktspel.com,
http://www.konfliktspel.com/corps/}

{\it ((That's not bad, but it does leave out a few, like {\bf Psychozine} on the
Web side and Alex Richardson's szine on the postal side.
That's still way more than what is left in North America, as I think we're under ten
at the moment where I only get four, other than this one.))}

\bigskip

\centerline{\bf MUSIC AND MOVIES SECTION (WITH COMMENTS ON OTHER ARTS AND SOCIETY)}
     
\smallskip

I want to pick up the music commentary again and run a ``23 tunes'' contest here
(stolen blatantly from Mark Wightman and the late lamented {\bf The Sprouts of Wrath}.
You send me 23 tunes and five or six lines of commentary on each.  I print them
with comments from me 2-3 at a time and then YOU have to guess who submitted each
set of tunes for that issue.  I give ``bonus points" for quality and subtract points
for really lame selections.
Mark, forget how the scoring goes, one point for each person you guess right each issue,
correct?
To enter, you can send them 2-3 at a time, or you can send me the whole list of 23 tunes.
But I think we should be able to get at least ten people playing.
I have an advance commitment from Brad Wilson to be in, so this should be FUN.
When we're done, whoever wins I'll try to figure out how to make a CD of tunes from
the list for them.
If anyone would like to send me a tape or CD of their 23 (which was the original point)
that would be great, but I don't intend to require that.  I will be playing in the
sense that I'll be putting 23 tunes in, and you have to guess me, but I obviously
won't score points.
I'll start things up in a couple of issues once I have enough entrants.
I've got three people in now, I need more of you.
To get started, I need THREE songs, the first turn will be three songs, and then
two for each of the next ten rounds.
Send me three tunes now with a bit of commentary, and we'll see if people can
guess who you are!!!
And already there is a LOT of diversity in defining tunes and styles, so 
BE CREATIVE!!!
I should be able to get a dozen entrants!!!
 
%To encourage voting early, I picked five voters at random to receive five US
%dollars from me (either in cash or paid to someone for Dip stuff or to get
%a free tape).
%Tony Dickinson won the Round 5 prize, so we had three of the six Round 1 voters
%won and one of the three Round 2 postal voters who also got five chances to win.
%That showed the value of getting in early!!
%Voters in Round 1 were Mike Barno(\$5), Rick Desper (\$5), Tony Dickinson (\$5),
%Drew James, Heath Gardner, and John Harrington.
%Round 2 postal voters were John Schultz (\$5) Ian Moore, and Stan Johnson.
%Round 2 E-Mail voters were Scott Morris, 
%Warren Goesle, Peter Sullivan, and Michael Lowrey.
%Round 3 voters were Dick Martin, Richard Weiss, and Rip Gooch.
%Round 4 voters were Roland Sasseville, Jr. (\$5),
%Don Williams, Brent McKee, and Andy York.
%Round 5 voters were Mark Larzelere, Al Tabor, Jody McCullough, and that's it.
%We'll end up with a monster party tape at the end of it that I plan
%to segue and sequence and copy for distribution.
%The result will be a great New Millenium party tape -- we're going for 90 minutes.
%I've also been thinking that I should put this out on CD
%as truly emblematic of the new millenium.  
%I don't have the capability to do that quite yet, but I think
%I might by then.
%Any suggestions (or especially volunteers) on this front will
%be cheerfully accepted and could receive monetary payments!
%The CD way may still occur if someone steps forward and actually does it for me.
%So far, we have ``I Melt With You'' by Modern English; George Gershwin's
%``I got Plenty O' Nuttin' '' from {\it Porgy and Bess} in the 1957 concert
%recording with Ella Fitzgerald finishing off the vocals after Louis
%Armstrong blows and sings through the tune; Duke Ellington performing
%Billy Strayhorn's ``Take the A Train''; Frank Sinatra's ``New York,
%New York''; something from the B-52's;
%the original Van Morrison and Them version of ``Gloria'';
%The (English) Beat's 12 inch version of ``Save It for Later'' 
%ratchets things up to the next level (wherever you put it!);
%Buster Poindexter's ``Hot, Hot, Hot'' keeps you there;
%``Atomic Dog'' by George Clinton blows the doors off,
%and Koko Taylor cleans up singing Willie Dixon's ``Wang Dang Doodle''.
%After I get timings down, I'll choose exactly which songs below make the list.
%
%EXTRA SPECIAL B-52'S BULLPEN: (7) ``Love Shack'';
%``Rock Lobster". {\it ((A tie, a tie!!!!))}
%
%BULLPEN: (9) Nirvana -- ``Smells Like Teen Spirit";
%``Cumberland Blues'' -- the Grateful Dead.
%(8) ``Twistin the Night Away" -- Sam Cooke; ``In Between Days'' -- The Cure;
%``Mannish Boy" -- Muddy Waters; ``Shake, Rattle, \& Roll" -- Big Joe Turner; 
%``Proud Mary'' -- Ike and Tina Turner.
%(7)  ``I Wanna Be Sedated" -- Ramones; ``Twist \& Shout" -- Beatles.
%(6) ``Magic Carpet Ride" -- Steppenwolf;
%``Crossroads'' -- Eric Clapton; ``Play That Funky Music'' -- Wild Cherry;
%``I Fel Good" -- James Brown;
%``Radar Love'' -- Golden Earring; 
%Devo -- ``Whip It"; ``Echo Beach'' -- Martha and The Muffins.
%(5) ``Sing Sing Sing'' -- Benny Goodman; ``Rocking the Casbah'' -- The Clash; 
%Squeeze -- ``If I Didn't Love You"; ``Roadrunner'' -- 
%Jonathan Richman and the Modern Lovers.
%
%SPECIAL ROLLING STONES BULLPEN: (6) ``Paint It Black''. 
%
%SPECIAL TALKING HEADS BULLPEN: (9) ``Take me to the River".
%(4) the entire {\it Speaking in Tongues} record
%(special call for ``Road to Nowhere'').
%
%SPECIAL ALPHABET SONG BULLPEN: (6) ``YMCA" -- Village People. 
%
%SPECIAL DRUG MUSIC BULLPEN: 
%(8) ``Rd, Red Wine'' -- UB40.
%(6) ``Don't Bogart that Joint'' 
%-- Fraternity of Man; ``The Old Dope Peddler'' -- Tom Lehrer.
%(5) ``Cocaine'' -- Eric Clapton's version; ``Casey Jones'' -- the Grateful Dead.
%(4) ``White Rabbit'' -- Jefferson Airplane; ``Love Is the Drug'' -- Roxy Music.

\bigskip
%Brendan Whyte <bwhyte@mscc.huji.ac.il>
%The "Hallelujah" Chorus from Handel's "Messiah"
%The title tells you what the words are, and the middle few bars are 
%so famous, but how many people, apart from those that sing it, know 
%the whole movement? A great little number this, boppy and exciting to 
%sing, to sing along to, or just to tap ones fingers to on the 
%steering wheel while caught in traffic, though with the new bridge to 
%replace the Woodrow Wilson drawbridge in DC should ease the latter at least.
%
%"Libera Me" from Andrew Lloyd Webber's "Requiem"
%The final movement of this impressive modernist-classical piece 
%leaves the boy soprano on his own to hold pitch and rhythm singing 
%about eternal peace, when the organ comes crashing in over him with 
%dissonance and gusto trying to drown him out in chaos, but its waves 
%of noise break and underneath the sweet high "perpertua" carries on. 
%It's a brave young lad who can maintain that, especially in any live 
%performance in front of an audience. But live or recorded, this is 
%great music and a fascinating musical analogy of peace and goodness 
%and light triumphing over noise and chaos.
%
%"Mau Kamu Suka Kamu" by Rano Karno
%An interesting delve into singing by TV presenter Karno comes up 
%trumps with this sugary but fun silly love song in a disco-dangdut 
%style (one could never call Karno himself 'dangdut', he's too 
%respectable!). Mothers and daughters will sing along in the catchy 
%chorus. A difficult track to find outside Java, but worth the effort 
%of hunting down, especially to see the expression on the faces of 
%expat Indonesians when you play it!

{\bf Pete Gaughan (Tue, 29 Aug 2006 08:19:59 -0700)}

Jim, you faithfully continue to wave ``hello" to me every issue, and I 
faithfully intend to write back but never do. Thanks for keeping me on the 
string.
{\it ((You're quite welcome, it is part of the mission around here.))}

I just don't game any more. Jason B{\it ((Bergmann))} and I get together occasionally for 
one-on-one (when he's wrapping up a bike ride in my neighborhood) but more 
often for a Giants game or a business lunch. I love to know that {\it TAP}, 
{\it Graustark}, World DipCon, and so many other familiar names are still going 
strong. In fact, I'm astonished sometimes at some people's longevity (and 
not just Dr. John): Mark Berch in your letter column? You're searching for 
Jeff Key?? (Did you know that I brought Jeff Key out of retirement once 
already? He hadn't played in years when he attended the DipCon I TD'd in 
Dallas in '83.)
{\it ((Nope, didn't realize that.  Then after that, he came to a few other
things before disappearing again.))}

Sports: My World Cup record was excellent until the semis. The biggest 
glitch was, I had Australia picked to beat the Italians--and didn't they, 
really? I picked all the quarters correctly; but I picked both semis wrong 
(yeah, I had the same finals prediction as Goz!). God, what a mediocre 
tournament; like your other readers, I hate dives even more than I hate 
shootouts. But this is a cultural thing; we're taught as children that 
it's unethical and un-macho to fake an injury or ``game" the game. As long 
as the international game chooses to incorporate diving, the U.S. team 
will be second-rate.

In a lot of ways, this has been a good year for close races. The Cardinals 
slipped to just ``good"; Alonzo and Schumacher have been almost in lockstep 
(even DNFing in the same race!); even Tiger needed a playoff this week. My 
Dodgers don't have enough to hold off San Diego, but at least they've kept 
the summer interesting.
{\it ((Well, you might have more in the Dodgers than you think.))}

By the way, Jim: there are no liberal Republicans any more. The 
big-bidness theocrats don't want you, they're redefining government to 
prevent you from being seen or heard. You're extinct, my friend, and just 
haven't realized it yet.

\centerline{Pete Gaughan, pgaughan of wiley.com}

{\it ((Oh no, believe me, I realize it.
We're going to defeat Lincoln Chafee here in Rhode Island for just
that reason.  We have Karl Rove and his hit squad running all over
RI now defending and supporting Chafee in his primary battle.
And that pretty much says it all.
And that's why I'm not voting for Chafee either, even though most
of his positions match up with mine.
But ultimately, he has not dared to stand up for the losing positions
and oppose the other Republicans to any substantive degree.
He may well lose the Primary next week.
At which point the Republicans will walk away from RI.
But what I think will really surprise everyone is how
vulnerable Olympia Snowe is in Maine.
People in Maine really like Snowe, just as we here in RI like
Chafee.
But we can't vote for extinct dinosaurs.
It just gives the other Republicans the power.
After the liberal Republicans go 0 for New England, 
that will leave only Susan Collins from Maine (who isn't up for
reelection or she would be gone too) as the only liberal Republican
left in office.))}

\bigskip

{\bf Doug Kent (Tue, 22 Aug 2006 08:09:52 -0700 (PDT))}

Oh, the Red Sox...finished...nice series, eh?  Now 6
1/2 back...and the Rangers are ALSO 6 1/2 back after
being unable to score more than 3 runs again st Tampa
Bay while Oakland came back against Tampa from an 8-0
deficit...resulting in Ted Lilly bloodying his
manager's nose.  What fun!

\centerline{Doug, dougray30 of yahoo.com}

\bigskip

{\bf Warren Goesle (Mon, 21 Aug 2006 22:43:39 -0500)}

Hey!  It's only the middle of August!  Only Cubs' fans are supposed to 
be here in the ``Bummed-Out-Bar"!  What are all these people doing in 
here with caps that have a ``B" on them?!?

\centerline{Goz, wgoesle of comcast.net}  

{\it ((You think we were bummed on August 21, you should see us today.
Most of the other sports fans around here have gone on to watch that
other team that wears the funny helmets.
But I'm still suffering with the Red Sox.
As Dave says, and why not get the suffering over with early.))}

\bigskip

{\bf Dave Partridge (Tue, 22 Aug 2006 05:59:20 -0700 (PDT))}

Choke early, avoid the rush!

\centerline{Dave, rebhuhn of rocketmail.com}

\bigskip

{\bf Rick Desper (Tue, 22 Aug 2006 06:08:31 -0700 (PDT))}

It's not really a choke if nobody thinks you're going to win, and
you're not ahead in the first place.  It's more like a collapse.

\centerline{Rick, rick\_desper of yahoo.com}

{\it ((That's right, the signs were all there as the pitching staff
hadn't been rallying around Lopez and Mirabelli and they'd been
losing to Kansas City and Tampa Bay.  I am still a fan though, 
hopeful until the last magic number falls.  They can come back
and nab the wild card as Minn/Chi/Det beat each other up.
--- I wrote that at the time, I still think they will fight there
way back closer to the Wild Card, but we knew that all the depth
on the Red Sox were rookies, and it showed when the injuries hit.
To the Yankees credit, they fought their way through their injuries
earlier in the season much better.
Though I think it is fair to say that almost EVERYONE of consequence
on the Red Sox got injured, catcher, 2nd, SS, 3rd, all three outfield
positions, DH, and about half a dozen pitchers.
Let's give Rick another shot, with some responses to Goz...))}

\bigskip

{\bf Rick Desper (Tue, 29 Aug 2006 07:05:32 -0700 (PDT))}

--- Warren Goesle (wgoesle of comcast.net) wrote: 
Goz fantasy NASCAR update:  I don't have this week's standings (I
did great, but they're not yet posted), but as of last week in one
league I'm 1st out of 67, and in the other I'm 23rd out of 516. 
Apparently I'm running for commissioner of the wrong sport.
It appears that the Red Sox will not qualify for the playoffs in
2006, so they should run as an independent.  The Cubs, of course,
won't be able to collect enough signatures to qualify as an
independent in 2006, but they will for ``next year".

The Red Sox claim that they will be running as an independent, but
they claim they will still "represent the AL".  But for some reason
they are trading many of their prospects to NL teams.
(I'm trying to extend the Lieberman analogy.  It's not quite
working.)
 
--- Warren Goesle (wgoesle of comcast.net) wrote: 
The Reds, at 67-65, are currently the wild-card leader in the NL. 
I don't think it's mathematically likely for the WC from the NL to
be under .500 (not with 10 teams within 5 games), but it is
possible, and it seems likely that 84 or 85 wins will do it.  Note
that one of the teams in contention is Colorado, whom all of us
left off of our preseason picks entirely (how come we didn't note
that we'd only had 4 teams in the NL West?).

Did I do NL picks?  If I did, I didn't pick the complete standings.
I thought I only picked the playoff teams.  I believe I picked St.
Louis, the Dodgers, Mets, and Braves.  But I might not have picked
the Mets.  

--- Warren Goesle (wgoesle of comcast.net) wrote: 
The hottest teams in both leagues right now are the Dodgers and the
A's.  I can't stay up late enough to watch...does anyone know how
they're doing it?

The Dodgers have accumulated some decent talent over the past few
years.  I don't know how the As are doing it, but I think I picked
them to win the division.  (It's my only AL pick that looks tolerable
these days.)  But I might have picked the Angels.  
Incidentally, I see that the Red Sox have Youkilis hitting cleanup
now.

*bangs head on desk* 

I think they should just go whole hog with this injury thing and have
Schilling and Beckett get into a knife fight (that Papelbon valiantly
tries to break up).
{\it ((Soon after this, Papelbon and Schilling did go down, without
the benefit of a knife fight.))}

In brighter news, the Pats are destroying their opposition in the
preseason.  I'm thinking they'll win at least 13 games this season.

\smallskip

preliminary post-season award picks

AL
MVP: Jeter;
This is more of a prediction than who I would vote for.  I would say
Ortiz is ahead right now, but if he's not going to play much in
September, he's got no chance of winning.  

Cy Young: Santana;
By a whisker over Roy Halladay.  

Rookie: Papelbon;
Based a lot on his early season stats, and Liriano's injury.

Manager: Leyland;
Should run away with this.

\smallskip

NL
MVP: Pujols;
Beltran also a good candidate.

Cy Young: no idea;
Who can you give this to?  Brandon Backe?  No really dominating
pitcher in the NL this year.  Even Gagne's not a candidate.  Trevor
Hoffman?  Billy Wagner?  Maybe somebody will pull ahead in September.
Could be Oswalt or Penny or any of a number of people.

Rookie: Josh Johnson;
Leading NL starters in ERA.

Manager: Willie Randolph;
Also likely to run away with the award.  Mangers of the Year are the
easiest to pick this year.

\centerline{Rick, rick\_desper of yahoo.com}

--- Warren Goesle (wgoesle of comcast.net) wrote:
Let me throw my 2 cents worth back in...
Rick picked the Dodgers to win the NL West, but did not comment on
the entire division.
I'm not one that's big on individual awards in team sports but:
Jermaine Dye has to be considered for AL MVP, and Carlos Zambrano
has to be considered for NL Cy Young.

\bigskip

{\bf Rick Desper (Tue, 29 Aug 2006 08:29:24 -0700 (PDT))}

Oh right, Zambrano.  He was the one, along with Webb (I said Backe
but meant Webb) that I thought would be leading in the NL right now. 
But 14-5 isn't with a 3.31 ERA isn't {\it that} impressive.  He'll need
to finish strong.

{\it ((More than not impressive, for the National League, it downright stinks.  
He'd have an ERA of about 4.50 in the AL.))}

Usually I expect a couple pitchers to have 17-18 wins at the
beginning of September.  Nobody in the NL has more than 14.  Also I'm
looking for an ERA below 3.00 and a WHIP below 1.20.  None of the
leading candidates has all of that in the NL.  If Pedro Martinez were
not injured the award would be his to steal with a strong September. 

{\it ((That is for sure, but Pedro is doing the slow breakdown that we all knew 
would happen when we let him go in Boston.  He's also doing an ERA point 
better in the NL than he would do in the AL, and he knows it!))}

Jermaine Dye's had a nice season, but I don't think it's quite
MVP-ish.  He isn't even the scariest hitter on his own team.  (Maybe
he should be but I'd much rather see him at the plate in a clutch
situation than Thome or Konerko.)  If you want to go by hitting
alone, I would take Ortiz or Manny before Dye.  

{\it ((Yeah, but Manny and Ortiz have no chance, so I think Dye does have a 
chance.))}

The MVP is a silly award in any case.  It rarely goes to the best
player, because lughead writers go off in an absurd re-definition of
the word ``valuable" which apparently includes ``playing for a division
winner" as well as ``not a pitcher, unless we're stuck looking for a
candidate".  (It still annoys me that Pedro lost to Pudge in 1999.)

\centerline{Rick, rick\_desper of yahoo.com}

{\it ((But that IS the definition of it, why not accept reality and lower
your heartburn level???))}

{\it ((Let's try to push the Spy Diplomacy..... here are the rules again,
playing this game is FREE!!!
See the questions Andy York asks at the end.))}

\bigskip

\centerline{\bf SPY DIPLOMACY (Variant, revised Dec. 1986)}

by Jim Burgess

Rules:

1) Unless otherwise specified, the standard rules of Diplomacy apply.

2) Players receive adjudications for their own armies and fleets, but not
the armies and fleets of other powers.  Similarly, each player sees only
his or her own section of the supply center chart.

3) In addition to the standard units, an unit called a "spy" is added.

     A) Each of the seven powers begins with a spy in each home supply center.

     B) Spies are supplied only by home supply centers (i.e. Russia may have
as many as four spies at a time while other powers are limited to a maximum
of three).

     C) Spies are "built" and "disbanded" in Winter seasons at the same time
as other units.

     D) There is no limit to the number of spies that may be present in any
province and spies may be ``stacked" with armies or fleets (exceptions are
listed in Rule 6).

4) Spy Reports

     A) Spies report the location and nationality of armies and fleets in
the province they occupy and all adjacent provinces immediately following
the standard Winter, Spring, Summer, and Fall seasons (i.e. just prior to
the spy movement seasons).  Spies can differentiate between units in retreat
and successful attackers when two units "occupy" a province.

     B) Spies also report the nationality of spies in the province they occupy
and the presence (but not nationality) of spies in adjacent provinces at the
same time.

5) Movement of Spies

     A) Spy movement follows the collection of spy reports, so orders to spies
may be made conditional on any information gathered by spies on opposing troop
movements or the adjudication of one's own units.

     B) Spies move after each of the following standard seasons: Winter,
Spring, Summer, and Fall (note that all spy movements PRECEDE Autumn
retreats), beginning with Winter 1900.

     C) Spies move as armies do with the following exceptions:

          a) Spy movements cannot be stood off by movements of any other unit.

          b) Spies may be convoyed by fleets of any power during any of the
four movement seasons for spies.  The convoy orders for fleets in these
seasons must be ordered by their owner in the usual fashion or else the spy
convoy movement fails of execution.  Fleet convoy orders for spies may be made
in addition to regular Spring and Fall moves (note, however, that the fleets
themselves never move during spy movement seasons).

          c) Spies may also be "picked up" and carried by fleets of any
power. Embarkation and debarkation are moves that must be made during a
spy movement season and "permission to board" is not required.  Embarkation
consists of a movement from a land province to an adjacent sea province
containing a fleet.  Debarkation consists of a movement from a sea province
containing a fleet to an adjacent land province.  A spy may not "switch
fleets in midstream".  Once boarded, a spy may only get off by debarking.
After boarding a fleet, the spy moves with the fleet during regular movement.
A spy may not debark from a fleet awaiting retreat (e.g. if a fleet carrying
a spy is dislodged in Spring, the spy may not debark until the spy movement
season following the standard Summer retreat season).

6) Spy Mortality

     A) This rule will outline the circumstances under which spies may be
captured or killed.  Spies may be disbanded in Winter seasons at the same
time as other units to meet the requirement that a power may not have more
spies than the number of currently held home supply centers and spies are
annihilated when they are on board a fleet that retreats off the board.
Otherwise, spies may only be removed from the board (there is no difference
in the game between capturing and killing a spy, but players should feel
free to delineate between the two states in writing press) immediately
following the four spy movement seasons.

     B) Spies killed or captured in a given season do not submit written
spy reports for that season, though their final movement may have been
made conditional on that spy report.  Players may never know for sure how
a spy was lost, just as in real life.

     C) Spies are "killed" by being assassinated by other spies.  When a
spy moves, he or she may attempt an assassination, specifying the nationality
of spies to be executed if discovered.  Each spy may hunt for only one
nationality in each of the four seasons.  The following rules and examples
will govern the adjudication of assassinations:

          a) A spy may attempt an assassination without moving (for instance
if the target is in the same province).  In this case, any spies of the target
nationality that end the spy movement phase in that province are assassinated
with one exception.  If the spy attempting the stationary assassination is
himself or herself assassinated by a moving assassin then that spy
assassinates no one in that season (not even a potential target other than the
one that assassinates that spy).

          b) A spy attempting a moving assassination (may include a move of
embarkation or debarkation from a fleet) is always successful in assassinating
spies of the target nationality that finish the spy movement phase in the
province that the spy moves to.  This makes "mutual assassinations" possible.

          c) Example: French spy is on board a French fleet in the Channel.
An English spy is in London.  Both powers specify assassination attempts
against the spies of the other.  If the English spy embarks on the French
fleet in the channel (remember that embarkation does not require the
permission of the fleet being boarded) and the French spy doesn't move, the
French spy is killed, but the English spy isn't (he may be immediateIy
captured, however, see part D).  If a German spy is also on board and the
French spy tried to assassinate the German spy, that operation would fail
as well. If the French spy debarks to London at the same time, the two spies
"pass in the night" and neither is killed.

     D) Spies are "captured" by opposing armies and fleets.  Players may
attempt to capture spies, specifying the nationality of spies to be captured
if discovered.  Each army and fleet on the board may search for spies of one
nationality in each of the four seasons.  The following rules and examples
will govern the adjudication of attempts to capture spies:

          a) Players may specify a nationality to be hunted separately for
each unit or they may issue blanket searches to be applied to all units.

          b) At the end of the spy movement phase, any spies of the
nationality specified in the same province are captured (for example, if
the French player specifies a hunt for English spies on their Channel fleet
in the above example, then the English spy is captured).

          c) Players are informed when they successfully capture an opposing
spy.  Note that the "owner" of the spy, however, is not informed of the
capture.  Communication just is cut.  This rule is the only exception to the
generaI rule that armies and fleets are blind.  It is possible to play the
game without allowing capture of spies by armies and fleets if one wishes
to allow freer movement of spies (i.e. RuIe D may be ignored).

7) It is suggested that the game be adjudicated in four separate seasons
in the following order:

     A) Spring: (for Spring 1901 this sequence is preceded by a spy movement
phase (no spy reports are necessary) followed by assassinations or captures)

          a) Standard movement by fleets and armies, adjudication reported
only for one's own units

          b) Spy report phase, spies collect information

          c) Spy movement phase, spies move according to Rule 4

          d) Spy assassination and capture phase

     B) Summer:

          a) Standard retreats by fleets and armies, adjudication reported
only for one's own units

          b) Spy report phase, spies collect information

          c) Spy movement phase, spies move according to Rule 4

          d) Spy assassination and capture phase

     C) Fall:

          a) Standard movement by fleets and armies, adjudication reported
only for one's own units

          b) Spy report phase, spies collect information

          c) Spy movement phase, spies move according to Rule 4

          d) Spy assassination and capture phase

     D) Winter:

          a) Standard Autumn retreats by fleets and armies, adjudication
reported only for one's own units

          b) Standard Winter builds and removals, also applies to spies

          c) Spy report phase, spies collect information

          d) Spy movement phase, spies move according to Rule 4

          e) Spy assassination and capture phase

\medskip

These rules have been produced by Jim Burgess (with helpful comments from
Bernie Oaklyn and Dick Martin).  Permission is granted to reproduce and use
these rules without restrictions.  The author would be interested to hear
any comments and criticisms regarding any aspect of the play of this variant.
The rules have been deposited with the North American Variant Bank.  They are
also available from the author for the cost of postage or free by E-Mail.

\bigskip

{\bf Andy York (Aug 21, 2006 08:27:01 PM)}

The printed issue arrived today, so there shouldn't be too much trouble for
folks in getting their orders in (presuming they read the issue and see the
deadline). If so, I'll hold the game until the next deadline and just have
commentary (presuming you don't mind my doing that!).
{\it ((No, I think people have been enjoying your commentary, I really
liked your review of ``The Illusionist''!))}

Thanks for the kind words about ``By The WAY". I'm trying to keep up with
you!
In reading the Spy Dip rules, I've some questions:
 
Rule 4 and 5 -- though not stated explicitly, I presume spies on fleets (at
sea) give reports similar to a spy on a land province. [[from one
viewpoint, it makes sense to give the reports; but from another (you're at
sea and have limited contact with your information gathering network), it
doesn't]]
 
{\it ((Yes, the spies report the same way.  I had three ideas that led me to that
solution in building the rules.  First, he's a spy on a fleet of ships, he
is presumed to be spying on what the fleet captain and crew knows about 
what is around.  
The spy might pose as a cook or something on a tanker ship.
Second, practical, I didn't want to make the rules too 
complicated around the fleets with spies.  And third, it is a tradeoff,
the spy gets ``carted around by the fleet" in ways that the spy might not
choose, so in return it gets to look.  I wanted spies on fleets to be a 
fun thing to do.))} 

Rule 5Cc -- from reading this, since spies can be carried by fleets of any
power and ``permission to board" is not required, you can sneak aboard an
enemy fleet and ride it around whether the owner wants you to or not.
Correct? I did note Rule 6D about capturing them. [[from the game's side,
it makes sense; from a real-world aspect -- how can someone really sneak on
a naval fleet without being noticed]]
 
{\it ((See above, that's absolutely right!!  The idea of capturing them is that
you hunt around for Frenchmen and capture people who speak French....
on the sneaking on a fleet, I was thinking a bit more earlier nineteenth
century when you have crews that are brought in.  
My wife and I love the Patrick O'Brien novels with Aubrey and Maturin.
But also the idea that
a fleet has support ships that need cooks and cleaners and people like
that.  The spy doesn't need to be on the flagship, perhaps he is on
the coal tender shoveling coal.))}

Rule 5Cc clarification -- as spies may not move from a fleet ``in retreat"
and as the spy movement phase is before ``Autumn" retreats, a spy on a fleet
dislodged in Fall is stuck on it until after the Winter adjustments are
completed.

{\it ((That is precisely correct.  And indeed the Spy is at risk of being 
disbanded!
That isn't especially realistic, I know, when you disband a fleet, presumably
one wouldn't just sink it with all hands (including spies) aboard, but I 
don't believe in pure realism in rules, the variant plays better this way.))}

I take it that it this will be a regular game (all players known). If you
have a Press-Gunboat game in the future, keep me in mind.
         
\centerline{--Andy, wandrew of compuserve.com}
 
{\it ((Absolutely, this will be a regular game, I don't do Gunboat, so you'll
have to look elsewhere for that.
Ordinarily, I wouldn't print such a statement, since it might give a hint for
a game, but I mean I ***NEVER*** do Gunboat..... I really do have an objection
to it as a variant.
In the E-Mail world I've achieved a bit of fame about it.
I've been asked about the Wing Rules for Modern.
Here they are, I can't find the Starting Positions with the Wings,
can anyone help me out, I think three of the Powers start with Wings.))}

\bigskip

\centerline{Wing Rules} 

1.A wing unit can move over both land and water spaces. 
   
2.A wing unit can support actions in any space adjacent to the one it occupies. 
   
3.A wing can give, receive and cut support in the same way as armies and fleets. 
   
4.A wing unit cannot convoy or be convoyed. 

5.A wing unit cannot capture an SC, but instead blockades it: 
        
\indent\indent 5.1.A blockade occurs when a wing unit occupies the SC of 
another player in a fall season. 
        
\indent\indent 5.2.The player who owns a blockaded SC does not count 
it when counting his total number of SCs. 
        
\indent\indent 5.3.A blockade ends as soon as the wing unit no longer occupies the SC. 
        
\indent\indent 5.4.Builds only take place in the winter phase, just as in games without wings. 

\vfill\eject

\centerline{\bf {\it THE ABYSSINIAN PRINCE} GAMES SECTION}

\smallskip

``So I called up George and he called up Jim, I said let's make a deal.

He said he'd talk to him.  Gonna start a church where you can save yourself,

You can make some noise, When you've got no choice...

You told me useful things, what people think of me, I guess I should thank you.

It's true, then I agree... I'm all alone, I've got no choice,

I'm all alone, I've got no choice."

From ``Got No Choice" by the incomparable Mark Cutler, from the CD
{\it Mark Cutler and Useful Things}.

\smallskip

\indent If you want to submit orders, press, or letters by E-Mail,
you can find me through the Internet system at
``burgess of world.std.com''.
If anyone has an interest in having an E-Mail address listed so people
can negotiate with you by computer, just let me know.
FAX orders to (401) 277-9904 if you let me know in advance to be sure
the fax machine is set up. 

I am continuing to note cut or failed support orders with a 
small ``s'' instead of a capital ``S''.
This will make it easier on the E-Mailed version of the szine to see
what happened, since the italics don't show there.
The italics DO show on the web page just fine.

\indent Standby lists:

Mike Barno, Dick Martin, Brad Wilson, Jack McHugh, Glenn
Petroski, Steve Emmert, Mark Kinney, Vince Lutterbie, Eric Brosius,
Paul Rauterberg, Bob Osuch, Doug Kent, Sean O'Donnell, Vern Parker,
Heath Gardner, Paul Kenny, and Jeff O'Donnell
stand by for regular Diplomacy.
%I am willing to take over for NMR or start new-Diplomacy.
%Vern Parker
%337 Winter Hill Pl.
%Powell, OH 43065
%VSParker of aol.com
%614-402-5139

Let me know if you want on or off these lists, especially OFF.
Standbies get the szine for free and receive my personal thanks.

\bigskip

\centerline{GAME OPENING INFORMATION} 

\smallskip

We've got lots of openings in the subszines, check them out!!!
Especially, contact Rip Gooch for Railway Rivals,
see Rip's subszine elsewhere in most issues of {\it TAP}.
Contact Rip Gooch directly at xyropedes of canada.com and try to entice him to return.
Rip has been a bit missing in action lately, but I am assured that he
SHALL return.

I'm ready to start a new Breaking Away game, who's interested???
Challenge David Partridge again as he is in, so are 
Brendan Whyte and Alexander Woo.
I also am giving a free spot to Eric Martin.
Anyone else?
Rick Desper is in too.
That leaves us looking for ONE more spot, can I convince someone to take that now???
Please, please, I'd like to get toward starting that next issue!!!

I am willing to open another new game of REGULAR Diplomacy if there is enough interest!!!
Sean O'Donnell starts the list, who would like to join him???

Also, is there any interest in another game of Nuclear Yuppie Evil Empire 
7x7 Dip?
I know it may be getting tired, but I really like it.
We have Karl Schmit and Sean O'Donnell on the list, let's get seven!!
It's FREE!!!

I also am starting a game of the variant I designed, Spy Diplomacy.
Signups for that are now open.
Bruce Edwards and Eric Ozog are signed up.
The rules were published recently, ask to see them if you missed them!!!

John Harrington is offering to guest GM a game of Office Politics.
Any interest in that??
Let me or John know!
Jody McCullough and Bruce Edwards are interested, anyone else?

And since Colonia is over, Harold Reynolds is looking to start something else.

Also, I am going to design some postal rules for Devil Take the Hindmost,
and we have an opening here:
Bruce Edwards, Mike Barno, and Eoghan Barry are signed up.
Postal rules from me will be forthcoming shortly, on my never ending to-do list.
I will get them in SOON!
I'm more likely to get these things started if I see some interest.....
I've GOT to do this now,
Eoghan is getting tired of waiting....

Right now, the other thing going is the Modern
Diplomacy game with Wings.
Sean O'Donnell, Jeff O'Donnell, Steve Koehler, Art Schleinkofer,
Bob Holt, Rick Desper, Alexander Woo, and Dave Partridge are signed up for that.
I will start it when I get a full complement of players, we only need TWO more!
%Sean's list: Britain, Spain, Germany, France, Egypt, Turkey, Russia, Ukraine, Italy, and Poland.

\bigskip

\centerline{\bf TAKING OVER ISHKIBIBBLE'S REGULAR DIPLOMACY GAMES ((NOT))}

\smallskip

Last chance for anyone who was a subber to {\it Ishkibibble} to join any new
game for free, but this is a ONE TIME only offer, get your request in now.
It is going to expire VERY shortly.
Marc Ellinger and Fred Wiedemeyer already have taken us up on this request.
Come on, let me call by name who qualifies
for this deal..... Karl Schmit, John Power, Tim Snyder,
Dave Partridge, Graham Wilson, and Kevin Wilson.
I especially would like to fill the Modern Diplomacy game that Dave Partridge
already is in.

\bigskip

\centerline{\bf THE PHIL REYNOLDS MEMORIAL: 2006B, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SPRING 1901 IS SEPTEMBER 30TH, 2006}

\smallskip

\indent {\it Winter 1900}

\noindent AUSTRIA (Burgess): has a BUD, a VIE, f TRI, 

\noindent ENGLAND (James): has a LVP, f LON, f EDI.

\noindent FRANCE (Williams): has f BRE, a PAR, a MAR.

\noindent GERMANY (Ellinger): has a MUN, f KIE, a BER.

\noindent ITALY (Crow): has a VEN, a ROM, f NAP.
%A Rom-Apu, F Nap-Ion, A Ven-Tyo
%A Apu-Tun, F Ion C A Apu-Tun, A Tyo-Mun

\noindent RUSSIA (O'Donnell): has a WAR, f SEV, a MOS, 
f STP(SC).

\noindent TURKEY (Wiedemeyer): has f ANK, a CON, a SMY.

%\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Burgess):&TRI,VIE,BUD,ser,bul,rum,gre&(has 6, bld 1)\cr
%\+ ENGLAND (James):&EDI,LVP,LON,nwy&(has 4 or 5, even(r:otb) or rem 1)\cr
%\+ FRANCE (Williams):&PAR,BRE,spa,por&(has 5, rem 1)\cr
%\+ GERMANY (Ellinger):&KIE,BER,MUN,hol,den,bel,swe,&(has 6, bld 2)\cr
%\+ &\enskip mar \cr
%\+ ITALY (Crow):&ROM,NAP,VEN,tun&(has 5, rem 1)\cr
%\+ RUSSIA (O'Donnell):&WAR,STP,SEV,MOS&(has 4, even)\cr
%\+ TURKEY (Wiedemeyer):&ANK,SMY,CON&(has 3, even)\cr
%\+ Neutral:&none&(Total=34)\cr
%
\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: David Burgess, 101 Laurel Lane, Queensbury, NY  12804

(518) 761-6687, dburgess of glensfallshosp.org

\noindent ENGLAND: Drew James, 3644 Whispering Woods Terrace,
Baldwinsville, NY  13027

(315) 652-1956, kjames01 of twcny.rr.com 

\noindent FRANCE: Don Williams, 27505 Artine Drive, Saugus, CA 91350, 
(661) 297-3947, 

wllmsfmly of earthlink.net or dwilliams of fontana.org (\$5)

\noindent GERMANY: Marc Ellinger, 751 Turnberry Drive,
Jefferson City, MO 65109

ellingermc of aol.com

\noindent ITALY: John Crow, 824 Kinwest Parkway \#101,
Irving, TX  75063, (214) 532-1418

\noindent RUSSIA: Jeff O'Donnell, 402 Middle Ave., Elyria, OH  44035-5728,

(440) 322-2920 or (440) 225-9203 (cell, as late as midnight Eastern)

\noindent TURKEY: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  

CANADA  T6T 1N1, (780) 465-6432, wiedem of planet.eon.net 
%cell 780-497-8283; fax 780-468-6432

\bigskip

{\it Game Notes:}

1) Welcome to our newest regular Dip game.
David is my brother, but I've decided to let him play here after debating it back 
and forth for awhile.
You can see how unbiased I can be to start as he ended up with Austria in the 
Random Draw, and there he stays.
John Crow and Drew James are returning after relatively long absences from the
Dip Scene, welcome back!!!
Jeff, Don, and Fred have been in lots of games here recently.
And Marc is a recipient of one of the Phil Reynolds memorial slots.
I thought it would be a good tribute to name this the Phil Reynolds Memorial.

2) Note the 2006B Boardman Number above.

3) John Crow and Jeff O'Donnell are NOT on-line, I don't believe.  But both enjoy
getting cell phone calls about the game, I believe.
Otherwise, you'll have to work out your own ways of communicating.
I think I have all the relevant contact information filled in above.
I do have lots of the orders in hand, with this delay, you'll have a few
more weeks to interact.
I fixed my brother David's E-Mail address, which I got wrong -- of course.

\bigskip
 
{\it Press:}

(JEFF O'DONNELL to JIM AND EVERYONE ELSE): Anyone who wants to contact me by going on-line
and contacting my nephew Sean O'Donnell may do so.
I will get the message.

(SEAN to BOARD): If you do send me mail for Jeff please put the game name in 
the subject line. Also if I ever do get called into this game as a standby 
please consider this option null and voided. Nothing spoils a game intrigue 
than sending a mail to setup a stab of dear ol Seany than announcing it to 
me. Wouldn't you all agree? I want to figure it out not get it announced if 
you all follow.

(EVIL COMMANDER WORF to UNIVERSE): I encourage the destruction of the 
Empire. When the moment is right perhaps I can send the Evil Captain Kirk 
to battle Kirk for supremacy.

\bigskip

\centerline{\bf SPIRALS OF PARANOIA: 2005A, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR FALL 1904 IS SEPTEMBER 30TH, 2006}

\smallskip

\indent {\it Summer 1904}

\noindent AUSTRIA (Rauterberg): R a bul-GRE; has a BUD, a VIE, a SER, 
a GAL, a GRE, 

a TRI, f ION.

\noindent ENGLAND (Wiedemeyer): has f NAT, a WAL, f ENG, f NWG.

\noindent FRANCE (Tretick): R f nat-CLY; has f MID, f CLY, a LVP, f IRI.
%f mid-bre, f iri s a lvp, f cly s a lvp, a lvp s ger a hol-edi

\noindent GERMANY (Ozog for Tallman): has a MUN, a HOL, a BOH, a TYO, 

f NWY, a MAR, a PIC, f NTH.

\noindent ITALY (O'Donnell): has f TUS, a PIE, a VEN, 
f ADR.

\noindent RUSSIA (Sundstrom): R a gal-UKR; has a UKR, 
a SEV, a WAR, a LVN.

\noindent TURKEY (Biehl): has f AEG, f BUL(SC), f SMY.
 
%\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Rauterberg):&TRI,VIE,BUD,ser,bul,rum,gre&(has 6, bld 1)\cr
%\+ ENGLAND (Wiedemeyer):&EDI,LVP,LON,nwy&(has 4 or 5, even(r:otb) or rem 1)\cr
%\+ FRANCE (Tretick):&PAR,BRE,spa,por&(has 5, rem 1)\cr
%\+ GERMANY (Ozog/Tallman):&KIE,BER,MUN,hol,den,bel,swe,&(has 6, bld 2)\cr
%\+ &\enskip mar \cr
%\+ ITALY (O'Donnell):&ROM,NAP,VEN,tun&(has 5, rem 1)\cr
%\+ RUSSIA (Sundstrom):&WAR,STP,SEV,MOS&(has 4, even)\cr
%\+ TURKEY (Biehl):&ANK,SMY,CON&(has 3, even)\cr
%\+ Neutral:&none&(Total=34)\cr
%
\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Paul Rauterberg, 3116 W.~American Dr., 
Greenfield, WI  53221, 

(414) 281-2339 (E-Mail)  trauterberg of wi.rr.com

\noindent ENGLAND: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  CANADA  T6T 1N1, 

(780) 465-6432, wiedem of planet.eon.net 
%cell 780-497-8283; fax 780-468-6432

\noindent FRANCE: Buddy Tretick, 5023 Sewell's Pointe Way,
Fredericksburg, VA  22407, (540) 898-3386

cell (540) 226-5571 (E-Mail) berniebuddy32 of aol.com

\noindent GERMANY: Terry Tallman, PO Box 782, Clinton, WA  98236,
(360) 331-5698 (\$2) 

terryt of whidbey.net

\noindent GERMANY: Temporary Standby is Eric Ozog, PO Box 1138, Granite Falls, WA  
98252-1138,

(360) 691-4264, ElfEric of Juno.com

\noindent ITALY: Jeff O'Donnell, 402 Middle Ave., Elyria, OH  44035-5728,

(440) 322-2920 or (440) 225-9203 (cell, as late as midnight Eastern)

\noindent RUSSIA: Matt Sundstrom, 1760 Robincrest Lane South, Glenview, IL  60025, 
(847) 729-1882, 

Matt.Sundstrom of bbdoch.com or mattandzoe of earthlink.net

\noindent TURKEY: John Biehl, \#8 -- 11530 84th Avenue, Delta, BRITISH COLUMBIA,
V4C 2M1  CANADA, 

(604) 816-0460 (cell) (\$7); jrb of dccnet.com

\bigskip

{\it Game Notes:}

1) Terry is still having some medical problems, 
Eric Ozog is continuing to
negotiate and submit orders for Terry.
Eric originally brought Terry into the Diplomacy hobby all those many
years ago, and so I'm glad he's agreed to do this.

\bigskip
 
{\it Press:}

(SEAN to BOARD): Please put the game name in the subject line if you write 
me to get hold of Jeff.

(7 OF 9'S LOG): Help!
I really screwed up!
The Cardassians did not attack and have signed a peace agreement but the 
Starship Excelsior is now desperately out of position.
Everyone seems to be attacking everyone, I hope our reconciliation
with Cardassia holds...

(JEFF--WORLD): As if the economic situation was not bad enough with
Ford reorganizing and the price of oil, comes news from the 
International Astronomical Society that the planet Pluto is
being laid off.
This news comes at a bad time for the Bush administration
as it was being considered an alterntative location
for the prisoners at Guantanimo Bay.
When asked to comment, Pluto was quoted as saying, ``I'm no
longer a planet but I've had a great run.
I've been declared the largest ice sculpture in the galaxy.
My advisors say that although my days as a planet are done,
I can still try to find a new career by running for Senator
of the State of New York.

(JIM-BOB OPINES): Excelsior, indeed!!!
And you think New York State needs more Carpetbaggers?
Note the groaner triple entendres on both sides....
I don't think we need to feel sorry for Pluto since, as we all know,
this means EVEN greater fame and fortune for Pluto as the planet
that is no more.
Can Venus or Mercury say the same???
Besides, Pluto is the god of death and the underworld, we should never
have let him see the light of day in the first place.
Yet more evidence that baby boomers are continuing their fantastical campaign
to abolish death, Woody Allen excepted.
Well, it won't work, gosh darn it, they're ALL going to die in the end.
Really.
As an economist, what I will find most interesting about the Ford
buyouts (which will precede any layoffs) is how workers respond to the
three choices they face:
(1) Take a lower financial buyout and keep their medical care [this will
be people who have the largest aversions to risk AND think about the 
future rationally]; (2) Take the higher financial buyout and give up
their medical care [these will be the people that traditional economists
call irrational, but really are just expressing that large amount of 
impatience that is growing in our population and confounding the 
economists who thought that we got more patient as we got older and
more educated... not this group, and that's rational if that's what
they really want -- we can't be bailing them out later when the
consequences of their choices come back to bite them in the butt!];
or (3) Take the risk of staying on and seeing if they are laid off
later, the risk includes the strong possibility that they will be
moved to another location 
(believe you me, some of my brother and sister economists will be
studying the wonderful natural experiment, I'll report back later).

\bigskip

\centerline{\bf FLIP FLOP: 2003G, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SPRING 1908 IS SEPTEMBER 30TH, 2006}

\smallskip

\indent {\it Winter 1907}

\noindent AUSTRIA (Wiedemeyer): R a rum-GAL, a rom otb; rem a nap; 
has f ADR, a BUD, a GAL,  

a UKR, a MOS, a TRI.

\noindent ENGLAND (Schmit): rem a nwy, f por; has a BUR, a HOL, f ENG, 
a RUH,

f BEL, f NWG, f NTH.

\noindent FRANCE (Jeff O'Donnell): bld a par; has a PAR, a BRE, f SPA(SC), 
a GAS.

\noindent GERMANY (Sundstrom): R f nwy-SKA; bld a ber; has a BER, f HEL, 
f SWE, a DEN, 

a STP, a MUN, f SKA.

\noindent TURKEY (Levinson): bld a ank, f con; has a ANK, f CON, a BUL, f ION, f ROM, 
a ALB, 

f TYH, f BLA, a RUM, a SER.

\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Wiedemeyer):&TRI,VIE,BUD,ven,nap,mos&(has 6 or 7 or 8, even(2 r:otb) or\cr 
%\+ &&\enskip rem 1(1 r:otb) or 2)\cr
%\+ ENGLAND (Schmit):&EDI,LVP,LON,nwy,bel,hol,por&(has 9, rem 2)\cr
%\+ FRANCE (Jeff O'Donnell):&PAR,MAR,spa,BRE&(has 3, bld 1)\cr
%\+ GERMANY (Sundstrom):&KIE,BER,MUN,den,swe,war,stp&(has 5 or 6, bld 2(r:otb) or 1)\cr
%\+ TURKEY (Levinson):&ANK,SMY,CON,bul,sev,ser,gre,&(has 8, bld 2)\cr
%\+ &\enskip tun,rom,rum \cr
%\+ Neutral:&none&(Total=34)\cr
%
%\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  CANADA  T6T 1N1, 

(780) 465-6432, wiedem of planet.eon.net 
%cell 780-497-8283; fax 780-468-6432

\noindent ENGLAND: Karl Schmit, 1509 O'Keefe Road, DePere, WI  54115, (920) 338-8402, 

diplomacy of new.rr.com (\$4)

\noindent FRANCE: Jeff O'Donnell, 402 Middle Ave., Elyria, OH  44035-5728,

(440) 322-2920 or (440) 225-9203 (cell, as late as midnight Eastern)

\noindent GERMANY: Matt Sundstrom, 1760 Robincrest Lane South, Glenview, IL  60025, 
(847) 729-1882, 

Matt.Sundstrom of bbdoch.com or mattandzoe of earthlink.net

\noindent ITALY: Don Williams, 27505 Artine Drive, Saugus, CA 91350, 
(661) 297-3947, 

wllmsfmly of earthlink.net or dwilliams of fontana.org

\noindent RUSSIA: Sean O'Donnell, 1044 Wellfleet Drive, Grafton, OH  44044,
(440) 926-0230, 

sean\_o\_donnell of hotmail.com

\noindent TURKEY: Alexandre Levinson, Beeklaan 504, 2562BP Den Haag
THE NETHERLANDS, don't need phone, 

levinson7 of hotmail.com (\$5)

\bigskip

{\it Game Notes:}

1) Lots of press, lots of changes, what now for this game year???
No draw proposals yet, that's for sure.

\bigskip

{\it Press:}

(SEAN--PETTY DICTATOR (UNCLE JEFFY POOH)): Laughing out loud. I still can't 
believe that it took so long for you to realize that was me.

(SEAN to BOARD): If you do write me to get hold of Jeff, so he resembles 
having an e-mail please make sure to put the game name in the subject line. 
Thanks.

(JEFF O'DONNELL to WORLD): Not only is Jim's brother David very welcome 
to the Phil Reynolds game, I'm confused why anyone would comment
about possible conflict of interest in this situation or when I'm
in any game with my nephew Sean.
There is no conflict of interest because there is no real money involved.
My feeling is that Jim could add his own name 
{\it ((It would be REALLY hard for me to GM a game and play in at the
same time, not COMPLETELY impossible, but really hard.))}
or the names of any number
of friends, and or relatives and I'd be happy to play, in fact, 
I don't think who is playing should be a factor in the decision
to ro not to play.

(DARTH VADER to DARTH SIDIUS): Sooner or later, we will finish this in the 
traditions of the Sith as Apprentice kills their master for supremacy.

(RUSSIAN UNDERGROUND to ENGLAND): What happened?

(RUSSIAN O'DONNELL--RUSSIAN O'DONNELL): Russia sucks.

(STAR TREK PRESS): Captain's Log ``Hopeful".
We thought we were all dead, instead we ahve withour Ferengi allies achieved
a major victory over the Romulans.
We are commissioning a new troop transport and our Ferengi allies are 
adding to their force.
The Romulans have been forced to decommission two unknown ships.

S: Spock to Captain Kirk. 

K: Report.

S: I have interesting news.
Our Ferengi allies are not rally Ferengi after all.

K: Really!
I thought we changed them from Federation to Ferengi!

S: So did I, but our victory over the Romulans revealed prison exchanges
that showed them to be Andorian.
The Andorians were aided by an unknown alien group currently at war with
the Children of Tomari.

K: The Tomarians scare me.
Agreed, but for the moment all we cna hope is that they don't engage us...

(SEAN--BOARD): My guess for England's removals. R F Bel and R F Ech. My second 
choice is R F Por and R F Bel. Note if it's not my first choice. I guess 
wrong.....
{\it ((You're pretty close to completely wrong.... you're not inside Karl's head.
I hope that isn't what your Uncle was assuming...))}

(FRANCE to WORLD): France is building!
This is not a drill, repeat, this is not a drill...

(SEAN--PETTY DICTATOR PART 2): What can I say? You taught me well. Did you 
not teach me when in doubt attack your enemy or something? Didn't you also 
teach me that when you are losing attempt to obliterate units even though I 
do try to do that while I'm winning to. Didn't you also teach me to the best 
of your ability that this is a game of deception; therefore, words are 
meaningless? Finally, didn't you teach me to always woot for myself? (I 
don't recall needing a mentor there.) Oh, there is one more thing that you 
taught me. I'll tell you what. I give you my word as a Diplomacy player that 
I will not encourage Karl (England) of Flip Flop to wipe you out, and I 
further give my word as a Diplomacy player not to encourage anyone else to 
attack the Petty Dicator.

(JEFF to SEAN): It doesn't matter that I'm Russia in Phil Reynolds, Russia 
still sucks!
(Deal with it!)

(SEAN--THE BOARD): Attack France!
{\it ((Sean, if I don't print this now, I'm going to misplace it, so I think
we'll go with it here.))}

(FLIP FLOP ENDGAME STATEMENT RUSSIA):
I have to start by saying congratulations to a game well played. I made 
a couple of mistakes. Has anyone seen the movie Zulu? It's essentially what I 
did. I went out to meet the loins and got carved up. My other major mistake 
was not managing a peace in the southern border. My third mistake  
coincides with the first. I should have allied with Germany opposed to 
putting everything into being able to steal England as an ally from France. 
It was fun though learning the lesson that I should have known all along.

My strategy was to form an E/R/T without directly forming a triple 
alliance. I wanted to form R/T to have a strong alliance even though I 
shouldn't have made the mistake of not really trying to allow Austria into 
the alliance. I tried discouraging this triple which may have been yet 
another mistake. What can I say, I didn't play that alliance very well.
    
My strategy was based on trying to anticipate what Jeff was planning. In 
a one on one game with Jeff (France) I know that R/T and E/F is an even 
counter alliance unless Turkey's standard build included F Smy opposed to 
Ank, or France starts with a fleet in Mar.
     
I figured France would be encouraging a E/F alliance, so I should 
encourage a counter alliance, but I misscalculated how to handle my southern 
borders wanting a R/A/T alliance. Since I openly opposed the alliance with 
Turkey, I'd have to say that's my second largest mistake. It's most likely 
what encouraged wiping me out even though I did try getting Austria to fight 
Germany and Italy. This would have allowed Turkey into a dominant naval 
policy and hopefully reach the Mid stalemate line with all possible speed. 
Neither strategy here worked. Meanwhile, English and Russian diplomacy 
apparently broke down. I was counting on being able to steal England away 
from France, and I wanted to begin negotiations in this regard before 
England was fully engaged with Germany. What I had in mind was blitz 
Germany, and aid England into France while A/T batters Italy and I'm able to 
breach the Germany stalemate line. I focused on the attempt to get England 
to attack France after Germany fell even though I wasn't asking for 
anything. Being the largest starting power, I thought if need be the offer 
of France likely Spa, Por, Par, Bre, Bel, and Mar. England didn't engage 
Germany as I hoped. I offered Stp as a peace offering, but I neglecting my 
southern border trying to gain England against France, and A/T launched an 
offensive against Russia inevitably leaving me with every border hostile to 
Russia. This left me allyless and going down. My strategy to counter and 
destroy E/F inevitably failed. Russia fell not long later.
Maybe, I'll have better luck in the next game. Good game.

\bigskip

\centerline{\bf I CAN'T FIND MY MONEY!: 2001F, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR WINTER 1913 IS SEPTEMBER 30TH, 2006}

\smallskip

\noindent {\bf THE DUE DATE FOR SPRING 1914 IS OCTOBER 21ST, 2006}

\smallskip

\indent {\it Fall 1913}

\noindent AUSTRIA (Parker): NMR, NO STANDBY CALLED; f ADR h, f TUN h, f TYH h, 
a WAR h, a LVN h, 

f EAS h, a PIE h, a CON h, a VIE h, a VEN h, a ARM h, a SMY h, 
a TRI h, a MOS h, f AEG h.

\noindent FRANCE (Kent): f BRE S a par-gas, {\it a PAR-gas, f MID s a par-gas, 
f WES-spa(sc)}.

\noindent GERMANY (Wilson): a MUN h, f ENG C a lon-pic, f BEL S a lon-pic, 
a BUR S a gas-par, 

f LVP h, {\it a SPA s f por}, f POR S a spa, a lon-PIC, a STP h, 
a MAR S a spa, 

{\it f NAO-mid, a GAS-par}.

\noindent TURKEY (Miller): a SYR h, a ANK h. 

\bigskip

\indent {\it Supply Center Chart}

\+ AUSTRIA (Parker):&TRI,BUD,VIE,ser,rum,nap,&(has 15, bld 1)\cr
\+ &\enskip war,mos,sev,ven,rom,bul,gre,smy,con,tun\cr
\+ FRANCE (Kent):&PAR,BRE&(has 4, rem 2)\cr
\+ GERMANY (Wilson):&KIE,BER,hol,den,bel,MUN,swe,&(has 12, bld 2 (PLAYS ONE SHORT))\cr
\+ &\enskip nwy,mar,edi,lon,spa,por,stp,lvp\cr
\+ TURKEY (Miller):&ANK&(has 2, rem 1)\cr
\+ Neutral:&none&(Total=34)\cr
 
\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Vern Parker, 337 Winter Hill Place, Powell, OH 43065,
(614) 402-5139

VernDip of aol.com is preferred

\noindent ENGLAND: Mark Kinney, 4830 Westport Road, Apt D,
Louisville KY  40222

alberich of iglou.com

\noindent FRANCE: Doug Kent, 11111 Woodmeadow Pkwy \#2327, Dallas, TX  75228

dougray30 of yahoo.com 

\noindent GERMANY: Kevin Wilson, 18623 Santa Maria Drive, Baton Rouge, LA  70809,
225-751-3857,

ckevinw1 of cox.net

\noindent ITALY: Formerly was Heath Gardner, metaphorman of gmail.com

\noindent ITALY: Mike Barno, 634 Dawson Hill Road, 
Spencer, NY 14883 

mpbarno of lightlink.com 

\noindent RUSSIA: Rick Desper, 

rick\_desper of yahoo.com

\noindent TURKEY: Tim Miller, 258 New Mark Esplanade, Rockville, MD 20850,

tim of webjudge.net

\noindent GM: Jim-Bob Burgess, 664 Smith Street, Providence, RI  02908-4327,
$+$1 401-351-0287

burgess of world.std.com

\bigskip

{\it Game Notes:}

1) The GAFT draw proposal is defeated and amazingly, the GA-GA sallies forth again.
If you have finally become GA-GA over this game, vote yes to this with your Winter
orders.
If you fail to vote, as usual, you veto the proposal.
Oh wait, we also have the GAFT reproposed, you can vote on that with the same restrictions.
People occasionally ask me what happens if two draws pass, it always is the SMALLER draw
that is the final result when that happens.

2) I did talk to Vern, and he submitted orders for the other game, but he didn't submit
orders here. 
So all his units hold, but I can't believe he wants to walk away from the game.
As always, though, even though I'm not calling a standby now, he has to get orders
in for Winter, and his build, or else I will replace him.

\bigskip

{\it Press:}


\bigskip

\centerline{\bf SECRETS: 1999D, Regular Diplomacy}

\smallskip

\noindent {\bf THE NEW DUE DATE FOR WINTER 1921 IS SEPTEMBER 30TH, 2006}

\smallskip

\noindent {\bf THE NEW DUE DATE FOR SPRING 1922 IS OCTOBER 21ST, 2006}

\smallskip

\indent {\it Fall 1921}

\noindent ENGLAND (Kent): f ENG S f nth, a GAS S FRENCH f mar, 
f NAO S f mid, 

{\it a kie s RUSSIAN a ber-mun} (nso; d r:ruh,otb),
{\it f MID s FRENCH f spa(sc)}, f NTH h, 

f HOL S a kie, f POR S FRENCH f spa(sc).

\noindent FRANCE (Sasseville): {\it f MAR s f spa(sc), f SPA(SC) s f mar}, 
a par-BUR.     
%standing orders, yes to ANY draw
                                             
\noindent GERMANY (Barno): a BUL h.
%votes yes to FREGT, no to EFRT 
%vote YES to FREGT draw

\noindent RUSSIA (Parker): f NWY S f hel-nth, a WAR h, a swe-DEN, 
a BER S a den-kie, 

{\it f HEL-nth}, a den-KIE, a PRU S a ber.

\noindent TURKEY (Linsey): a ARM h, f AEG h, a sev-RUM, 
a GAL S a sil, a SIL S a mun, {\it f WES-spa(sc)}, 

a UKR S a sev-rum, f GOL S f wes-spa(sc), a MUN S RUSSIAN a den-kie, 
a TRI h (uno), {\it f NAF-mid}, 

f ion-TYH, a TYO S a mun, {\it f PIE-mar}, a BOH S a sil, 
{\it a vie-tri} (nsu).

\bigskip

\indent {\it Supply Center Chart}

\+ ENGLAND (Kent):&LON,LVP,EDI,bre,por,bel,hol&(has 7 or 8, even(r:otb) or rem 1)\cr
\+ FRANCE (Sasseville):&PAR,MAR,spa&(has 3, even)\cr
\+ GERMANY (Barno):&con,bul&(has 1, PLAYS ONE SHORT)\cr
\+ RUSSIA (Parker):&MOS,STP,nwy,swe,den,ber,WAR,kie&(has 7, bld 1)\cr
\+ TURKEY (Linsey):&ANK,SMY,rum,gre,&(has 15, rem 1)\cr
\+ &\enskip bud,nap,ven,tun,sev,rom,tri,vie,ser,mun \cr
\+ Neutral:&none&(Total=34)\cr

\bigskip

\indent {\it Addresses of the Participants}

\noindent ENGLAND: Doug Kent, 11111 Woodmeadow Pkwy \#2327, Dallas, TX  75228

dougray30 of yahoo.com 

\noindent FRANCE: Roland Sasseville, Jr., 38 Bucklin Street, Pawtucket,
RI 02861, (401) 481-4280 (\$0)

roland6 of cox.net  

\noindent GERMANY: Mike Barno, 634 Dawson Hill Road, 
Spencer, NY 14883, (607) 589-4906 

mpbarno of lightlink.com 

\noindent RUSSIA: Vern Parker, 337 Winter Hill Place, Powell, OH 43065,
(614) 402-5139

VernDip of aol.com is preferred

\noindent TURKEY: Bruce Linsey, PO Box 234, Kinderhook, NY
12106

GonzoHQ of aol.com

\bigskip

{\it Game Notes:}

1) There are no current proposals at the moment.

\bigskip

{\it Press:}
 
\bigskip

\bigskip

\bigskip

\centerline{\bf FINDING THE COMMUNITY: Breaking Away, Designer's Rules}

\smallskip

\noindent {\bf CONGRATULATIONS TO RICK DESPER WHO HUNG ON FOR THE VICTORY!!!}

%\smallskip
%
%\noindent {\bf GAME OVER -- DUE DATE FOR ENDGAME STATEMENTS IS SEPTEMBER 10TH, 2005}
%
%\smallskip
%
%--F--I--N--A--L-- --F--I--N--I--S--H-- --L--I--N--E--
%--S--P--R--I--N--T-- --F--I--N--I--S--H-- --L--I--N--E--
%
%\centerline{\it Turn 16}
%
%\smallskip
%
%\+ Finished:                &Pebble, Homer, Spades (12), Clay (10), El Vez (8),  \cr
%\+                          &\indent Carl Sagan (6), James (4), Paige (2)    \cr

%--F--I--N--A--L-- --F--I--N--I--S--H-- --L--I--N--E--

%\+ 120 (replenish with a 3) &Spades  \cr
%\+ 119 (no replenishment)   &Empty   \cr
%\+ 118 (replenish with a 3) &Clay, El Vez   \cr
%\+ 117 (replenish with a 5) &Carl Sagan, James   \cr
%\+ 116 (replenish with a 7) &Sand, Paige  \cr
%\+ 115 (replenish with a 9) &Hearts, Geri Lee Lewis, Johnny Peso   \cr
%\+ 114 (replenish with a 12)&Marge   \cr
%\+ 113 (replenish with a 13)&Franklin  \cr
%\+ 112 (replenish with a 14)&Wade, Diamonds   \cr
%\+ 111 (no replenishment)   &Empty     \cr
%\+ 110 (replenish with a 3) &Frederick, Clubs, Edmond   \cr

\bigskip
%Sprint Points: 10,8,6,5,4,3,2,1 (final are just double these)
%Movement Order: A/B/C/D; highest card played that turn; highest card in hand

%\indent {\it Addresses of the Participants -- Their Team and Their Cards}

%\smallskip

%\noindent TEAM 1 (Rick Desper): rick\_desper of yahoo.com (55 points, efficiency
%score 13.7\%)

%Team Name: Team Springfield

%\+ A: Homer Simpson &&Finished \cr
%\+ B: Marge Simpson &&(3) 3 3 12  \cr
%\+ C: Bart Simpson  &&Sulks \cr
%\+ D: Lisa Simpson  &&(4) 3 5 6 \cr

%Total Replenishments: $22+63+46+13+15+29+21+17+25+17+18+33+32+10+13+18 = 402$
                
%\smallskip

%\noindent TEAM 2 (Bruce Edwards): kactusjak of ntlworld.com (8 points, efficiency
%score 2.3\%)

%Team Name: Last Again

%\+ A: Zedd   &&(3) 3 3 3 \cr
%\+ B: Omega  &&(4) 3 3 3 \cr
%\+ C: Paige  &&(13) 5 10 7 \cr
%\+ D: James  &&(16) 3 6 5 \cr

%Total Replenishments: $16+37+29+25+12+13+26+24+21+18+16+15+30+23+32+18 = 355$        
   
%\smallskip

%\noindent TEAM 3 (Tom Howell): off-the-shelf of olympus.net (31 points, efficiency
%score 8.0\%)%360-928-9698

%Team Name:  The Soils; Manager:   Boulder

%\+ A:   Clay    &&(7) 3 5 3 \cr
%\+ B:   Silt    &&(4) 4 4 4  \cr
%\+ C:   Sand    &&(10) 3 3 7 \cr
%\+ D:   Pebble  &&Finished \cr

%Total Replenishments: $17+62+63+25+12+13+12+29+27+21+17+31+15+15+13+14 = 386$   
               
%\smallskip

%\noindent TEAM 4 (Dennis Menear): dmenear of wirefire.com (9 points, efficiency
%score 2.2\%)

%Team Name: The Firm

%\+ A: Edmond    &&(5) 3 3 3 3  \cr
%\+ B: Franklin  &&(10) 4 4 13 \cr
%\+ C: Frederick &&(4) 4 3 3 \cr
%\+ D: Wade      &&(8) 3 3 14 \cr

%Total Replenishments: $12+28+32+35+38+25+24+17+29+21+15+26+21+35+26+33 = 417$

%\smallskip

%\noindent TEAM 5 (David Partridge): rebhuhn of rocketmail.com (36 points, efficiency
%score 8.5\%)

%Team Name: It's In The Cards; Manager: The Joker

%\+ A: Spades   &&(7) 3 3 3 3 \cr
%\+ B: Hearts   &&(6) 2 3 9 \cr
%\+ C: Diamonds &&(8) 5 6 14 \cr  
%\+ D: Clubs    &&(5) 3 3 3 \cr
           
%Total Replenishments: $17+55+51+25+30+24+26+20+34+15+15+25+18+20+22+29 = 426$ 

%\smallskip 

%\noindent TEAM 6 (Karl Schmit): diplomacy of new.rr.com (17 points, efficiency
%score 3.6\%)

%Team Name: 25 Dollar Quartet

%\+ A: Carl Sagan      &&(15) 3 9 13 5 \cr
%\+ B: El Vez          &&(15) 13 10 3 \cr
%\+ C: Geri Lee Lewis  &&(13) 9 9 9 \cr
%\+ D: Johnny Peso     &&(13) 1 8 9 \cr

%Total Replenishments: $12+37+22+44+16+27+28+27+32+39+33+20+24+39+49+26 = 475$

\bigskip

{\it Game Notes:}

1) The rules are on the {\it TAP} website in the {\it Tinamou} section.
Ask if you have any questions.
New game start in this, who wants to play again (or for the first time)???
We have five signed up so far, see the list in the game opening section.
I want to start this up soon, so sign up!!!
Can I twist arms on just ONE more of you to join???

%Up above in parentheses is the card you played to get to where you are
%in the field.  The replenishment card is the last card in your list.
%Be careful to note that the card you played (the one in parentheses) is
%not available for you, for next turn.
%Just for fun, I'm going to keep track of total replenishment, by turn, which is a 
%rough measure of how the teams are doing.
%Of course, it is lining up to get across the sprint and final lines in the
%right places that really counts.
%We can calculate an ``efficiency score" later, which will be the ratio
%of scoring points per replenishment.
%If I'm predicting how the future of this will come out, a 10\% score will
%be really tremendous for this measure.

\bigskip

{\it Press:}


\bigskip

{\it Personal Note to You:}

\vfill\eject
\end
