\nopagenumbers 
\font\twelverm=cmbx12 at 12pt
\centerline{\bf\twelverm THE ABYSSINIAN PRINCE \#311}
\line{\hfil June 1, 2007}    
\smallskip                                                    
\settabs 3 \columns 
\beginsection

\medskip

Produced by Jim Burgess, 664 Smith Street, Providence, RI 02908-4327  USA,
(401)351-0287 
 
\noindent Accessible through Internet at burgess of world.std.com (all E-Mail
addresses are reported in this format, replace the `` of '' with ``@''; if you 
bounce try sending to me from another account. 
Some of you have been getting bounced messages from
my ISP's spam protection, if that happens to you, USE my backup E-Mail
at jfburgess of gmail.com!!!  Don't complain that my E-Mail keeps bouncing
without forwarding the bounced message to that address.
Then I can forward it to the ISP help to get it dealt with.
 
\noindent Web Page Address: http://www.diplom.org/DipPouch/Postal/Zines/TAP/index.html

\bigskip

I expect ALL players to be signed up on the E-Mail notification list for the szine,
see below.
Some of you have been complaining about this, but it is up to you to get on this list,
it's easy, come ask me if you have trouble.
THIS IS A PROBLEM, sign up now if you're playing!!!

So, what can I say?  I was REALLY wrong about the szine being able to stay on schedule.
So we lost two months.  I think that was just ``this two months", at least I am going
to try to ensure it becomes only these two months.
As a result, it sent all the subszines behind and this issue is huge in subszines, if
a bit light on me.
Still, the main point is to get the games back on track, which I think it does.
I've set what should be reasonable deadlines for the next two issues, with some adjustments
so that they aren't the usual three weekers, but focused on when I actually can 
produce it.
Enough of that. 

On the GOOD side, I helped Doug Kent get one issue of {\it Diplomacy World} out,
and we are well on the way to a dynamite second one, so I think we will reach
the century mark very shortly.
I helped do the testing so that we move to the next step so 
the new Diplomacy National World Cup is recruiting players, interested?
See below.
And, I've been having fun actually playing Dip again.
So I have been busy, just the szine hasn't gotten to the top of the list.

\bigskip
%Dave Partridge's unlisted phone number 603-672-2879 -- probably corrected!!!
%Tinamou players: Schwarzschild:  Graham Wilson (NO 
%but E-mails: grahamaw of home.com (or gwilson of dvnet.com)),
%Berry Renken, Heath Gardner
%Copernicus:  Warren Goesle, Heath Gardner, Art Schleinkofer, Bruce Reiff,
%Eric Brosius, Bob Dowrey
%Tour De Farce:  Jim Burgess, Eric Brosius, Warren Goesle, Sara Reichert,
%Phil Reynolds, Rick Desper
%Milk and Cookies: Jim Burgess, Warren Goesle, Sara Reichert, Phil Reynolds,
%Rick Desper, Richard Weiss, John Schultz
%Who's Your Buddy:  Sara Reichert, Phil Reynolds, Art Schleinkofer, 
%Brad Wilson, Rick Copeland, Karl Muller

The postal sub price is still
\$1.50 per issue in the US and Canada,
with double that for other foreign subbers(or \$3.00 per
issue sent airmail).
Players in current games and standbys will
continue to get the issues for free, and future game starts 
(except for Nuclear Yuppie Evil Empire Diplomacy, which is free) cost 
\$20.00 (\$15.00 for a life of the
game subscription and \$5 for the NMR Insurance.
Anyone may play in subszines 
for free and just jack up the issue page count. 
See the revised game start announcements below!

Check out the connections in the Diplomatic Pouch with all of
the information you need to play Diplomacy on the Internet at:
http://www.diplom.org/DipPouch/

I also have taken over the Postal port/DipPouch/Postal

\noindent and {\it TAP} on the web is there at:
http://www.diplom.org/DipPouch/Postal/Zines/TAP/index.html

where the szine resides in html format. 
Presently, issues from \#190 to the current issue
are there, and I will be updating the back issues gradually someday. 
 
Peter Sullivan's subszine is out of stasis, and all the
back issues can be accessed via :

http://www.burdonvale.co.uk/octopus/index.html.

Peter is now back.
Rip Gooch is probably permanently missing.
Dave Partridge had been picking up the choo-choo
game slack.
Contact Dave
at rebhuhn of rocketmail.com for more info on getting into choo-choo games.
And Andy York has been my most frequent subszine guest lately!!!
He's been in every issue, thanks, Andy!!!
And so has Doug Kent, so we have a full stable of subszines.
And Michael Lowrey gets his in every few issues too!

The {\it TAP} mailing list has moved!
It now is even BETTER protected than it was.
I even have a bit of trouble posting to it.
To post to this list, send your email to: tap of diplom.org.
But this is completely moderated, it won't go out to the list unless
I approve it.
In general, I intend to keep traffic down to just the szine, as we've
been doing and I'll put your LOCs in here.
I {\bf EXPECT} all players to be on this list, especially those of you who
are from foreign countries!!! 
You need this to find out when the szine is up on the web to check in on results.

General information about the mailing list is at:
http://www.diplom.org/mailman/listinfo/tap

You can sign up from there, or send E-Mails to:
Tap-request of diplom.org;
with the word `help' in the subject or body (don't include the
quotes), and you will get back a message with instructions.
You must know your password to change your options (including changing
the password, itself) or to unsubscribe.  
Normally, Mailman will remind you of your diplom.org mailing list
passwords once every month, although you can disable this if you
prefer.  This reminder will also include instructions on how to
unsubscribe or change your account options.  There is also a button on
your options page that will email your current password to you.
A big, big thank you for Millis Miller for setting this all up!!

\bigskip

\centerline{\bf THE SEARCH FOR ERIC JUST -- HE'S FOUND TOO!!!}

\smallskip

As I should have known, Jeff Key knew how to find Eric Just, so
Jeff wins the fifty dollar prize.
Jeff, anything you want to do with that that I can help you with?
Or you can follow Edi's lead and donate to my travel fund, 
which NO ONE has claimed yet!!!

\bigskip

Feel free to spend the time looking for some of the backlog.
Let's get Margaret, Derek, Sylvain, Steve, Ed, Tom, Gregory, and 
ESPECIALLY Kevin found too!!!
This is a regular continuing feature of the szine
and I will be introducing a new ``search for'' every five issues.
Moreover, you can win a \$25 prize for finding some previous
target who went unfound in the original \$50 period.
That means that if Margaret Gemignani or 
Steve Heinowski or Ed Henry or Tom Hurst or 
Gregory Stewart or Derek Nelson or Sylvain LaRose or John Smythe
is ``found'' from now on it is worth \$25.

\bigskip

Winners will receive credit for Dip hobby activities
that I will pay out as requested by the winner.
Subscribe to szines here or abroad, run your
own contests, publish a szine, finance a web page, 
GO TO A DIPLOMACY CONVENTION or whatever.
Spend it all right away or use me as a bank to cover hobby activities
for years.
What must you do to win?
Get me a letter to the editor for {\it TAP} from the person we're
searching for.

This is very important, just finding them doesn't do it.
They have to write me a letter.     
The final judge as to the winner of any contest will be the target 
himself and I reserve the right to investigate the winning entry.
When you find someone I'm looking for, you should ask him to send me a 
letter for print that includes a verification of who ``found'' him.
%Michael Swift, Mike Stewart, and 
%Jason Yarbrough , Tim Stabosz, 
%Eric Ozog has $25
%Leslie Obata is owed $25
%Derek Nelson, winner of the first postal game in Graustark.  I last saw him
%at the '76 DipCon in Baltimore.
%Charles Wells, former publisher
%John McCallum, former publisher (Brobdignag, SerenDip, etc.)
%Dan/Charles Brannan, former publisher (Wild 'n Wooly)

\bigskip

{\bf Jeff Key (Apr 22, 2007, at 5:14 AM)}

{\it The Abyssinian Prince} \#310 arrived here last evening and I am  
mightly impressed.  My, how Diplomacy magazines have changed since  
those early days of memographs and spirit duplicators of the mid-60's.

You didn't tell me that you were looking for Eric Just as well!  Of  
course I know where my water brother is!  All you had to do was  
ask...  You may contact Eric in Oklahoma City at Ericose of aol.com.   
In addition to Just's Right Hand Rule, in the world of Diplomacy he  
should be recognized as one of the originators of Postal Diplomacy.

\centerline{My regards to you all, Jeff, geoffri of sbcglobal.net}

\bigskip

{\bf Edi Birsan (Sun, 22 Apr 2007 08:00:13 -0700)}

I also recall that you played this version where the armies and  
fleets were numbered
and if the unit was destroyed you could not bring it back and played  
one unit short forever or
maybe it was that you had only 8 Armies and 8 fleets and regardless  
of your center count you could never get more
that those on the board...
What was the exact weirdness around that anyway?

\centerline{Edi Birsan, EdiBirsan of astound.net}

\bigskip

{\bf Jeff Key (Sun, 22 Apr 2007 11:49:33 -0700 (PDT))}

Edi,
You have it partially right.  My 1959 Edition of Diplomacy 
did have numbered units and legal orders could be written such as 
3A to Bulgaria and 1F (S) 3A to Bulgaria.  
That set came with 10 numbered armies (70 blocks) for each Great 
Power and either 9 or 10 numbered fleets apiece (66 blocks).  
 
The only ``odd" rule that we played was that one could win by having 
a majority of the pieces on the board.  If I remember the details correctly, 
I won my first postal game because of that rule.  
Eric Just and I had agree to a 17-17 split of the centers on the board.  
I reached my 17 first.  On a Spring turn Eric attacked Jim Bradley's 
one remaining German army in Belgium from the Ruhr and Holland.  
I moved into Picardy and Burgundy blocking Jim's retreat and 
forcing the death of his army.  As a result, I had 17 centers and 
17 units while Eric had 17 centers and only 16 units on the board.  
I could therefore declare a victory while maintaining 
the letter of my agreement with Eric.

I have three regular Diplomacy sets:  that original 1959 
Allan B. Calhamer edition with a boxed set of numbered armies and fleets 
(I got my board autographed by Allan Calhamer on July 23rd, 1972), 
a 1961 Games research, Inc. edition which still came with 
wooden armies and fleets in a tray but sans the numbers, 
and a copy of the 1958 edition that Allen sent me.  
Unfortunately, those rules were thermofaxed and are almost unreadable in places.  
There were differences in the board as well.  White Russia (Ukraine); 
Transylvania; Montenegro; Pontus; Anatolia; Erzurum and Persia (Armenia); 
Mesopotamia; Calabria; The Sea of Marmora; The Bay of Tunis; Algeria and 
Morocco (North Africa), Cape Saint Vincent, Cape Finesterre, 
The Bay of Biscay and Point Saint Mathieu (the Mid-Atlantic); Lorraine; 
Flanders;  Cologne (The Ruhr); The Palatinate and Bavaria (Munich), 
The North Baltic (The Gulf of Bothnia); Wessex; Clyde; and The Kattegat.

There were thirty five supply centers:
Austria had three centers (Vienna, Budapest and Trieste) plus Tyrol, Bohemia and Galicia.  
England had three centers (London, Liverpool and Edinburgh) plus Wessex, Wales, Yorkshire and Clyde.
France had three centers (Paris, Brest and Marseilles) plus Burgundy, Gascony, Flanders and Lorraine.
Germany's three centers were Berlin, Kiel and Cologne.  Its other provinces were Bavaria, Silesia and Prussia.
Italy had Rome, Naples and Venice as centers.  Other provinces were Piedmont, Tuscany, Apulia and Calabria.
Russia had four centers (Moscow, Warsaw, St Petersburg and Sevastopol 
plus Livonia, White Russia, Finland and Caucasia.
Turkey's centers are Constantinople, Ankara and Erzurum.  Other provinces were  
Smyrna, Anatolia, Pontus, Syria, Mesopotamia and Persia.
The thirteen neutral centers are Portugal, Spain, Switzerland, Belgium, Holland, 
Denmark, Norway, Sweden, Serbia, Rumania, Bulgaria, Albania and Greece.

I hope you found this bit of history interesting.

\centerline{Regards, Jeff}

\bigskip

{\bf Eric Just (Sun, 22 Apr 2007 14:02:20 EDT)}

We did have numbered armies and fleets, which simplified order writing  
somewhat, but the rule about not bringing a destroyed unit back in was not our 
rule.  We did some things strangely, but not that strange.  We were the only 
game I know of to have had the gamesmaster playing in it.  That was for two 
reasons: first of all I wanted to play which was why I started the game; and 
second, because I barely knew six other players at the time, let alone seven!
 
\centerline{Eric, Ericose of aol.com}

\bigskip

{\bf Edi Birsan (Sun, 22 Apr 2007 11:13:53 -0700)}

By the way Eric/Jeff,
the World DipCon Championships are in Vancouver this year in August,
would be a hoot to have you two come up there and donate a pint or  
two of blood.

\centerline{Edi Birsan, EdiBirsan of astound.net}

\bigskip

{\bf Eric Just (Sun, 22 Apr 2007 14:17:55 EDT)}

Alas, since experiencing a partial meltdown early this millennium, I have  
been unable to travel more than about 33 miles from home.  If it ever comes  to 
central Oklahoma, you can count on me, if my new-found crowd-aversion doesn't  
grab me by the throat.
 
\centerline{Eric, Ericose of aol.com}

{\it ((That's too bad, this discussion also brought the following from Walt Buchanan....))}

\bigskip

{\bf Walt Buchanan (Apr 02, 2007 08:45:53 AM)} 

Hi Jim,

Thanks so much for {\it DW} \#96 and {\it TAP} \#310, plus the fantastic news! 
I will be honored to write an intro for {\it DW} \#100. 
It is hard to believe that it has been 1/3 a century since {\it DW} started.
{\it ((It's equally amazing that it is still going.
As Doug and I are working on it together now, we are very aware of trying to link the 
ages of the Hobby.))}

That is also neat that you found Jeff Key. 
Could you give me his and Edi Birsan's email? 
I saw Edi probably 20 years ago in the Bay area, but I'll bet is it 30 since I saw Jeff last.

\centerline{Thanks again! Walt, Buchanan of entc.tamu.edu}

{\it ((Thanks to YOU, Walt, also see Eric Just's E-Mail too as a special bonus.))}

\bigskip

\centerline{\bf INTERNATIONAL SUBSCRIPTION EXCHANGE NEWS}

\smallskip

John Harrington and I have agreed to close the ISE.
In this age of PayPal, the traffic on the ISE had fallen almost to zero,
and what was left almost entirely was me facilitating orders of 
Breaking Away and John's other Fiendish Games.
So, I'm still going to help John out with that, but there will be no
ISE.
If anyone still needs assistance with this, though, since I'm helping
John out, like if you're in a foreign country and need to send dollars
for dipping things to someone in the US, I may be able to help you out.

\bigskip  

\centerline{\bf WORLDMASTERS04 SECTION}

\smallskip

See http://www.worldmasters.net/wm04/
for details on progress on the WORLDMASTERS04, the Finals are now nearly 
set to start.  
I'll report in detail on that next issue.

I've joined the Yahoogroup WM04-Chat where some of this
discussion is happening.
You can join too!
However, this forum has been very, very quiet, I hope it picks up with
finals, since it was dead for the semis, maybe I'll have to start some discussion.
I had to go the main Worldmasters site at www.worldmasters.net/wm04/ to
find some of the results.
The new Tournament rankings for FTF also are out there that supercede the
ones that were on 18centres.
Go check out:

http://eurodip.nuxit.net/php/ranking/index.php?lang=Ang


\bigskip

\centerline{\bf DIPDOM NEWS SECTION (with letters)}

\smallskip
 
Obscure and not-so-obscure ramblings on the state of the hobby
and its publications, custodians, events, and individuals with
no guarantee of relevance from the fertile keyboard of Jim-Bob,
the E-Mail Dip world, and the rest of the postal hobby.
My comments are in {\it italics} and {\it ((double 
quotation marks))} like this.
{\bf Bold face} is used to set off each individual speaker.
I should also make a note that I do edit for syntax and spelling
on occasion.

%A VERY light discussion is taking place that will address what 
%stance we (the hobby) should take (proactive in some way for sure) 
%toward Hasbro, the new owners of the rights to Diplomacy.
%More on this will be forthcoming, but it looks like Hasbro might
%have its version of Diplomacy on the market for the Christmas
%season and they actually will be employing ``play-testers''.
%No word on precisely what this means yet, could it mean that
%they will offer a series of ``official'' variants?
%Stay tuned....
%If you want to be part of the discussion, send the MESSAGE:
%
%subscribe hasbro
%
%to majordomo of diplom.org, it works just like the tap mailing list
%described below.  Sending messages to hasbro of www.diplom.org
%sends the mail to the whole list.
%The big news this time is the beginning of the breakout of
%Hasbro into official contact with the hobby.

The game Diplomacy is a copyrighted product owned by Hasbro and all
reproductions or other use of that material in this szine is intended to
be personal use and not infringe on those rights in any way.
All reproductions are done at a heavy financial loss to the editor
and thus are without the remotest possibility of commercial intent,
except to promote THE game, the Game of Diplomacy, which you all 
should purchase from Hasbro or other duly licensed distributors.
 
Stephen Agar has matched the Hasbro rule lists 
and more with some of the even older
rulebooks.
Check these out if you like:

http://www.hasbro.com/default.asp?xcc\_gameandtoyinstructions

http://www.hasbro.com/instruct/Diplomacy.PDF

http://www.hasbro.com/instruct/Diplomacy(OlderVers).PDF

Nice of them to make BOTH of these available.
And all seven different US rulebooks for Diplomacy can now be found here
courtesy of Stephen Agar (relatively new address for this):

http://www.diplomacy-archive.com/diplomacy\_rules.htm

%1: The Reformer, who seeks perfection (crusading type).
%2: The Helper, who seeks love (altruistic type).
%3: The Performer, who seeks status (competitive type).
%4: The Individualist, who seeks an identity (imaginative type).
%5: The Investigator, who seeks knowledge (analytical type).
%6: The Loyalist, who seeks security (ambivalent type).
%7: The Enthusiast, who seeks gratification (thrill-seeking type).
%8: The Leader, who seeks self-sufficiency (dominant type).
%9: The Peacemaker, who seeks contentment (accommodating type).
%See http://graphics.lcs.mit.edu/~becca/enneagram/
%new test at: http://www.9types.com
%My scores in order were: 9, 13, 15, 7, 15, 6, 17, 18, 14.
%Robert Lesco's Marco Poll, the defacto poll of the
%North American hobby since the Runestone is pretty much
%officially dead, continues to collect votes.
%This is an official {\it TAP} approved poll.
%Here are the particulars on the Marco Poll:
%Vote for your top five in each category and you can't vote (or at least
%it won't be tabulated) for Robert Lesco or his szine, which I don't see.
%I will send this to Robert and offer him a trade.
%The deadline is September 1st and either send your ballot to marcopoll of yahoo.com
%or mail to Robert Lesco, 49 Parkside Drive, Brampton, Ontario, CANADA  L6Y 2H1.
%For identification purposes, Robert would like you to identify yourself both
%by name and by affiliation (a game you play in or a szine you sub to).
%Here are the categories this year (I like some of the new ones!!):
%1) Favourite {\it ((Hey, what, he's Canadian, yeah.))} Zine  {\it ((What's a zine,
%shouldn't that be Szine???))}
%Backstabbers United Monthly, Costaguana, The Diplomatic Pouch, Absolute, Vertigo
%2) All Time Favourite Zine {\it ((Szine))}
%Magus, Europa Express, Thirty Miles of Bad Road, Perelandra, North Sealth West George
%3) Best Diplomacy Player
%John Quarto von Tivadar, Edi Birsan, Mark Fassio, Chris Martin, David Partridge
%4) All Time Best Diplomacy Player
%Edi Birsan, Mark Fassio, Kathy Caruso, Rod Walker, Hohn Cho
%5) Best GM
%Malcolm Cornelius, Tim Miller, Tim Richardson, Conrad von Metzke, Doug Massey
%6) Player Who Writes the Best Letters/E-Mails
%Don Williams, Richard Weiss, Mark Fassio, Toby Harris, Cal White 
%7) Folded Zine {\it ((Szine))} You Miss the Most
%Magus, Diplomacy by Moonlight, Le Front du Liberation de Diplomacy, Kathy's Korner
%8) Favourite Variant
%Modern, Nuclear Yuppie Evil Empire Diplomacy, Woolworth, Spy Diplomacy, Colonia

\bigskip

\centerline{\bf WEASEL MOOT I}

\smallskip

Calling All Weasels!
The Windy City Weasels’ Tournament Committee cordially invites you to attend 
Weasel Moot I (you have to start somewhere!), a three-round Diplomacy tournament 
to be held June 9 and 10 in Chicago.

What? A three-round Diplomacy tournament, and the sixth stop on the 
North American Diplomacy Federation’s 2007 Grand Prix Circuit.
 
When? June 9 and 10, 2007.
 
Where? At the breathtaking Elks Veterans Memorial, 2750 N Lakeview Ave.,Chicago, IL 60614. 
Don’t believe it’s breathtaking? Check out these links. 
We’ll be playing the games in these rooms!
 
http://elks.org/memorial/VirtualTour/Elks-gr.html

http://elks.org/memorial/VirtualTour/ElksMemorialRotunda.htm
 
Cool venue AND free parking on site!
 
Who? The Windy City Weasels is a Chicago area club dedicated to the play of 
the classic boardgame Diplomacy. We’ve been organizing games since September 2005. 
This is our club’s first annual (we hope) tournament.
 
Traveling Diplomacy players Jim O’Kelley, Greg Duenow and Jeremiah Peterson, 
along with Chicago’s most honest lawyer, Thom Comstock, comprise the 
Tournament Committee. O’Kelley will serve as Tournament Director.
 
How Much: The preregistration fee is \$35, payable by PayPal to Thom Comstock at 
Redpawn3 of yahoo.com. Just provide your name and mention Weasel Moot 
when you send the funds. We’ll charge \$40 at the door.
 
Schedule:

Saturday, June 9;
Round 1;
Registration: 9 to 9:30 a.m.;
Round Begins: 9:45 a.m.
 
Round 2;
Registration: 5:15 to 5:45 p.m.;
Round Begins: 6 p.m.
 
Round 1 and 2 games must be completed by a time known only to the 
tournament director between 3 a.m. and 5 a.m.
 
Sunday, June 10;
Round 3;
Registration: 8:15 to 8:45 a.m.;
Round Begins: 9 a.m.
 
Round 3 will end at a time known only to the tournament director between 3 p.m. and 5 p.m.
The awards ceremony will begin 15 minutes after the end of round 3.
 
Speaking of awards, what can I win? We’ll award plaques for first through seventh 
place and some of the coolest Best Country awards you’ll ever see. 
Plus, there might be a few surprises…
 
And how will said awards be determined? We’ll be using a draw-based 
scoring system with a center-count component. It will be either 
David Hood’s time-tested DixieCon scoring system or a modified version 
to give more weight to solos. Each player’s two best rounds will count 
for score. Players need only play in one round to be eligible for awards.
 
Housing? We have a limited supply of rooms at the Days Inn Lincoln Park North, 
which is two blocks from the tournament site, for the evenings of June 8 and 9. 
These rooms range in price from \$162 per night to \$180 per night 
and can hold two to four people, depending on the room. 
To make your reservation, call 1-888-LPN DAYS by May 14. 
Our rooms are being held under the name Weasel Moot.
 
If you’re looking for a cheaper housing alternative, contact 
Jim O’Kelley at jimthegrey1013 of yahoo.com. He has space available 
in two junior suites at the Best Western Hawthorne Terrace Hotel, 
which is about five blocks from the tournament site, 
for the evenings of June 8 and 9. Each suite can accommodate 
up to five people. 
Space will be available for \$55 per person per night, assuming five people per suite.
And if you want something even less expensive, contact Jim. 
He’ll attempt to connect you with a local host. 
 
Anything else? Well, if there’s sufficient interest, 
we’re going to organize a White Sox outing for Friday night. 
So, let us know if you’re interested! Also, we’re probably going 
to serve Chicago-style pizza in between rounds on Saturday. 
 
Questions? Contact Tournament Director Jim O’Kelley at jimthegrey1013 of yahoo.com. 
For more information about the Windy City Weasels, check out our Yahoo group at:
 
games.groups.yahoo.com/group/ChicagoDip/ 

or our new website at umbreho.dyndns.org/wcw.

\bigskip

We also have another Boston Massacre tournament coming on June 23-24.
I'll only be at the game on Sunday, June 24.  You can find info about Weaselmoot, 
Boston Massacre, the upcoming World DipCon in Vancouver, and all other manner of
tournaments on the Pouch tournament web site that David Norman set up.
Visit the FTF section at http://devel.diplom.org or E-Mail me for more info.
The Diplomacy FTF Tournament schedule, both here in North America and worldwide,
remains VERY, VERY active lately.
If I had only one slight negative thing to say about it, there is a tendency toward
inbreeding and usual suspects showing up at most of the tournaments.
That's GREAT in some ways, but I worry about attracting more FTFers in the future.
Go check out a tournament near you soon, you won't have to travel far.
Ask me if you need help (including financially).

\bigskip

\centerline{Check out current and back issues of {\it Diplomacy World} -- Yahoogroup diplomacyworld}
and at Doug Kent's new {\it Diplomacy World} web site at:

\noindent http://www.whiningkentpigs.com/DW/

Also, I need any Hobby Award Nominations NOW (!!!) for the :

\noindent The 2005 and 2006 Don Miller Award for Meritorious Service;

\noindent The 2005 and 2006 Rod Walker Award for Literature;

\noindent The 2005 and 2006 John Koning Award for Player Performance;

\noindent The 2005 and 2006 Fred Hyatt Award for GM Performance;

or

\noindent A 2005 and 2006 Kathy Byrne Caruso Award for Lifetime Achievement (if warranted).

The Hobby Awards Committee is Jim Burgess (Chair and Treasurer),
Fred Davis, Jr., Melinda Holley, Gary Behnen, Jamie Dreier,
Paul Kenny, Mark Stretch, and Robert Lesco.
I was going to publish the award ballot for this year 
in this issue, but I realized that I really just had to get this out first and
then do that.... and then, well, REAL SOON NOW!!!
And when I do, I'm going to give out two sets of awards and get caught up for the 
missed year, that seems to make the most sense.  
Committee.... you will be hearing from me soon!
This also fell apart with my move, but I will get this out NEXT issue come hell or high water.
I want voting to be able to happen by World DipCon.

\bigskip

{\it Diplomacy World} Issue Deadline is now:

\noindent Deadline Summer 2007, Issue \#98: July 15, 2007

I'm really pleased that former editor Doug Kent has agreed to come 
back and get this back on track and get us to \#100.
Thanks, Doug!
We're putting things together for the
next issue and it looks good, but if any of you want to write anything
there's always more room,
contact Doug!

See http://www.whiningkentpigs.com/DW/ for some exciting back issue material being
posted as well as the new Issue \#97.

%\noindent Final Hobby Awards Ballot for 2004, nominations now to:
%burgess of world.std.com
%
%The qualifications for the Kathy Byrne Caruso Lifetime Achievement 
%Award are that the awardee must have been: (1) Active in the 
%Diplomacy Hobby in at least Three Separate Decades; 
%(2) Multidimensional in their Contributions to the Hobby 
%(e.g. writing, playing, publishing); (3) Taking Retirement or 
%Semi-Retirement from the Diplomacy Hobby; and (4) One of the 
%Hobby’s Unique Personalities Worthy of Being Remembered as Long 
%as THE Game Continues to be Played.  This award need not be awarded
%each year, but only as worthy candidates are identified.  The only
%past honoree is the late Richard Sharp.
%
%The other award categories are self-explanatory:
%
%\noindent Nominees for the 2004 Don Miller Award for Meritorious Service
%
%\noindent Nominees for the 2004 Rod Walker Award for Literary Achievement
%
%\noindent Nominees for the 2004 John Koning Award for Player Performance
%
%\noindent Nominees for the 2004 Fred Hyatt Award for GM Performance
%
%--- --- --- --- --- --- ---

Editorial Board for {\it Diplomacy World}:

\noindent  Doug Kent, NEW Lead Executive Editor!, 11111 Woodmeadow Pkwy 
\#2327, Dallas, TX  75228, dougray30 of yahoo.com 

\noindent Tim Haffey, 810 53rd Ave., Oakland, CA 94601 USA; trhaffey of
aol.com -- Ex-Lead Editor and Archives Editor

\noindent Jim Burgess, 664 Smith Street, Providence, RI 02908-4327, USA;
burgess of world.std.com -- Co-Editor and Publisher

\noindent Rick Desper, 5440 Marinelli Road, \#204, Rockville, MD  20852, USA;
rick\_desper of yahoo.com -- Demo Games

\noindent Dave Partridge, 15 Woodland Drive, Brookline, NH  03033, USA;
rebhuhn of rocketmail.com -- US Postal

\bigskip

\centerline{\bf MUSIC AND MOVIES SECTION (WITH COMMENTS ON OTHER ARTS AND SOCIETY)}
     
\smallskip

We're running a ``23 tunes'' contest here
(stolen blatantly from Mark Wightman and the late lamented {\bf The Sprouts of Wrath}.
If anyone would like to send me a tape or CD of their 23 (which was the original point)
that would be great, but I don't intend to require that.  I will be playing in the
sense that I'll be putting 23 tunes in, and you have to guess me, but I obviously
won't score points.
Send commentary with your choices, and we'll see if people can
guess who you are!!!
And already there is a LOT of diversity in defining tunes and styles, so 
BE CREATIVE!!!
 
%To encourage voting early, I picked five voters at random to receive five US
%dollars from me (either in cash or paid to someone for Dip stuff or to get
%a free tape).
%Tony Dickinson won the Round 5 prize, so we had three of the six Round 1 voters
%won and one of the three Round 2 postal voters who also got five chances to win.
%That showed the value of getting in early!!
%Voters in Round 1 were Mike Barno(\$5), Rick Desper (\$5), Tony Dickinson (\$5),
%Drew James, Heath Gardner, and John Harrington.
%Round 2 postal voters were John Schultz (\$5) Ian Moore, and Stan Johnson.
%Round 2 E-Mail voters were Scott Morris, 
%Warren Goesle, Peter Sullivan, and Michael Lowrey.
%Round 3 voters were Dick Martin, Richard Weiss, and Rip Gooch.
%Round 4 voters were Roland Sasseville, Jr. (\$5),
%Don Williams, Brent McKee, and Andy York.
%Round 5 voters were Mark Larzelere, Al Tabor, Jody McCullough, and that's it.
%We'll end up with a monster party tape at the end of it that I plan
%to segue and sequence and copy for distribution.
%The result will be a great New Millenium party tape -- we're going for 90 minutes.
%I've also been thinking that I should put this out on CD
%as truly emblematic of the new millenium.  
%I don't have the capability to do that quite yet, but I think
%I might by then.
%Any suggestions (or especially volunteers) on this front will
%be cheerfully accepted and could receive monetary payments!
%The CD way may still occur if someone steps forward and actually does it for me.
%So far, we have ``I Melt With You'' by Modern English; George Gershwin's
%``I got Plenty O' Nuttin' '' from {\it Porgy and Bess} in the 1957 concert
%recording with Ella Fitzgerald finishing off the vocals after Louis
%Armstrong blows and sings through the tune; Duke Ellington performing
%Billy Strayhorn's ``Take the A Train''; Frank Sinatra's ``New York,
%New York''; something from the B-52's;
%the original Van Morrison and Them version of ``Gloria'';
%The (English) Beat's 12 inch version of ``Save It for Later'' 
%ratchets things up to the next level (wherever you put it!);
%Buster Poindexter's ``Hot, Hot, Hot'' keeps you there;
%``Atomic Dog'' by George Clinton blows the doors off,
%and Koko Taylor cleans up singing Willie Dixon's ``Wang Dang Doodle''.
%After I get timings down, I'll choose exactly which songs below make the list.
%
%EXTRA SPECIAL B-52'S BULLPEN: (7) ``Love Shack'';
%``Rock Lobster". {\it ((A tie, a tie!!!!))}
%
%BULLPEN: (9) Nirvana -- ``Smells Like Teen Spirit";
%``Cumberland Blues'' -- the Grateful Dead.
%(8) ``Twistin the Night Away" -- Sam Cooke; ``In Between Days'' -- The Cure;
%``Mannish Boy" -- Muddy Waters; ``Shake, Rattle, \& Roll" -- Big Joe Turner; 
%``Proud Mary'' -- Ike and Tina Turner.
%(7)  ``I Wanna Be Sedated" -- Ramones; ``Twist \& Shout" -- Beatles.
%(6) ``Magic Carpet Ride" -- Steppenwolf;
%``Crossroads'' -- Eric Clapton; ``Play That Funky Music'' -- Wild Cherry;
%``I Fel Good" -- James Brown;
%``Radar Love'' -- Golden Earring; 
%Devo -- ``Whip It"; ``Echo Beach'' -- Martha and The Muffins.
%(5) ``Sing Sing Sing'' -- Benny Goodman; ``Rocking the Casbah'' -- The Clash; 
%Squeeze -- ``If I Didn't Love You"; ``Roadrunner'' -- 
%Jonathan Richman and the Modern Lovers.
%
%SPECIAL ROLLING STONES BULLPEN: (6) ``Paint It Black''. 
%
%SPECIAL TALKING HEADS BULLPEN: (9) ``Take me to the River".
%(4) the entire {\it Speaking in Tongues} record
%(special call for ``Road to Nowhere'').
%
%SPECIAL ALPHABET SONG BULLPEN: (6) ``YMCA" -- Village People. 
%
%SPECIAL DRUG MUSIC BULLPEN: 
%(8) ``Rd, Red Wine'' -- UB40.
%(6) ``Don't Bogart that Joint'' 
%-- Fraternity of Man; ``The Old Dope Peddler'' -- Tom Lehrer.
%(5) ``Cocaine'' -- Eric Clapton's version; ``Casey Jones'' -- the Grateful Dead.
%(4) ``White Rabbit'' -- Jefferson Airplane; ``Love Is the Drug'' -- Roxy Music.

\bigskip

\centerline{\bf {\it 23 Tunes Game}}

\smallskip

Here are the rules for 23 TUNES.  You send me three tunes for the first turn,
and then two tunes in each of the last ten turns for a total of 23.
If you missed the first turn, you can still catch up by sending five tunes next
issue, and guess on submitters to this issue.
I am also submitting my tunes.
After we're done, I'd like to exchange CD's/Tapes for as many of the tunes players
as possible, but this is not required.
I'll be sending the winner both my LAST 23 tune list and my NEW 23 tune list.
The winner is determined by having you guess each issue who submitted what list
(I will tell you who the submitters are).  For each list you get right, you get
a point, you also can win bonus points from me for really cool tune selections.
That's it, not complicated.
I hope by starting this up, we'll get more to join, five songs required to enter
late.
Playing this issue (guess who is whom by number, scores are in parentheses) 
is, in alphabetical order, 
Jim-Bob Burgess, Rick Desper (1), %Steve Emmert, Doug Kent, 
Dick Martin, %Jim Reader,
Richard Smith (3), Joakim Spangberg, %Brendan Whyte, 
and Brad Wilson (4).
The linking theme thing didn't seem to go over too well.
No one really figured out the true linking theme.  
Rick Desper was using Underground tube stops and songs with that as the title,
they were things like that.  
I'll let you guys talk a bit to each other on that with your guesses.
I have added some kind of comment on each tune.

WHAT I NEED: two more tunes (seven if you're joining up new, four if you NTRed (NO TUNES
Quite a number of you SAID you would join but haven't yet, so we'll get started and
put the pressure on you.
This part is still a MESS and I'm getting this issue out and then will catch up next time.
I think I'm going to simplify the rules to get it back on track.
%Rick Desper: Anyway, my tunes this time are "Set the Controls for the Heart of Sun" by Pink Floyd, 
%in honor of the film Sunshine, and "Afternoon Delight" by the Starland Vocal Band, 
%that Will Hunting just sang a snippet from, and Ron Burgundy covered in "Anchorman".  
%The latter is really becoming an anthem of the Goofy 70s.
%I have no idea what this game is supposed to mean, but we can't go wrong with "Afternoon Delight".

\bigskip

{\bf Rick Desper (Tue, 24 Apr 2007 00:52:23 -0700 (PDT))}

Just saw the English sci-fi film ``Sunshine" a few weeks ago.  Very nice.  My review at:

\noindent http://chalant.blogspot.com/2007/04/sunshine-is-best-sf-film-ive-seen-in.html
 
I was interested to see Doug Kent's subzine called {\it Eternal Sunshine}, 
since that was recently on Channel 4.  I posted a brief response to the film 
on my blog titled ``Meet me in Montauk," just a few days before reading the 'zine.  
Didn't realize that Doug's zine grabbed its title from the film, 
and that his film review bit was also titled ``Meet me in Montauk".  
Part of my thinking about what I'm looking for in SF.  
(And not just Kate Winslet, who is probably the best actress of her generation, 
though I wish she would do more films like ESSM and fewer period dramas -- but 
her latest film ``Little Children" was also good.)
{\it ((I thought in particular the child actors in ``Little Children" were
excellent in doing what they needed to do and staying out of the way of the
other action.
The actress who played Kate Winslet's daughter was especially noteworthy,
I really liked when she was staring up at the lamplight.))}

I've got ``Good Will Hunting" on TV in the background.  
I want a posse with a guy like Morgan to say ``my boy is wicked smaht!"  
One of my grad school colleagues, Tom Bohman, was at MIT when Affleck and 
Damon were researching this film.  
He was fairly dismissive of them, and they later included a postdoc character 
``Tom" who was a bit dweebish.  Anyway, I'm digressing.
 
You're a Helen Mirren fan, aren't you?  I've been watching the Prime Suspect DVDs.  
If you haven't seen them, you must, esp. the first one.   

\centerline{Rick, rick\_desper of yahoo.com}
 
{\it ((I am, you're right, but I haven't, sounds like a NetFlix request!!))}

\bigskip

{\bf Mike Barno (Wed, 18 Apr 2007 22:07:26 -0400)}

Jim, I've mailed you a CD copy of {\it Live from the Studio}, 
the second album from the Morgan String Band.  
{\it ((Thanks very much, this is way cool, it's been good commuting music in my car.))}
This is the five-piece group that I named as 
``the best band I heard in 2005" in {\it TAP} issue 300.  
Flattop guitar, banjo, fiddle, mandolin, standup bass.

I was never a bluegrass fan until I got turned on to these folks.  
As a kid, I would watch entire seasons of {\it Hee Haw} on TV and 
only hear one or two performances that made me say ``Wow"; 
the rest of the music seemed as lame and corny as the jokes.  
{\it ((I like the ``Car Talk" theme song too, that's really cool.))}
Occasionally one of the ``Wow" songs was Buck Owens in the 
studio looking twenty years younger than he did in the same episode's 
``Pickin' and Grinnin'" segment, 
which is probably one of the thousand reasons I grew up so cynical.

MSB, though, really kicks it up.  The album is fine but their live 
shows are what really do it for me.  I attended seven or eight full shows last year, 
most at different locations, and caught the tail end of a couple of 
other gigs after all-day trail hikes.  
After a winter break, they've returned with several new songs 
(both originals and covers), and I've heard three more gigs.  
The worst I've heard them was maybe a seven on a ten-point scale; 
most were nines or tens.  Even if I've been hiking or snowshoeing for 
three or four hours, they get me dancing.  
The stuff rocks more than anything I hear on any genre of commercial radio.

I can't tell you more about their first disc, {\it First Cut}, 
than you can find on their website at:

\noindent http://www.cfmsites.com/morganstring/

\noindent the self-produced album is sold out and apparently won't be reissued.  
Nor can I tell you about their third CD since it hasn't been recorded yet.  
So I guess I have to tell you about this one.
{\it ((Sounds like a plan, let's go to it.))}

They definitely lean toward bluegrass traditions in general, 
and they went hardcore in that direction by recording all of 
{\it Live from the Studio} around a single microphone, 
the way it was done in the good old days before you or I were born.  
It really feels like you're sitting around a crystal radio set; 
the downside is that it's often tough to pick out the fourth 
and fifth instruments unless you turn the volume up to eleven.  
That's why I sit or stand up front at live shows, 
to hear all the richness of these well-orchestrated songs.
{\it ((I've been listening to it in the car, the energy comes
through, but I'm completely losing the background.))}

There are bluegrass classics here: Doc Watson's ``Wild Bill Jones", 
Millie Clements' ``Lonesome Fiddle Blues", the public-domain ``Old Joe Clark", 
and so forth.  There are also some fine originals: 
mandolinist Chris Brown wrote ``Stop Rocking the Boat" and 
``Guess You Should Have Known".  Both are among my favorite MSB tunes, 
even if both are among their more ``accessible" 
(i.e., melodic to a mainstream lister) songs.  
The other original here is the instrumental ``Jones Road", 
by guitar player Dave Carey (son of Mark the bassist).  
It's good here, but when they played it eight to ten beats-per-minute 
quicker at one early-2006 show, my fifteen-pound heavy wooden chair 
started jumping three feet side-to-side because my butt wouldn't hold still.  
(There were other fine originals on the first album such as Chris' 
``That's Right" and Mark's instrumental ``Carey Breakdown".)

One of my favorite song types is well-represented on this album: 
fun songs that feature a violent death.  
From ``Wild Bill Jones", over a lad trying to put the moves on the 
narrator's girlfriend: ``He said `My age is twenty-one, too old to be controlled.' 
/ I pulled my revolver from my side, and I destroyed that poor boy's soul."  
From the public-domain ``Duncan and Brady", over a sheriff 
who tries to arrest a bar's big-shot: ``White-tailed carriage 
just a-standin' around / to carry King Brady to the buryin' ground / 
Them rubber tired buggies, them rubber tired hacks / 
They took him to the graveyard, never brung him back."  
I'll bet if the Mekons played either song you'd be bouncing off the ceiling, Jim.
{\it ((Indeed, they are cool songs.
I can like how these guys play too!))}

There are a couple of modern songs here: the Bruce Hornsby/Don Henley collaboration 
``The End of the Innocence" is way too Eighties for my tastes, but they do it well.  
Don't overlook the encore that doesn't appear on the track listing.  
And at live shows, they do fine cross-genre reworkings of Rolling Stones and 
Grateful Dead tunes among others.

There are some AVI-format videos on the website, and they have 
something on MySpace that I haven't checked out, but most of the magic is in 
hearing them rather than watching them.  One notable exception 
(not on the first two albums) is ``Nashville Cats", as they constantly circle 
around to get the right instruments highlighted as they swap focus every 
two or three seconds.  I'd better not write much about 
fiddler Carol Simek being the most fun to watch on most songs, 
as she's married.  
{\it ((Why not, I suppose you might be afraid he'll google her and find this???))}
(Her husband's a musician in a different band.)  
Quite often she gets the most graceful dancing-in-place going, 
not for show but just for her own feeling.  
If you don't want to be a lecher, you can just watch her ankle, 
and on that alone you'll want to get out on the dance floor.  Day-yam!
{\it ((I don't know about everyone else, but I think an ankle fetish
is, well, more weird.))}

Anyhow, I hope you enjoy the music.  
I've never been inspired to follow a band around this much, 
even when I lived with members of two hardcore punk bands in 1989.

\centerline{-- Mike, mpbarno of lightlink.com}

{\it ((I can see why, thanks!
Up next, I have an exchange with Goz, I think there was an earlier
note that I seem to have misplaced that I was going to include.
I wasn't going to include the kid stuff.... but why not??
You haven't yet been exposed to my grandchild talk, but it
is one of the things consuming free time these days instead
of Dip.....))}

\bigskip

{\bf Warren Goesle (Fri, 27 Apr 2007 21:31:55 -0500)}

Jim-Bob,
The good news is: it appears that what was on Curt Schilling's sock in 
Game 6 of the 2004 ALCS was blood.
The bad news is:  it was Jimmy Hoffa's blood.
{\it ((That was Goz's reaction to the Boston brewhaha of a month
ago about whether or not the ``sock blood" was real.
This was because of the incredibly stupid commentary by Gary Thorne,
the Orioles broadcaster about this on a telecast.....
for those of you who never saw the story, you didn't miss anything.
Anyway, in Goz's letter I'm missing he commented on how much he
is getting ``into" Thomas the Tank Engine, to which I replied: 
``Cool, my granddaughter (now 2.5 years old) also loves Thomas the Tank
Engine, do you also have all the ``kid Lego" track for him?  We've given
Emily three sets so she has lots of track and trains.''))}
Nathan has a mile of track, but not Thomas scale.  He's got some 
Fisher-Price set, with something like 10 remote-controlled engines and 
enough cars, scenery, etc. to cover maybe half a state's worth.  We can't 
set the whole thing up in any one room.  We've been able to connect the 
entire upstairs with it before Carol caught us once.

\centerline{Goz, wgoesle of comcast.net}

%
%\bigskip
%
%\centerline{\bf SPY DIPLOMACY (Variant, revised Dec. 1986)}
%
%by Jim Burgess
%
%Rules:
%
%1) Unless otherwise specified, the standard rules of Diplomacy apply.
%
%2) Players receive adjudications for their own armies and fleets, but not
%the armies and fleets of other powers.  Similarly, each player sees only
%his or her own section of the supply center chart.
%
%3) In addition to the standard units, an unit called a "spy" is added.
%
%     A) Each of the seven powers begins with a spy in each home supply center.
%
%     B) Spies are supplied only by home supply centers (i.e. Russia may have
%as many as four spies at a time while other powers are limited to a maximum
%of three).
%
%     C) Spies are "built" and "disbanded" in Winter seasons at the same time
%as other units.
%
%     D) There is no limit to the number of spies that may be present in any
%province and spies may be ``stacked" with armies or fleets (exceptions are
%listed in Rule 6).
%
%4) Spy Reports
%
%     A) Spies report the location and nationality of armies and fleets in
%the province they occupy and all adjacent provinces immediately following
%the standard Winter, Spring, Summer, and Fall seasons (i.e. just prior to
%the spy movement seasons).  Spies can differentiate between units in retreat
%and successful attackers when two units "occupy" a province.
%
%     B) Spies also report the nationality of spies in the province they occupy
%and the presence (but not nationality) of spies in adjacent provinces at the
%same time.
%
%5) Movement of Spies
%
%     A) Spy movement follows the collection of spy reports, so orders to spies
%may be made conditional on any information gathered by spies on opposing troop
%movements or the adjudication of one's own units.
%
%     B) Spies move after each of the following standard seasons: Winter,
%Spring, Summer, and Fall (note that all spy movements PRECEDE Autumn
%retreats), beginning with Winter 1900.
%
%     C) Spies move as armies do with the following exceptions:
%
%          a) Spy movements cannot be stood off by movements of any other unit.
%
%          b) Spies may be convoyed by fleets of any power during any of the
%four movement seasons for spies.  The convoy orders for fleets in these
%seasons must be ordered by their owner in the usual fashion or else the spy
%convoy movement fails of execution.  Fleet convoy orders for spies may be made
%in addition to regular Spring and Fall moves (note, however, that the fleets
%themselves never move during spy movement seasons).
%
%          c) Spies may also be "picked up" and carried by fleets of any
%power. Embarkation and debarkation are moves that must be made during a
%spy movement season and "permission to board" is not required.  Embarkation
%consists of a movement from a land province to an adjacent sea province
%containing a fleet.  Debarkation consists of a movement from a sea province
%containing a fleet to an adjacent land province.  A spy may not "switch
%fleets in midstream".  Once boarded, a spy may only get off by debarking.
%After boarding a fleet, the spy moves with the fleet during regular movement.
%A spy may not debark from a fleet awaiting retreat (e.g. if a fleet carrying
%a spy is dislodged in Spring, the spy may not debark until the spy movement
%season following the standard Summer retreat season).
%
%6) Spy Mortality
%
%     A) This rule will outline the circumstances under which spies may be
%captured or killed.  Spies may be disbanded in Winter seasons at the same
%time as other units to meet the requirement that a power may not have more
%spies than the number of currently held home supply centers and spies are
%annihilated when they are on board a fleet that retreats off the board.
%Otherwise, spies may only be removed from the board (there is no difference
%in the game between capturing and killing a spy, but players should feel
%free to delineate between the two states in writing press) immediately
%following the four spy movement seasons.
%
%     B) Spies killed or captured in a given season do not submit written
%spy reports for that season, though their final movement may have been
%made conditional on that spy report.  Players may never know for sure how
%a spy was lost, just as in real life.
%
%     C) Spies are "killed" by being assassinated by other spies.  When a
%spy moves, he or she may attempt an assassination, specifying the nationality
%of spies to be executed if discovered.  Each spy may hunt for only one
%nationality in each of the four seasons.  The following rules and examples
%will govern the adjudication of assassinations:
%
%          a) A spy may attempt an assassination without moving (for instance
%if the target is in the same province).  In this case, any spies of the target
%nationality that end the spy movement phase in that province are assassinated
%with one exception.  If the spy attempting the stationary assassination is
%himself or herself assassinated by a moving assassin then that spy
%assassinates no one in that season (not even a potential target other than the
%one that assassinates that spy).
%
%          b) A spy attempting a moving assassination (may include a move of
%embarkation or debarkation from a fleet) is always successful in assassinating
%spies of the target nationality that finish the spy movement phase in the
%province that the spy moves to.  This makes "mutual assassinations" possible.
%
%          c) Example: French spy is on board a French fleet in the Channel.
%An English spy is in London.  Both powers specify assassination attempts
%against the spies of the other.  If the English spy embarks on the French
%fleet in the channel (remember that embarkation does not require the
%permission of the fleet being boarded) and the French spy doesn't move, the
%French spy is killed, but the English spy isn't (he may be immediateIy
%captured, however, see part D).  If a German spy is also on board and the
%French spy tried to assassinate the German spy, that operation would fail
%as well. If the French spy debarks to London at the same time, the two spies
%"pass in the night" and neither is killed.
%
%     D) Spies are "captured" by opposing armies and fleets.  Players may
%attempt to capture spies, specifying the nationality of spies to be captured
%if discovered.  Each army and fleet on the board may search for spies of one
%nationality in each of the four seasons.  The following rules and examples
%will govern the adjudication of attempts to capture spies:
%
%          a) Players may specify a nationality to be hunted separately for
%each unit or they may issue blanket searches to be applied to all units.
%
%          b) At the end of the spy movement phase, any spies of the
%nationality specified in the same province are captured (for example, if
%the French player specifies a hunt for English spies on their Channel fleet
%in the above example, then the English spy is captured).
%
%          c) Players are informed when they successfully capture an opposing
%spy.  Note that the "owner" of the spy, however, is not informed of the
%capture.  Communication just is cut.  This rule is the only exception to the
%generaI rule that armies and fleets are blind.  It is possible to play the
%game without allowing capture of spies by armies and fleets if one wishes
%to allow freer movement of spies (i.e. RuIe D may be ignored).
%
%7) It is suggested that the game be adjudicated in four separate seasons
%in the following order:
%
%     A) Spring: (for Spring 1901 this sequence is preceded by a spy movement
%phase (no spy reports are necessary) followed by assassinations or captures)
%
%          a) Standard movement by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     B) Summer:
%
%          a) Standard retreats by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     C) Fall:
%
%          a) Standard movement by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     D) Winter:
%
%          a) Standard Autumn retreats by fleets and armies, adjudication
%reported only for one's own units
%
%          b) Standard Winter builds and removals, also applies to spies
%
%          c) Spy report phase, spies collect information
%
%          d) Spy movement phase, spies move according to Rule 4
%
%          e) Spy assassination and capture phase
%
%\medskip
%
%These rules have been produced by Jim Burgess (with helpful comments from
%Bernie Oaklyn and Dick Martin).  Permission is granted to reproduce and use
%these rules without restrictions.  The author would be interested to hear
%any comments and criticisms regarding any aspect of the play of this variant.
%The rules have been deposited with the North American Variant Bank.  They are
%also available from the author for the cost of postage or free by E-Mail.
%
%\bigskip
%
%\centerline{Wing Rules} 
%
%1.A wing unit can move over both land and water spaces. 
%  
%2.A wing unit can support actions in any space adjacent to the one it occupies. 
%   
%3.A wing can give, receive and cut support in the same way as armies and fleets. 
%   
%4.A wing unit cannot convoy or be convoyed. 
%
%5.A wing unit cannot capture an SC, but instead blockades it: 
%        
%\indent\indent 5.1.A blockade occurs when a wing unit occupies the SC of 
%another player in a fall season. 
%        
%\indent\indent 5.2.The player who owns a blockaded SC does not count 
%it when counting his total number of SCs. 
%        
%\indent\indent 5.3.A blockade ends as soon as the wing unit no longer occupies the SC. 
%        
%\indent\indent 5.4.Builds only take place in the winter phase, just as in games without wings. 


\vfill\eject

\centerline{\bf {\it THE ABYSSINIAN PRINCE} GAMES SECTION}

\smallskip

``So I called up George and he called up Jim, I said let's make a deal.

He said he'd talk to him.  Gonna start a church where you can save yourself,

You can make some noise, When you've got no choice...

You told me useful things, what people think of me, I guess I should thank you.

It's true, then I agree... I'm all alone, I've got no choice,

I'm all alone, I've got no choice."

From ``Got No Choice" by the incomparable Mark Cutler, from the CD
{\it Mark Cutler and Useful Things}.

\smallskip

\indent If you want to submit orders, press, or letters by E-Mail,
you can find me through the Internet system at
``burgess of world.std.com''.
If anyone has an interest in having an E-Mail address listed so people
can negotiate with you by computer, just let me know.
FAX orders to (401) 277-9904 if you let me know in advance to be sure
the fax machine is set up. 

I am continuing to note cut or failed support orders with a 
small ``s'' instead of a capital ``S''.
This will make it easier on the E-Mailed version of the szine to see
what happened, since the italics don't show there.
The italics DO show on the web page just fine.

\indent Standby lists:

Mike Barno, Dick Martin, Brad Wilson, Jack McHugh, Glenn
Petroski, Steve Emmert, Mark Kinney, Vince Lutterbie, Eric Brosius,
Paul Rauterberg, Bob Osuch, Doug Kent, Sean O'Donnell, Vern Parker,
Heath Gardner, Paul Kenny, and Jeff O'Donnell
stand by for regular Diplomacy.
%I am willing to take over for NMR or start new-Diplomacy.
%Vern Parker
%337 Winter Hill Pl.
%Powell, OH 43065
%VSParker of aol.com
%614-402-5139

Let me know if you want on or off these lists, especially OFF.
Standbies get the szine for free and receive my personal thanks.

\bigskip

\centerline{GAME OPENING INFORMATION} 

\smallskip

We've got lots of openings in the subszines, check them out!!!
Contact Rip Gooch directly at xyropedes of canada.com and try to entice him to return.
Rip has been a bit missing in action lately, but I am assured that he
SHALL return.

Breaking Away starts in this issue!!! 

I am willing to open another new game of REGULAR Diplomacy if there is enough interest!!!
Fred Wiedemeyer, %e,f,r,i,g,t,a
Brad Wilson, and Shaun Thompson start the list, who would like to join them???

Also, is there any interest in another game of Nuclear Yuppie Evil Empire 
7x7 Dip?
I know it may be getting tired, but I really like it.
We have Karl Schmit on the list, let's get seven!!
It's FREE!!!
I may drop this one shortly if we still have no interest.

I also am starting a game of the variant I designed, Spy Diplomacy.
Signups for that are now open.
Bruce Edwards and Eric Ozog are signed up.
The rules were published recently, ask to see them if you missed them!!!

John Harrington is offering to guest GM a game of Office Politics.
Any interest in that??
Let me or John know!
Jody McCullough and Bruce Edwards are interested, anyone else?
I think I'm going to drop this one as having no interest.

And since Colonia is over, Harold Reynolds is looking to start something else.

Also, I am going to design some postal rules for Devil Take the Hindmost,
and we have an opening here:
Bruce Edwards, Mike Barno, and Eoghan Barry are signed up.
Postal rules from me will be forthcoming shortly, on my never ending to-do list.
I will get them in SOON!
I'm more likely to get these things started if I see some interest.....
I've GOT to do this now,
Eoghan is getting tired of waiting....

Right now, the other thing going is the Modern
Diplomacy game with Wings.
Sean O'Donnell, Jeff O'Donnell, Steve Koehler, Art Schleinkofer,
Bob Holt, Rick Desper, Alexander Woo, and Dave Partridge are signed up for that.
I will start it when I get a full complement of players, we only need TWO more!
%Sean's list: Britain, Spain, Germany, France, Egypt, Turkey, Russia, Ukraine, Italy, and Poland.

\bigskip

\centerline{\bf TAKING OVER ISHKIBIBBLE'S REGULAR DIPLOMACY GAMES ((NOT))}

\smallskip

Last chance for anyone who was a subber to {\it Ishkibibble} to join any new
game for free, but this is a ONE TIME only offer, get your request in now.
It is going to expire VERY shortly.
Marc Ellinger and Fred Wiedemeyer already have taken us up on this request.
Come on, let me call by name who qualifies
for this deal..... Karl Schmit, John Power, Tim Snyder,
Dave Partridge, Graham Wilson, and Kevin Wilson.
I especially would like to fill the Modern Diplomacy game that Dave Partridge
already is in.
As soon as one more game fills (I'm not counting the new Breaking Away game), 
I'm going to pull this offer.

\bigskip

\centerline{\bf THE PHIL REYNOLDS MEMORIAL: 2006B, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SUMMER 1902 IS JUNE 23RD, 2007}

\smallskip

\noindent {\bf THE DUE DATE FOR FALL 1902 IS JULY 21ST, 2007}

\smallskip

\indent {\it Spring 1902}

\noindent AUSTRIA (Burgess): a vie-TRI, f tri-ALB, a ser-GRE, a bud-SER, f gre-AEG. 

\noindent ENGLAND (James): f lon-ENG, f lvp-NAO, {\it a BRE-par}, f eng-IRI, 
f nwy-NTH.

\noindent FRANCE (Williams): {\it a PAR s a spa-gas}, f por-MID, 
a BUR S ITALIAN a mun, a spa-GAS.

\noindent GERMANY (Ellinger): {\it a KIE-mun}, a BER S a kie-mun, f bel-HOL, 
{\it a DEN-kie}.

\noindent ITALY (Crow): a ven-TYO, f nap-TYH, {\it a MUN s a ven-tyo}, a tun-APU, 
f ION C a tun-apu.

\noindent RUSSIA (O'Donnell): {\it f SEV s f bul(ec)-rum}, a war-LVN, a UKR S f bul(ec)-rum, 
f bul(ec)-RUM, 

a MOS S f sev, f swe-GOB.

\noindent TURKEY (Wiedemeyer): f bla-BUL(EC), a CON S f bla-bul(ec), 
{\it a ARM-sev}.

\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Burgess):&TRI,VIE,BUD,ser,gre&(has 3, bld 2)\cr
%\+ ENGLAND (James):&EDI,LVP,LON,nwy,bre&(has 3, bld 2)\cr
%\+ FRANCE (Williams):&PAR,MAR,spa,por&(has 3, bld 1)\cr
%\+ GERMANY (Ellinger):&KIE,BER,den,bel,&(has 2 or 3, bld 2(r:otb) or 1)\cr
%\+ ITALY (Crow):&ROM,NAP,VEN,tun,mun&(has 3, bld 2)\cr
%\+ RUSSIA (O'Donnell):&WAR,STP,SEV,MOS,bul,swe&(has 4, bld 2)\cr
%\+ TURKEY (Wiedemeyer):&ANK,SMY,CON&(has 2 or 3, bld 1(r:otb) or even)\cr
%\+ Neutral:&hol,rum&(Total=34)\cr
%
%\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: David Burgess, 101 Laurel Lane, Queensbury, NY  12804

(518) 761-6687, burgesscd of roadrunner.com or dburgess of glensfallshosp.org

\noindent ENGLAND: Drew James, 3644 Whispering Woods Terrace,
Baldwinsville, NY  13027

(315) 652-1956, kjames01 of twcny.rr.com 

\noindent FRANCE: Don Williams, 27505 Artine Drive, Saugus, CA 91350, 
(661) 297-3947, 

wllmsfmly of earthlink.net or dwilliams of fontana.org (\$5)

\noindent GERMANY: Marc Ellinger, 751 Turnberry Drive,
Jefferson City, MO 65109

ellingermc of aol.com

\noindent ITALY: John Crow, 824 Kinwest Parkway \#101,
Irving, TX  75063, 

(214) 532-1418, johnny.crow of hotmail.com

\noindent RUSSIA: Jeff O'Donnell, 1345 Simpson Drive, Hurst, TX  76053
%402 Middle Ave., Elyria, OH  44035-5728,

(440) 322-2920 or (440) 225-9203 (cell, as late as midnight Eastern),
unclestaush of yahoo.com

\noindent TURKEY: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  

CANADA  T6T 1N1, (780) 465-6432, wiedem of planet.eon.net 
%cell 780-497-8283; fax 780-468-6432

\bigskip

{\it Game Notes:}

1) Note that my brother David and John Crow add their home Internet addresses
in the usual format.

\bigskip
 
{\it Press:}

\bigskip

\centerline{\bf SPIRALS OF PARANOIA: 2005A, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SUMMER 1906 IS JUNE 23RD, 2007}

\smallskip

\noindent {\bf THE DUE DATE FOR FALL 1906 IS JULY 21ST, 2007}

\smallskip

\indent {\it Spring 1906}

\noindent AUSTRIA (Rauterberg): {\it a RUM s a tri-bud}, a SER S a tri-bud, 
a rom-NAP, {\it a tri-bud} (d r:alb,otb), 

f nap-TYH.

\noindent ENGLAND (Wiedemeyer): {\it f POR-mid}.

\noindent FRANCE (Tretick): f BRE h, a GAS S f mid-spa(sc), f mid-SPA(SC), 
{\it f LON-eng}, a spa-MAR, f IRI h.

\noindent GERMANY (Ozog for Tallman): a MUN S a tyo, a sil-GAL, 
a BOH S a sil-gal, a RUH h, 

a TYO S RUSSIAN a bud-tri, f SKA h, a PIE S ITALIAN f apu-ven, 
a mar-BUR, {\it f ENG-mid}.

\noindent ITALY (O'Donnell): a VIE S RUSSIAN a bud-tri, f apu-VEN.

\noindent RUSSIA (Sundstrom): a war-UKR, {\it a SEV-rum, a ARM-smy}, 
a bud-TRI, a MOS S a war-ukr.

\noindent TURKEY (Biehl): {\it a ANK-arm}, f SMY h,
f BUL(EC) S AUSTRIAN a rum, f ion-TUN, 

f gre-ION, f tun-WES.

\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Rauterberg):&TRI,ser,rum,nap,rom&(has 5, even)\cr
%\+ ENGLAND (Wiedemeyer):&por?&(has 1, even or out)\cr
%\+ FRANCE (Tretick):&PAR,BRE,spa,por?,lvp,edi,lon&(has 5, bld 1 (or 2 if ENG out))\cr
%\+ GERMANY (Ozog/Tallman):&KIE,BER,MUN,hol,den,bel,swe,&(has 9, even)\cr
%\+ &\enskip mar,nwy \cr
%\+ ITALY (O'Donnell):&VEN,vie&(has 3, rem 1)\cr
%\+ RUSSIA (Sundstrom):&WAR,STP,SEV,MOS,bud&(has 4, bld 1)\cr
%\+ TURKEY (Biehl):&ANK,SMY,CON,gre,tun,bul&(has 4, bld 2)\cr
%\+ Neutral:&none&(Total=34)\cr
%
%\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Paul Rauterberg, 3116 W.~American Dr., 
Greenfield, WI  53221, 

(414) 281-2339 (E-Mail)  trauterberg of wi.rr.com

\noindent ENGLAND: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  CANADA  T6T 1N1, 

(780) 465-6432, wiedem of planet.eon.net 
%cell 780-497-8283; fax 780-468-6432

\noindent FRANCE: Buddy Tretick, 5023 Sewell's Pointe Way,
Fredericksburg, VA  22407, (540) 898-3386

cell (540) 226-5571 (E-Mail) berniebuddy32 of aol.com

\noindent GERMANY: Terry Tallman, PO Box 782, Clinton, WA  98236,
(360) 331-5698 (\$2) 

terryt of whidbey.net

\noindent GERMANY: Temporary Standby is Eric Ozog, PO Box 1138, Granite Falls, WA  
98252-1138,

(360) 691-4264, ElfEric of Juno.com

\noindent ITALY: Jeff O'Donnell, 1345 Simpson Drive, Hurst, TX  76053
%402 Middle Ave., Elyria, OH  44035-5728,

(440) 322-2920 or (440) 225-9203 (cell, as late as midnight Eastern),
unclestaush of yahoo.com

\noindent RUSSIA: Matt Sundstrom, 1760 Robincrest Lane South, Glenview, IL  60025, 
(847) 729-1882, 

Matt.Sundstrom of bbdoch.com or mattandzoe of earthlink.net

\noindent TURKEY: John Biehl, \#8 -- 11530 84th Avenue, Delta, BRITISH COLUMBIA,
V4C 2M1  CANADA, 

(604) 816-0460 (cell) (\$7); jrb of dccnet.com

\bigskip

{\it Game Notes:}

1) Terry is still having some medical problems, 
Eric Ozog is continuing to
negotiate and submit orders for Terry.
Eric originally brought Terry into the Diplomacy hobby all those many
years ago, and so I'm glad he's agreed to do this.

2) As someone asked, in this particular game EVERYONE now has E-Mail access, see the 
addresses above.
I think they are all up to date, aren't they??

\bigskip
 
{\it Press:}

(FRANCE to ENGLAND): Gee, guy!  Did you think I would make you go down in 
flames so soon?  Sweat it out.  I have bigger fish to fry such as the Turk.  
Frankly, I hate the smoke from all of those burning bridges lit by Austria.  Be 
realistic!  Ally with Germany, Russia, and France while you are somewhat of a 
force.  You might be allowed to survive the game.

(BOOB to GAME): The above press was sent first.... and then....

(FRANCE to ENGLAND): I wonder what squashed Englishmen look like in the 
Portuguese surf?    

(BOOB to GAME): Hmmmm.....

(STAR TREK PRESS -- 7 OF 9'S LOG): Having sent a tactical
plan to the Andorians and the Ferengi for our joint
effort against the now crumbling Cardassians, the plan
was analyzed by the Ferengi ally, the Packletts, an
annoying race who are much smarter then they led
everyone to believe. They noticed a flaw in my plan
suggesting that it would put the Enterprise at risk
and that could be long term critical as we are the
only allied starship this deep into Cardassian space
other the Cardassian's Dominion allies. 
It's possible we may have turned a corner here. 
Too bad we don't possess a cloak.
We have adjusted our stratagy thanks to the Packletts.
7 out...

(JEFF to JIM): My idiot Indians were in New York against
the Evil Empire this week.   The winning run is on 2nd
base with first base open in the bottom of the 9th
with A-Rod up. 
Our genius manager Eric Wedge 
{\it ((Actually, I think Eric Wedge IS a genius manager, the
best of the current young managers.
The Red Sox just beat up on the Indians this week though,
sorry about that.))}
decides to let our journeyman closer Scott Borowski pitch to
A-Rod rather then walking him and he hits a walk off
home run. AHHHHHHHHHHHHHHHHHHHH! I mean what in the
name of Mike Hargrove iz goin' on here?! 
Have I ever mentioned that I hate the Yankees...
{\it ((Uh, yeah...
we're all vicariously enjoying the Yankees failure.
As I've been saying for years now, this is just the 
continuation of losing the character guys like Paul O'Neill
who really were responsible for the Yankees' success a decade
ago.
Jeter is presently the only one left, after Bernie Williams
was forced out.
I still think that you can't make snap judgments about
managers, hey criticize each decision all you want, but
Eric is still a great manager.
You do well to get more than half of them right.))}
Hey Jim, I have an idea for the name of the new Modern
game: ``Fear and Sleep Deprivation".
{\it ((I'll take it under advisement.))}

\bigskip

\centerline{\bf FLIP FLOP: 2003G, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SUMMER 1909 IS JUNE 23RD, 2007}

\smallskip

\noindent {\bf THE DUE DATE FOR FALL 1909 IS JULY 21ST, 2007}

\smallskip

\indent {\it Spring 1909}

\noindent AUSTRIA (Wiedemeyer): {\it f ven-tri} (d ann), a BUD S a tri-ser, 
a war-GAL,  

{\it a UKR-rum, a MOS-sev, a tri-ser} (d r:vie,tyo,otb).

\noindent ENGLAND (Schmit): a bel-DEN, a HOL S a ruh-kie, {\it a RUH-kie},
f NTH C a bel-den, 

{\it f NWG-nwy}, f HEL S a bel-den.

\noindent FRANCE (Jeff O'Donnell): a bur-BEL, a PIC S a bur-bel, f spa(sc)-MID, 
a gas-SPA.

\noindent GERMANY (Sundstrom): f BER S a den-kie, {\it a KIE-hol,
f SWE-nwy, a den-kie} (d ann),
 
a nwy-STP, {\it a MUN-ruh, f SKA-nth}.

\noindent TURKEY (Levinson): f SMY h, {\it a SEV s a rum}, f ion-TUN, a BUL S a ser, 
f apu-VEN, f nap-TYH, 

a alb-TRI, f ADR S f apu-ven, f BLA S a sev, {\it a RUM s a sev}, a SER S a alb-tri.

\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Wiedemeyer):&TRI,VIE,BUD,ven,mos,war&(has 5 or 6, bld 1(r:otb) or even)\cr 
%\+ ENGLAND (Schmit):&EDI,LVP,LON,por,bel,hol&(has 7, rem 1)\cr
%\+ FRANCE (Jeff O'Donnell):&PAR,MAR,BRE,spa&(has 4, even)\cr
%\+ GERMANY (Sundstrom):&KIE,BER,MUN,den,swe,stp,nwy&(has 6, bld 1)\cr
%\+ TURKEY (Levinson):&ANK,SMY,CON,bul,sev,ser,gre,&(has 10, bld 1)\cr
%\+ &\enskip tun,rom,rum,nap \cr
%\+ Neutral:&none&(Total=34)\cr
%
%\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  CANADA  T6T 1N1, 

(780) 465-6432, wiedem of planet.eon.net 
%cell 780-497-8283; fax 780-468-6432

\noindent ENGLAND: Karl Schmit, 1509 O'Keefe Road, DePere, WI  54115, (920) 338-8402, 

diplomacy of new.rr.com (\$3)

\noindent FRANCE: Jeff O'Donnell, 1345 Simpson Drive, Hurst, TX  76053
%402 Middle Ave., Elyria, OH  44035-5728,

(440) 322-2920 or (440) 225-9203 (cell, as late as midnight Eastern),
unclestaush of yahoo.com

\noindent GERMANY: Matt Sundstrom, 1760 Robincrest Lane South, Glenview, IL  60025, 
(847) 729-1882, 

Matt.Sundstrom of bbdoch.com or mattandzoe of earthlink.net

\noindent ITALY: Don Williams, 27505 Artine Drive, Saugus, CA 91350, 
(661) 297-3947, 

wllmsfmly of earthlink.net or dwilliams of fontana.org

\noindent RUSSIA: Sean O'Donnell, 1044 Wellfleet Drive, Grafton, OH  44044,
(440) 926-0230, 

sean\_o\_donnell of hotmail.com

\noindent TURKEY: Alexandre Levinson, Beeklaan 504, 2562BP Den Haag
THE NETHERLANDS, don't need phone, 

levinson7 of hotmail.com (\$5)

\bigskip

{\it Game Notes:}

1) All set here, I think I have more press that I didn't print, I'll get caught up next time.

\bigskip

{\it Press:}


\bigskip

\centerline{\bf I CAN'T FIND MY MONEY!: 2001F, Regular Diplomacy}

\smallskip

\noindent {\bf TWO WAY DRAW BETWEEN AUSTRIA AND GERMANY WAS DECLARED!}

This one is done now, except I need to do the endgame chart for Tom Howell,
as he knows, I'm usually really slow with these, but I'll try to do it
next issue.

\bigskip

\centerline{\bf SECRETS: 1999D, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SUMMER 1923 IS JUNE 23RD, 2007}

\smallskip

\noindent {\bf THE DUE DATE FOR FALL 1923 IS JULY 21ST, 2007}

\smallskip

\indent {\it Spring 1923}

\noindent ENGLAND (Kent): f ENG S f mid, a GAS S FRENCH f mar, 
{\it a bel-ruh} (d r:pic,otb), 

{\it f MID s FRENCH f spa(sc)}, f POR S FRENCH f spa(sc).

\noindent FRANCE (Sasseville): {\it f MAR s f spa(sc)}, f SPA(SC) S f mar, 
a BUR S f mar.     
%standing orders, yes to ANY draw
                                             
\noindent GERMANY (Barno): {\it a SER-blacksburg} (imp).
%votes yes to FREGT, no to EFRT 
%vote YES to FREGT draw

\noindent RUSSIA (Parker): f stp(nc)-NWY, a mos-STP,
f nwy-NWG, f edi-CLY, a WAR h, 

a DEN S a kie, a KIE S a hol, f hel-NTH, 
a HOL S TURKISH a ruh-bel, a lvn-PRU.

\noindent TURKEY (Linsey): a ank-ARM, a con-BUL, f ion-TYH, a bul-RUM, 
a boh-MUN, 

a SIL h, f WES S f naf-mid, a gal-BOH, f GOL S f pie-mar, 
a ruh-BEL, a TRI h, 

{\it f NAF-mid}, a tyo-VEN, {\it f PIE-mar}, a mun-RUH.

\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ ENGLAND (Kent):&LON,LVP,bre,por,bel&(has 6, rem 1)\cr
%\+ FRANCE (Sasseville):&PAR,MAR,spa&(has 3, even)\cr
%\+ GERMANY (Barno):&ser&(has 1, even)\cr
%\+ RUSSIA (Parker):&MOS,STP,nwy,swe,den,ber,WAR,kie,&(has 8, bld 2)\cr
%\+ &\enskip edi,hol   \cr
%\+ TURKEY (Linsey):&CON,ANK,SMY,rum,gre,bul,&(has 14, bld 1)\cr
%\+ &\enskip bud,nap,ven,tun,sev,rom,tri,vie,mun \cr
%\+ Neutral:&none&(Total=34)\cr
%
%\bigskip

\indent {\it Addresses of the Participants}

\noindent ENGLAND: Doug Kent, 11111 Woodmeadow Pkwy \#2327, Dallas, TX  75228

dougray30 of yahoo.com 

\noindent FRANCE: Roland Sasseville, Jr., 38 Bucklin Street, Pawtucket,
RI 02861, (401) 481-4280 (\$0)

roland6 of cox.net  

\noindent GERMANY: Mike Barno, 634 Dawson Hill Road, 
Spencer, NY 14883, (607) 589-4906 

mpbarno of lightlink.com 

\noindent RUSSIA: Vern Parker, 337 Winter Hill Place, Powell, OH 43065,
(614) 402-5139

VernDip of aol.com is preferred

\noindent TURKEY: Bruce Linsey, PO Box 234, Kinderhook, NY
12106

GonzoHQ of aol.com

\bigskip

{\it Game Notes:}

1) An RT Juggernaut draw and a concession to Turkey are proposed, please vote
with your summer orders. 
Failure to vote is the same as a no.

2) This game has been going on for eight years now, I believe Roland
Sasseville is the only original player, isn't he?  Laugh now, Roland!

\bigskip

{\it Press:}
 

\bigskip

\centerline{\bf CAST NO SHADOWS: Breaking Away, Designer's Rules}

\smallskip

Rules are at:

\noindent http://devel.diplom.org/DipPouch/Postal/Zines/TAP/Tinamou/rules/BreakingAway.htm

\noindent Note the special rules for replenishments on the first turn, and I'm glad the 
math was double checked, we did have a card error, which is now corrected and we have
the first turn below.

\smallskip

\noindent {\bf DUE DATE FOR TURN 2 IS JUNE 23RD, 2007}

\smallskip

%--F--I--N--A--L-- --F--I--N--I--S--H-- --L--I--N--E--
%--S--P--R--I--N--T-- --F--I--N--I--S--H-- --L--I--N--E--
%
\centerline{\it Turn 1}

\smallskip

\+ 13 (replenish with a 3)&Sanctus (Breaking Away!!!)  \cr
\+ 12 (no replenishment)  &Empty  \cr
\+ 11 (no replenishment)  &Empty  \cr 
\+ 10 (replenish with a 3)&Bonham  \cr
\+ 9 (no replenishment)   &Empty  \cr
\+ 8 (no replenishment)   &Empty   \cr
\+ 7 (replenish with a 3) &Bowie, Travis, Crockett   \cr
\+ 6 (no replenishment)   &Empty  \cr
\+ 5 (no replenishment)   &Empty   \cr
\+ 4 (replenish with a 3) &Kyoto, Vidic   \cr
\+ 3 (replenish with a 3) &Rincewind, Mideast, Wally, Xavier, Yorick, Kyrie, Gavrancic  \cr
\+ 2 (replenish with a 3) &Granny, Carrot, Drugs, Zorro, Dragutinovic   \cr
\+ 1 (replenish with a 3) &Death, Water, Agnus, Gloria, Krstajic    \cr

\bigskip
%Sprint Points: 10,8,6,5,4,3,2,1 (final are just double these)
%Movement Order: A/B/C/D; highest card played that turn; highest card in hand

\indent {\it Addresses of the Participants -- Their Team and Their Cards}

\smallskip

\noindent TEAM 1 (Rick Desper): rick\_desper of yahoo.com (0 points)

Team Name: The Turtle Moves; Captained by Cut-My-Own-Throat Dibbler

\+ A: Rincewind the Wizzard &&14 12 1 3 (3) \cr
\+ B: Granny Weatherwax     &&12 11 3  (2) \cr
\+ C: Captain Carrot        &&15 3 3   (2) \cr
\+ D: Death                 &&13 2 3   (1) \cr

(note, Rincewind is accompanied by the Luggage, Granny is on Her Broom, 
Carrot is of the City Watch, and Death is just DEATH!)

Total Replenishments: $12 = 12$
                
\smallskip

\noindent TEAM 2 (Tom Howell): off-the-shelf of olympus.net (0 points)

Team Name: Never Ending Worry Source; Manager: Rumour; Team Captain: Ye Olde Manager

\+ A: Water    &&15 11 3 3 (1) \cr
\+ B: Kyoto    &&14 7 3 (4) \cr
\+ C: Mideast  &&11 6 3 (3) \cr
\+ D: Drugs    &&9 5 3 (2) \cr

Total Replenishments: $12 = 12$        
   
\smallskip

\noindent TEAM 3 ((David Partridge): rebhuhn of rocketmail.com (0 points)
%360-928-9698

Team Name: Famous Four  

\+ A: Krstajic      &&6 8 15 3 (1) \cr
\+ B: Vidic         &&8 13 3   (4) \cr
\+ C: Gavrancic     &&8 9 3    (3) \cr
\+ D: Dragutinovic  &&6 8 3    (2) \cr

Total Replenishments: $12 = 12$   
               
\smallskip

\noindent TEAM 4 (Brendan Whyte): obiwonfive of hotmail.com (0 points)

Team Name: The Reverse Alphabeticists

\+ A: Zorro    && 3 10 15 3 (2) \cr
\+ B: Yorick  && 10 12 3 (3) \cr
\+ C: Xavier   && 7 10 3  (3) \cr
\+ D: Wally    && 3 10 3  (3) \cr

Total Replenishments: $12 = 12$

\smallskip

\noindent TEAM 5 (Alexander Woo): aswoo of yahoo.com (0 points) %awoo@math.ucdavis.edu

Team Name: Just Ordinary; Manager: Credo

\+ A: Agnus     && 15 12 2 3 (1) \cr
\+ B: Sanctus   && 8 4 3  (13)   \cr
\+ C: Kyrie     && 10 7 3  (3)    \cr  
\+ D: Gloria    && 12 3 3  (1)    \cr
           
Total Replenishments: $12 = 12$ 

\smallskip 

\noindent TEAM 6 (Andy York): wandrew of compuserve.com (0 points)

Team Name: Alamo

\+ A: Crockett      && 15 5 3 3 (7) \cr
\+ B: Travis        && 15 3 3 (7)\cr
\+ C: Bowie         && 10 3 3 (7) \cr
\+ D: Bonham        && 3 3 3 (10) \cr

Total Replenishments: $12 = 12$

\bigskip

{\it Game Notes:}

1) The rules are on the {\it TAP} website in the {\it Tinamou} section.
Ask if you have any questions.
Up above in parentheses is the card you played to get to where you are
in the field.  The replenishment card is the last card in your list.
Be careful to note that the card you played (the one in parentheses) is
not available for you, for next turn.
Just for fun, I'm going to keep track of total replenishment, by turn, which is a 
rough measure of how the teams are doing.
Of course, it is lining up to get across the sprint and final lines in the
right places that really counts.
We can calculate an ``efficiency score" later, which will be the ratio
of scoring points per replenishment.
If I'm predicting how the future of this will come out, a 10\% score will
be really tremendous for this measure.

2) Wow, as many of you predicted, EVERYONE replenished with a three.
So one thing that everyone has is threes..... we'll see how many people
play a three next turn.

\bigskip

{\it Press:}


\bigskip

{\it Personal Note to You:}

\vfill\eject
\end
