\nopagenumbers 
\font\twelverm=cmbx12 at 12pt
\centerline{\bf\twelverm THE ABYSSINIAN PRINCE \#309}
\line{\hfil February 19, 2007}    
\smallskip                                                    
\settabs 3 \columns 
\beginsection

\medskip

Produced by Jim Burgess, 664 Smith Street, Providence, RI 02908-4327  USA,
(401)351-0287 
 
\noindent Accessible through Internet at burgess of world.std.com (all E-Mail
addresses are reported in this format, replace the `` of '' with ``@''; if you 
bounce try sending to me from another account. 
Some of you have been getting bounced messages from
my ISP's spam protection, if that happens to you, USE my backup E-Mail
at jfburgess of gmail.com!!!  Don't complain that my E-Mail keeps bouncing
without forwarding the bounced message to that address.
Then I can forward it to the ISP help to get it dealt with.
 
\noindent Web Page Address: /Postal/Zines/TAP/index.html

\bigskip

I expect ALL players to be signed up on the E-Mail notification list for the szine,
see below.
Some of you have been complaining about this, but it is up to you to get on this list,
it's easy, come ask me if you have trouble.

Sorry about the lateness of this issue.  As I think I mentioned, I was moving my office
at work, and rather than be completely unproductive I tried to ``do it all'' and what
fell apart was the szine.
I am still not completely moved since my new office is stacked with boxes which I can't
see having time to unpack for another couple of weeks, but hey, I can't keep you all 
waiting any longer.
I think we're all set with things in here, with a couple of exceptions, 
I advanced one game ahead past a ``do nothing'' deadline, but I still don't
have everyone's card setups for Breaking Away and I think the 23 tunes is
still a bit of a mess.
But hey, that one's just for fun.
I think at least for 23 tunes I don't have anyone with tunes they've submitted
that I don't have.
Last issue I forgot to include Doug Kent's tunes.
Despite that, we have another new subszine, Doug is spreading his wings a bit
with a subszine here.
I think, if the demand/need is out there, he would prefer to have his own 
separate szine.
So if you're interested in that, tell him.
I'm willing to be completely flexible here.

\bigskip

%Dave Partridge's unlisted phone number 603-672-2879 -- probably corrected!!!
%Tinamou players: Schwarzschild:  Graham Wilson (NO 
%but E-mails: grahamaw of home.com (or gwilson of dvnet.com)),
%Berry Renken, Heath Gardner
%Copernicus:  Warren Goesle, Heath Gardner, Art Schleinkofer, Bruce Reiff,
%Eric Brosius, Bob Dowrey
%Tour De Farce:  Jim Burgess, Eric Brosius, Warren Goesle, Sara Reichert,
%Phil Reynolds, Rick Desper
%Milk and Cookies: Jim Burgess, Warren Goesle, Sara Reichert, Phil Reynolds,
%Rick Desper, Richard Weiss, John Schultz
%Who's Your Buddy:  Sara Reichert, Phil Reynolds, Art Schleinkofer, 
%Brad Wilson, Rick Copeland, Karl Muller

The postal sub price is still
\$1.50 per issue in the US and Canada,
with double that for other foreign subbers(or \$3.00 per
issue sent airmail).
Players in current games and standbys will
continue to get the issues for free, and future game starts 
(except for Nuclear Yuppie Evil Empire Diplomacy, which is free) cost 
\$20.00 (\$15.00 for a life of the
game subscription and \$5 for the NMR Insurance.
Anyone may play in subszines 
for free and just jack up the issue page count. 
See the revised game start announcements below!

Check out the connections in the Diplomatic Pouch with all of
the information you need to play Diplomacy on the Internet at:
/

I also have taken over the Postal port/DipPouch/Postal

\noindent and {\it TAP} on the web is there at:
/Postal/Zines/TAP/index.html

where the szine resides in html format. 
Presently, issues from \#190 to the current issue
are there, and I will be updating the back issues gradually someday. 
Also, check out Stephen Agar's more extensive efforts at:
http://www.diplomacy-archive.com and http://www.diplomacy.co.uk
 
Peter Sullivan's subszine is out of stasis, and all the
back issues can be accessed via :

http://www.burdonvale.co.uk/octopus/index.html.

Peter now seems to be sliding back into stasis!
Rip Gooch and Dave Partridge had been picking up the choo-choo
game slack,
but Rip also has been missing in action completely for over a year now, 
I don't have an update but he
and Dave Partridge communicate. 
Contact Rip at xyropedes of canada.com or Dave
at rebhuhn of rocketmail.com for more info on getting into choo-choo games.
And Andy York has been my most frequent subszine guest lately!!!
He's been in every issue, thanks, Andy!!!

The {\it TAP} mailing list has moved!
It now is even BETTER protected than it was.
I even have a bit of trouble posting to it.
To post to this list, send your email to: tap of diplom.org.
But this is completely moderated, it won't go out to the list unless
I approve it.
In general, I intend to keep traffic down to just the szine, as we've
been doing and I'll put your LOCs in here.
I {\bf EXPECT} all players to be on this list, especially those of you who
are from foreign countries!!! 
You need this to find out when the szine is up on the web to check in on results.

General information about the mailing list is at:
/mailman/listinfo/tap

You can sign up from there, or send E-Mails to:
Tap-request of diplom.org;
with the word `help' in the subject or body (don't include the
quotes), and you will get back a message with instructions.
You must know your password to change your options (including changing
the password, itself) or to unsubscribe.  
Normally, Mailman will remind you of your diplom.org mailing list
passwords once every month, although you can disable this if you
prefer.  This reminder will also include instructions on how to
unsubscribe or change your account options.  There is also a button on
your options page that will email your current password to you.
A big, big thank you for Millis Miller for setting this all up!!

\bigskip

\centerline{\bf THE SEARCH FOR MARGARET GEMIGNANI}

\smallskip

OK, now, why Margaret?  Margaret, of course, is one of the most famous personalities in 
Dipdom, Science Fiction, Star Trek, Comic, etc. fandom.  
She was a nurse in the DC area, I believe, and then retired to Florida some years ago.
Many people had an address for her in Fort Lauderdale (including me), but that address
went missing around 1994.
If you do Google searching, as I have done off and on, there is a Margaret Gemignani
that contributes to the Baltimore and Ohio Historical Railroad Association, along with 
a husband, Gino (anyone know if that matches.... the B\&O matches where she used to live...
but don't tell me, use it as info to go looking yourself!!!)
Margaret has a couple of mentions in the Diplomacy AtoZ and I first encountered her
in the old Bernie Oaklyn {\it Le Front} szine.
I think it would be fun to find her.
You have until issue 310 and then we move on to someone else.
Bill Quinn is found!!!
Plus we re-find Dan Stafford.  
More on the former BNC, Bill Quinn, below.
Doug Kent wins \$25 for the find.

\bigskip

Feel free to spend the time looking for some of the backlog.
Let's get Jeff, Derek, Sylvain, Steve, Ed, Tom, Gregory, and 
ESPECIALLY Kevin found too!!!
This is a regular continuing feature of the szine
and I will be introducing a new ``search for'' every five issues.
Moreover, you can win a \$25 prize for finding some previous
target who went unfound in the original \$50 period.
That means that if Jeff Key or Steve Heinowski or Ed Henry or Tom Hurst or 
Gregory Stewart or Derek Nelson or Sylvain LaRose or John Smythe
is ``found'' from now on it is worth \$25.

\bigskip

Winners will receive credit for Dip hobby activities
that I will pay out as requested by the winner.
Subscribe to szines here or abroad, run your
own contests, publish a szine, finance a web page, 
GO TO A DIPLOMACY CONVENTION or whatever.
Spend it all right away or use me as a bank to cover hobby activities
for years.
What must you do to win?
Get me a letter to the editor for {\it TAP} from the person we're
searching for.

This is very important, just finding them doesn't do it.
They have to write me a letter.     
The final judge as to the winner of any contest will be the target 
himself and I reserve the right to investigate the winning entry.
When you find someone I'm looking for, you should ask him to send me a 
letter for print that includes a verification of who ``found'' him.
%Michael Swift, Mike Stewart, and 
%Jason Yarbrough , Tim Stabosz, 
%Eric Ozog has $25
%Leslie Obata is owed $25
%Derek Nelson, winner of the first postal game in Graustark.  I last saw him
%at the '76 DipCon in Baltimore.
%Charles Wells, former publisher
%John McCallum, former publisher (Brobdignag, SerenDip, etc.)
%Dan/Charles Brannan, former publisher (Wild 'n Wooly)

\bigskip

{\bf Bill Quinn (Feb 25, 2007 9:18 AM)}   

Dear Jim,

Doug Kent found me. I didn't know I had been misplaced. Until then I had
not thought much about the hobby. Passages in life have drawn me away.  I gave
myself a tour of what I could find on the net about the hobby. Kathy Byrne
Caruso's passing caused me sorrow. We corresponded and spoke often during
our tenures as BNC and when I published ``Everything...". Even when she broke
up our happy alliance in the only game we started together we laughed about
it. At least I could say, ``I've been Byrned"
  
I'm not surprised to find the postal segment in steep decline and most
likely headed to extinction. The e-mail generation has far more games to
play in a more instantaneous mode. I traded notes with Tom Howell to learn
that few numbers had been issued and the office of BNC had run into some
neglect since 1997.  He reports that the e-mail Diplomacy gaming is quite
active but no numbers are issued and chaos reigns.

Just to see what relics it contained I brought my 1976 Bookcase Edition
of Diplomacy down from it's quiet corner of a little used book shelf. Inside
were Issue \#121 and 122 of {\it Claw and Fang}. It was fun to read the original
spoofs of Robert Frost and John LeCarre from a supposed ``Famous Writers
Game". There was a copy of Doug Beyerlein's ``Adjudicating Postal Diplomacy
Games". Was he meticulous! A game start announcement on the back of a
conference map turned up. Hope it got a number. Last I found a Diplomacy
tournament procedures pamphlet for Origins XV. I attended it mainly to meet
the influential members of the hobby at the time. The inspiration lasted for
years. A few other items were there. Diplomacy Digest \#99 was residing
there. The issue that touched on the GREAT FEUD and several articles about
Turkish strategy and the results of the Runestone Poll. In all a nice stroll
through some memories.
  
To avoid boring readers I'll stop now. If anyone would like to send me a
note (either postal or e-mail) please do.  Good gaming to all.

\centerline{Bill Quinn, 3032 Meador Lane, Conroe, TX 77303, q\_bar of hotmail.com}

{\it ((Thanks, Bill, good to have you around.
We find it fun here to keep the legends of the 60s, 70s and 80s connected to the
hobby.
I have fun doing it.
I suspect Doug Kent will find more of these people if I give him a chance.))}

\bigskip

\centerline{\bf INTERNATIONAL SUBSCRIPTION EXCHANGE NEWS}

\smallskip

The British representative is the editor of
{\it Mission From God}, John Harrington.
John may be contacted at 1 Churchbury Close, Enfield, Middlesex
EN1 3UW, UK.

E-Mail: fiendish of operamail.com, John.Harrington of tfeurope.com 

Please include the full name and address of the foreign publisher with
your order, if possible, as well as the szine title.
Make your check in US dollars out to me personally or in GBP to John
if you're doing things from that end.
I will conduct business for Canadians as well, if I can, but prefer
to deal in US dollars with them if possible, or Canadian dollars cash.
To subscribe to American szines, the system works in reverse.

We have closed the European continental branch, as I think most
of you had figured out.

And the ISE in Australia hadn't had much real action in recent
years, and Brendan Whyte has moved on to Jerusalem!!!
Brendan still produces what I find to be the most readable
small szine in the worldwide hobby.
Did you all realize that?
Write to Brendan at his new Jerusalem address and ask him
about subscribing, I'm not sure what the new deal will be.
Department of Geography, Faculty of Social Sciences,
The Hebrew University of Jerusalem, Mount Scopus, Jerusalem
91905, ISRAEL.
His travelogues are wonderful.

\bigskip  

\centerline{\bf WORLDMASTERS04 SECTION}

\smallskip

See http://www.worldmasters.net/wm04/
for details on progress on the WORLDMASTERS04, the Semifinals have now begun.  
Some semifinal notables include: Egg Ferreira, Buffalo Bartalone, Lee Simpson, 
Joe Janbu, Sebastian Beer, Doug Moore,
Jerry Fest, Twerg O'Donnchu, Tim Sweeney, Dave Partridge, Glenn Ledder,
Adam Silverman, Toby Harris, and Thomas Franke.
This is one of the deepest semifinal fields for this great tournament 
that I've seen, with representatives from nearly all of the world's
hobby communities.
Actually, the Semifinal games began in October.
I was wondering why I hadn't seen anything on progress in these games,
and that's why.
More on that next issue!!!
Thomas Franke and David Partridge are in a game together that seems
on first glance to be the weakest in the rest of the players.
So my first thought is that one of those two will have a slot in
the finals.
I am getting raked over the coals for it, but I just ended a game
in a three way draw between me, Thomas, and Ray Setzer that I might
have had a chance in ekeing out a win mostly because Thomas asked
for it to end so he could focus on this semi-final.
Sorry, David, but I had to do it.....
Of course, after saying that, David Partridge is in England getting beaten
on by Guy Thomas in France, who is allied with Thomas Franke in Italy.
But Italy has a Juggernaut bearing down on him from Mike Tombu and
Julio Cardoza.
And Toby Harris just got crunched in his game where he is Turkey, but
I don't count him out yet, he has more lives than a cat!!
But never mind, I don't know how ANY of this will turn out!!!
Doug Moore is doing pretty well as Russia in his game so far, but
Russia can always be crunched after doing well early.
Buffalo is doing pretty well in his game as France taking down Germany
and now attacking Adam Silverman's England, I think, that part is still
developing.

I've joined the Yahoogroup WM04-Chat where some of this
discussion is happening.
You can join too!
However, this forum has been very, very quiet, I hope it picks up with
semis, maybe I'll have to start some discussion.
I had to go the main Worldmasters site at www.worldmasters.net/wm04/ to
find some of these results.
The new Tournament rankings for FTF also are out there that supercede the
ones that were on 18centres.
Go check out:

http://eurodip.nuxit.net/php/ranking/index.php?lang=Ang

It ranks 4792 FTF players and is the most complete known compilation of FTF play
ever in the hobby.
You really want to check it out.
Poor Eve Smith ends up 4791st, having been in 33 tournaments in the last ten years,
an achievement in itself!
And of course Don Del Grande is down near the bottom at 4787th, off of 13 tournaments,
two of them in Australia.
For having the Don Challenge Cup named after him, he didn't do THAT badly in his
tournaments Down Under, better than I'd been led to believe at 54/78 and 34/57
And Frank Johansen is a well deserved \#1.
And I'm amazingly in the top quarter with a ranking of 1154, accurately reflecting
the nine tournaments that I know I've been to (i.e. I don't see any missing).
Yann Clouet (if I counted right) has been to 95 tournaments, I'd be surprised if
someone surpasses him in number, and he ranks 11th.
Guaranteed to be a fun browse....

\bigskip

\centerline{\bf DIPDOM NEWS SECTION (with letters)}

\smallskip
 
Obscure and not-so-obscure ramblings on the state of the hobby
and its publications, custodians, events, and individuals with
no guarantee of relevance from the fertile keyboard of Jim-Bob,
the E-Mail Dip world, and the rest of the postal hobby.
My comments are in {\it italics} and {\it ((double 
quotation marks))} like this.
{\bf Bold face} is used to set off each individual speaker.
I should also make a note that I do edit for syntax and spelling
on occasion.

%A VERY light discussion is taking place that will address what 
%stance we (the hobby) should take (proactive in some way for sure) 
%toward Hasbro, the new owners of the rights to Diplomacy.
%More on this will be forthcoming, but it looks like Hasbro might
%have its version of Diplomacy on the market for the Christmas
%season and they actually will be employing ``play-testers''.
%No word on precisely what this means yet, could it mean that
%they will offer a series of ``official'' variants?
%Stay tuned....
%If you want to be part of the discussion, send the MESSAGE:
%
%subscribe hasbro
%
%to majordomo of diplom.org, it works just like the tap mailing list
%described below.  Sending messages to hasbro of www.diplom.org
%sends the mail to the whole list.
%The big news this time is the beginning of the breakout of
%Hasbro into official contact with the hobby.

The game Diplomacy is a copyrighted product owned by Hasbro and all
reproductions or other use of that material in this szine is intended to
be personal use and not infringe on those rights in any way.
All reproductions are done at a heavy financial loss to the editor
and thus are without the remotest possibility of commercial intent,
except to promote THE game, the Game of Diplomacy, which you all 
should purchase from Hasbro or other duly licensed distributors.
 
Stephen Agar has matched the Hasbro rule lists 
and more with some of the even older
rulebooks.
Check these out if you like:

http://www.hasbro.com/default.asp?xcc\_gameandtoyinstructions

http://www.hasbro.com/instruct/Diplomacy.PDF

http://www.hasbro.com/instruct/Diplomacy(OlderVers).PDF

Nice of them to make BOTH of these available.
And all seven different US rulebooks for Diplomacy can now be found here
courtesy of Stephen Agar (relatively new address for this):

http://www.diplomacy-archive.com/diplomacy\_rules.htm

%1: The Reformer, who seeks perfection (crusading type).
%2: The Helper, who seeks love (altruistic type).
%3: The Performer, who seeks status (competitive type).
%4: The Individualist, who seeks an identity (imaginative type).
%5: The Investigator, who seeks knowledge (analytical type).
%6: The Loyalist, who seeks security (ambivalent type).
%7: The Enthusiast, who seeks gratification (thrill-seeking type).
%8: The Leader, who seeks self-sufficiency (dominant type).
%9: The Peacemaker, who seeks contentment (accommodating type).
%See http://graphics.lcs.mit.edu/~becca/enneagram/
%new test at: http://www.9types.com
%My scores in order were: 9, 13, 15, 7, 15, 6, 17, 18, 14.
%Robert Lesco's Marco Poll, the defacto poll of the
%North American hobby since the Runestone is pretty much
%officially dead, continues to collect votes.
%This is an official {\it TAP} approved poll.
%Here are the particulars on the Marco Poll:
%Vote for your top five in each category and you can't vote (or at least
%it won't be tabulated) for Robert Lesco or his szine, which I don't see.
%I will send this to Robert and offer him a trade.
%The deadline is September 1st and either send your ballot to marcopoll of yahoo.com
%or mail to Robert Lesco, 49 Parkside Drive, Brampton, Ontario, CANADA  L6Y 2H1.
%For identification purposes, Robert would like you to identify yourself both
%by name and by affiliation (a game you play in or a szine you sub to).
%Here are the categories this year (I like some of the new ones!!):
%1) Favourite {\it ((Hey, what, he's Canadian, yeah.))} Zine  {\it ((What's a zine,
%shouldn't that be Szine???))}
%Backstabbers United Monthly, Costaguana, The Diplomatic Pouch, Absolute, Vertigo
%2) All Time Favourite Zine {\it ((Szine))}
%Magus, Europa Express, Thirty Miles of Bad Road, Perelandra, North Sealth West George
%3) Best Diplomacy Player
%John Quarto von Tivadar, Edi Birsan, Mark Fassio, Chris Martin, David Partridge
%4) All Time Best Diplomacy Player
%Edi Birsan, Mark Fassio, Kathy Caruso, Rod Walker, Hohn Cho
%5) Best GM
%Malcolm Cornelius, Tim Miller, Tim Richardson, Conrad von Metzke, Doug Massey
%6) Player Who Writes the Best Letters/E-Mails
%Don Williams, Richard Weiss, Mark Fassio, Toby Harris, Cal White 
%7) Folded Zine {\it ((Szine))} You Miss the Most
%Magus, Diplomacy by Moonlight, Le Front du Liberation de Diplomacy, Kathy's Korner
%8) Favourite Variant
%Modern, Nuclear Yuppie Evil Empire Diplomacy, Woolworth, Spy Diplomacy, Colonia

\bigskip

\centerline{Check out current and back issues of {\it Diplomacy World} -- Yahoogroup diplomacyworld}

Also, I need any Hobby Award Nominations NOW (!!!) for the :

\noindent The 2005 and 2006 Don Miller Award for Meritorious Service;

\noindent The 2005 and 2006 Rod Walker Award for Literature;

\noindent The 2005 and 2006 John Koning Award for Player Performance;

\noindent The 2005 and 2006 Fred Hyatt Award for GM Performance;

or

\noindent A 2005 and 2006 Kathy Byrne Caruso Award for Lifetime Achievement (if warranted).

The Hobby Awards Committee is Jim Burgess (Chair and Treasurer),
Fred Davis, Jr., Melinda Holley, Gary Behnen, Jamie Dreier,
Paul Kenny, Mark Stretch, and Robert Lesco.
I was going to publish the award ballot for this year 
in this issue, but I realized that I really just had to get this out first and
then do that.... and then, well, REAL SOON NOW!!!
And when I do, I'm going to give out two sets of awards and get caught up for the 
missed year, that seems to make the most sense.  
Committee.... you will be hearing from me soon!
This also fell apart with my move, but I will get this out next issue come hell or high water.

\bigskip

{\it Diplomacy World} Issue Deadlines were:

\noindent Deadline Spring 2006, Issue \#97: March 1, 2006

\noindent Deadline Summer 2006, Issue \#98: June 1, 2006

Note that Andrew Neumann had taken 
over the lead editorship from Tim Haffey, but he clearly wasn't up to it.
So, I'm officially looking for a lead editor again.
As we have had for the last five years or so, the Pouch is back up and
running again, and Diplomacy World is dead in the water, it seems that is
the way it is.
One runs, and the other one stops.
This occurs even though there really is no direct connection.
If you'd like to do this, let me know, I make it pretty easy, but I
CANNOT be lead editor for two szines at once, I just can't.

%\noindent Final Hobby Awards Ballot for 2004, nominations now to:
%burgess of world.std.com
%
%The qualifications for the Kathy Byrne Caruso Lifetime Achievement 
%Award are that the awardee must have been: (1) Active in the 
%Diplomacy Hobby in at least Three Separate Decades; 
%(2) Multidimensional in their Contributions to the Hobby 
%(e.g. writing, playing, publishing); (3) Taking Retirement or 
%Semi-Retirement from the Diplomacy Hobby; and (4) One of the 
%Hobby’s Unique Personalities Worthy of Being Remembered as Long 
%as THE Game Continues to be Played.  This award need not be awarded
%each year, but only as worthy candidates are identified.  The only
%past honoree is the late Richard Sharp.
%
%The other award categories are self-explanatory:
%
%\noindent Nominees for the 2004 Don Miller Award for Meritorious Service
%
%\noindent Nominees for the 2004 Rod Walker Award for Literary Achievement
%
%\noindent Nominees for the 2004 John Koning Award for Player Performance
%
%\noindent Nominees for the 2004 Fred Hyatt Award for GM Performance
%
%--- --- --- --- --- --- ---

Editorial Board for Diplomacy World (need a Lead!!!):

\noindent Andrew Neumann, andrewneum of gmail.com -- Missing Lead Executive Editor!

\noindent Tim Haffey, 810 53rd Ave., Oakland, CA 94601 USA; trhaffey of
aol.com -- Ex-Lead Editor and Archives Editor

\noindent Jim Burgess, 664 Smith Street, Providence, RI 02908-4327, USA;
burgess of world.std.com -- Co-Editor and Publisher

\noindent Stephen Agar, 4 Cedars Gardens, Brighton, UNITED KINGDOM  BN1 6YD;
stephen of stephenagar.com -- Webmaster and Non-US Postal

\noindent Rick Desper, 5440 Marinelli Road, \#204, Rockville, MD  20852, USA;
rick\_desper of yahoo.com -- Demo Games

\noindent Dave Partridge, 15 Woodland Drive, Brookline, NH  03033, USA;
rebhuhn of rocketmail.com -- US Postal

\bigskip

{\it ((I've got two con reports this issue, one from Mike Barno, the
other from me.
First Mike for Bruce Linsey's New Year's KniziaKon.....))}

\bigskip

{\bf Mike Barno (Wed, 10 Jan 2007 23:21:53 -0500)}

Invitational-only (so I couldn't bring my workplace or weekend people), 
KniziaKon hosted a bunch of folks for 192 plays of 108 different games, 
including 44 different Reiner Knizia games.  (Knizia is the designer of 
TAJ MAHAL, INGENIOUS, TIGRIS \& EUPHRATES, LOST CITIES, MEDICI, MODERN 
ART, RA, THROUGH THE DESERT, TRAUMFABRIK, and other notable games.  This 
con emphasized casual play of his games, but was otherwise for casual 
play of darn near any strategy games including one or two collectible 
card games.) 

Lots of friends including a few from the 1980s.  First time I'd seen 
Steve Hutton in fifteen years.  I was there Friday noonish until Monday 
noonish and played two dozen games without trying hard.  For example of 
not gaming every waking moment, I took two decent-length hikes and 
several short ones.  On one of the hikes at the Martin Van Buren Trails, 
I saw a nesting pair of hawks drive off a larger group of other birds... 
peregrine falcons, possibly... who were trying to chase them out or kill 
their eggs.  Noisy, impressive.

At the same house the previous New Year, I won a game (a short 
pirate-themed card game) at 11:59 pm on 31-Dec, the last finish of the 
old year.  This time, I won a game of ZUM KUCKUCK!, a short 
cockatoo-themed card game, at 12:01 am on 1-Jan, the first finish of the 
new year.  Woo hoo!

I had only two repeats, so there were 22 different titles, including 8 
designed by Reiner Knizia:

-- Grand National Derby [Piotnik Games], 4 players, learned, Knizia : 
steeplechase horse racing, bet on horses and play cards, worst horse at 
each fence is eliminated.

-- Money! [Gold Sieber Games], 5 players, Knizia : set collecting among 
several types of currencies, with an interesting mechanic: bid some of 
your cards, players choose in high-to-low-bid order to swap the bid 
cards for one of two groups on the table or for another player's bid cards.

-- Medici [Amigo Spiele], 5 players, Knizia : classic abstract Eurogame, 
auction of cards of five colors, bonuses for winning each color and for 
best total card value.

-- Crokinole, 4 players in 2 teams, won : disk-flicking game on a wood 
board with bumpers, trying to get your disks into a hole in the middle, 
simple rules give enough strategy to make it more than flick-skill exercise.

-- Gheos [Z-Man Games], 4 players, learned : a build/merge/split game 
somewhat like Java or Taluva, with a military element.  Less fiddly and 
more actiony than most similar games like those named or LASS DIE KIRCHE 
INS DORF.

-- Settlers of Catan, on 3-D set with miniatures sculpted by Klaus 
Teuber, 4 players, won : plain vanilla Settlers except the big fancy 
board and pieces.  Pretty, but I'm told that kind of resin shatters if 
you drop it.

-- Yspahan [Y'stari Games], 4 players : roll a bunch of dice, players 
choose them for resources or buildings or improvements or caravans with 
a vague theme and little interaction.

-- City and Guilds [JKLM Games], 3 players, learned, won : tile placement 
with a medieval city-building theme, seemed more interesting than 
Carcassonne for our tastes.

-- Ticket to Ride: USA 1910, Mega Game [Days of Wonder], 3 players : All 
the old and new ticket cards, more tickets when you draw, both bonuses 
(longest road and most fulfilled tickets).

-- Ta Yu [Rio Grande Games], 2 players, taught : Just pipe-connecting 
tile-laying like dominoes, but so much strategic richness in such a 
simple set of rules.  My favorite game to teach to non-gamers.
{\it ((I've wanted to get and learn this one, you've nudged me to do it.))}

-- Stephenson's Rocket [Rio Grande Games], 4 players, Knizia : railroad 
building in Britain, merging like Acquire, but very much a Knizia game 
in having multiple ways to earn points.

-- Taj Mahal [Rio Grande Games], 5 players, Knizia : ingenious 
card-driven six simultaneous auctions, multiple ways to score, theme is 
political jockeying in India.
{\it ((I agree, this is a really cool game.))}

-- Ta Yu again, 2 players : one of just two games that I repeated.

-- Too Many Cooks [R\&R Games], 4 players, learned, Knizia : a 
trick-taking card game where players are trying to make the best soup of 
various types.

-- Alhambra [Queen Games] with 3 expansions from expansion box 3, 5 
players, learned expansions : we tried the City Walls, Thieves, and 
Change variants.  City Walls adds tiles letting you add extra walls to 
your current tiles on specific tile sides.  Thieves lets you steal a 
particular color of the face-up money cards twice a game.  Change gives 
you a random color's \$1 coin for every \$2 overpayment, helping you make 
exact change later.  All seem to be interesting additions to the basic 
game.  I liked these better than the four in The Vizier's Favor (box 1): 
moneychangers, huts, play out of turn, bonus cards for particular buildings.

-- Can't Stop [Parker Brothers], 3 players : outdoor on a picnic table on 
New Year's Eve!  dice-rolling push-your-luck silliness.

-- Einfach Genial [Kosmos], 4 players, taught, Knizia : You guys know 
this as Ingenious.  Tiles covering two hexes, each hex has one of six 
colors, play one tile from a Scrabble-rack of six, and score points for 
hexes of the same color in straight lines all directions away from the 
new tile's two hexes.  Your worst color (not your best color or total 
score) determines whether you win the game.  A big score for you may 
risk a bigger score for the next player, but you might be able to keep 
an opponent from scoring in his worst color.  Plenty of strategy in a 
fairly simple game.

-- Underground [JKLM Games / Rio Grande Games], 4 players, learned : On a 
map of the London Underground system, players build networks of subway 
connections, trying to help a passenger (everybody shares one big white 
passenger) move to one express and one regular station out of four 
random station cards.  The passenger moves under simple rules: walks 
fewest blocks, then (if tied) changes between different networks fewest 
times, then (if still tied) the active player chooses.  You're mainly 
using your current turn's builds to get the passenger to ride your lines 
to certain destinations rather than riding opponents' lines, perhaps to 
other destinations.
{\it ((I'd like to get this one, it sounds like fun.))}

-- Scrabble [Selchow \& Righter], 2 players.

-- Crokinole again, 2 teams of 2, the only game I repeated except Ta Yu.

-- Zum Kuckuck [FX Schmid], 4 players, learned, won : simple but fun 
game, auctioning numbered Cluck cards where high bid gets the 
lower/better card and second-high bid gets the higher/worse card, lower 
bidders get nothing new, and whoever has the highest card (old or new) 
showing after each auction gets one of their cute yellow cockatoos SHOT 
DEAD!  Since the hands with many high/low bidding cards are more 
powerful, they get fewer cockatoos to start; and after each hand, you 
pass the bidding cards clockwise and play again, repeating until all 
players have played each set of cards.  That takes out the ``luck of the 
draw".

-- Ra [alea], 4 players, Knizia : One of the classic Eurogames, it uses a 
nice bidding mechanism (winning bid stays in the pot for the next 
winning bidder to use later) in auctions for goodies of various 
categories with various kinds of category scoring.

-- Industrial Waste [Rio Grande Games], 3 players, won : managing a 
business to produce orders and earn money without having too much 
pollution build up.  I won by refusing to sell raw materials on a couple 
of occasions when the best player needed them, forcing him to discard a 
couple of orders.

-- Tumblin' Dice [I forget the manufacturer], 4 players : flicking or 
rolling dice onto a terraced board, this is part shuffleboard, part 
Crokinole.  A ``1" on the 1x level might get knocked and become a ``5" on 
the 3x level (worth fifteen points instead of one), but might later get 
knocked off the end and prove to be worth zero when scored.  Fun.

In all those games, I won a bit less than my share, but came in second 
(of 3-5 players) more than my share.  I learned a bunch of games 
including at least two or three that I'll likely purchase.  Gheos is a 
nifty and competitive game with nice components at a low price.  Zum 
Kuckuck is a pretty neat game with the luck virtually removed but with 
every game different.  Underground is different enough from the other 
connection games, with a sort of puzzle element, to be interesting, and 
it's not too pricey.  I might also get Grand National Derby because of 
its combative element (just before the fence is scored, put a zero card 
on the horse somebody has bet twice on, and the horse gets SHOT DEAD!, 
well, no, it doesn't say that, just says the horse gets eliminated from 
the rest of the race).  I could imagine buying Money! for its auction 
mechanic.

And I had a lot of fun without getting busted or getting killed by a 
drunk driver or other less fun ways to ring out an old year and ring in 
a new year.

\centerline{-- Mike}

{\it ((I was hoping to come by, but I was doing some tight relative visiting
and didn't even try to convince Charlotte to do a drive by stop.
I'll get to one of these events sooner or later.... the TempleCon write up
is down below.))}

\bigskip

\centerline{\bf MUSIC AND MOVIES SECTION (WITH COMMENTS ON OTHER ARTS AND SOCIETY)}
     
\smallskip

We're running a ``23 tunes'' contest here
(stolen blatantly from Mark Wightman and the late lamented {\bf The Sprouts of Wrath}.
If anyone would like to send me a tape or CD of their 23 (which was the original point)
that would be great, but I don't intend to require that.  I will be playing in the
sense that I'll be putting 23 tunes in, and you have to guess me, but I obviously
won't score points.
Send commentary with your choices, and we'll see if people can
guess who you are!!!
And already there is a LOT of diversity in defining tunes and styles, so 
BE CREATIVE!!!
 
%To encourage voting early, I picked five voters at random to receive five US
%dollars from me (either in cash or paid to someone for Dip stuff or to get
%a free tape).
%Tony Dickinson won the Round 5 prize, so we had three of the six Round 1 voters
%won and one of the three Round 2 postal voters who also got five chances to win.
%That showed the value of getting in early!!
%Voters in Round 1 were Mike Barno(\$5), Rick Desper (\$5), Tony Dickinson (\$5),
%Drew James, Heath Gardner, and John Harrington.
%Round 2 postal voters were John Schultz (\$5) Ian Moore, and Stan Johnson.
%Round 2 E-Mail voters were Scott Morris, 
%Warren Goesle, Peter Sullivan, and Michael Lowrey.
%Round 3 voters were Dick Martin, Richard Weiss, and Rip Gooch.
%Round 4 voters were Roland Sasseville, Jr. (\$5),
%Don Williams, Brent McKee, and Andy York.
%Round 5 voters were Mark Larzelere, Al Tabor, Jody McCullough, and that's it.
%We'll end up with a monster party tape at the end of it that I plan
%to segue and sequence and copy for distribution.
%The result will be a great New Millenium party tape -- we're going for 90 minutes.
%I've also been thinking that I should put this out on CD
%as truly emblematic of the new millenium.  
%I don't have the capability to do that quite yet, but I think
%I might by then.
%Any suggestions (or especially volunteers) on this front will
%be cheerfully accepted and could receive monetary payments!
%The CD way may still occur if someone steps forward and actually does it for me.
%So far, we have ``I Melt With You'' by Modern English; George Gershwin's
%``I got Plenty O' Nuttin' '' from {\it Porgy and Bess} in the 1957 concert
%recording with Ella Fitzgerald finishing off the vocals after Louis
%Armstrong blows and sings through the tune; Duke Ellington performing
%Billy Strayhorn's ``Take the A Train''; Frank Sinatra's ``New York,
%New York''; something from the B-52's;
%the original Van Morrison and Them version of ``Gloria'';
%The (English) Beat's 12 inch version of ``Save It for Later'' 
%ratchets things up to the next level (wherever you put it!);
%Buster Poindexter's ``Hot, Hot, Hot'' keeps you there;
%``Atomic Dog'' by George Clinton blows the doors off,
%and Koko Taylor cleans up singing Willie Dixon's ``Wang Dang Doodle''.
%After I get timings down, I'll choose exactly which songs below make the list.
%
%EXTRA SPECIAL B-52'S BULLPEN: (7) ``Love Shack'';
%``Rock Lobster". {\it ((A tie, a tie!!!!))}
%
%BULLPEN: (9) Nirvana -- ``Smells Like Teen Spirit";
%``Cumberland Blues'' -- the Grateful Dead.
%(8) ``Twistin the Night Away" -- Sam Cooke; ``In Between Days'' -- The Cure;
%``Mannish Boy" -- Muddy Waters; ``Shake, Rattle, \& Roll" -- Big Joe Turner; 
%``Proud Mary'' -- Ike and Tina Turner.
%(7)  ``I Wanna Be Sedated" -- Ramones; ``Twist \& Shout" -- Beatles.
%(6) ``Magic Carpet Ride" -- Steppenwolf;
%``Crossroads'' -- Eric Clapton; ``Play That Funky Music'' -- Wild Cherry;
%``I Fel Good" -- James Brown;
%``Radar Love'' -- Golden Earring; 
%Devo -- ``Whip It"; ``Echo Beach'' -- Martha and The Muffins.
%(5) ``Sing Sing Sing'' -- Benny Goodman; ``Rocking the Casbah'' -- The Clash; 
%Squeeze -- ``If I Didn't Love You"; ``Roadrunner'' -- 
%Jonathan Richman and the Modern Lovers.
%
%SPECIAL ROLLING STONES BULLPEN: (6) ``Paint It Black''. 
%
%SPECIAL TALKING HEADS BULLPEN: (9) ``Take me to the River".
%(4) the entire {\it Speaking in Tongues} record
%(special call for ``Road to Nowhere'').
%
%SPECIAL ALPHABET SONG BULLPEN: (6) ``YMCA" -- Village People. 
%
%SPECIAL DRUG MUSIC BULLPEN: 
%(8) ``Rd, Red Wine'' -- UB40.
%(6) ``Don't Bogart that Joint'' 
%-- Fraternity of Man; ``The Old Dope Peddler'' -- Tom Lehrer.
%(5) ``Cocaine'' -- Eric Clapton's version; ``Casey Jones'' -- the Grateful Dead.
%(4) ``White Rabbit'' -- Jefferson Airplane; ``Love Is the Drug'' -- Roxy Music.

\bigskip

\centerline{\bf {\it 23 Tunes Game}}

\smallskip

Here are the rules for 23 TUNES.  You send me three tunes for the first turn,
and then two tunes in each of the last ten turns for a total of 23.
If you missed the first turn, you can still catch up by sending five tunes next
issue, and guess on submitters to this issue.
I am also submitting my tunes.
After we're done, I'd like to exchange CD's/Tapes for as many of the tunes players
as possible, but this is not required.
I'll be sending the winner both my LAST 23 tune list and my NEW 23 tune list.
The winner is determined by having you guess each issue who submitted what list
(I will tell you who the submitters are).  For each list you get right, you get
a point, you also can win bonus points from me for really cool tune selections.
That's it, not complicated.
I hope by starting this up, we'll get more to join, five songs required to enter
late.
Playing this issue (guess who is whom by number, scores are in parentheses) 
is, in alphabetical order, 
Jim-Bob Burgess, Rick Desper (1), %Steve Emmert, Doug Kent, 
Dick Martin, %Jim Reader,
Richard Smith (3), Joakim Spangberg, %Brendan Whyte, 
and Brad Wilson (4).
The linking theme thing didn't seem to go over too well.
No one really figured out the true linking theme.  
Rick Desper was using Underground tube stops and songs with that as the title,
they were things like that.  
I'll let you guys talk a bit to each other on that with your guesses.
I have added some kind of comment on each tune.

WHAT I NEED: two more tunes (seven if you're joining up new, four if you NTRed (NO TUNES
RECEIVED!!) and want to get back in), your guesses as to who
submitted which lists, and guesses about people's themes if any.
Quite a number of you SAID you would join but haven't yet, so we'll get started and
put the pressure on you.
This part is a MESS and I'm getting this issue out and then will catch up next time.

%
%\bigskip
%
%\centerline{\bf SPY DIPLOMACY (Variant, revised Dec. 1986)}
%
%by Jim Burgess
%
%Rules:
%
%1) Unless otherwise specified, the standard rules of Diplomacy apply.
%
%2) Players receive adjudications for their own armies and fleets, but not
%the armies and fleets of other powers.  Similarly, each player sees only
%his or her own section of the supply center chart.
%
%3) In addition to the standard units, an unit called a "spy" is added.
%
%     A) Each of the seven powers begins with a spy in each home supply center.
%
%     B) Spies are supplied only by home supply centers (i.e. Russia may have
%as many as four spies at a time while other powers are limited to a maximum
%of three).
%
%     C) Spies are "built" and "disbanded" in Winter seasons at the same time
%as other units.
%
%     D) There is no limit to the number of spies that may be present in any
%province and spies may be ``stacked" with armies or fleets (exceptions are
%listed in Rule 6).
%
%4) Spy Reports
%
%     A) Spies report the location and nationality of armies and fleets in
%the province they occupy and all adjacent provinces immediately following
%the standard Winter, Spring, Summer, and Fall seasons (i.e. just prior to
%the spy movement seasons).  Spies can differentiate between units in retreat
%and successful attackers when two units "occupy" a province.
%
%     B) Spies also report the nationality of spies in the province they occupy
%and the presence (but not nationality) of spies in adjacent provinces at the
%same time.
%
%5) Movement of Spies
%
%     A) Spy movement follows the collection of spy reports, so orders to spies
%may be made conditional on any information gathered by spies on opposing troop
%movements or the adjudication of one's own units.
%
%     B) Spies move after each of the following standard seasons: Winter,
%Spring, Summer, and Fall (note that all spy movements PRECEDE Autumn
%retreats), beginning with Winter 1900.
%
%     C) Spies move as armies do with the following exceptions:
%
%          a) Spy movements cannot be stood off by movements of any other unit.
%
%          b) Spies may be convoyed by fleets of any power during any of the
%four movement seasons for spies.  The convoy orders for fleets in these
%seasons must be ordered by their owner in the usual fashion or else the spy
%convoy movement fails of execution.  Fleet convoy orders for spies may be made
%in addition to regular Spring and Fall moves (note, however, that the fleets
%themselves never move during spy movement seasons).
%
%          c) Spies may also be "picked up" and carried by fleets of any
%power. Embarkation and debarkation are moves that must be made during a
%spy movement season and "permission to board" is not required.  Embarkation
%consists of a movement from a land province to an adjacent sea province
%containing a fleet.  Debarkation consists of a movement from a sea province
%containing a fleet to an adjacent land province.  A spy may not "switch
%fleets in midstream".  Once boarded, a spy may only get off by debarking.
%After boarding a fleet, the spy moves with the fleet during regular movement.
%A spy may not debark from a fleet awaiting retreat (e.g. if a fleet carrying
%a spy is dislodged in Spring, the spy may not debark until the spy movement
%season following the standard Summer retreat season).
%
%6) Spy Mortality
%
%     A) This rule will outline the circumstances under which spies may be
%captured or killed.  Spies may be disbanded in Winter seasons at the same
%time as other units to meet the requirement that a power may not have more
%spies than the number of currently held home supply centers and spies are
%annihilated when they are on board a fleet that retreats off the board.
%Otherwise, spies may only be removed from the board (there is no difference
%in the game between capturing and killing a spy, but players should feel
%free to delineate between the two states in writing press) immediately
%following the four spy movement seasons.
%
%     B) Spies killed or captured in a given season do not submit written
%spy reports for that season, though their final movement may have been
%made conditional on that spy report.  Players may never know for sure how
%a spy was lost, just as in real life.
%
%     C) Spies are "killed" by being assassinated by other spies.  When a
%spy moves, he or she may attempt an assassination, specifying the nationality
%of spies to be executed if discovered.  Each spy may hunt for only one
%nationality in each of the four seasons.  The following rules and examples
%will govern the adjudication of assassinations:
%
%          a) A spy may attempt an assassination without moving (for instance
%if the target is in the same province).  In this case, any spies of the target
%nationality that end the spy movement phase in that province are assassinated
%with one exception.  If the spy attempting the stationary assassination is
%himself or herself assassinated by a moving assassin then that spy
%assassinates no one in that season (not even a potential target other than the
%one that assassinates that spy).
%
%          b) A spy attempting a moving assassination (may include a move of
%embarkation or debarkation from a fleet) is always successful in assassinating
%spies of the target nationality that finish the spy movement phase in the
%province that the spy moves to.  This makes "mutual assassinations" possible.
%
%          c) Example: French spy is on board a French fleet in the Channel.
%An English spy is in London.  Both powers specify assassination attempts
%against the spies of the other.  If the English spy embarks on the French
%fleet in the channel (remember that embarkation does not require the
%permission of the fleet being boarded) and the French spy doesn't move, the
%French spy is killed, but the English spy isn't (he may be immediateIy
%captured, however, see part D).  If a German spy is also on board and the
%French spy tried to assassinate the German spy, that operation would fail
%as well. If the French spy debarks to London at the same time, the two spies
%"pass in the night" and neither is killed.
%
%     D) Spies are "captured" by opposing armies and fleets.  Players may
%attempt to capture spies, specifying the nationality of spies to be captured
%if discovered.  Each army and fleet on the board may search for spies of one
%nationality in each of the four seasons.  The following rules and examples
%will govern the adjudication of attempts to capture spies:
%
%          a) Players may specify a nationality to be hunted separately for
%each unit or they may issue blanket searches to be applied to all units.
%
%          b) At the end of the spy movement phase, any spies of the
%nationality specified in the same province are captured (for example, if
%the French player specifies a hunt for English spies on their Channel fleet
%in the above example, then the English spy is captured).
%
%          c) Players are informed when they successfully capture an opposing
%spy.  Note that the "owner" of the spy, however, is not informed of the
%capture.  Communication just is cut.  This rule is the only exception to the
%generaI rule that armies and fleets are blind.  It is possible to play the
%game without allowing capture of spies by armies and fleets if one wishes
%to allow freer movement of spies (i.e. RuIe D may be ignored).
%
%7) It is suggested that the game be adjudicated in four separate seasons
%in the following order:
%
%     A) Spring: (for Spring 1901 this sequence is preceded by a spy movement
%phase (no spy reports are necessary) followed by assassinations or captures)
%
%          a) Standard movement by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     B) Summer:
%
%          a) Standard retreats by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     C) Fall:
%
%          a) Standard movement by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     D) Winter:
%
%          a) Standard Autumn retreats by fleets and armies, adjudication
%reported only for one's own units
%
%          b) Standard Winter builds and removals, also applies to spies
%
%          c) Spy report phase, spies collect information
%
%          d) Spy movement phase, spies move according to Rule 4
%
%          e) Spy assassination and capture phase
%
%\medskip
%
%These rules have been produced by Jim Burgess (with helpful comments from
%Bernie Oaklyn and Dick Martin).  Permission is granted to reproduce and use
%these rules without restrictions.  The author would be interested to hear
%any comments and criticisms regarding any aspect of the play of this variant.
%The rules have been deposited with the North American Variant Bank.  They are
%also available from the author for the cost of postage or free by E-Mail.
%
%\bigskip
%
%\centerline{Wing Rules} 
%
%1.A wing unit can move over both land and water spaces. 
%  
%2.A wing unit can support actions in any space adjacent to the one it occupies. 
%   
%3.A wing can give, receive and cut support in the same way as armies and fleets. 
%   
%4.A wing unit cannot convoy or be convoyed. 
%
%5.A wing unit cannot capture an SC, but instead blockades it: 
%        
%\indent\indent 5.1.A blockade occurs when a wing unit occupies the SC of 
%another player in a fall season. 
%        
%\indent\indent 5.2.The player who owns a blockaded SC does not count 
%it when counting his total number of SCs. 
%        
%\indent\indent 5.3.A blockade ends as soon as the wing unit no longer occupies the SC. 
%        
%\indent\indent 5.4.Builds only take place in the winter phase, just as in games without wings. 

\bigskip

\centerline{\bf Diplomacy at TempleCon -- February 16-18}

\medskip

\centerline{\it Tournament Director: Jim Burgess}

\smallskip

Game: Diplomacy

Teaching Session: Friday night, 8 PM to 11PM, Regular Diplomacy and/or
Escalation Diplomacy depending on numbers.  Escalation Diplomacy II
can be found at:

\noindent http://www.variantbank.org/results/rules/e/escalation2.htm

We will use the ``five minute teaching guide" that I'll have to hand out as well:

This part did not go too wonderfully.  
I went and set up, I talked to five or six people, but didn't manage to get an Escalation game
started.
There were mostly Miniatures and Magic types around.  
A few knew what Diplomacy was, but they were busy with their games.
We ended up playing two games on Saturday, same players in each game, had a fun time and
decided not to come back on Sunday.
That worked, I probably will do it again.

\vfill\eject

\centerline{\bf {\it THE ABYSSINIAN PRINCE} GAMES SECTION}

\smallskip

``So I called up George and he called up Jim, I said let's make a deal.

He said he'd talk to him.  Gonna start a church where you can save yourself,

You can make some noise, When you've got no choice...

You told me useful things, what people think of me, I guess I should thank you.

It's true, then I agree... I'm all alone, I've got no choice,

I'm all alone, I've got no choice."

From ``Got No Choice" by the incomparable Mark Cutler, from the CD
{\it Mark Cutler and Useful Things}.

\smallskip

\indent If you want to submit orders, press, or letters by E-Mail,
you can find me through the Internet system at
``burgess of world.std.com''.
If anyone has an interest in having an E-Mail address listed so people
can negotiate with you by computer, just let me know.
FAX orders to (401) 277-9904 if you let me know in advance to be sure
the fax machine is set up. 

I am continuing to note cut or failed support orders with a 
small ``s'' instead of a capital ``S''.
This will make it easier on the E-Mailed version of the szine to see
what happened, since the italics don't show there.
The italics DO show on the web page just fine.

\indent Standby lists:

Mike Barno, Dick Martin, Brad Wilson, Jack McHugh, Glenn
Petroski, Steve Emmert, Mark Kinney, Vince Lutterbie, Eric Brosius,
Paul Rauterberg, Bob Osuch, Doug Kent, Sean O'Donnell, Vern Parker,
Heath Gardner, Paul Kenny, and Jeff O'Donnell
stand by for regular Diplomacy.
%I am willing to take over for NMR or start new-Diplomacy.
%Vern Parker
%337 Winter Hill Pl.
%Powell, OH 43065
%VSParker of aol.com
%614-402-5139

Let me know if you want on or off these lists, especially OFF.
Standbies get the szine for free and receive my personal thanks.

\bigskip

\centerline{GAME OPENING INFORMATION} 

\smallskip

We've got lots of openings in the subszines, check them out!!!
Contact Rip Gooch directly at xyropedes of canada.com and try to entice him to return.
Rip has been a bit missing in action lately, but I am assured that he
SHALL return.

Breaking Away starts in this issue!!! 

I am willing to open another new game of REGULAR Diplomacy if there is enough interest!!!
Fred Wiedemeyer, %e,f,r,i,g,t,a
Brad Wilson, Shaun Thompson,
and Sean O'Donnell start the list, who would like to join them???

Also, is there any interest in another game of Nuclear Yuppie Evil Empire 
7x7 Dip?
I know it may be getting tired, but I really like it.
We have Karl Schmit and Sean O'Donnell on the list, let's get seven!!
It's FREE!!!

I also am starting a game of the variant I designed, Spy Diplomacy.
Signups for that are now open.
Bruce Edwards and Eric Ozog are signed up.
The rules were published recently, ask to see them if you missed them!!!

John Harrington is offering to guest GM a game of Office Politics.
Any interest in that??
Let me or John know!
Jody McCullough and Bruce Edwards are interested, anyone else?
I think I'm going to drop this one as having no interest.

And since Colonia is over, Harold Reynolds is looking to start something else.

Also, I am going to design some postal rules for Devil Take the Hindmost,
and we have an opening here:
Bruce Edwards, Mike Barno, and Eoghan Barry are signed up.
Postal rules from me will be forthcoming shortly, on my never ending to-do list.
I will get them in SOON!
I'm more likely to get these things started if I see some interest.....
I've GOT to do this now,
Eoghan is getting tired of waiting....

Right now, the other thing going is the Modern
Diplomacy game with Wings.
Sean O'Donnell, Jeff O'Donnell, Steve Koehler, Art Schleinkofer,
Bob Holt, Rick Desper, Alexander Woo, and Dave Partridge are signed up for that.
I will start it when I get a full complement of players, we only need TWO more!
%Sean's list: Britain, Spain, Germany, France, Egypt, Turkey, Russia, Ukraine, Italy, and Poland.

\bigskip

\centerline{\bf TAKING OVER ISHKIBIBBLE'S REGULAR DIPLOMACY GAMES ((NOT))}

\smallskip

Last chance for anyone who was a subber to {\it Ishkibibble} to join any new
game for free, but this is a ONE TIME only offer, get your request in now.
It is going to expire VERY shortly.
Marc Ellinger and Fred Wiedemeyer already have taken us up on this request.
Come on, let me call by name who qualifies
for this deal..... Karl Schmit, John Power, Tim Snyder,
Dave Partridge, Graham Wilson, and Kevin Wilson.
I especially would like to fill the Modern Diplomacy game that Dave Partridge
already is in.
As soon as one more game fills (I'm not counting the new Breaking Away game), 
I'm going to pull this offer.

\bigskip

\centerline{\bf THE PHIL REYNOLDS MEMORIAL: 2006B, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SPRING 1902 IS MARCH 10TH, 2007}

\smallskip

\indent {\it Winter 1901}

\noindent AUSTRIA (Burgess): bld a vie, f tri; has a VIE, f TRI, a SER, a BUD, f GRE. 

\noindent ENGLAND (James): bld f lon, f lvp; has f LON, f LVP, a BRE, f ENG, f NWY.

\noindent FRANCE (Williams): bld a par; has a PAR, f POR, a BUR, a SPA.

\noindent GERMANY (Ellinger): R a mun-BER; bld a KIE; has a KIE, a BER, f BEL, 
a DEN.

\noindent ITALY (Crow): bld a ven, f nap; has a VEN, f NAP, a MUN, a TUN, f ION.

\noindent RUSSIA (O'Donnell): bld f sev, a war; has f SEV, a WAR, a UKR, 
f BUL(EC), a MOS, f SWE.

\noindent TURKEY (Wiedemeyer): R a bul-CON; has f BLA, a CON, 
a ARM.

\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Burgess):&TRI,VIE,BUD,ser,gre&(has 3, bld 2)\cr
%\+ ENGLAND (James):&EDI,LVP,LON,nwy,bre&(has 3, bld 2)\cr
%\+ FRANCE (Williams):&PAR,MAR,spa,por&(has 3, bld 1)\cr
%\+ GERMANY (Ellinger):&KIE,BER,den,bel,&(has 2 or 3, bld 2(r:otb) or 1)\cr
%\+ ITALY (Crow):&ROM,NAP,VEN,tun,mun&(has 3, bld 2)\cr
%\+ RUSSIA (O'Donnell):&WAR,STP,SEV,MOS,bul,swe&(has 4, bld 2)\cr
%\+ TURKEY (Wiedemeyer):&ANK,SMY,CON&(has 2 or 3, bld 1(r:otb) or even)\cr
%\+ Neutral:&hol,rum&(Total=34)\cr
%
%\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: David Burgess, 101 Laurel Lane, Queensbury, NY  12804

(518) 761-6687, dburgess of glensfallshosp.org

\noindent ENGLAND: Drew James, 3644 Whispering Woods Terrace,
Baldwinsville, NY  13027

(315) 652-1956, kjames01 of twcny.rr.com 

\noindent FRANCE: Don Williams, 27505 Artine Drive, Saugus, CA 91350, 
(661) 297-3947, 

wllmsfmly of earthlink.net or dwilliams of fontana.org (\$5)

\noindent GERMANY: Marc Ellinger, 751 Turnberry Drive,
Jefferson City, MO 65109

ellingermc of aol.com

\noindent ITALY: John Crow, 824 Kinwest Parkway \#101,
Irving, TX  75063, (214) 532-1418

\noindent RUSSIA: Jeff O'Donnell, 1345 Simpson Drive, Hurst, TX  76053
%402 Middle Ave., Elyria, OH  44035-5728,

(440) 322-2920 or (440) 225-9203 (cell, as late as midnight Eastern)

\noindent TURKEY: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  

CANADA  T6T 1N1, (780) 465-6432, wiedem of planet.eon.net 
%cell 780-497-8283; fax 780-468-6432

\bigskip

{\it Game Notes:}

1) And here we go, sorry for the delay.
If the fast follow up deadline for March 10th doesn't work, one request
will be sufficient to delay it until the end of March.
I'm presuming that's what you will decide.

\bigskip
 
{\it Press:}

(WARSAW to GERMANY): I'm moving to Livonia, not Silesia or Bohemia or Galicia.

(RUSSIA to ENGLAND): Nice!

(SWEDEN to DENMARK): I will leave you alone, if you leave me alone.

(TURKEY -- I/A/R): Cute, very cute. What a nice group you are.

(JIM-BOB to FRED): Boy, they don't show a veteran any respect, do they???

(FRED to JIM): Is that what they mean by ``All's fair in love and war"?

\noindent Maybe, my communication skills aren't what they used to be!!!!!!!!!

\noindent Maybe, I've slacked off over the last 30 years.

\noindent Maybe, I've mellowed over the years.

\noindent Maybe, one of these games, I'll get riled up again, and give them all
a good spanking.

(STAR TREK PRESS [whether you like it or not!] SISKO'S LOG):
Life is good!
With help from QII we have achieved a great victory against
the Gorn invasion.
We successfully liberated Bajor from its Gorn occupiers and have 
established Deep Space One on the other side of the Federation.
We also obliterated a front line Gorn troop transport and are now
negotiating with QII as to the coordination and disposition of
our invasion of the Gorn home worlds.
We did not start this war, but we intend to finish it!
I am also telling my dad to come up with a good recipe for lizard meat....

(STAR TREK PRESS 2, A CONVERSATION BETWEEN PARAMOUNT EXECUTIVES (P) AND
GENE RODDENBERRY (G)):

P: Gene, we have to tell you honestly, we've been getting some complaints
about Star Trek.
The person who complained didn't have the balls to say who he was
but that might be because he says he has 5XL balls and they are 
on fire, maybe as a result of Star Trek itself.
We have no proof who he is, but we think it's the Intelligent Tribbles.

G: ... but the Tribbles don't have any balls, in fact they are just
one big large ball.
He must have been speaking metaphorically.
How exactly it is that a character I created can complain about the show.
Doesn't he realize that if the show ends, so does he?
By the way, I think I know why his balls are on fire!
He just dropped his pants in the face of the Dominion invasion of the Tribble system.
The Dominion has already taken one of the three Tribble home worlds.
The Gem Hadar warriors were smokin' cigarettes after that one.
Maybe that's where the fire started?!?!
By the way, I have an idea for a Star Trek ``Christmas Carol''.
We could have the evil Captain Kirk play Scrooge, Commander Riker
could play Bob Cratchit, Commander Data could play Tiny Tim
and Worf could play the Ghost of Christmas Past.

P: There's just one problem, Gene!
No one on any of these shows are Christians.
How can you ever think about doing a Christmas show?
Besides, if we did a ``Star Trek Christmas Carol'', you should
play the Ghost of Christmas Past, not Worf!

G: Why?

P: Because you are already dead!

G: Good point!  A belated Merry Christmas everyone, and a Happy New Year!

P: You too, Gene!

(SEAN--STAR TREK POSTER): You do realize that you are giving out tactical 
data when you send out the Star Trek Press right?

(BASE to BLACK FIRE): That's B--L--A--C--K Fire, not Backfire.

(BOOB to BLACK FIRE): Black indeed, and every film noir I've ever seen starts 
out the way this next one does, just do a liberal substitution in for
the Rap.

(RED KINGS):  ``Imido clop non, lipid mono con, Monic idol plo..."

That was about all the shit I could take before I got up and shut the window.  
I hate that fucking rap music.  
My head was pounding, my tongue was sand paper dry and felt like it was 
two sizes too big, or my mouth two sizes too small. 
Mental laugh that, me and my big mouth were pretty much mated for laugh.
  
I shoved a couple of dirty fingers into the venetian blinds to spread them apart, 
trying to judge from the glare through the smudged windows what time of day it was.  
The sun sets hard over the Hobby, days are it’s days, 
and suddenly it’s darkest night... there’s a cliché there somewhere.  
Between the sun doing braindamage glare on the photonic rods 
of my eyes and one squinted glance back at my desk where the 
bottle of Cheater’s sat dry I knew it was time to get up.  
Crack o’ noon, up and at ‘em… well up anyway.

I put two thumbs into my eye sockets to jump-start the whole 
consciousness routine, rubbed them counter clockwise and 
thought about throwing cold water in my face.  
Thought about it, but the plumbing had been out for a week... or more.  
Consciousness is probably over-rated, plumbing is not. 
About the only water I got now was in my whiskey... or not.  
I’m a pretty neat fellow.

Thinking that; I looked again at the bottle of Cheaters.  
It looked languid, pale and empty.  Key word being empty.  
Empty.  It had been vibrant when full, teeming with 
possibilities and potential; a lot could happen with 
a full bottle of whiskey. 
Now empty it seemed somehow devoid of its purpose in life. 
We were a match.

But hey; it was still worth a nickel.

I flipped the empty into the air, caught it by the neck 
and gently stacked it with the others.  
Had about a buck and a half, almost time to trade them in.  
There was more potential out there, a lot could happen 
with a full bottle of whiskey.

But now to the day’s agenda.  It was Tuesday... or not, 
which meant it was Simone’s day off.  Or she was shopping, 
or maybe getting her nails done... anyway, she wasn’t 
at her desk in the outer office, which meant it was Tuesday... 
or not.  I walked out to her desk and looked at the appointments book.  
No appointments, go figure.  
Well, that left the day pretty wide open.  
I could go downstairs to Macgillicutty’s and pick up another bottle 
of Cheaters, one of the few advantages to having your office above a bar.  
As Simone would say ``youse have to avail yerself of the accoutrements", 
she was always a little hoitty-toitty, but she had some great pegs and 
she actually could type... or not.  
I don’t think I’d ever actually needed anything typed.

I stepped back into my office to get my stuff.  
It’s my mantra... my gun, my cigs, my hat... 
not necessarily in that order.  
I’ve got a great hat, a beat up slouch fedora that has been 
more faithful to me than a couple of wives I could name.  
A hat is what it is; it keeps your head warm and the sun 
out of your eyes, it doesn’t lie, it doesn’t spend the 
Christmas money or sleep with your pal Fred, it doesn’t ...hey, it’s a hat.  
It is what it is.

Now my gun, it’s a good gun.  I don’t need the big bang, 
don’t need the showy piece.  I’ve got a good solid revolver that 
I know I can hock for 30 bucks when the chips are down, 
or the well is dry... if you know what I mean.  
That gun has bought me more than a few bottles of Cheaters in its time.  
A lot of guys like the big firepower, the automatics, 
me hey I know this is fiction, hell it’s Hobby press.  
I’ve gotten eight, ten shots out of this puppy in a gun fight.  
The editors don’t count the bullets, and the readers don’t care.  
I killed a guy once with an empty gun... it didn’t take, 
but it got me to the next page.  
A lot of times that’s what it’s all its about... getting to the next page.

The cigs were some brand I hadn’t heard of before... Red Kings. 
They were a ``loner pack'', which means I took em off some 
patsy that owed me money or information or both, and couldn’t pay... or did.  
Anyway, I didn’t buy them.  They were loners the way your 
last dollar or your sister’s phone number was, it wasn’t coming back. 
I didn’t much care what cigarettes I smoked, I was partial to cigars.  
Afterall, a cigarette is just a cigarette, a good cigar is a smoke.  
Good line, that should be in a movie or something.

The pack lay partially crumpled on my desk, only a couple of fags left.  
Would have to pick up more with the Cheaters.  
I don’t think I enjoyed em so much, but I was using them to cut down 
on the cigars, and the drinking... and the women.  Seemed to be working.

Red Kings?  I looked up... weird, sounded like someone said Red Kings?  

Red Kings, Green Kings... menthol?  No way would I smoke menthol.
	
Damn, I need a drink.

(SEAN--MALICE): I can think of someone else that is trying to rival Jim-Bob 
with the press.

(MALICE IN CENTERLAND -- PART THREE: DOWN THE NORTH ATLANTIC DOT):

\noindent Malice decided that reading TAP was a tedious experience indeed.

``Tediouser and tediouser," he muttered, turning yet another page.  
``What good is a szine without pictures or poems or press or humor or intelligent prose?"  
He was thinking about returning home with the demon when he realized he was alone, 
the demon nowhere in sight.  
Don was gone, as were the woods, save for the tree under which he sat.  
He found this unusual and, slowly realizing something was amiss, rose to his feet.  
As he stood, a bizarre and misshapen mechanical creation ran up, 
looking for all the world like a mutant butler.  
The Mutant Butler which had become a proper noun since the preceding sentence) ran close by, 
LED eyes blinking brightly and entirely too redly.  
It whirred and rattled as it came to a stop on the far side of the tree.

``I'm late, so incredibly late.  Oh, Hell!  Oh, Hell!  The deadline's on me!  
It's come!  It's come!  I'll be too late!  Too, too late!  Much, much too late!"  
There was nothing so incredibly odd about this, thought Malice 
(though he'd later believe himself to have been hitting a crack pipe 
to think such a thing), but when the android Mutant Butler pulled a 
folded-over calendar from its red waistcoat and peered at it, 
then hurried off at a whirring, rattling run, Malice's interest was piqued;  
he'd never seen a mechanical Mutant Butler wearing a 
red waistcoat with a pocket before, or one owning a calendar to take out of it, 
and so without much thought he ran after the noisy android, 
for the Mutant Butler was an android indeed.

\noindent The Mutant Butler did not run fast, but it did run far.  
Very far.  Malice followed, increasingly and continually perplexed 
as the green ground beneath his running feet turned blue, 
and as the blue turned to water, and as the water turned to waves, 
and as the waves eventually turned frigidly cold.  
He indeed also found it curious that both he and the 
Mutant Butler could even run on water.  
It seemed absurd, of course, that he could run on watery waves -- for 
he had never done so before -- but beyond this logical impossibility 
his brain did not go, and neither should yours.  
They ran this way across the waves for a very long time, 
always with the Mutant Butler ahead and so, when the android abruptly 
disappeared right in front of him into a gaping hole in the gelid water, 
Alex was startled.  He struggled to a stop, and found himself standing 
alone at the very edge of a large round hole, floating in the middle 
of the watery expanse of what (I will share with you Gentle Reader, 
though our Alex has not a clue) is the North Atlantic Ocean.  
Some aspect of the hole's composition looked strange to him and he 
noted that it appeared to float on top of the waves rather than extend into them; 
it seemed rather like a large, solid, black dot.  
Alex tossed his copy of TAP toward the hole and it vanished instantly into 
darkness, as if it had fallen not into the hole, but rather through it.  
Alex found the hole's qualities -- both floating on top of the water 
yet extending into it as well -- confusing and, well, paradoxical.  
Perplexed or not, though, he had lost all feeling below his knees 
in the freezing water.  
Hypothermia was soon to follow and he somehow dimly realized, 
his nearly frozen heels and soles screaming for respite, 
that he must take some action to avoid an unspeakable 
(and narrative-ending) fate.  
Dazed and confused, he decided to do as he always had done 
in the past when faced with paradoxical and contradictory information; 
he shut off his brain.  
Not surprisingly, this clarified his thinking and he hesitated not a moment 
longer before jumping into the North Atlantic Dot, 
not considering for an instant how he might ever return.

\bigskip

\centerline{\bf SPIRALS OF PARANOIA: 2005A, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR WINTER 1905 IS MARCH 10TH, 2007}

\smallskip

\indent {\it Fall 1905}

\noindent AUSTRIA (Rauterberg): a bud-RUM, {\it a vie-gal} (d ann), 
a SER S a bud-rum, 

{\it a ROM-ven}, a TRI S a rom-ven, f tyh-NAP.

\noindent ENGLAND (Wiedemeyer): f spa(sc) h (d r:por,wes,gol,otb).

\noindent FRANCE (Tretick): a GAS S a wal-spa, f MID C a wal-spa, 
f yor-LON, a wal-SPA, 

f IRI C a wal-spa.

\noindent GERMANY (Ozog for Tallman): a ber-MUN, {\it a SIL-gal}, 
a BOH S ITALIAN a tyo-vie,
 
a hol-RUH, a mun-TYO, f nwy-SKA, {\it a PIE-ven}, 
a bur-MAR, f nth-ENG.

\noindent ITALY (O'Donnell): a tyo-VIE, {\it a VEN-tri}, f APU S GERMAN a pie-ven.

\noindent RUSSIA (Sundstrom): a rum-SEV, a sev-ARM, a gal-BUD, a lvn-MOS.

\noindent TURKEY (Biehl): f bla-BUL(EC), f aeg-ION, f GRE S f aeg-ion, f ion-TUN.

\bigskip

\indent {\it Supply Center Chart}

\+ AUSTRIA (Rauterberg):&TRI,ser,rum,nap,rom&(has 5, even)\cr
\+ ENGLAND (Wiedemeyer):&por?&(has 1, even or out)\cr
\+ FRANCE (Tretick):&PAR,BRE,spa,por?,lvp,edi,lon&(has 5, bld 1 (or 2 if ENG out))\cr
\+ GERMANY (Ozog/Tallman):&KIE,BER,MUN,hol,den,bel,swe,&(has 9, even)\cr
\+ &\enskip mar,nwy \cr
\+ ITALY (O'Donnell):&VEN,vie&(has 3, rem 1)\cr
\+ RUSSIA (Sundstrom):&WAR,STP,SEV,MOS,bud&(has 4, bld 1)\cr
\+ TURKEY (Biehl):&ANK,SMY,CON,gre,tun,bul&(has 4, bld 2)\cr
\+ Neutral:&none&(Total=34)\cr

\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Paul Rauterberg, 3116 W.~American Dr., 
Greenfield, WI  53221, 

(414) 281-2339 (E-Mail)  trauterberg of wi.rr.com

\noindent ENGLAND: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  CANADA  T6T 1N1, 

(780) 465-6432, wiedem of planet.eon.net 
%cell 780-497-8283; fax 780-468-6432

\noindent FRANCE: Buddy Tretick, 5023 Sewell's Pointe Way,
Fredericksburg, VA  22407, (540) 898-3386

cell (540) 226-5571 (E-Mail) berniebuddy32 of aol.com

\noindent GERMANY: Terry Tallman, PO Box 782, Clinton, WA  98236,
(360) 331-5698 (\$2) 

terryt of whidbey.net

\noindent GERMANY: Temporary Standby is Eric Ozog, PO Box 1138, Granite Falls, WA  
98252-1138,

(360) 691-4264, ElfEric of Juno.com

\noindent ITALY: Jeff O'Donnell, 1345 Simpson Drive, Hurst, TX  76053
%402 Middle Ave., Elyria, OH  44035-5728,

(440) 322-2920 or (440) 225-9203 (cell, as late as midnight Eastern)

\noindent RUSSIA: Matt Sundstrom, 1760 Robincrest Lane South, Glenview, IL  60025, 
(847) 729-1882, 

Matt.Sundstrom of bbdoch.com or mattandzoe of earthlink.net

\noindent TURKEY: John Biehl, \#8 -- 11530 84th Avenue, Delta, BRITISH COLUMBIA,
V4C 2M1  CANADA, 

(604) 816-0460 (cell) (\$7); jrb of dccnet.com

\bigskip

{\it Game Notes:}

1) Terry is still having some medical problems, 
Eric Ozog is continuing to
negotiate and submit orders for Terry.
Eric originally brought Terry into the Diplomacy hobby all those many
years ago, and so I'm glad he's agreed to do this.

2) Everyone got fall orders in, and so here is Fall.  
Winter deadline is quick, so please get your builds and removals to me
quickly.
Anyone may make their Winter orders conditional on the English retreat, 
but I expect France especially will need to do that.

3) I had the year of the game wrong, it IS 1905.....

\bigskip
 
{\it Press:}

(STAR TREK PRESS, 7 OF 9'S LOG): Have declared a Federation wide
simultaneous Red Alert and Distress Signal.
The Ferengi are the only power to answer the call for assistance.
Our existences are now in the hands of the Grand Negus...
we shall see, 7 out!

(SEAN--ERIC AND PAUL): Looks like that you two will achieve what I have not 
been able to achieve by the map situation....

(BREST):  No long to go, Winston.  Owning Portugal prolongs your demise one 
season.  And, then ...
 
(BUDDY to PLAYERS AND GM):  Wishing you and yours a happy new year.  Still 
looking for the Grinch.

(SEAN--JEFF): Way to go Stosh!

\bigskip

\centerline{\bf FLIP FLOP: 2003G, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SPRING 1909 IS MARCH 10, 2007}

\smallskip

\indent {\it Winter 1908}

\noindent AUSTRIA (Wiedemeyer): R a sev-MOS; has f VEN, a BUD, a WAR,  
a UKR, a MOS, a TRI.

\noindent ENGLAND (Schmit): rem f mid; has a BEL, a HOL, a RUH,
f NTH, f NWG, f HEL.

\noindent FRANCE (Jeff O'Donnell): has a BUR, a PIC, f SPA(SC), a GAS.

\noindent GERMANY (Sundstrom): bld a ber; has a BER, a KIE,
f SWE, a DEN,
 
a NWY, a MUN, f SKA.

\noindent TURKEY (Levinson): bld f smy; has f SMY, a SEV, f ION, a BUL, f APU, 
f NAP, a ALB, 

f ADR, f BLA, a RUM, a SER.

\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Wiedemeyer):&TRI,VIE,BUD,ven,mos,war&(has 5 or 6, bld 1(r:otb) or even)\cr 
%\+ ENGLAND (Schmit):&EDI,LVP,LON,por,bel,hol&(has 7, rem 1)\cr
%\+ FRANCE (Jeff O'Donnell):&PAR,MAR,BRE,spa&(has 4, even)\cr
%\+ GERMANY (Sundstrom):&KIE,BER,MUN,den,swe,stp,nwy&(has 6, bld 1)\cr
%\+ TURKEY (Levinson):&ANK,SMY,CON,bul,sev,ser,gre,&(has 10, bld 1)\cr
%\+ &\enskip tun,rom,rum,nap \cr
%\+ Neutral:&none&(Total=34)\cr
%
%\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  CANADA  T6T 1N1, 

(780) 465-6432, wiedem of planet.eon.net 
%cell 780-497-8283; fax 780-468-6432

\noindent ENGLAND: Karl Schmit, 1509 O'Keefe Road, DePere, WI  54115, (920) 338-8402, 

diplomacy of new.rr.com (\$3)

\noindent FRANCE: Jeff O'Donnell, 1345 Simpson Drive, Hurst, TX  76053
%402 Middle Ave., Elyria, OH  44035-5728,

(440) 322-2920 or (440) 225-9203 (cell, as late as midnight Eastern)

\noindent GERMANY: Matt Sundstrom, 1760 Robincrest Lane South, Glenview, IL  60025, 
(847) 729-1882, 

Matt.Sundstrom of bbdoch.com or mattandzoe of earthlink.net

\noindent ITALY: Don Williams, 27505 Artine Drive, Saugus, CA 91350, 
(661) 297-3947, 

wllmsfmly of earthlink.net or dwilliams of fontana.org

\noindent RUSSIA: Sean O'Donnell, 1044 Wellfleet Drive, Grafton, OH  44044,
(440) 926-0230, 

sean\_o\_donnell of hotmail.com

\noindent TURKEY: Alexandre Levinson, Beeklaan 504, 2562BP Den Haag
THE NETHERLANDS, don't need phone, 

levinson7 of hotmail.com (\$5)

\bigskip

{\it Game Notes:}

1) ONE request will be sufficient to push the tight Spring deadline off to the end of March.
I'm presuming that is what will happen.   

\bigskip

{\it Press:}

(SEAN--BOOB): No problem, I'm just not taking the game seriously within the 
Diplomacy theme. Any objection if Jeff does join that I pre-empt an assault 
against Jeff? It would be hard to nuke Jeff when he isn't in the game.....

\bigskip

\centerline{\bf I CAN'T FIND MY MONEY!: 2001F, Regular Diplomacy}

\smallskip

\noindent {\bf TWO WAY DRAW BETWEEN AUSTRIA AND GERMANY WAS DECLARED!}

%\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Parker):&TRI,BUD,VIE,ser,rum,nap,&(has 15, bld 1)\cr
%\+ &\enskip war,mos,sev,ven,rom,bul,gre,smy,con,tun\cr
%\+ FRANCE (Kent):&PAR,BRE&(has 4, rem 2)\cr
%\+ GERMANY (Wilson):&KIE,BER,hol,den,bel,MUN,swe,&(has 12, bld 2 (PLAYS ONE SHORT))\cr
%\+ &\enskip nwy,mar,edi,lon,spa,por,stp,lvp\cr
%\+ TURKEY (Miller):&ANK&(has 2, rem 1)\cr
%\+ Neutral:&none&(Total=34)\cr
% 
\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Vern Parker, 337 Winter Hill Place, Powell, OH 43065,
(614) 402-5139

VernDip of aol.com is preferred

\noindent ENGLAND: Mark Kinney, 4830 Westport Road, Apt D,
Louisville KY  40222

alberich of iglou.com

\noindent FRANCE: Doug Kent, 11111 Woodmeadow Pkwy \#2327, Dallas, TX  75228

dougray30 of yahoo.com 

\noindent GERMANY: Kevin Wilson, 18623 Santa Maria Drive, Baton Rouge, LA  70809,
225-751-3857,

ckevinw1 of cox.net

\noindent ITALY: Formerly was Heath Gardner, metaphorman of gmail.com

\noindent ITALY: Mike Barno, 634 Dawson Hill Road, 
Spencer, NY 14883 

mpbarno of lightlink.com 

\noindent RUSSIA: Rick Desper, 

rick\_desper of yahoo.com

\noindent TURKEY: Tim Miller, 258 New Mark Esplanade, Rockville, MD 20850,

tim of webjudge.net

\noindent GM: Jim-Bob Burgess, 664 Smith Street, Providence, RI  02908-4327,
$+$1 401-351-0287

burgess of world.std.com

\bigskip

{\it Game Notes:}

1) I have some comments in hand from Kevin Wilson that he wrote three or four months ago
which I will use next issue.
Thanks to everyone who played!

\bigskip

{\it Press:}


\bigskip

\centerline{\bf SECRETS: 1999D, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR WINTER 1923 IS MARCH 10, 2007}

\smallskip

\indent {\it Fall 1922}

\noindent ENGLAND (Kent): f ENG S f mid, a GAS S FRENCH f mar, 
{\it a BEL s RUSSIAN a kie-ruh} (nso), 

f MID S FRENCH f spa(sc), {\it f NTH s f hol, f hol s RUSSIAN f hel-kie} (d ann), 
f POR S FRENCH f spa(sc).
%rem f nth

\noindent FRANCE (Sasseville): f MAR S f spa(sc), f SPA(SC) S f mar, a BUR h.     
%standing orders, yes to ANY draw
                                             
\noindent GERMANY (Barno): a SER h.
%votes yes to FREGT, no to EFRT 
%vote YES to FREGT draw

\noindent RUSSIA (Parker): {\it f NWY-nth}, f nwg-EDI, a WAR h, 
a DEN h, a ber-KIE, 

f HEL S a kie-hol, a kie-HOL, a LVN h.

\noindent TURKEY (Linsey): a smy-CON, f aeg-ION, {\it a BUL s GERMAN a ser-gre}, 
a BOH S a mun, 

a SIL S a mun, f WES S f gol, a GAL S a sil, f GOL S f wes, 
a RUH S RUSSIAN a kie-hol, a TRI h, 

f NAF S f wes, a TYO S a mun, f PIE S f gol, a MUN S a ruh.
%Build A Ank
%Build F Smy (if I get a second build)

\bigskip

\indent {\it Supply Center Chart}

\+ ENGLAND (Kent):&LON,LVP,bre,por,bel&(has 6, rem 1)\cr
\+ FRANCE (Sasseville):&PAR,MAR,spa&(has 3, even)\cr
\+ GERMANY (Barno):&ser&(has 1, even)\cr
\+ RUSSIA (Parker):&MOS,STP,nwy,swe,den,ber,WAR,kie,&(has 8, bld 2)\cr
\+ &\enskip edi,hol   \cr
\+ TURKEY (Linsey):&CON,ANK,SMY,rum,gre,bul,&(has 14, bld 1)\cr
\+ &\enskip bud,nap,ven,tun,sev,rom,tri,vie,mun \cr
\+ Neutral:&none&(Total=34)\cr

\bigskip

\indent {\it Addresses of the Participants}

\noindent ENGLAND: Doug Kent, 11111 Woodmeadow Pkwy \#2327, Dallas, TX  75228

dougray30 of yahoo.com 

\noindent FRANCE: Roland Sasseville, Jr., 38 Bucklin Street, Pawtucket,
RI 02861, (401) 481-4280 (\$0)

roland6 of cox.net  

\noindent GERMANY: Mike Barno, 634 Dawson Hill Road, 
Spencer, NY 14883, (607) 589-4906 

mpbarno of lightlink.com 

\noindent RUSSIA: Vern Parker, 337 Winter Hill Place, Powell, OH 43065,
(614) 402-5139

VernDip of aol.com is preferred

\noindent TURKEY: Bruce Linsey, PO Box 234, Kinderhook, NY
12106

GonzoHQ of aol.com

\bigskip

{\it Game Notes:}

1) The concession to Turkey fails.
New proposals are for RT draw and REFT draw.
Please vote with your winter orders.

\bigskip

{\it Press:}
 


\bigskip

\centerline{\bf CAST NO SHADOWS: Breaking Away, Designer's Rules}

\smallskip

\noindent {\bf NEW GAME START, GET ME YOUR RIDERS AND CARDS!!}

\smallskip

Players are: David Partridge, Brendan Whyte, Alexander Woo, Andy York, Rick Desper, and 
Tom Howell.
I have Andy York and Tom Howell setups, but NOTHING from the rest of you.
Rules are at:

\noindent http://devel.diplom.org/DipPouch/Postal/Zines/TAP/Tinamou/rules/BreakingAway.htm
%\smallskip
%
%\noindent {\bf GAME OVER -- DUE DATE FOR ENDGAME STATEMENTS IS SEPTEMBER 10TH, 2005}
%
%\smallskip
%
%--F--I--N--A--L-- --F--I--N--I--S--H-- --L--I--N--E--
%--S--P--R--I--N--T-- --F--I--N--I--S--H-- --L--I--N--E--
%
%\centerline{\it Turn 16}
%
%\smallskip
%
%\+ Finished:                &Pebble, Homer, Spades (12), Clay (10), El Vez (8),  \cr
%\+                          &\indent Carl Sagan (6), James (4), Paige (2)    \cr

%--F--I--N--A--L-- --F--I--N--I--S--H-- --L--I--N--E--

%\+ 120 (replenish with a 3) &Spades  \cr
%\+ 119 (no replenishment)   &Empty   \cr
%\+ 118 (replenish with a 3) &Clay, El Vez   \cr
%\+ 117 (replenish with a 5) &Carl Sagan, James   \cr
%\+ 116 (replenish with a 7) &Sand, Paige  \cr
%\+ 115 (replenish with a 9) &Hearts, Geri Lee Lewis, Johnny Peso   \cr
%\+ 114 (replenish with a 12)&Marge   \cr
%\+ 113 (replenish with a 13)&Franklin  \cr
%\+ 112 (replenish with a 14)&Wade, Diamonds   \cr
%\+ 111 (no replenishment)   &Empty     \cr
%\+ 110 (replenish with a 3) &Frederick, Clubs, Edmond   \cr

\bigskip
%Sprint Points: 10,8,6,5,4,3,2,1 (final are just double these)
%Movement Order: A/B/C/D; highest card played that turn; highest card in hand

%\indent {\it Addresses of the Participants -- Their Team and Their Cards}

%\smallskip

%\noindent TEAM 1 (Rick Desper): rick\_desper of yahoo.com (55 points, efficiency
%score 13.7\%)

%Team Name: Team Springfield

%\+ A: Homer Simpson &&Finished \cr
%\+ B: Marge Simpson &&(3) 3 3 12  \cr
%\+ C: Bart Simpson  &&Sulks \cr
%\+ D: Lisa Simpson  &&(4) 3 5 6 \cr

%Total Replenishments: $22+63+46+13+15+29+21+17+25+17+18+33+32+10+13+18 = 402$
                
%\smallskip

%\noindent TEAM 2 (Bruce Edwards): kactusjak of ntlworld.com (8 points, efficiency
%score 2.3\%)

%Team Name: Last Again

%\+ A: Zedd   &&(3) 3 3 3 \cr
%\+ B: Omega  &&(4) 3 3 3 \cr
%\+ C: Paige  &&(13) 5 10 7 \cr
%\+ D: James  &&(16) 3 6 5 \cr

%Total Replenishments: $16+37+29+25+12+13+26+24+21+18+16+15+30+23+32+18 = 355$        
   
%\smallskip

%\noindent TEAM 3 (Tom Howell): off-the-shelf of olympus.net (31 points, efficiency
%score 8.0\%)%360-928-9698

%Team Name:  The Soils; Manager:   Boulder

%\+ A:   Clay    &&(7) 3 5 3 \cr
%\+ B:   Silt    &&(4) 4 4 4  \cr
%\+ C:   Sand    &&(10) 3 3 7 \cr
%\+ D:   Pebble  &&Finished \cr

%Total Replenishments: $17+62+63+25+12+13+12+29+27+21+17+31+15+15+13+14 = 386$   
               
%\smallskip

%\noindent TEAM 4 (Dennis Menear): dmenear of wirefire.com (9 points, efficiency
%score 2.2\%)

%Team Name: The Firm

%\+ A: Edmond    &&(5) 3 3 3 3  \cr
%\+ B: Franklin  &&(10) 4 4 13 \cr
%\+ C: Frederick &&(4) 4 3 3 \cr
%\+ D: Wade      &&(8) 3 3 14 \cr

%Total Replenishments: $12+28+32+35+38+25+24+17+29+21+15+26+21+35+26+33 = 417$

%\smallskip

%\noindent TEAM 5 (David Partridge): rebhuhn of rocketmail.com (36 points, efficiency
%score 8.5\%)

%Team Name: It's In The Cards; Manager: The Joker

%\+ A: Spades   &&(7) 3 3 3 3 \cr
%\+ B: Hearts   &&(6) 2 3 9 \cr
%\+ C: Diamonds &&(8) 5 6 14 \cr  
%\+ D: Clubs    &&(5) 3 3 3 \cr
           
%Total Replenishments: $17+55+51+25+30+24+26+20+34+15+15+25+18+20+22+29 = 426$ 

%\smallskip 

%\noindent TEAM 6 (Karl Schmit): diplomacy of new.rr.com (17 points, efficiency
%score 3.6\%)

%Team Name: 25 Dollar Quartet

%\+ A: Carl Sagan      &&(15) 3 9 13 5 \cr
%\+ B: El Vez          &&(15) 13 10 3 \cr
%\+ C: Geri Lee Lewis  &&(13) 9 9 9 \cr
%\+ D: Johnny Peso     &&(13) 1 8 9 \cr

%Total Replenishments: $12+37+22+44+16+27+28+27+32+39+33+20+24+39+49+26 = 475$
%Tom Howell
%
%Team Name:  Never Ending Worry Source
%Manager:  Rumour
%
%Riders:
%
%A Water: 15 11 3 1
%
%B Kyoto:  14 7 4
%
%C Mideast:  11 6 3
%
%D Drugs:  9 5 2
%
%I can have a team captain?  What about ye olde manager?
%
%The captain should be "mind your own business", but everone already has names!
%
%ANDY YORK:
%Breaking Away
%
%OK - no idea on what's the best strategy for card choice. But, here goes
%(and I assume you want a "theme" team).
%
%Team "Alamo"
%
%A - Crocket (20, 7, 3)
%B - Travis (15, 7, 3)
%C - Bowie (10, 7, 3)
%D - Bonham (10, 3, 3)
%
%        --Andy

\bigskip

{\it Game Notes:}

1) The rules are on the {\it TAP} website in the {\it Tinamou} section.
Ask if you have any questions.
Send in your riders and their starting cards NOW!!!
Your A rider can have three or four cards that need to add up to 30,
your B rider three cards adding up to 25, your C rider three cards
adding up to 20, and your D rider three cards adding up to 16.
You also need to name your team, and can have a team captain if you want.

%Up above in parentheses is the card you played to get to where you are
%in the field.  The replenishment card is the last card in your list.
%Be careful to note that the card you played (the one in parentheses) is
%not available for you, for next turn.
%Just for fun, I'm going to keep track of total replenishment, by turn, which is a 
%rough measure of how the teams are doing.
%Of course, it is lining up to get across the sprint and final lines in the
%right places that really counts.
%We can calculate an ``efficiency score" later, which will be the ratio
%of scoring points per replenishment.
%If I'm predicting how the future of this will come out, a 10\% score will
%be really tremendous for this measure.

2) The name of this new game is CAST NO SHADOWS, a great name for a pelaton based
game.
But of course, this is a very excellent Mekons song. 
I don't have all your cards and setups, get them to me now!

\bigskip

{\it Press:}


\bigskip

{\it Personal Note to You:}

\vfill\eject
\end
