\nopagenumbers 
\font\twelverm=cmbx12 at 12pt
\centerline{\bf\twelverm THE ABYSSINIAN PRINCE \#314}
\line{\hfil February 20, 2008}    
\smallskip                                                    
\settabs 3 \columns 
\beginsection

\medskip

Produced by Jim Burgess, 664 Smith Street, Providence, RI 02908-4327  USA,
(401)351-0287 
 
\noindent Accessible through Internet at burgess of world.std.com (all E-Mail
addresses are reported in this format, replace the `` of '' with ``@''; if you 
bounce try sending to me from another account. 
Some of you have been getting bounced messages from
my ISP's spam protection, if that happens to you, USE my backup E-Mail
at jfburgess of gmail.com!!!  Don't complain that my E-Mail keeps bouncing
without forwarding the bounced message to that address.
Then I can forward it to the ISP help to get it dealt with.
 
\noindent Web Page Address: http://www.diplom.org/DipPouch/Postal/Zines/TAP/index.html

\bigskip

I expect ALL players to be signed up on the E-Mail notification list for the szine,
see below.
Some of you have been complaining about this, but it is up to you to get on this list,
it's easy, come ask me if you have trouble.
THIS IS A PROBLEM, sign up now if you're playing!!!

This is going to be a very short, get the adjustments out issue.  And in fact, I'm 
mailing issues \#313 and \#314 together, so if you're seeing this first on the web
and saying ``gee, I've not seen \#313 in the post yet" you are quite right, you haven't.
This gets me all caught up and back on track though, and that's important for the games.
Probably the next few issues are going to be a bit light on reading materials as I just
try to crank some games out for awhile.  
Thanks for understanding.
All that being said, we have lots of subszines, even with {\it Octopus' Garden} being
back.

Also Jeff O'Donnell has to back out of all of his games, so I'm appointing standbys 
in each one who are taking over with these adjustment orders.
In light of that (and my own difficulties in staying on schedule) I'm extending the
deadlines a bit to the 22nd to compensate for Spring.
We're all very concerned about Jeff. 
On the good side, he sounds good (cell phone is the best way to reach him),
but he just cannot play at this time.
I hope things get better for him and he can return later, but we need to keep
the games going, so thanks to all the standbys.

\bigskip
%Dave Partridge's unlisted phone number 603-672-2879 -- probably corrected!!!
%Tinamou players: Schwarzschild:  Graham Wilson (NO 
%but E-mails: grahamaw of home.com (or gwilson of dvnet.com)),
%Berry Renken, Heath Gardner
%Copernicus:  Warren Goesle, Heath Gardner, Art Schleinkofer, Bruce Reiff,
%Eric Brosius, Bob Dowrey
%Tour De Farce:  Jim Burgess, Eric Brosius, Warren Goesle, Sara Reichert,
%Phil Reynolds, Rick Desper
%Milk and Cookies: Jim Burgess, Warren Goesle, Sara Reichert, Phil Reynolds,
%Rick Desper, Richard Weiss, John Schultz
%Who's Your Buddy:  Sara Reichert, Phil Reynolds, Art Schleinkofer, 
%Brad Wilson, Rick Copeland, Karl Muller

The postal sub price is still
\$1.50 per issue in the US and Canada,
with double that for other foreign subbers(or \$3.00 per
issue sent airmail).
Players in current games and standbys will
continue to get the issues for free, and future game starts 
(except for Nuclear Yuppie Evil Empire Diplomacy, which is free) cost 
\$20.00 (\$15.00 for a life of the
game subscription and \$5 for the NMR Insurance.
Anyone may play in subszines 
for free and just jack up the issue page count.
Since I have to get caught up this issue with all sorts of subszines, 
I'm going to be fairly limited with other items this issue.  
See the revised game start announcements below!

Check out the connections in the Diplomatic Pouch with all of
the information you need to play Diplomacy on the Internet at:
http://www.diplom.org/DipPouch/

I also have taken over the Postal port/DipPouch/Postal

\noindent and {\it TAP} on the web is there at:
http://www.diplom.org/DipPouch/Postal/Zines/TAP/index.html

where the szine resides in html format. 
Presently, issues from \#190 to the current issue
are there, and I will be updating the back issues gradually someday. 
 
Peter Sullivan's subszine is out of stasis, and all the
back issues can be accessed via :

http://www.burdonvale.co.uk/octopus/index.html.

Peter is now back at least sometimes.
Rip Gooch is probably permanently missing.
Dave Partridge had been picking up the choo-choo
game slack.
Contact Dave
at rebhuhn of rocketmail.com for more info on getting into choo-choo games
and other sorts of different games.
And Andy York and Doug Kent have been my most frequent subszine guests lately!!!
Andy has been in every issue, thanks, Andy!!!
And Doug Kent has been coming out faster than {\it TAP} lately, so
many issues have been having multiple {\it Eternal Sunshine}'s. 
And Michael Lowrey gets his in every few issues too!
So, we have a full set of subszines at the moment.

The {\it TAP} mailing list has moved!
It now is even BETTER protected than it was.
I even have a bit of trouble posting to it.
To post to this list, send your email to: tap of diplom.org.
But this is completely moderated, it won't go out to the list unless
I approve it.
In general, I intend to keep traffic down to just the szine, as we've
been doing and I'll put your LOCs in here.
I {\bf EXPECT} all players to be on this list, especially those of you who
are from foreign countries!!! 
You need this to find out when the szine is up on the web to check in on results.

General information about the mailing list is at:
http://www.diplom.org/mailman/listinfo/tap

You can sign up from there, or send E-Mails to:
Tap-request of diplom.org;
with the word `help' in the subject or body (don't include the
quotes), and you will get back a message with instructions.
You must know your password to change your options (including changing
the password, itself) or to unsubscribe.  
Normally, Mailman will remind you of your diplom.org mailing list
passwords once every month, although you can disable this if you
prefer.  This reminder will also include instructions on how to
unsubscribe or change your account options.  There is also a button on
your options page that will email your current password to you.
A big, big thank you for Millis Miller for setting this all up!!

\bigskip

\centerline{\bf THE SEARCH FOR JERRY JONES}

\smallskip

With the 100th issue of {\it Diplomacy World} upcoming, the ONLY
former publisher who has not definitively been located is Jerry
Jones.  Doug Kent and I have some idea where he is, but we've not
succeeded in getting him to respond to us.  Find him and win
a fifty dollar prize, only one more issue to do that before 
we move on to the next victim!!!

I am running out of people on MY list of who to search for, so
I am looking for ideas, who would you like to find?
Send me some names.
I may go into Jim Meinel's Encyclopedia of North American Diplomacy
szines and find some more szine editors to search for, that's
what I usually do, but I'd like to find people that some of you
will search for or want to find!!!
Come on, help me out.

\bigskip

Feel free to spend the time looking for some of the backlog.
Let's get Margaret, Derek, Sylvain, Steve, Ed, Tom, Gregory, and 
ESPECIALLY Kevin found too!!!
This is a regular continuing feature of the szine
and I will be introducing a new ``search for'' every five issues.
Moreover, you can win a \$25 prize for finding some previous
target who went unfound in the original \$50 period.
That means that if Margaret Gemignani or 
Steve Heinowski or Ed Henry or Tom Hurst or 
Gregory Stewart or Derek Nelson or Sylvain LaRose or John Smythe
is ``found'' from now on it is worth \$25.

\bigskip

Winners will receive credit for Dip hobby activities
that I will pay out as requested by the winner.
Subscribe to szines here or abroad, run your
own contests, publish a szine, finance a web page, 
GO TO A DIPLOMACY CONVENTION or whatever.
Spend it all right away or use me as a bank to cover hobby activities
for years.
What must you do to win?
Get me a letter to the editor for {\it TAP} from the person we're
searching for.

This is very important, just finding them doesn't do it.
They have to write me a letter.     
The final judge as to the winner of any contest will be the target 
himself and I reserve the right to investigate the winning entry.
When you find someone I'm looking for, you should ask him to send me a 
letter for print that includes a verification of who ``found'' him.
%Michael Swift, Mike Stewart, and 
%Jason Yarbrough , Tim Stabosz, 
%Eric Ozog has $25
%Leslie Obata is owed $25
%Derek Nelson, winner of the first postal game in Graustark.  I last saw him
%at the '76 DipCon in Baltimore.
%Charles Wells, former publisher
%John McCallum, former publisher (Brobdignag, SerenDip, etc.)
%Dan/Charles Brannan, former publisher (Wild 'n Wooly)

\bigskip


\bigskip

\centerline{\bf INTERNATIONAL SUBSCRIPTION EXCHANGE NEWS}

\smallskip

John Harrington and I have agreed to close the ISE.
In this age of PayPal, the traffic on the ISE had fallen almost to zero,
and what was left almost entirely was me facilitating orders of 
Breaking Away and John's other Fiendish Games.
So, I'm still going to help John out with that, but there will be no
ISE.
If anyone still needs assistance with this, though, since I'm helping
John out, like if you're in a foreign country and need to send dollars
for dipping things to someone in the US, I may be able to help you out.

\bigskip  

\centerline{\bf WORLDMASTERS04 SECTION}

\smallskip

See the Yahoo Group WM04-Results for more information and 
for details on progress on the WORLDMASTERS04,   
you can join the Yahoogroup too! 
Attention, attention, this just in.....

In the finals were Mike Tombu as Austria, Mike ``Smacko" McMillie as
England, Jerry ``JT" Fest as France, Georg ``Shef" Kotschy as Germany,
Randolph Ruff as Italy, Michael Weinzimer as Russia, and Tim Sweeney
as Turkey.  
The maneuvering is done, at the end of 1908 England ``enveloped" France and
achieved an 18 center victory, congratulations to WM World Champion 
``Smacko" McMillie.

The final standings according to the WM-rules are:

\noindent *1 and World Champion Email Diplomacy Mike ``Smacko" McMillie -- England 
-- 18 centers*

\noindent 2 Tim Sweeney -- Turkey -- 6 centers

\noindent 3 JT ``Jerry" Fest -- France -- 4 centers

\noindent 4 Randolph Ruff -- Italy -- 2 centers

\noindent 5 Mike Tombu -- Austria -- 2 centers

\noindent 6 Michael Weinzimer -- Russia -- 2 centers

\noindent 7 Georg ``Schef" Kotschy -- Germany -- 0 centers

The game and history can be viewed at:

http://www20.brinkster.com/jeewoo/showadj.asp?game=wm04final 

\medskip

The new Tournament rankings for FTF also are out there that supercede the
ones that were on 18centres.
Go check out:

http://eurodip.nuxit.net/php/ranking/index.php?lang=Ang

There are all sorts of rankings there. Doug Moore leads the 
DipPouch rankings as done by Matt Shields, but Cyrille Sevin
is still WAY ahead in the C-Diplo based rankings that Edi Birsan
has been organizing with the French.  And Cyrille also leads
in Lei Saarlainen's World Performance Evaluation ratings. 
You can lose many hours poring through all these records and
stats.

\bigskip

\centerline{\bf DIPDOM NEWS SECTION (with letters)}

\smallskip
 
Obscure and not-so-obscure ramblings on the state of the hobby
and its publications, custodians, events, and individuals with
no guarantee of relevance from the fertile keyboard of Jim-Bob,
the E-Mail Dip world, and the rest of the postal hobby.
My comments are in {\it italics} and {\it ((double 
quotation marks))} like this.
{\bf Bold face} is used to set off each individual speaker.
I should also make a note that I do edit for syntax and spelling
on occasion.

%A VERY light discussion is taking place that will address what 
%stance we (the hobby) should take (proactive in some way for sure) 
%toward Hasbro, the new owners of the rights to Diplomacy.
%More on this will be forthcoming, but it looks like Hasbro might
%have its version of Diplomacy on the market for the Christmas
%season and they actually will be employing ``play-testers''.
%No word on precisely what this means yet, could it mean that
%they will offer a series of ``official'' variants?
%Stay tuned....
%If you want to be part of the discussion, send the MESSAGE:
%
%subscribe hasbro
%
%to majordomo of diplom.org, it works just like the tap mailing list
%described below.  Sending messages to hasbro of www.diplom.org
%sends the mail to the whole list.
%The big news this time is the beginning of the breakout of
%Hasbro into official contact with the hobby.

The game Diplomacy is a copyrighted product owned by Hasbro and all
reproductions or other use of that material in this szine is intended to
be personal use and not infringe on those rights in any way.
All reproductions are done at a heavy financial loss to the editor
and thus are without the remotest possibility of commercial intent,
except to promote THE game, the Game of Diplomacy, which you all 
should purchase from Hasbro or other duly licensed distributors.
 
Stephen Agar has matched the Hasbro rule lists 
and more with some of the even older
rulebooks.
Check these out if you like:

http://www.hasbro.com/default.asp?xcc\_gameandtoyinstructions

http://www.hasbro.com/instruct/Diplomacy.PDF

http://www.hasbro.com/instruct/Diplomacy(OlderVers).PDF

Nice of them to make BOTH of these available.
And all seven different US rulebooks for Diplomacy can now be found here
courtesy of Stephen Agar (relatively new address for this):

http://www.diplomacy-archive.com/diplomacy\_rules.htm

%1: The Reformer, who seeks perfection (crusading type).
%2: The Helper, who seeks love (altruistic type).
%3: The Performer, who seeks status (competitive type).
%4: The Individualist, who seeks an identity (imaginative type).
%5: The Investigator, who seeks knowledge (analytical type).
%6: The Loyalist, who seeks security (ambivalent type).
%7: The Enthusiast, who seeks gratification (thrill-seeking type).
%8: The Leader, who seeks self-sufficiency (dominant type).
%9: The Peacemaker, who seeks contentment (accommodating type).
%See http://graphics.lcs.mit.edu/~becca/enneagram/
%new test at: http://www.9types.com
%My scores in order were: 9, 13, 15, 7, 15, 6, 17, 18, 14.
%Robert Lesco's Marco Poll, the defacto poll of the
%North American hobby since the Runestone is pretty much
%officially dead, continues to collect votes.
%This is an official {\it TAP} approved poll.
%Here are the particulars on the Marco Poll:
%Vote for your top five in each category and you can't vote (or at least
%it won't be tabulated) for Robert Lesco or his szine, which I don't see.
%I will send this to Robert and offer him a trade.
%The deadline is September 1st and either send your ballot to marcopoll of yahoo.com
%or mail to Robert Lesco, 49 Parkside Drive, Brampton, Ontario, CANADA  L6Y 2H1.
%For identification purposes, Robert would like you to identify yourself both
%by name and by affiliation (a game you play in or a szine you sub to).
%Here are the categories this year (I like some of the new ones!!):
%1) Favourite {\it ((Hey, what, he's Canadian, yeah.))} Zine  {\it ((What's a zine,
%shouldn't that be Szine???))}
%Backstabbers United Monthly, Costaguana, The Diplomatic Pouch, Absolute, Vertigo
%2) All Time Favourite Zine {\it ((Szine))}
%Magus, Europa Express, Thirty Miles of Bad Road, Perelandra, North Sealth West George
%3) Best Diplomacy Player
%John Quarto von Tivadar, Edi Birsan, Mark Fassio, Chris Martin, David Partridge
%4) All Time Best Diplomacy Player
%Edi Birsan, Mark Fassio, Kathy Caruso, Rod Walker, Hohn Cho
%5) Best GM
%Malcolm Cornelius, Tim Miller, Tim Richardson, Conrad von Metzke, Doug Massey
%6) Player Who Writes the Best Letters/E-Mails
%Don Williams, Richard Weiss, Mark Fassio, Toby Harris, Cal White 
%7) Folded Zine {\it ((Szine))} You Miss the Most
%Magus, Diplomacy by Moonlight, Le Front du Liberation de Diplomacy, Kathy's Korner
%8) Favourite Variant
%Modern, Nuclear Yuppie Evil Empire Diplomacy, Woolworth, Spy Diplomacy, Colonia

\bigskip
 
\centerline{Check out current and back issues of {\it Diplomacy World} -- Yahoogroup diplomacyworld}
and at Doug Kent's new {\it Diplomacy World} web site at:

\noindent http://www.diplomacyworld.net/

\bigskip

Also, I need any Hobby Award Nominations NOW (!!!) for the :

\noindent The 2005 and 2006 and 2007 Don Miller Award for Meritorious Service;

\noindent The 2005 and 2006 and 2007 Rod Walker Award for Literature;

\noindent The 2005 and 2006 and 2007 John Koning Award for Player Performance;

\noindent The 2005 and 2006 and 2007 Fred Hyatt Award for GM Performance;

or

\noindent A 2005 and 2006 and 2007 Kathy Byrne Caruso Award for Lifetime Achievement (if warranted).

The Hobby Awards Committee is Jim Burgess (Chair and Treasurer),
Fred Davis, Jr., Melinda Holley, Gary Behnen, Jamie Dreier,
Paul Kenny, Mark Stretch, and Robert Lesco.
I was going to publish the award ballot for this year 
in this issue, but I realized that I really just had to get this out first and
then do that.... and then, well, REAL SOON NOW!!!
And when I do, I'm going to give out three sets of awards and get caught up for the 
missed years, that seems to make the most sense.  
Committee.... you will be hearing from me soon!
This also fell apart with my move, but I think I can get it together for next
issue when all the games are in Winter.

\bigskip

{\it Diplomacy World} Issue Deadline is now:

\noindent Deadline Spring 2008, Issue \#101: beginning of April

I'm really pleased that former editor Doug Kent has agreed to come 
back and get this back on track and get us to \#100.
Thanks, Doug!
We're putting things together for the
next issue and it looks good too, but if any of you want to write anything
there's always more room,
contact Doug!
Most every old fart getting this szine sent something in for \#100,
so if you missed out, send something now for \#101!!!
We're looking for all sorts of kinds of articles, come talk to us if you
want some ideas.

See http://www.diplomacyworld.net/ for some exciting back issue material being
posted as well as the new Issues, including the monstrous Issue \#100.  
Highlights of \#100 include Walt Buchanan's ex-wife Carol showing us who REALLY
was in charge of the hobby back in the Hoosier Archives days, Eric Ozog augmenting
the oft-heard, but never get enough of, love story between Eric and Cathy,
and the start of the new Diplomacy World Demo Game.
In addition to the first two issues, we have 
every issue back to issue number 53 posted.  Eventually they all will be up.

%\noindent Final Hobby Awards Ballot for 2004, nominations now to:
%burgess of world.std.com
%
%The qualifications for the Kathy Byrne Caruso Lifetime Achievement 
%Award are that the awardee must have been: (1) Active in the 
%Diplomacy Hobby in at least Three Separate Decades; 
%(2) Multidimensional in their Contributions to the Hobby 
%(e.g. writing, playing, publishing); (3) Taking Retirement or 
%Semi-Retirement from the Diplomacy Hobby; and (4) One of the 
%Hobby’s Unique Personalities Worthy of Being Remembered as Long 
%as THE Game Continues to be Played.  This award need not be awarded
%each year, but only as worthy candidates are identified.  The only
%past honoree is the late Richard Sharp.
%
%The other award categories are self-explanatory:
%
%\noindent Nominees for the 2004 Don Miller Award for Meritorious Service
%
%\noindent Nominees for the 2004 Rod Walker Award for Literary Achievement
%
%\noindent Nominees for the 2004 John Koning Award for Player Performance
%
%\noindent Nominees for the 2004 Fred Hyatt Award for GM Performance
%
%--- --- --- --- --- --- ---

Editorial Board for {\it Diplomacy World}:

\noindent  Doug Kent, NEW Lead Executive Editor!, 11111 Woodmeadow Pkwy 
\#2327, Dallas, TX  75228, dougray30 of yahoo.com 

\noindent Tim Haffey, 810 53rd Ave., Oakland, CA 94601 USA; trhaffey of
aol.com -- Ex-Lead Editor and Archives Editor

\noindent Jim Burgess, 664 Smith Street, Providence, RI 02908-4327, USA;
burgess of world.std.com -- Co-Editor and Interview Editor

\noindent Rick Desper, 5440 Marinelli Road, \#204, Rockville, MD  20852, USA;
rick\_desper of yahoo.com -- Demo Games

\bigskip

OK, and then we have FTF tournaments.
See the Pouch FTF tournament page at:

\smallskip

\noindent http://devel.diplom.org/Face/cons/index.php

\smallskip

\noindent and one that is not there yet is this year's DipCon.
DipCon will be held on the campus of the University of Maine at Orono, just
outside Bangor, Maine.
It is set for the last weekend in July, starting Thursday, July 24th and running
through Sunday, July 27th.
We hope to have more details soon, but I am planning to go and hope
many of you may be coming as well.
Talk to me if you're thinking about it.
I haven't been to DipCon in a few years now, so this year I'm planning it way
in advance.
I hope we get this going soon with the publicity so a lot of you come and make it.
Jim O'Kelley also has been coordinating a number of Chicago events etc.
that are on the web page, go to a FTF tournament near you soon.

\bigskip

\centerline{\bf MUSIC AND MOVIES SECTION (WITH COMMENTS ON OTHER ARTS AND SOCIETY)}
     
\smallskip

We were running a ``23 tunes'' contest here
(stolen blatantly from Mark Wightman and the late lamented {\bf The Sprouts of Wrath}.
If anyone would like to send me a tape or CD of their 23 (which was the original point)
that would be great, but I don't intend to require that.  I will be playing in the
sense that I'll be putting 23 tunes in, and you have to guess me, but I obviously
won't score points.
Send commentary with your choices, and we'll see if people can
guess who you are!!!
And already there is a LOT of diversity in defining tunes and styles, so 
BE CREATIVE!!!
This kind of died, mostly because of me.  I don't want to take this last issue
getting it back together, but might next issue.
Feel free to send along general music comments any time.
 
%To encourage voting early, I picked five voters at random to receive five US
%dollars from me (either in cash or paid to someone for Dip stuff or to get
%a free tape).
%Tony Dickinson won the Round 5 prize, so we had three of the six Round 1 voters
%won and one of the three Round 2 postal voters who also got five chances to win.
%That showed the value of getting in early!!
%Voters in Round 1 were Mike Barno(\$5), Rick Desper (\$5), Tony Dickinson (\$5),
%Drew James, Heath Gardner, and John Harrington.
%Round 2 postal voters were John Schultz (\$5) Ian Moore, and Stan Johnson.
%Round 2 E-Mail voters were Scott Morris, 
%Warren Goesle, Peter Sullivan, and Michael Lowrey.
%Round 3 voters were Dick Martin, Richard Weiss, and Rip Gooch.
%Round 4 voters were Roland Sasseville, Jr. (\$5),
%Don Williams, Brent McKee, and Andy York.
%Round 5 voters were Mark Larzelere, Al Tabor, Jody McCullough, and that's it.
%We'll end up with a monster party tape at the end of it that I plan
%to segue and sequence and copy for distribution.
%The result will be a great New Millenium party tape -- we're going for 90 minutes.
%I've also been thinking that I should put this out on CD
%as truly emblematic of the new millenium.  
%I don't have the capability to do that quite yet, but I think
%I might by then.
%Any suggestions (or especially volunteers) on this front will
%be cheerfully accepted and could receive monetary payments!
%The CD way may still occur if someone steps forward and actually does it for me.
%So far, we have ``I Melt With You'' by Modern English; George Gershwin's
%``I got Plenty O' Nuttin' '' from {\it Porgy and Bess} in the 1957 concert
%recording with Ella Fitzgerald finishing off the vocals after Louis
%Armstrong blows and sings through the tune; Duke Ellington performing
%Billy Strayhorn's ``Take the A Train''; Frank Sinatra's ``New York,
%New York''; something from the B-52's;
%the original Van Morrison and Them version of ``Gloria'';
%The (English) Beat's 12 inch version of ``Save It for Later'' 
%ratchets things up to the next level (wherever you put it!);
%Buster Poindexter's ``Hot, Hot, Hot'' keeps you there;
%``Atomic Dog'' by George Clinton blows the doors off,
%and Koko Taylor cleans up singing Willie Dixon's ``Wang Dang Doodle''.
%After I get timings down, I'll choose exactly which songs below make the list.
%
%EXTRA SPECIAL B-52'S BULLPEN: (7) ``Love Shack'';
%``Rock Lobster". {\it ((A tie, a tie!!!!))}
%
%BULLPEN: (9) Nirvana -- ``Smells Like Teen Spirit";
%``Cumberland Blues'' -- the Grateful Dead.
%(8) ``Twistin the Night Away" -- Sam Cooke; ``In Between Days'' -- The Cure;
%``Mannish Boy" -- Muddy Waters; ``Shake, Rattle, \& Roll" -- Big Joe Turner; 
%``Proud Mary'' -- Ike and Tina Turner.
%(7)  ``I Wanna Be Sedated" -- Ramones; ``Twist \& Shout" -- Beatles.
%(6) ``Magic Carpet Ride" -- Steppenwolf;
%``Crossroads'' -- Eric Clapton; ``Play That Funky Music'' -- Wild Cherry;
%``I Fel Good" -- James Brown;
%``Radar Love'' -- Golden Earring; 
%Devo -- ``Whip It"; ``Echo Beach'' -- Martha and The Muffins.
%(5) ``Sing Sing Sing'' -- Benny Goodman; ``Rocking the Casbah'' -- The Clash; 
%Squeeze -- ``If I Didn't Love You"; ``Roadrunner'' -- 
%Jonathan Richman and the Modern Lovers.
%
%SPECIAL ROLLING STONES BULLPEN: (6) ``Paint It Black''. 
%
%SPECIAL TALKING HEADS BULLPEN: (9) ``Take me to the River".
%(4) the entire {\it Speaking in Tongues} record
%(special call for ``Road to Nowhere'').
%
%SPECIAL ALPHABET SONG BULLPEN: (6) ``YMCA" -- Village People. 
%
%SPECIAL DRUG MUSIC BULLPEN: 
%(8) ``Rd, Red Wine'' -- UB40.
%(6) ``Don't Bogart that Joint'' 
%-- Fraternity of Man; ``The Old Dope Peddler'' -- Tom Lehrer.
%(5) ``Cocaine'' -- Eric Clapton's version; ``Casey Jones'' -- the Grateful Dead.
%(4) ``White Rabbit'' -- Jefferson Airplane; ``Love Is the Drug'' -- Roxy Music.

\bigskip

\centerline{\bf {\it 23 Tunes Game}}

\smallskip

Here are the rules for 23 TUNES.  You send me three tunes for the first turn,
and then two tunes in each of the last ten turns for a total of 23.
If you missed the first turn, you can still catch up by sending five tunes next
issue, and guess on submitters to this issue.
I am also submitting my tunes.
After we're done, I'd like to exchange CD's/Tapes for as many of the tunes players
as possible, but this is not required.
I'll be sending the winner both my LAST 23 tune list and my NEW 23 tune list.
The winner is determined by having you guess each issue who submitted what list
(I will tell you who the submitters are).  For each list you get right, you get
a point, you also can win bonus points from me for really cool tune selections.
%That's it, not complicated.
%I hope by starting this up, we'll get more to join, five songs required to enter
%late.
%Playing this issue (guess who is whom by number, scores are in parentheses) 
%is, in alphabetical order, 
%Jim-Bob Burgess, Rick Desper (1), %Steve Emmert, Doug Kent, 
%Dick Martin, %Jim Reader,
%Richard Smith (3), Joakim Spangberg, %Brendan Whyte, 
%and Brad Wilson (4).
%The linking theme thing didn't seem to go over too well.
%No one really figured out the true linking theme.  
%Rick Desper was using Underground tube stops and songs with that as the title,
%they were things like that.  
%I'll let you guys talk a bit to each other on that with your guesses.
%I have added some kind of comment on each tune.

WHAT I NEED: 
Quite a number of you SAID you would join but haven't yet, so we'll get started and
put the pressure on you.
This part is still a MESS and I'm getting this issue out and then will catch up next time.
I think I'm going to simplify the rules to get it back on track.
%Rick Desper: Anyway, my tunes this time are "Set the Controls for the Heart of Sun" by Pink %Floyd, 
%in honor of the film Sunshine, and "Afternoon Delight" by the Starland Vocal Band, 
%that Will Hunting just sang a snippet from, and Ron Burgundy covered in "Anchorman".  
%The latter is really becoming an anthem of the Goofy 70s.
%I have no idea what this game is supposed to mean, but we can't go wrong with "Afternoon %Delight".

\bigskip

{\bf Mike Barno (Wed, 19 Dec 2007 22:24:40 -0500)}

One of my favorite local bands, the Parlor Cats from Binghamton, NY 
(known as ``the Parlor City" a century ago) has their first CD out.  
It's called {\it Help Me!} with an exclamation point and with the band's 
frontman looking to weasel a way out of jail for the band.

They did well to select a theme and opening song that lots of people 
might know: ``Help Me", which was written by Sonny Boy Williamson II 
(Aleck ``Rice" Miller, the second ``Sonny Boy Williamson").  
The song was a hit for SBW2, for Junior Wells, for John Mayall's Bluesbreakers, 
and for Van Morrison.  (I found this Horrid Example, category Pronouns, 
in the liner notes from the Rhino Records anthology 
{\it Blues Masters Volume 4: Harmonica Classics}:  ``A young disciple 
of Williamson's was Junior Wells, who recorded `Help Me' as a tribute to 
Williamson shortly after his death."  Wells recorded postmortem?  
Maybe that's why it can sound so eerie.)  
I just listened to Williamson's version (with Matt Murphy on guitar) and the 
Parlor Cats' new one back-to-back.  They sound plenty different but the crying
harp gives the same feeling.  That sets the tone for the whole album: authentic
traditional postwar blues, led by HOT HOT HOT harmonica and (often slide) 
electric guitar.  Even the originals (more than half the songs) sound 
like they could have been written in Chicago in the 1940s.  
The title song is also a tribute to Rod Piazza (of Rod Piazza and the Mighty Flyers), 
who turned Brian Potenziano onto this kind of music and helped him learn 
how to make a harp howl and wail:  the song's intro and outro are an answering 
machine message from Piazza, who wrote the arrangement used here.  
Brian P plays through the Rod Piazza modification
of the Harp King amp from Kinder Instruments, and this gives GREAT sound.  
You don't lose the most soulful sounds; they fill the room and they come 
through on the recording.  The other covers are also familiar 
(and happy) for old-blues fans...  Willie Dixon's ``Back Door Man" was 
first released by Howlin' Wolf (1961), and was covered by the Doors (1967), 
the Grateful Dead, Shadows of Knight, Bob Weir, Harmonica Slim \& 
Hosea Leavy, Sam Gopal, Frank Marino, and Quicksilver Messenger Service 
if the Wikipedia entry I'm seeing is correct.  On this one, the 
'Cats sound more like Howlin' Wolf than like the later versions.  
It feels raw, which is right for this song.  There's another Willie Dixon 
song, "Dixon City", which was a multiple hit under the title 
``Bring It On Home": first for Sonny Boy Williamson (the second one again) 
in 1959, then by Led Zeppelin on the very influential {\it Led Zeppelin II} 
in 1969.  There's Eddie ``Cleanhead" Vinson's ``Alimony Blues", and 
Junior Wells' 1960 ``Messin' With The Kid".

The originals are as hot as the covers, and being pretty much 
good ol' blues and a bit of swing, they're easy to pick up on; 
after a couple of listens, they can become almost as familiar as the 
oldies-but-goodies.  Brian P's ``Love My Baby" is just dirty enough that 
it could have been written by Eddie Vinson in the days when he couldn't 
record many of his best songs.  
``The Bounce" is credited to ``Swan, Osterhout and Brown" because 
it's what Brian S, Jamie, and John play first
after break, when Brian P is still drinking.  
Brian P's ``Lazy Lovin' Woman" has a fun bounce and some nice sleazy lyrics.  
Jamie-O's "Uptown Strut" and Brian P's ``Be My Friend" and ``Don't Tell Me" 
get it done in various ways.  The last original on the album is 
``The Parlor Cat Boogie", which (as you might guess from the
title) is a swing strut.  
It's lots of fun, especially at live shows when Brian P takes his harp 
and a wireless mic around the audience, playing wild licks while peeping 
over people's shoulders.  This worked well at the last two years' 
Blues on the Bridge festival in Binghamton.  
All the Parlor Cats original songs that I hear, on this CD or at live shows, 
show both originality and understanding of where this music came from.  
They rock, in some of the ways that R\&B rocked so people so hard 
that rock'n'roll overpowered conformist society.  
Some of them make me dance as readily as my favorites among their oldies.

So I recommend their CD (contact information is on www dot theparlorcats dot com), 
and I recommend their live shows, which so far have been in 
Binghamton (NY) and the surrounding counties.  
I've been hearing them various bars and restaurants for over a year, 
and every show is lively and colorful.  Most songs are a bit
different each time and it always sounds fresh and real.

\centerline{Mike, mpbarno@lightlink.com}

{\it ((Mega-cool, and thanks for the CD, let's get my own little review out here.
Just so the band and the public don't think I'm a shill for them, let me start with
the nits to pick.
You could really see how ``The Parlor Cat Boogie" is a huge hit at their live shows,
but this one drags a bit as car or home listening.
It doesn't help that Willie D.'s ``Backdoor Man" then starts off a bit slow
(only in comparison to the original, of course, in the vocals and intensity), 
though I did like that rhythm that I guess drummer John Brown is playing out
on the sticks.
Luckily for us it really builds though as we get ``shot full of holes''
and finishes the disc with you wanting and begging for more.
For this one it is better once it leads with the instrumentals.))

((I thought front man Brian Potenziano was better singing his own songs.
Mike, you and I did not quite agree, as perhaps my favorite song on the
entire disk that really made my hips shake was ``Be My Friend" that 
makes me really like their tricks!!!
So it is the tongue that does it, eh?
Well, let me be clear, {\bf I'm} not looking for Brian's tricks, but if he
gets the crowd moving, I'm all for it.
This tune also reflects what I thought was the strength of the band, you
emphasized the hot, hot heat, but I'd emphasize the restrained coolness.
``Love My Baby", another Potenziano original pops up next keeping up the 
back door metaphors and the cool moving.
I don't think I want to be ANYWHERE near any back door with these guys.....
I liked this one much better at home than on the road where the subtleties
of the smoldering feeling get lost a bit.
It does remind me of Eddie ``Cleanhead'' Vinson who I was lucky enough 
to see live in the early 1980's before his death in mid-decade or so.
I think I've not heard ``Alimony Blues", the song of his here, since then!
I think they would be best in a dirty, grimy blues bar.))

((On the other hand, while you correctly identify that Brian Potenziano hits
the harp with a West Coast soulful sound (tutored by Tom Townsley), my harp
tastes lean a bit more toward the folk sounds of our Providence based pal
Chris Turner (who hosts a MEAN.... New Year's Day party), you can find
Chris, also protecting him from the spammers and crazies at 
www dot fiddleandharmonica dot com.  Don't get me wrong, I thought Potenziano
was great, it just some of it was not my favored style of harp playing.))

((What I really liked were Brian Swan's guitar solos, especially the ones on 
the Potenziano compositions ``Love My Baby" and ``Don't Tell Me",
and especially on the lead song ``Help Me!"
I highly recommmend the {\bf Essential John Mayall}, 
with the disk {\bf Exclusive Live Rarities} for ``Help Me!" featuring Mick Taylor.
I'm more of a Mayall guy, I don't have any original SBW II recordings,
but I thought they stood up to Mayall and Taylor, better praise isn't possible
from me.
As a whole a great starting disk, they probably need a touch more range
to make a truly great album, but for the most part I liked their originals
as much or more than the covers, so that suggests promise.
Thanks much for turning me on to the Parlor Cats, Mike!!))} 

{\it ((Let's see, we have about half a page to fill.
I'm looking for some testers to help J\'er\'emie LeFrancois test his new 
playsystem for tournament Diplomacy at http://www.stabbeurfou.org, he is 
looking in particular for postal/non-Internet type players to see how 
easy the system is for those types of people to play.
Contact jeremie.lefrancois of gmail.com for more information, questions,
or to volunteer.))}

\smallskip

\centerline{\bf Szine sports announcements are next}

{\it ((Baseball: get your predictions and comments on the new season in 
to me for next issue.
The local Red Sox will be off to Japan, that should be interesting.
Will Barry Bonds play again?
Do we care whether anyone talks about Roger Clemens again?
I maintain my view that the ``ignore the steroids because they don't 
matter'' stance that baseball took in the 1990's and the ``everything
people did depended on steroids" stance are equally nonsensical.
What needs to happen is light, some rules that can be monitored
and enforced and a growing understanding that what was was.
I find it immensely fascinating to watch how people react to this
story.
And yes, I still am a fan of Barry Bonds and I hope he eventually 
achieves the peace with his life that he's struggling for.
I hope Barry plays and stays well ahead of A-Rod, who I am most 
definitely NOT a fan of.))

((College Basketball March Madness: Jamie McQuinn is probably going
to run the group I'm going to join, if you're interested, 
E-Mail jamiemcquinn of yahoo.com and let him know so he can let you
know when he starts up his group.
I think we have some fascinating stories this year.
What will Cinderellas like Cornell and Davidson from the ``academic
institutions" be able to do?
Do teams like Tennessee, Memphis etc. have a chance?
Will the Big Ten only get a handful of teams like they deserve?
And will the Big East get the ten or so that THEY deserve??))}
%
%\bigskip
%
%\centerline{\bf SPY DIPLOMACY (Variant, revised Dec. 1986)}
%
%by Jim Burgess
%
%Rules:
%
%1) Unless otherwise specified, the standard rules of Diplomacy apply.
%
%2) Players receive adjudications for their own armies and fleets, but not
%the armies and fleets of other powers.  Similarly, each player sees only
%his or her own section of the supply center chart.
%
%3) In addition to the standard units, an unit called a "spy" is added.
%
%     A) Each of the seven powers begins with a spy in each home supply center.
%
%     B) Spies are supplied only by home supply centers (i.e. Russia may have
%as many as four spies at a time while other powers are limited to a maximum
%of three).
%
%     C) Spies are "built" and "disbanded" in Winter seasons at the same time
%as other units.
%
%     D) There is no limit to the number of spies that may be present in any
%province and spies may be ``stacked" with armies or fleets (exceptions are
%listed in Rule 6).
%
%4) Spy Reports
%
%     A) Spies report the location and nationality of armies and fleets in
%the province they occupy and all adjacent provinces immediately following
%the standard Winter, Spring, Summer, and Fall seasons (i.e. just prior to
%the spy movement seasons).  Spies can differentiate between units in retreat
%and successful attackers when two units "occupy" a province.
%
%     B) Spies also report the nationality of spies in the province they occupy
%and the presence (but not nationality) of spies in adjacent provinces at the
%same time.
%
%5) Movement of Spies
%
%     A) Spy movement follows the collection of spy reports, so orders to spies
%may be made conditional on any information gathered by spies on opposing troop
%movements or the adjudication of one's own units.
%
%     B) Spies move after each of the following standard seasons: Winter,
%Spring, Summer, and Fall (note that all spy movements PRECEDE Autumn
%retreats), beginning with Winter 1900.
%
%     C) Spies move as armies do with the following exceptions:
%
%          a) Spy movements cannot be stood off by movements of any other unit.
%
%          b) Spies may be convoyed by fleets of any power during any of the
%four movement seasons for spies.  The convoy orders for fleets in these
%seasons must be ordered by their owner in the usual fashion or else the spy
%convoy movement fails of execution.  Fleet convoy orders for spies may be made
%in addition to regular Spring and Fall moves (note, however, that the fleets
%themselves never move during spy movement seasons).
%
%          c) Spies may also be "picked up" and carried by fleets of any
%power. Embarkation and debarkation are moves that must be made during a
%spy movement season and "permission to board" is not required.  Embarkation
%consists of a movement from a land province to an adjacent sea province
%containing a fleet.  Debarkation consists of a movement from a sea province
%containing a fleet to an adjacent land province.  A spy may not "switch
%fleets in midstream".  Once boarded, a spy may only get off by debarking.
%After boarding a fleet, the spy moves with the fleet during regular movement.
%A spy may not debark from a fleet awaiting retreat (e.g. if a fleet carrying
%a spy is dislodged in Spring, the spy may not debark until the spy movement
%season following the standard Summer retreat season).
%
%6) Spy Mortality
%
%     A) This rule will outline the circumstances under which spies may be
%captured or killed.  Spies may be disbanded in Winter seasons at the same
%time as other units to meet the requirement that a power may not have more
%spies than the number of currently held home supply centers and spies are
%annihilated when they are on board a fleet that retreats off the board.
%Otherwise, spies may only be removed from the board (there is no difference
%in the game between capturing and killing a spy, but players should feel
%free to delineate between the two states in writing press) immediately
%following the four spy movement seasons.
%
%     B) Spies killed or captured in a given season do not submit written
%spy reports for that season, though their final movement may have been
%made conditional on that spy report.  Players may never know for sure how
%a spy was lost, just as in real life.
%
%     C) Spies are "killed" by being assassinated by other spies.  When a
%spy moves, he or she may attempt an assassination, specifying the nationality
%of spies to be executed if discovered.  Each spy may hunt for only one
%nationality in each of the four seasons.  The following rules and examples
%will govern the adjudication of assassinations:
%
%          a) A spy may attempt an assassination without moving (for instance
%if the target is in the same province).  In this case, any spies of the target
%nationality that end the spy movement phase in that province are assassinated
%with one exception.  If the spy attempting the stationary assassination is
%himself or herself assassinated by a moving assassin then that spy
%assassinates no one in that season (not even a potential target other than the
%one that assassinates that spy).
%
%          b) A spy attempting a moving assassination (may include a move of
%embarkation or debarkation from a fleet) is always successful in assassinating
%spies of the target nationality that finish the spy movement phase in the
%province that the spy moves to.  This makes "mutual assassinations" possible.
%
%          c) Example: French spy is on board a French fleet in the Channel.
%An English spy is in London.  Both powers specify assassination attempts
%against the spies of the other.  If the English spy embarks on the French
%fleet in the channel (remember that embarkation does not require the
%permission of the fleet being boarded) and the French spy doesn't move, the
%French spy is killed, but the English spy isn't (he may be immediateIy
%captured, however, see part D).  If a German spy is also on board and the
%French spy tried to assassinate the German spy, that operation would fail
%as well. If the French spy debarks to London at the same time, the two spies
%"pass in the night" and neither is killed.
%
%     D) Spies are "captured" by opposing armies and fleets.  Players may
%attempt to capture spies, specifying the nationality of spies to be captured
%if discovered.  Each army and fleet on the board may search for spies of one
%nationality in each of the four seasons.  The following rules and examples
%will govern the adjudication of attempts to capture spies:
%
%          a) Players may specify a nationality to be hunted separately for
%each unit or they may issue blanket searches to be applied to all units.
%
%          b) At the end of the spy movement phase, any spies of the
%nationality specified in the same province are captured (for example, if
%the French player specifies a hunt for English spies on their Channel fleet
%in the above example, then the English spy is captured).
%
%          c) Players are informed when they successfully capture an opposing
%spy.  Note that the "owner" of the spy, however, is not informed of the
%capture.  Communication just is cut.  This rule is the only exception to the
%generaI rule that armies and fleets are blind.  It is possible to play the
%game without allowing capture of spies by armies and fleets if one wishes
%to allow freer movement of spies (i.e. RuIe D may be ignored).
%
%7) It is suggested that the game be adjudicated in four separate seasons
%in the following order:
%
%     A) Spring: (for Spring 1901 this sequence is preceded by a spy movement
%phase (no spy reports are necessary) followed by assassinations or captures)
%
%          a) Standard movement by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     B) Summer:
%
%          a) Standard retreats by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     C) Fall:
%
%          a) Standard movement by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     D) Winter:
%
%          a) Standard Autumn retreats by fleets and armies, adjudication
%reported only for one's own units
%
%          b) Standard Winter builds and removals, also applies to spies
%
%          c) Spy report phase, spies collect information
%
%          d) Spy movement phase, spies move according to Rule 4
%
%          e) Spy assassination and capture phase
%
%\medskip
%
%These rules have been produced by Jim Burgess (with helpful comments from
%Bernie Oaklyn and Dick Martin).  Permission is granted to reproduce and use
%these rules without restrictions.  The author would be interested to hear
%any comments and criticisms regarding any aspect of the play of this variant.
%The rules have been deposited with the North American Variant Bank.  They are
%also available from the author for the cost of postage or free by E-Mail.
%
%\bigskip
%
%\centerline{Wing Rules} 
%
%1.A wing unit can move over both land and water spaces. 
%  
%2.A wing unit can support actions in any space adjacent to the one it occupies. 
%   
%3.A wing can give, receive and cut support in the same way as armies and fleets. 
%   
%4.A wing unit cannot convoy or be convoyed. 
%
%5.A wing unit cannot capture an SC, but instead blockades it: 
%        
%\indent\indent 5.1.A blockade occurs when a wing unit occupies the SC of 
%another player in a fall season. 
%        
%\indent\indent 5.2.The player who owns a blockaded SC does not count 
%it when counting his total number of SCs. 
%        
%\indent\indent 5.3.A blockade ends as soon as the wing unit no longer occupies the SC. 
%        
%\indent\indent 5.4.Builds only take place in the winter phase, just as in games without wings. 


\vfill\eject

\centerline{\bf {\it THE ABYSSINIAN PRINCE} GAMES SECTION}

\smallskip

``So I called up George and he called up Jim, I said let's make a deal.

He said he'd talk to him.  Gonna start a church where you can save yourself,

You can make some noise, When you've got no choice...

You told me useful things, what people think of me, I guess I should thank you.

It's true, then I agree... I'm all alone, I've got no choice,

I'm all alone, I've got no choice."

From ``Got No Choice" by the incomparable Mark Cutler, from the CD
{\it Mark Cutler and Useful Things}.

\smallskip

\indent If you want to submit orders, press, or letters by E-Mail,
you can find me through the Internet system at
``burgess of world.std.com''.
If anyone has an interest in having an E-Mail address listed so people
can negotiate with you by computer, just let me know.

I am continuing to note cut or failed support orders with a 
small ``s'' instead of a capital ``S''.
This will make it easier on the E-Mailed version of the szine to see
what happened, since the italics don't show there.
The italics DO show on the web page just fine.

\indent Standby lists:

Mike Barno, Dick Martin, Brad Wilson, Jack McHugh, Glenn
Petroski, Steve Emmert, Mark Kinney, Vince Lutterbie, Eric Brosius,
Paul Rauterberg, Bob Osuch, Doug Kent, Sean O'Donnell, Vern Parker,
Heath Gardner, Paul Kenny, and Jeff O'Donnell
stand by for regular Diplomacy.
%I am willing to take over for NMR or start new-Diplomacy.
%Vern Parker
%337 Winter Hill Pl.
%Powell, OH 43065
%VSParker of aol.com
%614-402-5139

Let me know if you want on or off these lists, especially OFF.
Standbies get the szine for free and receive my personal thanks.

\bigskip

\centerline{GAME OPENING INFORMATION} 

\smallskip

We've got lots of openings in the subszines, check them out!!!
Contact Rip Gooch directly at xyropedes of canada.com and try to entice him to return.
Rip has been a bit missing in action lately, but I am assured that he
SHALL return.
Can we get back to these game openings below?  
We just need a few more people for a couple of these.

I am willing to open another new game of REGULAR Diplomacy if there is enough interest!!!
Doug Kent, Fred Wiedemeyer, %e,f,r,i,g,t,a
Brad Wilson, and Shaun Thompson start the list, who would like to join them???

Also, is there any interest in another game of Nuclear Yuppie Evil Empire 
7x7 Dip?
I know it may be getting tired, but I really like it.
We have Karl Schmit on the list, let's get seven!!
It's FREE!!!
I may drop this one shortly if we still have no interest.

I also am starting a game of the variant I designed, Spy Diplomacy.
Signups for that are now open.
Bruce Edwards and Eric Ozog are signed up.
The rules were published recently, ask to see them if you missed them!!!

And since Colonia is over, Harold Reynolds is looking to start something else.
Harold has been updating the Diplomacy A to Z, go check it out at:
http://www.badpets.net/Diplomacy/AtoZ/index.html 

Also, I am going to design some postal rules for Devil Take the Hindmost,
and we have an opening here:
Bruce Edwards, Mike Barno, and Eoghan Barry are signed up.
Postal rules from me will be forthcoming shortly, on my never ending to-do list.
I will get them in SOON!
I'm more likely to get these things started if I see some interest.....
I've GOT to do this now,
Eoghan is getting tired of waiting....

Right now, the other thing going is the Modern
Diplomacy game with Wings.
Sean O'Donnell, Jeff O'Donnell, Steve Koehler, Art Schleinkofer,
Bob Holt, Rick Desper, Alexander Woo, and Dave Partridge are signed up for that.
I will start it when I get a full complement of players, we only need TWO more!
Only two, just TWO more...... come on.
%Sean's list: Britain, Spain, Germany, France, Egypt, Turkey, Russia, Ukraine, Italy, and Poland.

\bigskip

\centerline{\bf TAKING OVER ISHKIBIBBLE'S REGULAR DIPLOMACY GAMES ((NOT))}

\smallskip

Last chance for anyone who was a subber to {\it Ishkibibble} to join any new
game for free, but this is a ONE TIME only offer, get your request in now.
It is going to expire VERY shortly.
Marc Ellinger and Fred Wiedemeyer already have taken us up on this request.
Come on, let me call by name who qualifies
for this deal..... Karl Schmit, John Power, Tim Snyder,
Dave Partridge, Graham Wilson, and Kevin Wilson.
I especially would like to fill the Modern Diplomacy game that Dave Partridge
already is in.
As soon as one more game fills (I'm not counting the new Breaking Away game), 
I'm going to pull this offer.

\bigskip

\centerline{\bf THE PHIL REYNOLDS MEMORIAL: 2006B, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SPRING 1903 IS MARCH 22ND, 2008}

\smallskip

\indent {\it Autumn and Winter 1902}

\noindent AUSTRIA (Burgess): bld a vie; has a VIE, a TRI, f GRE, 
a BUL, a SER, f AEG. 

\noindent ENGLAND (James): has f ENG, f NAO, a BEL, 
f MID, f NTH.

\noindent FRANCE (Williams): R f mid-POR; bld f mar; has f MAR, a BRE, 
f POR, a PIC, a GAS.

\noindent GERMANY (Ellinger): has a KIE, a BER, 
f HOL, a DEN.

\noindent ITALY (Crow): has a TYO, f WES, a MUN, a VEN, 
f TYH.

\noindent RUSSIA (Gordon): has f BLA, a LVN, a UKR, f RUM, 
a SEV, f GOB.

\noindent TURKEY (Wiedemeyer): bld f con; has f CON,  
a ANK, a SMY.

%\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Burgess):&TRI,VIE,BUD,ser,gre,bul&(has 5, bld 1)\cr
%\+ ENGLAND (James):&EDI,LVP,LON,nwy,bel&(has 5, even)\cr
%\+ FRANCE (Williams):&PAR,MAR,BRE,spa,por&(has 3 or 4, bld 2(r:otb) or 1)\cr
%\+ GERMANY (Ellinger):&KIE,BER,den,hol&(has 4, even)\cr
%\+ ITALY (Crow):&ROM,NAP,VEN,tun,mun&(has 5, even)\cr
%\+ RUSSIA (Gordon):&WAR,STP,SEV,MOS,swe,rum&(has 6, even)\cr
%\+ TURKEY (Wiedemeyer):&ANK,SMY,CON&(has 2, bld 1)\cr
%\+ Neutral:&none&(Total=34)\cr
%
\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: David Burgess, 101 Laurel Lane, Queensbury, NY  12804

(518) 761-6687, burgesscd of roadrunner.com or dburgess of glensfallshosp.org

\noindent ENGLAND: Drew James, 3644 Whispering Woods Terrace,
Baldwinsville, NY  13027

(315) 652-1956, kjames01 of twcny.rr.com 

\noindent FRANCE: Don Williams, 27505 Artine Drive, Saugus, CA 91350, 
(661) 297-3947, 

wllmsfmly of earthlink.net or dwilliams of fontana.org (\$5)

\noindent GERMANY: Marc Ellinger, 751 Turnberry Drive,
Jefferson City, MO 65109

ellingermc of aol.com

\noindent ITALY: John Crow, 824 Kinwest Parkway \#101,
Irving, TX  75063, 

(214) 532-1418, johnny.crow of hotmail.com

\noindent RUSSIA: New Player is Heath Gordon, 741 E. John Street, Appleton, WI
54911, (757) 710-0808,

angrydogproductions of gmail.com

\noindent TURKEY: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  

CANADA  T6T 1N1, (780) 465-6432, wiedem of telus.net or wiedem of shaw.ca
%cell 780-497-8283; fax 780-468-6432

\bigskip

{\it Game Notes:}

1) Note Fred Wiedemeyer's two new E-Mail addresses.

2) As we will see in all of these games that Jeff O'Donnell has
to resign.  We wish him the best, of course.  Our new player is Heath Gordon.
This is Heath's first postal game and his debut in the szine.  
I trust that all of you will welcome him appropriately.
Heath, some of this crowd send postal letters, some E-Mails, and some 
call people on the phone. 
You'll figure it out.
We've played only two game years, let me know if you have any questions.

3) We also greet Heath Gordon with a proposal that he share in a two way draw
with Austria. 
There is a proposal for an RA two way draw.
Please vote with your Spring orders, failure to vote vetoes the proposal.

\bigskip
 
{\it Press:}

(FROM TURKEY): Hello?
Anyone out there?
Aus/Russ are planning to have me out by Fall 04.
Soon they will be concentrated on your doorsteps.
I propose an Austria/Russian draw and will vote for it.
It's up to you guys to stop it.

(RED KINGS 5 (DARK PRESS -- NOT FOR ATTRIBUTION) THE LADY RATTA-TAT-TATTED LACE):
So much for a shot in the dark.  It's not so much that I knew less than I knew 
before, it's just that now I knew what I knew wasn't enough to know what to do.   
A little work and that could be a Doctor Seuss riff, of course it would mean 
working in a gnu, but I didn't have that kind of motivation.  
I was frustrated, broke and hadn't had a drink in six paragraphs.

I watched as night bled into early day, and the bandage that was the 
streetlights timed off, letting the wound seep through to a halting, 
fit starting diorama of activity.

\noindent A newsboy started bleating out headlines...

{\bf ``Extra! Extra!  Read all about it... England Retreats Picardy.  
Forced to Disband!"}

\noindent My pique left me totally unappreciative of such a genius move.  
I was inert, despondent, devoid of perspective.  
I was a flatfoot with a mystery, which is better than a flatfoot without a mystery, 
but I had no clue what my next step was.  
Then again, this is when I do my best thinking.
	
\indent\indent ``I think I'll have a beer."  See, told ya so.

{\bf ``Extra, Extra.  Malice, heir to Centerland dynasty absconded into darkness!"}

\noindent The important thing was to stay focused, stay alert.  
If things were unfolding, if it was as big as Flat said it was, 
there would be indications... signs... okay, clues.  
And when it comes to clues, well that is my business.  
I'm just saying I didn't get to where I was today without having a good nose for clues.
    
{\bf ``Extra, Extra.  Maltese Dipcon reported missing!"}
	
\indent\indent Now the paperboy had my attention.  
	
\indent\indent ``Hey, you got a racing form?"  I asked him.
	
\noindent\noindent ``No sir, just the Daily..."
	
{\bf ``Then what are you hollering for!"}  Sheesh, I could get this 
aggravation anywhere, no need to hang around here.  
Macgillicutty's then.  
It hit me that I had a hot blond and a cold bottle of 
Cheater's waiting for me at home.  
I sashayed the fifteen szines home while I mulled over what I knew of the case. 
Elephants, otters and something important was missing. 
The only thing I knew for sure was that I needed a gnu for a rhyme.  
Baby needs a gnu pair of shoes, are you gonna like it once the 
gnu wears off, gnu and improved... free association is the 
devil's playground, that's what I always say...
actually I say a lot of other things, I don't always say that.  
In fact, I don't think I've ever said that before.
	
By then I was home and it was turning out to be an okay day.  
Burgess hadn't changed the locks and the lights were on.  
Life is measured in small victories. 

I went back into the Abyssinian Prince and climbed the stairs 
to my office.  I was expecting to find the blond from the 
Copasetic in full come hither mode, 
but naked with a machine gun was a little forward even for me.

``Baby, I'm not that hard a sell," I told her.

``Sweetface, keep your hands where I can see 'em," she smiled at me. 
 
The lips were still the glossy red I remembered from issue \#313.  
The eyes a deep blue that you could lose yourself in... 
okay, who am I kidding.  
She was naked, with a machine gun, but she was naked.  
Bazooms the size of Voice of Doom's old mailing list, 
a waist as thin as Ellinger's strategy, and her ass...
well, what can I say; she was facing me holding a machine gun.  
I'll describe her ass when she turns around.

``So, how ya doing?"  I am renowned for my repartee after all.
	
``I am holding a machine gun, y'know." She smacked her gum as she talked.

``Yeah, actually it makes you even hotter."  
Hard to believe she blushed at that, but since she was naked, the blush was definitely verifiable.  Trust, but verify. Ronnie was right about that.

``I gotta ask you some questions."  
She waved the barrel of the tommy gun indicating I should sit in one of my chairs.  
So I just sorta made myself at home. Seemed appropriate.

``Shoot... well, no I mean... go ahead," I said.

``Where are you on this case?"  
She tossed her head a little at the interrogative, giving the hair a sort of flip.  

``I've been following up leads, gathering information. 
I'm at my usual starting point... confused as hell."  

She licked her lips, giving a fresh coat to the wetness of the redness 
with the pinkness of her tongue... ness.  No, overkill.  
``So, do you know where the Hierophant is?"
	
``I do not know anything about any damn elephant.  
I don't even know why you're in my office naked."
	
``I'm in your office to find out what you know.  
I'm only naked because you're writing this," she said huskily.  
Her words breathed out in pants.

``In that case, turn around."

Yeah, an ass like... well you know that Final Conflict Diplomacy that took 
place on a global map?  Two of those.
	
``Can we get back to business here," she twirled back to face me, 
the tommy gun dangling menacingly between her breasts.

``Sorry, hard to concentrate," I apologized, 
``you're the most beautiful woman I ever wrote."
	
She smiled at the flattery, again with the blush.  
Strong heart, good circulation.

``I modeled you after one of my exes. 
I can't remember if it was the one that left with the car, the dog or the house."

``Oh, I'm not like that," she whispered,
``I would never leave you alone and lonely in the Hobby."  She waved the gun.  
``I’d kill you first, but never alone and lonely."

``Gotta admire the honesty... and the jugs."

``So, you're seeking the Diplonomicon too?"  
She said, her breasts heaved with punctuation. 
(In punctuation?  Every time I punctuate?!!, ,!!... ????!!... 
I need a cigarette... try a Red King)
	
``Babe, I love you, or would like to, but all I'm seeking is the rent 
and the next day's down payment on the trifecta," 
I fished out the Red Kings from my coat pocket and tapped out a fag, 
``I don’t have a notion what a Diplonomiwashmajig is."

``The Diplonomicon is an artifact of untold power.  
It can bend fate to its will, change the balance of power, 
accumulate vast wealth, and even polish Diplomacy press with its glamour..."
she exclaimed, her face awash in the ecstasy of her feeling, 
her arms, with the tommy gun gesticulating wildly in accompaniment, 
and her areola fully distended in the excitement of the moment.  

``Now that's impressive," I said.  
She looked at me quizzically, not sure if I was commenting on her narrative, 
or on her... or on her.
  
She stared at me intently, ``the Diplonomicon is a weapon of 
immense and catastrophic power.  
The board and blocks are manifestations of the dark force of the Tarot.  
The 112 stones, 56 of each in two shapes represent the Minor Arcana. 
The 22 starting positions represent the 22 cards of the Major Arcana, 
and the Hierophant is one of those major Arcana 
who is seeking to reunite the board and stones. IT IS NOT A DAMN ELEPHANT!"
	
I just looked at her.  A voluptuous, naked woman... in my home.  
I could overlook the tommy gun thing.  
I'm a guy.  We compartmentalize.  
It's hard to get past naked.  
But the whole detective part of me was latching onto the clues, 
putting it altogether 
(even as she was in her all together) and I still came up zilch.

``I don't understand any of this Major Minor Arkansas crap,"  
(steal the best lines you can find... that's what I always say), 
``what's this Hierophant got to do with me?"

``It's simple," she answered, the gun lowered to her side, 
``You are the Hierophant reversed."

\smallskip 

She said it solemnly, with weight.  Like it meant something.  
God bless her, because all I could think was; I thought 
Hierophant reversed was ``Tnahporeih".

\bigskip

\centerline{\bf SPIRALS OF PARANOIA: 2005A, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SPRING 1907 IS MARCH 22ND, 2008}

\smallskip

\indent {\it Winter 1906}

\noindent AUSTRIA (Rauterberg): rem a alb; has a SER, a NAP, f GOL.

\noindent ENGLAND (Wiedemeyer): has f POR.

\noindent FRANCE (Tretick): bld a par; has a PAR, f BRE, a GAS, 
f MAR,
 
f ENG, a BUR, f IRI.

\noindent GERMANY (Ozog for Tallman): has a BOH, a GAL, a VIE, 
a RUH, a TYO, f SKA, 

a TUS, a PIC, f MID.

\noindent ITALY (Kent): bld a ven; has a VEN, a BUD, a TRI.

\noindent RUSSIA (Sundstrom): bld f sev; has f SEV, a UKR, a RUM, 
a ARM, a MOS.

\noindent TURKEY (Biehl): has a ANK, f SMY, 
f BLA, f TUN, f TYH, f WES.

%\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Rauterberg):&ser,nap,rom&(has 4, rem 1)\cr
%\+ ENGLAND (Wiedemeyer):&por&(has 1, even)\cr
%\+ FRANCE (Tretick):&PAR,BRE,MAR,spa,lvp,edi,lon&(has 6, bld 1)\cr
%\+ GERMANY (Ozog/Tallman):&KIE,BER,MUN,hol,den,bel,swe,&(has 9, even)\cr
%\+ &\enskip nwy,vie \cr
%\+ ITALY (O'Donnell):&VEN,tri,bud&(has 2, bld 1)\cr
%\+ RUSSIA (Sundstrom):&WAR,STP,SEV,MOS,rum&(has 4, bld 1)\cr
%\+ TURKEY (Biehl):&ANK,SMY,CON,gre,tun,bul&(has 6, even)\cr
%\+ Neutral:&none&(Total=34)\cr
%
\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Paul Rauterberg, 3116 W.~American Dr., 
Greenfield, WI  53221, 

(414) 281-2339 (E-Mail)  trauterberg of wi.rr.com

\noindent ENGLAND: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  CANADA  T6T 1N1, 

(780) 465-6432, wiedem of telus.net or wiedem of shaw.ca 
%cell 780-497-8283; fax 780-468-6432

\noindent FRANCE: Buddy Tretick, 5023 Sewell's Pointe Way,
Fredericksburg, VA  22407, (540) 898-3386

cell (540) 226-5571 (E-Mail) berniebuddy32 of aol.com

\noindent GERMANY: Terry Tallman, PO Box 782, Clinton, WA  98236,
(360) 331-5698 (\$2) 

terryt of whidbey.net

\noindent GERMANY: Temporary Standby is Eric Ozog, PO Box 1138, Granite Falls, WA  
98252-1138,

(360) 691-4264, ElfEric of Juno.com

\noindent ITALY: New Player is Doug Kent, 11111 Woodmeadow Pkwy \#2327, Dallas, TX  75228

dougray30 of yahoo.com 

\noindent RUSSIA: Matt Sundstrom, 1760 Robincrest Lane South, Glenview, IL  60025, 
(847) 729-1882, 

Matt.Sundstrom of bbdoch.com or mattandzoe of earthlink.net

\noindent TURKEY: John Biehl, \#8 -- 11530 84th Avenue, Delta, BRITISH COLUMBIA,
V4C 2M1  CANADA, 

(604) 816-0460 (cell) (\$7); jrb of dccnet.com

\bigskip

{\it Game Notes:}

1) Terry is still having some medical problems, 
Eric Ozog is continuing to
negotiate and submit orders for Terry.
Eric originally brought Terry into the Diplomacy hobby all those many
years ago, and so I'm glad he's agreed to do this.

2) So, we had I) GIRF draw, II) GT draw, III) FAIRT draw, IV) Recalling 
Terry Tallman to play Germany.
On the last one, I don't have a note from Terry volunteering to return,
but since any one vote, or failure to vote, will veto the proposal, I will
presume that at least one person will check with Terry before voting yes
for this.
If everyone (including Eric, obviously) votes to have Eric leave and
Terry doesn't want to take back over, I will find another standby.
I don't see how that will happen, but thought I should be explicit and 
complete. 
Again, votes were due with the Winter orders, but I think I got such
little interest in any of these that I'll entertain more votes with the
Spring orders (and of course Jeff O'Donnell and/or Doug Kent didn't get
a chance to vote for the Italian position).

\bigskip
 
{\it Press:}


\bigskip

\centerline{\bf FLIP FLOP: 2003G, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SPRING 1910 IS MARCH 22ND, 2008}

\smallskip

\indent {\it Fall 1909}

\noindent AUSTRIA (Wiedemeyer): rem a war; has a BUD, a GAL,  
a MOS, a VIE.

\noindent ENGLAND (Kent): has a DEN, a RUH, f NTH, f NWG, f HEL.
%A Den-Kie
%F Hel S A Den-Kie
%A Ruh-Hol
%F Nth-Lon
%F Nwg-Nat

\noindent FRANCE (McHugh): bld f bre, f mar; has f BRE, f MAR,
a HOL, a BEL, 

f ENG, a SPA.

\noindent GERMANY (Sundstrom): has f BER, a KIE, 
f SWE,

a NWY, a MUN, f SKA.

\noindent TURKEY (Levinson): bld a con, a smy; has a CON, a SMY, 
f AEG, a SEV, f WES, 

a BUL, f VEN, f GOL, a TRI, f ION, f BLA, 
a RUM, a SER.

%\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Wiedemeyer):&VIE,BUD,mos,war&(has 5, rem 1)\cr 
%\+ ENGLAND (Schmit):&EDI,LVP,LON,por,den&(has 5, even)\cr
%\+ FRANCE (Jeff O'Donnell):&PAR,MAR,BRE,spa,bel,hol&(has 4, bld 2)\cr
%\+ GERMANY (Sundstrom):&KIE,BER,MUN,swe,stp,nwy&(has 6, even)\cr
%\+ TURKEY (Levinson):&ANK,SMY,CON,bul,sev,ser,gre,&(has 11, bld 2)\cr
%\+ &\enskip tun,rom,rum,nap,ven,tri \cr
%\+ Neutral:&none&(Total=34)\cr
%
\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  CANADA  T6T 1N1, 

(780) 465-6432, wiedem of telus.net or wiedem of shaw.ca
%cell 780-497-8283; fax 780-468-6432

\noindent ENGLAND: New Player is Doug Kent, 11111 Woodmeadow Pkwy \#2327, Dallas, TX  75228

dougray30 of yahoo.com 

\noindent FRANCE: New Player is Jack McHugh, 810 School Lane, Folcroft, PA  19032,
(856) 456-5984,

jwmchughjr of gmail.com

\noindent GERMANY: Matt Sundstrom, 1760 Robincrest Lane South, Glenview, IL  60025, 
(847) 729-1882, 

Matt.Sundstrom of bbdoch.com or mattandzoe of earthlink.net

\noindent ITALY: Don Williams, 27505 Artine Drive, Saugus, CA 91350, 
(661) 297-3947, 

wllmsfmly of earthlink.net or dwilliams of fontana.org

\noindent RUSSIA: Sean O'Donnell, 1044 Wellfleet Drive, Grafton, OH  44044,
(440) 926-0230, 

sean\_o\_donnell of hotmail.com

\noindent TURKEY: Alexandre Levinson, Beeklaan 504, 2562BP Den Haag
THE NETHERLANDS, don't need phone, 

levinson7 of hotmail.com (\$5)

\bigskip

{\it Game Notes:}

1) Doug Kent takes over as the English player of record as I've not heard from 
Karl Schmit, I hope he's OK, probably just busy like we all are.
Thanks, Doug, for your quick and expert standby orders. 
As called for under the house rules, I do have draft Spring orders from Doug
that he can change if he wishes.

2) I also made an error in the Supply Center Chart last time and put 35 units on 
it, giving Budapest to both Italy and Russia, Italy is of course sitting there,
so it does belong to Italy. 
As a result, Russia only gets ONE build.
Thanks for the eagle eye who caught that.

3) We also have to replace Jeff O'Donnell as France.
Jack McHugh will take over there.

4) And, there is a proposal for a concession to Turkey.
Please vote with your Spring orders.
If you fail to vote, that vetoes the proposal. 

\bigskip

{\it Press:}

(FROM AUSTRIA): I propose a concession to Turkey and will vote for it.  
Now it's up to you guys to step up to the plate to stop Turkey.

\bigskip

\centerline{\bf I CAN'T FIND MY MONEY!: 2001F, Regular Diplomacy}

\smallskip

\noindent {\bf TWO WAY DRAW BETWEEN AUSTRIA AND GERMANY WAS DECLARED!}

This one is done now, except I need to do the endgame chart for Tom Howell,
as he knows, I'm usually really slow with these, but I'll try to do it
next issue.

\bigskip

\centerline{\bf SECRETS: 1999D, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SPRING 1924 IS MARCH 22ND, 2008}

\smallskip

\indent {\it Winter 1923}

\noindent ENGLAND (Kent): rem a pic, f eng; has a GAS,  
f MID, f POR.

\noindent FRANCE (Sasseville): has f MAR, f SPA(SC), a BUR.     
%standing orders, yes to ANY draw
                                             
\noindent GERMANY (Barno): has a BUL.
%votes yes to FREGT, no to EFRT 
%vote YES to FREGT draw

\noindent RUSSIA (Parker): bld withheld; has f NWG, a NWY, f EDI, 
f LVP, a WAR, 

a DEN, a KIE, f NTH, a HOL, a BER.

\noindent TURKEY (Linsey): bld f con; has f CON, a SEV, a RUM, f TYH, 
a SER, a MUN, 

a SIL, f WES, a BOH, f GOL, a BEL, a TYO, 
f NAF, a VEN, f PIE, a RUH.

%\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ ENGLAND (Kent):&LON,bre,por&(has 5, rem 2)\cr
%\+ FRANCE (Sasseville):&PAR,MAR,spa&(has 3, even)\cr
%\+ GERMANY (Barno):&bul&(has 1, even)\cr
%\+ RUSSIA (Parker):&MOS,STP,nwy,swe,den,ber,WAR,&(has 10, bld 1)\cr
%\+ &\enskip kie,edi,hol,lvp   \cr
%\+ TURKEY (Linsey):&CON,ANK,SMY,rum,gre,ser,bud,&(has 15, bld 1)\cr
%\+ &\enskip nap,ven,tun,sev,rom,tri,vie,mun,bel \cr
%\+ Neutral:&none&(Total=34)\cr
%
\bigskip

\indent {\it Addresses of the Participants}

\noindent ENGLAND: Doug Kent, 11111 Woodmeadow Pkwy \#2327, Dallas, TX  75228

dougray30 of yahoo.com 

\noindent FRANCE: Roland Sasseville, Jr., 38 Bucklin Street, Pawtucket,
RI 02861, (401) 481-4280 (\$0)

roland6 of cox.net  

\noindent GERMANY: Mike Barno, 634 Dawson Hill Road, 
Spencer, NY 14883, (607) 589-4906 

mpbarno of lightlink.com 

\noindent RUSSIA: Vern Parker, 337 Winter Hill Place, Powell, OH 43065,
(614) 402-5139

VernDip of aol.com is preferred

\noindent TURKEY: Bruce Linsey, PO Box 234, Kinderhook, NY
12106

GonzoHQ of aol.com

\bigskip

{\it Game Notes:}

1) There are no current proposals.

\bigskip

{\it Press:}
 

\bigskip

\centerline{\bf CAST NO SHADOWS: Breaking Away, Designer's Rules}

\smallskip

Rules are at:

\noindent http://devel.diplom.org/DipPouch/Postal/Zines/TAP/Tinamou/rules/BreakingAway.htm

\smallskip

\noindent {\bf DUE DATE FOR TURN 5 IS MARCH 22ND, 2008}

\smallskip

%--F--I--N--A--L-- --F--I--N--I--S--H-- --L--I--N--E--
%--S--P--R--I--N--T-- --F--I--N--I--S--H-- --L--I--N--E--
%
\centerline{\it Turn 4}

\smallskip 

\+ 22 (replenish with a 3) &Sanctus   \cr
\+ 21 (replenish with a 4) &Agnus  \cr
\+ 20 (no replenishment)   &Empty  \cr 
\+ 19 (replenish with a 3) &Granny, Gloria, Drugs, Bonham \cr
\+ 18 (replenish with a 7) &Vidic, Krstajic, Gavrancic, Dragutinovic, Zorro, Water,  \cr
\+                         &\indent Xavier, Yorick, Wally, Kyrie  \cr
\+ 17 (replenish with a 17)&Kyoto, Mideast  \cr 
\+ 16 (replenish with a 19)&Bowie, Travis, Crockett  \cr
\+ 15 (no replenishment)   &Empty  \cr
\+ 14 (no replenishment)   &Empty  \cr 
\+ 13 (replenish with a 3) &Death  \cr
\+ 12 (replenish with a 4) &Rincewind  \cr
\+ 11 (replenish with a 5) &Carrot  \cr 

\bigskip
%Sprint Points at 40, 80: 10,8,6,5,4,3,2,1 (final are just double these)
%Movement Order: A/B/C/D; highest card played that turn; highest card in hand

\indent {\it Addresses of the Participants -- Their Team and Their Cards}

\smallskip

\noindent TEAM 1 (Rick Desper): rick\_desper of yahoo.com (0 points)

Team Name: The Turtle Moves; Captained by Cut-My-Own-Throat Dibbler

\+ A: Rincewind the Wizzard &&14 12 16 4 (5) \cr
\+ B: Granny Weatherwax     &&12 11 3  (3) \cr
\+ C: Captain Carrot        &&15 11 5  (3) \cr
\+ D: Death                 &&13 20 3 (7) \cr

(note, Rincewind is accompanied by the Luggage, Granny is on Her Broom, 
Carrot is of the City Watch, and Death is just DEATH!)

Total Replenishments: $12+58+18+15 = 103$
                
\smallskip

\noindent TEAM 2 (Tom Howell): off-the-shelf of olympus.net (0 points)

Team Name: Never Ending Worry Source; Manager: Rumour; Team Captain: Ye Olde Manager

\+ A: Water    &&15 16 5 7 (3) \cr
\+ B: Kyoto    &&14 13 17 (7) \cr
\+ C: Mideast  &&11 6 17 (5) \cr
\+ D: Drugs    &&11 13 3 (9) \cr

Total Replenishments: $12+35+37+44 = 128$        
   
\smallskip

\noindent TEAM 3 ((David Partridge): rebhuhn of rocketmail.com (0 points)
%360-928-9698

Team Name: Famous Four  

\+ A: Krstajic      &&15 16 13 7 (8) \cr
\+ B: Vidic         &&13 13 7  (8) \cr
\+ C: Gavrancic     &&8 9 7  (7) \cr
\+ D: Dragutinovic  &&8 11 7  (7) \cr

Total Replenishments: $12+35+40+28 = 115$   
               
\smallskip

\noindent TEAM 4 (Brendan Whyte): obiwonfive of hotmail.com (0 points)

Team Name: The Reverse Alphabeticists

\+ A: Zorro    && 15 11 3 7 (10) \cr
\+ B: Yorick  && 10 12 7 (7) \cr
\+ C: Xavier   && 7 10 7  (7) \cr
\+ D: Wally    && 10 3 7 (7) \cr

Total Replenishments: $12+26+24+28 = 90$

\smallskip

\noindent TEAM 5 (Alexander Woo): aswoo of yahoo.com (0 points) %awoo@math.ucdavis.edu

Team Name: Just Ordinary; Manager: Credo

\+ A: Agnus     && 12 20 7 4 (15) \cr
\+ B: Sanctus   && 8 4 3  (3)   \cr
\+ C: Kyrie     && 10 7 7 (7)    \cr  
\+ D: Gloria    && 16 5 3 (12)    \cr
         
Total Replenishments: $12+44+22+17 = 105$ 

\smallskip 

\noindent TEAM 6 (Andy York): wandrew of compuserve.com (0 points)

Team Name: Alamo

\+ A: Crockett      && 15 5 3 19 (3) \cr
\+ B: Travis        && 15 3 19 (3)\cr
\+ C: Bowie         && 10 3 19 (3) \cr
\+ D: Bonham        && 3 3 3 (3) \cr

Total Replenishments: $12+12+12+60 = 96$

\bigskip

{\it Game Notes:}

1) The rules are on the {\it TAP} website in the {\it Tinamou} section.
Ask if you have any questions.
Up above in parentheses is the card you played to get to where you are
in the field.  The replenishment card is the last card in your list.
Be careful to note that the card you played (the one in parentheses) is
not available for you, for next turn.
Just for fun, I'm going to keep track of total replenishment, by turn, which is a 
rough measure of how the teams are doing.
Of course, it is lining up to get across the sprint and final lines in the
right places that really counts.
We can calculate an ``efficiency score" later, which will be the ratio
of scoring points per replenishment.
If I'm predicting how the future of this will come out, a 10\% score will
be really tremendous for this measure.

2) I have to comment on this one!!!  I've never seen ten riders on a 
single space before.
And rookie Biker Andy York looks like a genius now, while Rick Desper's
riders missed the pack.
Remember that the Sprint Finish Line is after line 40, for the first 
time this turn, that can be reached.
That's a whole host of 7's awarded.

\bigskip

{\it Press:}

(ANONYMOUS to GM): Wally is my hero!

\bigskip

{\it Personal Note to You:}

\vfill\eject
\end
