\nopagenumbers 
\font\twelverm=cmbx12 at 12pt
\centerline{\bf\twelverm THE ABYSSINIAN PRINCE \#310}
\line{\hfil April 1, 2007}    
\smallskip                                                    
\settabs 3 \columns 
\beginsection

\medskip

Produced by Jim Burgess, 664 Smith Street, Providence, RI 02908-4327  USA,
(401)351-0287 
 
\noindent Accessible through Internet at burgess of world.std.com (all E-Mail
addresses are reported in this format, replace the `` of '' with ``@''; if you 
bounce try sending to me from another account. 
Some of you have been getting bounced messages from
my ISP's spam protection, if that happens to you, USE my backup E-Mail
at jfburgess of gmail.com!!!  Don't complain that my E-Mail keeps bouncing
without forwarding the bounced message to that address.
Then I can forward it to the ISP help to get it dealt with.
 
\noindent Web Page Address: http://www.diplom.org/DipPouch/Postal/Zines/TAP/index.html

\bigskip

I expect ALL players to be signed up on the E-Mail notification list for the szine,
see below.
Some of you have been complaining about this, but it is up to you to get on this list,
it's easy, come ask me if you have trouble.
THIS IS A PROBLEM, sign up now if you're playing!!!

This issue was going to fix up the 23 Tunes game, but it is taking me forever.
I totally confused myself with the randomizing of the order of the submissions
to keep them secret.  I need to make myself a little table, but I've spent a
few hours organizing them already and it still isn't close to done.
Sorry, but I can't hold up the szine any more.
It has a few sets of orders in the games, 
rebirths Peter Sullivan's {\it Octopus' Garden}, and gives the second issue
of Doug Kent's subszine, as well as another Andy York production.  
In that sense, this quick hitter has more to read than you might have expected.
I didn't manage to get this out so you all could join Jamie McQuinn's NCAA basketball 
tournament Challenge group.
I am doing this just before the finals, as my two choices for the finals, UCLA
and Georgetown lost.  I should have gone with my first gut that Florida would
win it again. As I write, that's what I expect to happen tomorrow.
Ohio State, coming from a weak Big 10 conference, has continued to surprise me 
though, so maybe I am just totally wrong about them.
Billy Donovan is a wonderful coach and played the go-around just right with that
talented Florida squad.
Other than that, I'm an upset special kinda guy, so I am going to be at the bottom of
Jamie's group, as this was the most by the book tournament ever.
I think the reason (the only thing different) is the new NBA rule that has all the
top freshmen playing in college instead of the NBA.  
I think it is a good rule, even if it is unfair to the superstars, who make more money
if they go straight to the pros and obviously value the choice.

We moved the deadlines back yet again to get me back on track.  I really think I should be.
As most of you know, I moved one of my offices in February and it was FAR more disruptive
to my whole life than I had anticipated.  I'm still not recovered, but I think the
szine can stay on schedule.
The worst part was finding the time to do the mailings, so for the THIRD time on this page,
I will remind you, SIGN up for E-Mail alerts and mailings if you're playing here.
If you're not on the list, it WILL hurt you.

\bigskip

%Dave Partridge's unlisted phone number 603-672-2879 -- probably corrected!!!
%Tinamou players: Schwarzschild:  Graham Wilson (NO 
%but E-mails: grahamaw of home.com (or gwilson of dvnet.com)),
%Berry Renken, Heath Gardner
%Copernicus:  Warren Goesle, Heath Gardner, Art Schleinkofer, Bruce Reiff,
%Eric Brosius, Bob Dowrey
%Tour De Farce:  Jim Burgess, Eric Brosius, Warren Goesle, Sara Reichert,
%Phil Reynolds, Rick Desper
%Milk and Cookies: Jim Burgess, Warren Goesle, Sara Reichert, Phil Reynolds,
%Rick Desper, Richard Weiss, John Schultz
%Who's Your Buddy:  Sara Reichert, Phil Reynolds, Art Schleinkofer, 
%Brad Wilson, Rick Copeland, Karl Muller

The postal sub price is still
\$1.50 per issue in the US and Canada,
with double that for other foreign subbers(or \$3.00 per
issue sent airmail).
Players in current games and standbys will
continue to get the issues for free, and future game starts 
(except for Nuclear Yuppie Evil Empire Diplomacy, which is free) cost 
\$20.00 (\$15.00 for a life of the
game subscription and \$5 for the NMR Insurance.
Anyone may play in subszines 
for free and just jack up the issue page count. 
See the revised game start announcements below!

Check out the connections in the Diplomatic Pouch with all of
the information you need to play Diplomacy on the Internet at:
http://www.diplom.org/DipPouch/

I also have taken over the Postal port/DipPouch/Postal

\noindent and {\it TAP} on the web is there at:
http://www.diplom.org/DipPouch/Postal/Zines/TAP/index.html

where the szine resides in html format. 
Presently, issues from \#190 to the current issue
are there, and I will be updating the back issues gradually someday. 
Also, check out Stephen Agar's more extensive efforts at:
http://www.diplomacy-archive.com and http://www.diplomacy.co.uk
 
Peter Sullivan's subszine is out of stasis, and all the
back issues can be accessed via :

http://www.burdonvale.co.uk/octopus/index.html.

Peter is now back.
Rip Gooch is probably permanently missing.
Dave Partridge had been picking up the choo-choo
game slack.
Contact Dave
at rebhuhn of rocketmail.com for more info on getting into choo-choo games.
And Andy York has been my most frequent subszine guest lately!!!
He's been in every issue, thanks, Andy!!!

The {\it TAP} mailing list has moved!
It now is even BETTER protected than it was.
I even have a bit of trouble posting to it.
To post to this list, send your email to: tap of diplom.org.
But this is completely moderated, it won't go out to the list unless
I approve it.
In general, I intend to keep traffic down to just the szine, as we've
been doing and I'll put your LOCs in here.
I {\bf EXPECT} all players to be on this list, especially those of you who
are from foreign countries!!! 
You need this to find out when the szine is up on the web to check in on results.

General information about the mailing list is at:
http://www.diplom.org/mailman/listinfo/tap

You can sign up from there, or send E-Mails to:
Tap-request of diplom.org;
with the word `help' in the subject or body (don't include the
quotes), and you will get back a message with instructions.
You must know your password to change your options (including changing
the password, itself) or to unsubscribe.  
Normally, Mailman will remind you of your diplom.org mailing list
passwords once every month, although you can disable this if you
prefer.  This reminder will also include instructions on how to
unsubscribe or change your account options.  There is also a button on
your options page that will email your current password to you.
A big, big thank you for Millis Miller for setting this all up!!

\bigskip

\centerline{\bf THE SEARCH FOR ERIC JUST -- JEFF KEY IS FOUND!!!}

\smallskip

Edi Birsan has found Jeff Key!
Thanks, Edi, and Edi is donating his \$25 to a fund to get New England area
players to World DipCon, and I'm adding to it.
If you're here in New England and going to World DipCon this summer, apply to me!
And since Jeff mentions Eric Just, let's find him too!!

\bigskip

Feel free to spend the time looking for some of the backlog.
Let's get Margaret, Derek, Sylvain, Steve, Ed, Tom, Gregory, and 
ESPECIALLY Kevin found too!!!
This is a regular continuing feature of the szine
and I will be introducing a new ``search for'' every five issues.
Moreover, you can win a \$25 prize for finding some previous
target who went unfound in the original \$50 period.
That means that if Margaret Gemignani or 
Steve Heinowski or Ed Henry or Tom Hurst or 
Gregory Stewart or Derek Nelson or Sylvain LaRose or John Smythe
is ``found'' from now on it is worth \$25.

\bigskip

Winners will receive credit for Dip hobby activities
that I will pay out as requested by the winner.
Subscribe to szines here or abroad, run your
own contests, publish a szine, finance a web page, 
GO TO A DIPLOMACY CONVENTION or whatever.
Spend it all right away or use me as a bank to cover hobby activities
for years.
What must you do to win?
Get me a letter to the editor for {\it TAP} from the person we're
searching for.

This is very important, just finding them doesn't do it.
They have to write me a letter.     
The final judge as to the winner of any contest will be the target 
himself and I reserve the right to investigate the winning entry.
When you find someone I'm looking for, you should ask him to send me a 
letter for print that includes a verification of who ``found'' him.
%Michael Swift, Mike Stewart, and 
%Jason Yarbrough , Tim Stabosz, 
%Eric Ozog has $25
%Leslie Obata is owed $25
%Derek Nelson, winner of the first postal game in Graustark.  I last saw him
%at the '76 DipCon in Baltimore.
%Charles Wells, former publisher
%John McCallum, former publisher (Brobdignag, SerenDip, etc.)
%Dan/Charles Brannan, former publisher (Wild 'n Wooly)

\bigskip

{\bf Edi Birsan (Mar 22, 2007 12:03 AM)}   

Jeff;
Hope this gets to you.
How is my good friend Mary Ann and her wonderful fried chicken recipe?
I am now in the San Francisco Bay area, still married to Carol and a Grandfather twice over.
I still play Diplomacy and recently your name come up in a search for the golden oldies...
Are you still playing?
I know that you got into the Civil War boat era with Ivan Travenchiek but other 
than that I sort of lost track of you.
So what is up?

\centerline{Edi Birsan, EdiBirsan of astound.net}

\bigskip
 
{\bf Jeff Key (March 22)}

LoL... Mary Ann and I invited Edi down to the Jersey shore from the Big Apple.  
If I remember correctly that was the first time he had been out of New York City.  
We met his bus, loaded him in our car and took off for Youngstown, Ohio... 
he didn't know that we were planning a cross-country trip.  
``A great time was had by all" and that was the start of Edi's legendary travels.

{\it ((Congratulations, Edi, you win} \${\it 25.))}

\bigskip

{\bf Edi Birsan (Thursday, March 22, 2007 3:34 PM)}

Jim: 
Use the money to start a Boston travel fund for young people.
Jeff was instrumental in getting me to DipCon 2 and helping me to start 
my traveling Diplomacy career.

{\it ((Better than that, for that reason, I'll triple it for} \${\it 75 and focus it on getting a 
young New England area dipper to World DipCon this summer.
If anyone here wants to apply, let me know!))}

\bigskip

{\bf Edi Birsan (Mar 22, 2007 6:22 PM)}   

It was the first time that I left NYC for Diplomacy, but I had been 
out of NY for other things (mostly family disasters) prior to that.

\centerline{Edi Birsan, EdiBirsan of astound.net}

\bigskip
 
{\bf Jeff Key (Mar 22, 2007 7:25 PM)}   
   
If YOU say so, Edi, I'll believe you but that's not the way 
I choose to remember it!  $:->$  I remember you asking what 
a tree was as well.... :-)

\bigskip
 
{\bf Edi Birsan (Mar 22, 2007 8:47 PM)}   

Trees were a bit of a shock, but those cow things were 
rather a disgusting display ... and they move.  
 
{\it ((Jeff, so do you remember how long it has been since you played
Diplomacy FTF at a gathering?  Must be almost 20 years??  You used to
play a lot in the NYC crowd, didn't you?
And, we still talk about the Key and Key Lepanto openings, they still
raise quite a ruckus when they are tried.))}

\bigskip

{\bf Jeff Key (Mar 23, 2007 10:33 AM)}   

Jim,
Actually, I think I only played one face-to-face Diplomacy game in NYC.  I
remember meeting John Boardman there (weren't you there as well, Edi?).
Most of my face-to-face was in Oklahoma City and at various DipCons around
the country... Youngstown, Lake Geneva, Chicago, Dallas (I actually won that
one), etc...  The last face-to-face game that comes to mind would have been
in Oklahoma City about 1985.

Eric Just once published that the strongest weapon I had was my reputation
for honesty... that I could be counted on to keep the letter of any
agreement I made.  I always felt that reputation was what enabled me to play
the Lepanto Opening so many times so successfully.  I always got a kick out
of the expression on the Turkish player's face when he/she realized what was
happening.  That said, I still feel that Austria-Hungary was my favorite
position to play because I always felt that it was the most difficult.  I
cannot remember ever letting an Italian player try a Lepanto Opening with me
as A-H!

\centerline{Regards, Jeff}

\bigskip
 
{\bf Edi Birsan (Mar 23, 2007 10:46 AM)}   
   
Yes, the game you played in NYC was with Boardman as I recall.  In fact I think it was at
Boardman's place in Brooklyn.

\centerline{Edi Birsan, EdiBirsan of astound.net}
 
\bigskip

{\bf Jeff Key (Mar 23, 2007, at 8:49 AM)}

Good morning Edi, you are up early.
Thanks, that verifies my memory as well.  And you were there, correct?  That is where and when we met.

\centerline{Regards, Jeff}
 
\bigskip

{\bf Edi Birsan (Mar 23, 2007 11:01 AM)}   

Sounds right...

\bigskip

{\bf Jeff Key (Mar 27, 2007 10:49 AM)}   
 
Jim,
My introduction to Diplomacy was, in fact, an accident.  In one scene of the movie 
``The Mouse that Roared," all the diplomats were sitting around outside the borders 
of Grand Fenwick waiting to get in and playing a board game called ``Diplomacy."  
That looked interesting so when I saw the game that summer of 1959 at Foley's 
in Houston I immediately purchased it.  I was initially disappointed to find that 
it was a different game and required seven players.  Flash forward a bit.  
I was at Oklahoma City University and was able to introduce a group of my 
friends to the game.   We became regular players.  By 1967 that group had 
scattered to the four winds and I was in the Army.  Eric Just, one of the original 
members of the group, came up with the original idea (for us) of playing 
Diplomacy by mail... after all, there was no form of luck such as a die roll 
involved.  We ended up with several games in progress before we eventually made 
contact with mainstream postal Diplomacy.  The rest is history.

\centerline{Regards, Jeff, Sieffre of sbcglobal.net, 3505 Elgenwood Trail, Arlington, TX 76015}

{\it ((Thanks, Jeff, great.
It inspired me to seek out Eric Just (famous for Just's Right Hand Rule) next.
You get a free lifetime sub from me for being found.))}

\bigskip

\centerline{\bf INTERNATIONAL SUBSCRIPTION EXCHANGE NEWS}

\smallskip

John Harrington and I have agreed to close the ISE.
In this age of PayPal, the traffic on the ISE had fallen almost to zero,
and what was left almost entirely was me facilitating orders of 
Breaking Away and John's other Fiendish Games.
So, I'm still going to help John out with that, but there will be no
ISE.

\bigskip  

\centerline{\bf WORLDMASTERS04 SECTION}

\smallskip

See http://www.worldmasters.net/wm04/
for details on progress on the WORLDMASTERS04, the Semifinals have now begun.  
Some semifinal notables include: Egg Ferreira, Buffalo Bartalone, Lee Simpson, 
Joe Janbu, Sebastian Beer, Doug Moore,
Jerry Fest, Twerg O'Donnchu, Tim Sweeney, Dave Partridge, Glenn Ledder,
Adam Silverman, Toby Harris, and Thomas Franke.
This is one of the deepest semifinal fields for this great tournament 
that I've seen, with representatives from nearly all of the world's
hobby communities.
Actually, the Semifinal games began in October.
I was wondering why I hadn't seen anything on progress in these games,
and that's why.
More on that next issue!!!
Thomas Franke and David Partridge are in a game together that seems
on first glance to be the weakest in the rest of the players.
So my first thought is that one of those two will have a slot in
the finals.
I am getting raked over the coals for it, but I just ended a game
in a three way draw between me, Thomas, and Ray Setzer that I might
have had a chance in ekeing out a win mostly because Thomas asked
for it to end so he could focus on this semi-final.
Sorry, David, but I had to do it.....
Of course, after saying that, David Partridge is in England getting beaten
on by Guy Thomas in France, who is allied with Thomas Franke in Italy.
But Italy has a Juggernaut bearing down on him from Mike Tombu and
Julio Cardoza.
And Toby Harris just got crunched in his game where he is Turkey, but
I don't count him out yet, he has more lives than a cat!!
But never mind, I don't know how ANY of this will turn out!!!
Doug Moore is doing pretty well as Russia in his game so far, but
Russia can always be crunched after doing well early.
Buffalo is doing pretty well in his game as France taking down Germany
and now attacking Adam Silverman's England, I think, that part is still
developing.

I've joined the Yahoogroup WM04-Chat where some of this
discussion is happening.
You can join too!
However, this forum has been very, very quiet, I hope it picks up with
semis, maybe I'll have to start some discussion.
I had to go the main Worldmasters site at www.worldmasters.net/wm04/ to
find some of these results.
The new Tournament rankings for FTF also are out there that supercede the
ones that were on 18centres.
Go check out:

http://eurodip.nuxit.net/php/ranking/index.php?lang=Ang

It ranks 4792 FTF players and is the most complete known compilation of FTF play
ever in the hobby.
You really want to check it out.
Poor Eve Smith ends up 4791st, having been in 33 tournaments in the last ten years,
an achievement in itself!
And of course Don Del Grande is down near the bottom at 4787th, off of 13 tournaments,
two of them in Australia.
For having the Don Challenge Cup named after him, he didn't do THAT badly in his
tournaments Down Under, better than I'd been led to believe at 54/78 and 34/57
And Frank Johansen is a well deserved \#1.
And I'm amazingly in the top quarter with a ranking of 1154, accurately reflecting
the nine tournaments that I know I've been to (i.e. I don't see any missing).
Yann Clouet (if I counted right) has been to 95 tournaments, I'd be surprised if
someone surpasses him in number, and he ranks 11th.
Guaranteed to be a fun browse....

\bigskip

\centerline{\bf DIPDOM NEWS SECTION (with letters)}

\smallskip
 
Obscure and not-so-obscure ramblings on the state of the hobby
and its publications, custodians, events, and individuals with
no guarantee of relevance from the fertile keyboard of Jim-Bob,
the E-Mail Dip world, and the rest of the postal hobby.
My comments are in {\it italics} and {\it ((double 
quotation marks))} like this.
{\bf Bold face} is used to set off each individual speaker.
I should also make a note that I do edit for syntax and spelling
on occasion.

%A VERY light discussion is taking place that will address what 
%stance we (the hobby) should take (proactive in some way for sure) 
%toward Hasbro, the new owners of the rights to Diplomacy.
%More on this will be forthcoming, but it looks like Hasbro might
%have its version of Diplomacy on the market for the Christmas
%season and they actually will be employing ``play-testers''.
%No word on precisely what this means yet, could it mean that
%they will offer a series of ``official'' variants?
%Stay tuned....
%If you want to be part of the discussion, send the MESSAGE:
%
%subscribe hasbro
%
%to majordomo of diplom.org, it works just like the tap mailing list
%described below.  Sending messages to hasbro of www.diplom.org
%sends the mail to the whole list.
%The big news this time is the beginning of the breakout of
%Hasbro into official contact with the hobby.

The game Diplomacy is a copyrighted product owned by Hasbro and all
reproductions or other use of that material in this szine is intended to
be personal use and not infringe on those rights in any way.
All reproductions are done at a heavy financial loss to the editor
and thus are without the remotest possibility of commercial intent,
except to promote THE game, the Game of Diplomacy, which you all 
should purchase from Hasbro or other duly licensed distributors.
 
Stephen Agar has matched the Hasbro rule lists 
and more with some of the even older
rulebooks.
Check these out if you like:

http://www.hasbro.com/default.asp?xcc\_gameandtoyinstructions

http://www.hasbro.com/instruct/Diplomacy.PDF

http://www.hasbro.com/instruct/Diplomacy(OlderVers).PDF

Nice of them to make BOTH of these available.
And all seven different US rulebooks for Diplomacy can now be found here
courtesy of Stephen Agar (relatively new address for this):

http://www.diplomacy-archive.com/diplomacy\_rules.htm

%1: The Reformer, who seeks perfection (crusading type).
%2: The Helper, who seeks love (altruistic type).
%3: The Performer, who seeks status (competitive type).
%4: The Individualist, who seeks an identity (imaginative type).
%5: The Investigator, who seeks knowledge (analytical type).
%6: The Loyalist, who seeks security (ambivalent type).
%7: The Enthusiast, who seeks gratification (thrill-seeking type).
%8: The Leader, who seeks self-sufficiency (dominant type).
%9: The Peacemaker, who seeks contentment (accommodating type).
%See http://graphics.lcs.mit.edu/~becca/enneagram/
%new test at: http://www.9types.com
%My scores in order were: 9, 13, 15, 7, 15, 6, 17, 18, 14.
%Robert Lesco's Marco Poll, the defacto poll of the
%North American hobby since the Runestone is pretty much
%officially dead, continues to collect votes.
%This is an official {\it TAP} approved poll.
%Here are the particulars on the Marco Poll:
%Vote for your top five in each category and you can't vote (or at least
%it won't be tabulated) for Robert Lesco or his szine, which I don't see.
%I will send this to Robert and offer him a trade.
%The deadline is September 1st and either send your ballot to marcopoll of yahoo.com
%or mail to Robert Lesco, 49 Parkside Drive, Brampton, Ontario, CANADA  L6Y 2H1.
%For identification purposes, Robert would like you to identify yourself both
%by name and by affiliation (a game you play in or a szine you sub to).
%Here are the categories this year (I like some of the new ones!!):
%1) Favourite {\it ((Hey, what, he's Canadian, yeah.))} Zine  {\it ((What's a zine,
%shouldn't that be Szine???))}
%Backstabbers United Monthly, Costaguana, The Diplomatic Pouch, Absolute, Vertigo
%2) All Time Favourite Zine {\it ((Szine))}
%Magus, Europa Express, Thirty Miles of Bad Road, Perelandra, North Sealth West George
%3) Best Diplomacy Player
%John Quarto von Tivadar, Edi Birsan, Mark Fassio, Chris Martin, David Partridge
%4) All Time Best Diplomacy Player
%Edi Birsan, Mark Fassio, Kathy Caruso, Rod Walker, Hohn Cho
%5) Best GM
%Malcolm Cornelius, Tim Miller, Tim Richardson, Conrad von Metzke, Doug Massey
%6) Player Who Writes the Best Letters/E-Mails
%Don Williams, Richard Weiss, Mark Fassio, Toby Harris, Cal White 
%7) Folded Zine {\it ((Szine))} You Miss the Most
%Magus, Diplomacy by Moonlight, Le Front du Liberation de Diplomacy, Kathy's Korner
%8) Favourite Variant
%Modern, Nuclear Yuppie Evil Empire Diplomacy, Woolworth, Spy Diplomacy, Colonia

\bigskip

\centerline{Check out current and back issues of {\it Diplomacy World} -- Yahoogroup diplomacyworld}

Also, I need any Hobby Award Nominations NOW (!!!) for the :

\noindent The 2005 and 2006 Don Miller Award for Meritorious Service;

\noindent The 2005 and 2006 Rod Walker Award for Literature;

\noindent The 2005 and 2006 John Koning Award for Player Performance;

\noindent The 2005 and 2006 Fred Hyatt Award for GM Performance;

or

\noindent A 2005 and 2006 Kathy Byrne Caruso Award for Lifetime Achievement (if warranted).

The Hobby Awards Committee is Jim Burgess (Chair and Treasurer),
Fred Davis, Jr., Melinda Holley, Gary Behnen, Jamie Dreier,
Paul Kenny, Mark Stretch, and Robert Lesco.
I was going to publish the award ballot for this year 
in this issue, but I realized that I really just had to get this out first and
then do that.... and then, well, REAL SOON NOW!!!
And when I do, I'm going to give out two sets of awards and get caught up for the 
missed year, that seems to make the most sense.  
Committee.... you will be hearing from me soon!
This also fell apart with my move, but I will get this out next issue come hell or high water.

\bigskip

{\it Diplomacy World} Issue Deadline is now:

\noindent Deadline Spring 2007, Issue \#97: May 1, 2007

I'm really pleased that former editor Doug Kent has agreed to come 
back and get this back on track and get us to \#100.
Thanks, Doug!
We're putting things together, but if any of you want to write anything,
contact Doug!

%\noindent Final Hobby Awards Ballot for 2004, nominations now to:
%burgess of world.std.com
%
%The qualifications for the Kathy Byrne Caruso Lifetime Achievement 
%Award are that the awardee must have been: (1) Active in the 
%Diplomacy Hobby in at least Three Separate Decades; 
%(2) Multidimensional in their Contributions to the Hobby 
%(e.g. writing, playing, publishing); (3) Taking Retirement or 
%Semi-Retirement from the Diplomacy Hobby; and (4) One of the 
%Hobby’s Unique Personalities Worthy of Being Remembered as Long 
%as THE Game Continues to be Played.  This award need not be awarded
%each year, but only as worthy candidates are identified.  The only
%past honoree is the late Richard Sharp.
%
%The other award categories are self-explanatory:
%
%\noindent Nominees for the 2004 Don Miller Award for Meritorious Service
%
%\noindent Nominees for the 2004 Rod Walker Award for Literary Achievement
%
%\noindent Nominees for the 2004 John Koning Award for Player Performance
%
%\noindent Nominees for the 2004 Fred Hyatt Award for GM Performance
%
%--- --- --- --- --- --- ---

Editorial Board for {\it Diplomacy World}:

\noindent  Doug Kent, NEW Lead Executive Editor!, 11111 Woodmeadow Pkwy 
\#2327, Dallas, TX  75228, dougray30 of yahoo.com 

\noindent Tim Haffey, 810 53rd Ave., Oakland, CA 94601 USA; trhaffey of
aol.com -- Ex-Lead Editor and Archives Editor

\noindent Jim Burgess, 664 Smith Street, Providence, RI 02908-4327, USA;
burgess of world.std.com -- Co-Editor and Publisher

\noindent Rick Desper, 5440 Marinelli Road, \#204, Rockville, MD  20852, USA;
rick\_desper of yahoo.com -- Demo Games

\noindent Dave Partridge, 15 Woodland Drive, Brookline, NH  03033, USA;
rebhuhn of rocketmail.com -- US Postal

\bigskip


\bigskip

\centerline{\bf MUSIC AND MOVIES SECTION (WITH COMMENTS ON OTHER ARTS AND SOCIETY)}
     
\smallskip

We're running a ``23 tunes'' contest here
(stolen blatantly from Mark Wightman and the late lamented {\bf The Sprouts of Wrath}.
If anyone would like to send me a tape or CD of their 23 (which was the original point)
that would be great, but I don't intend to require that.  I will be playing in the
sense that I'll be putting 23 tunes in, and you have to guess me, but I obviously
won't score points.
Send commentary with your choices, and we'll see if people can
guess who you are!!!
And already there is a LOT of diversity in defining tunes and styles, so 
BE CREATIVE!!!
 
%To encourage voting early, I picked five voters at random to receive five US
%dollars from me (either in cash or paid to someone for Dip stuff or to get
%a free tape).
%Tony Dickinson won the Round 5 prize, so we had three of the six Round 1 voters
%won and one of the three Round 2 postal voters who also got five chances to win.
%That showed the value of getting in early!!
%Voters in Round 1 were Mike Barno(\$5), Rick Desper (\$5), Tony Dickinson (\$5),
%Drew James, Heath Gardner, and John Harrington.
%Round 2 postal voters were John Schultz (\$5) Ian Moore, and Stan Johnson.
%Round 2 E-Mail voters were Scott Morris, 
%Warren Goesle, Peter Sullivan, and Michael Lowrey.
%Round 3 voters were Dick Martin, Richard Weiss, and Rip Gooch.
%Round 4 voters were Roland Sasseville, Jr. (\$5),
%Don Williams, Brent McKee, and Andy York.
%Round 5 voters were Mark Larzelere, Al Tabor, Jody McCullough, and that's it.
%We'll end up with a monster party tape at the end of it that I plan
%to segue and sequence and copy for distribution.
%The result will be a great New Millenium party tape -- we're going for 90 minutes.
%I've also been thinking that I should put this out on CD
%as truly emblematic of the new millenium.  
%I don't have the capability to do that quite yet, but I think
%I might by then.
%Any suggestions (or especially volunteers) on this front will
%be cheerfully accepted and could receive monetary payments!
%The CD way may still occur if someone steps forward and actually does it for me.
%So far, we have ``I Melt With You'' by Modern English; George Gershwin's
%``I got Plenty O' Nuttin' '' from {\it Porgy and Bess} in the 1957 concert
%recording with Ella Fitzgerald finishing off the vocals after Louis
%Armstrong blows and sings through the tune; Duke Ellington performing
%Billy Strayhorn's ``Take the A Train''; Frank Sinatra's ``New York,
%New York''; something from the B-52's;
%the original Van Morrison and Them version of ``Gloria'';
%The (English) Beat's 12 inch version of ``Save It for Later'' 
%ratchets things up to the next level (wherever you put it!);
%Buster Poindexter's ``Hot, Hot, Hot'' keeps you there;
%``Atomic Dog'' by George Clinton blows the doors off,
%and Koko Taylor cleans up singing Willie Dixon's ``Wang Dang Doodle''.
%After I get timings down, I'll choose exactly which songs below make the list.
%
%EXTRA SPECIAL B-52'S BULLPEN: (7) ``Love Shack'';
%``Rock Lobster". {\it ((A tie, a tie!!!!))}
%
%BULLPEN: (9) Nirvana -- ``Smells Like Teen Spirit";
%``Cumberland Blues'' -- the Grateful Dead.
%(8) ``Twistin the Night Away" -- Sam Cooke; ``In Between Days'' -- The Cure;
%``Mannish Boy" -- Muddy Waters; ``Shake, Rattle, \& Roll" -- Big Joe Turner; 
%``Proud Mary'' -- Ike and Tina Turner.
%(7)  ``I Wanna Be Sedated" -- Ramones; ``Twist \& Shout" -- Beatles.
%(6) ``Magic Carpet Ride" -- Steppenwolf;
%``Crossroads'' -- Eric Clapton; ``Play That Funky Music'' -- Wild Cherry;
%``I Fel Good" -- James Brown;
%``Radar Love'' -- Golden Earring; 
%Devo -- ``Whip It"; ``Echo Beach'' -- Martha and The Muffins.
%(5) ``Sing Sing Sing'' -- Benny Goodman; ``Rocking the Casbah'' -- The Clash; 
%Squeeze -- ``If I Didn't Love You"; ``Roadrunner'' -- 
%Jonathan Richman and the Modern Lovers.
%
%SPECIAL ROLLING STONES BULLPEN: (6) ``Paint It Black''. 
%
%SPECIAL TALKING HEADS BULLPEN: (9) ``Take me to the River".
%(4) the entire {\it Speaking in Tongues} record
%(special call for ``Road to Nowhere'').
%
%SPECIAL ALPHABET SONG BULLPEN: (6) ``YMCA" -- Village People. 
%
%SPECIAL DRUG MUSIC BULLPEN: 
%(8) ``Rd, Red Wine'' -- UB40.
%(6) ``Don't Bogart that Joint'' 
%-- Fraternity of Man; ``The Old Dope Peddler'' -- Tom Lehrer.
%(5) ``Cocaine'' -- Eric Clapton's version; ``Casey Jones'' -- the Grateful Dead.
%(4) ``White Rabbit'' -- Jefferson Airplane; ``Love Is the Drug'' -- Roxy Music.

\bigskip

\centerline{\bf {\it 23 Tunes Game}}

\smallskip

Here are the rules for 23 TUNES.  You send me three tunes for the first turn,
and then two tunes in each of the last ten turns for a total of 23.
If you missed the first turn, you can still catch up by sending five tunes next
issue, and guess on submitters to this issue.
I am also submitting my tunes.
After we're done, I'd like to exchange CD's/Tapes for as many of the tunes players
as possible, but this is not required.
I'll be sending the winner both my LAST 23 tune list and my NEW 23 tune list.
The winner is determined by having you guess each issue who submitted what list
(I will tell you who the submitters are).  For each list you get right, you get
a point, you also can win bonus points from me for really cool tune selections.
That's it, not complicated.
I hope by starting this up, we'll get more to join, five songs required to enter
late.
Playing this issue (guess who is whom by number, scores are in parentheses) 
is, in alphabetical order, 
Jim-Bob Burgess, Rick Desper (1), %Steve Emmert, Doug Kent, 
Dick Martin, %Jim Reader,
Richard Smith (3), Joakim Spangberg, %Brendan Whyte, 
and Brad Wilson (4).
The linking theme thing didn't seem to go over too well.
No one really figured out the true linking theme.  
Rick Desper was using Underground tube stops and songs with that as the title,
they were things like that.  
I'll let you guys talk a bit to each other on that with your guesses.
I have added some kind of comment on each tune.

WHAT I NEED: two more tunes (seven if you're joining up new, four if you NTRed (NO TUNES
Quite a number of you SAID you would join but haven't yet, so we'll get started and
put the pressure on you.
This part is a MESS and I'm getting this issue out and then will catch up next time.

\bigskip

{\bf Drew James (Thu, 29 Mar 2007 20:39:23 -0400)}

Jim,
Syracuse was completely hosed by the NCAA committee.  It made absolutely no
sense to take Arkansas, Illinois, or Stanford over SU.  I think we clearly
got a glimpse at how politics works on the committee.  It wouldn't have
bothered me as much if the last spots were taken up by mid majors rather
than average teams from power conferences who had representation on the
committee, while the Big East had none.  I'm hoping that Georgetown wins the
championship and SU becomes the last team to have beaten them -- and handily
at that.  To make matters worse, SU only received a 2 seed in the NIT and in
the South Region at that -- West Virginia got a \#1 seed over SU!  

{\it ((Well, to be fair, they did end up winning.
I think that was deserved, Beilein is turning into one of the game's great
coaches for that type of team.))}

Clearly the NIT was figuring that Arkansas would be the \#2 seed in the 
South and then just dropped SU into their spot.

{\it ((Good point, I think you're precisely right.  I guess the two committees
don't coordinate.))}

On the bright side I was able to go to 2 additional home games that were
incredibly entertaining.  What a difference it makes when the fans in the
best seats are the most rabid fans -- the ones willing to get on line early --
rather than the wealthiest fans.  A lot of fans called into radio shows and
said how they or their kids were able to see a game up close for the first
time ever from the first level of the Dome.  I enjoyed the fact that the NIT
games weren't commercialized.  Everything at the Carrier Dome is always
pre-programmed.  The same events -- be it promotions, the dance team, or
whatever -- happen at the same time outs in every game.  There was a lot of
negative publicity in Syracuse after the Notre Dame game (SU was totally
blown out) because the fans even booed the cheerleaders.   I hate it when
fans boo period, but a major contributing cause was that the cheerleaders
went on the floor to lead a cheer at a totally inappropriate time because
that was the pre-planned slot for that cheer.  The NIT games had no sponsors
or promotions and only cost \$10 for adults and \$5 for kids so lead one to
remember what college basketball was like before ESPN.  So, yes, I enjoy the
NIT games but I hope it is a long time before I have the chance to go again.

\centerline{Drew, kjames01 of twcny.rr.com}

\bigskip

{\bf Rick Desper (Mon, 2 Apr 2007 14:01:07 -0400 (EDT))}

OK, it's time for the annual ritual where Jim, Dave and I all pick
the Red Sox to do spectacularly well this season, while Goz laughs
at our deluded optimism.  But hey, we've been right at least once
in the past thirty years, which isn't so bad, is it?

So, let's look at this division by division:

AL East:
Yankees have monstruous hitting, even though ARod and Jeter are having
a spat, and bringing Pettitte back should help the pitching somewhat.
OTOH, they've lost Randy Johnson and Wang won't be as lucky this
season as he was last year.  (His stats were horrible for a 19-game
winner.)  The question with the Yankees in recent years has been
their age.  They are pretty much using the same cast of characters
that they did in 2000 (excepting Giambi and ARod), but most of them
aren't as good any more.   ARod has been exposed as a postseason
liability, and Giambi is only really scary when he's on the juice.
And Sheffield is gone.

{\it ((I agree with all this and think they will hugely miss Sheffield for the
balance he offers.))}

Meanwhile, the Red Sox have picked up the hottest young pitcher in
baseball in Dice-K.  I'm thinking that, at the end of the day, Matsuzaka
will be a legitimate ace at the Santana/old Pedro level.  In addition
they'll have Schilling and Beckett, and we can hope both pitch better
this season than last.  At least with Beckett that seems like a
reasonable proposition.

{\it ((Dice-K has an Ace mentality, which is half the battle.  No starter on
the Yankees now has that mentality, the Blue Jays have more of that now
than they do -- Halladay.  I think Beckett is going to have a monster season
too.  And I think Julian Tavares will surprise people by being the best
fifth starter in the league.))}

Rather than try to predict the finish, I'll put both of them in the playoffs.

The Blue Jays have one tremendous starter in Halladay, a good starter
in Burnett who gets injured too much, and a good deal of hitting, but
I'm still not scared of them.  (Except they seem to have a habit of
knocking Red Sox pitching around.)  The Os and Devil Rays will be also-rans.

{\it ((I think the Yankees will take the big third place fall this year.
Boston, Toronto, New York, Baltimore, Tampa Bay.
This is not wishful thinking, I really think their pitching will be
another order of magnitude worse this year, and it is even possible that
they'll burn out Mariano Rivera and that would be certain death.))}

AL Central:
Word is that this is the loaded division.  I'm still going to take a
Show-Me attitude towards the Indians, though.  Writers have loved them
in the past two offseasons, but they haven't done much.  The White Sox
are a bit concerned because Jose Contreras and Freddy Garcia regressed
a bit in the direction of their historical levels of mediocrity, after
being lights-out pitchers in 2005.  The Twins have the best pitcher in
baseball and a great closer, and a good deal of hitting, but I'm going
to go with the young arms of the Tigers here. Let's pencil them in for
the playoffs.

{\it ((I think Detroit will be helped immensely by Sheffield as the Yankees
suffer from losing him.  Most of the rest of this I agree with, Detroit,
Minnesota, Chicago, Cleveland, and poor Kansas City.  I don't think
the second place team here makes the playoffs, I think the other team
will come from the West.))}

AL West:
Going to ride with the Angels again.  I'll look great until the As
make their annual September run.

{\it ((I think Texas will be in there too.  But I see the Angels and A's both
making the playoffs, probably Angels first, then Texas and Seattle.
It will take a while to get adjusted, but Piazza will be a steal, and the
A's STILL have the best rotation in the division.))}

NL East:
Mets, Mets, Mets.  They were the only team in the NL to win more than
90 games last year, and they won 97.  I'll just pick them out of
inertia, presupposing they won't fall off very much.  Sure Pedro's
a year older, but Glavine is still pitching decently and they have a
ton of hitting.

{\it ((Pedro will not do much this year, but might in the playoffs.
The Mets are a bit of the leader by default, I don't think they have
that good a team, but there aren't any stunning teams in the NL.))}

Curiously, the Braves seem to have stopped their run of success
completely.  I don't quite get what the ownership's plan is, but they
are not stacking up the talent like they used to.  Phillies are a popular
Wildcard pick, but I'll defer that question for the moment.

{\it ((Mets first, but I disagree with you, Atlanta will finish second and
capture the Wild Card.  I think the Phillies, Washington, and Florida
will be bring up the rear in any order, probably the Phillies third,
but not sure.))}

NL Central: I'll go with the Cardinals.  They had a weird season
last year, as a number of their starters completely fell apart in
midseason.  But when they replaced them for the postseason, the
talent showed.  I'll pick them to win the division again, and with
more wins than last season.

{\it ((Cardinals for sure, lots of questions after that, very close, no
one except Pittsburgh is way out of it.
This ``large division'' is so hard to pick the exact finish.))}

NL West: I'll go with the Dodgers again.

{\it ((Dodgers will win, Giants will be second, Padres third, Diamondbacks
fourth, and Colorado fifth.))}

Well, that's a bit lame, having picked all the NL division winners
of last season to repeat.  I guess that means I'll have to pick the
Padres to miss the playoffs.  Well, I don't want to pick the Phillies
because they've been predictable in recent years in underperforming.
So I'll take the Marlins and their young Red Sox cast-offs to be the
Wild Card.

{\it ((I agree that the Marlins might be good, but I really think Atlanta
will surprise.))}

\smallskip

playoffs:

Red Sox over Angels  {\it ((Sure))}

Tigers over Yankees  {\it ((Tigers over Toronto))}

Marlins over Cardinals  {\it ((Atlanta over Cardinals))}

Mets over Dodgers  {\it ((Sure))}

\smallskip

LCS:

Red Sox over Tigers  {\it ((Yes!))}

Marlins over Mets    {\it ((Mets over Marlins))}

\smallskip

WS:

Red Sox over Marlins  {\it ((Red Sox avenging 1986.))}

\smallskip

Wow, I have to say I'm as surprised as anybody else that I
picked the Red Sox to win the World Series.  But keep this in mind:
last year I picked the Cardinals at this point, and I was right!

But it'll really suck if Hanley Ramirez is the World Series MVP.

\centerline{Rick, rick\_desper of yahoo.com}

{\it ((Could happen, even the disaster of Hanley Ramirez....))}

%
%\bigskip
%
%\centerline{\bf SPY DIPLOMACY (Variant, revised Dec. 1986)}
%
%by Jim Burgess
%
%Rules:
%
%1) Unless otherwise specified, the standard rules of Diplomacy apply.
%
%2) Players receive adjudications for their own armies and fleets, but not
%the armies and fleets of other powers.  Similarly, each player sees only
%his or her own section of the supply center chart.
%
%3) In addition to the standard units, an unit called a "spy" is added.
%
%     A) Each of the seven powers begins with a spy in each home supply center.
%
%     B) Spies are supplied only by home supply centers (i.e. Russia may have
%as many as four spies at a time while other powers are limited to a maximum
%of three).
%
%     C) Spies are "built" and "disbanded" in Winter seasons at the same time
%as other units.
%
%     D) There is no limit to the number of spies that may be present in any
%province and spies may be ``stacked" with armies or fleets (exceptions are
%listed in Rule 6).
%
%4) Spy Reports
%
%     A) Spies report the location and nationality of armies and fleets in
%the province they occupy and all adjacent provinces immediately following
%the standard Winter, Spring, Summer, and Fall seasons (i.e. just prior to
%the spy movement seasons).  Spies can differentiate between units in retreat
%and successful attackers when two units "occupy" a province.
%
%     B) Spies also report the nationality of spies in the province they occupy
%and the presence (but not nationality) of spies in adjacent provinces at the
%same time.
%
%5) Movement of Spies
%
%     A) Spy movement follows the collection of spy reports, so orders to spies
%may be made conditional on any information gathered by spies on opposing troop
%movements or the adjudication of one's own units.
%
%     B) Spies move after each of the following standard seasons: Winter,
%Spring, Summer, and Fall (note that all spy movements PRECEDE Autumn
%retreats), beginning with Winter 1900.
%
%     C) Spies move as armies do with the following exceptions:
%
%          a) Spy movements cannot be stood off by movements of any other unit.
%
%          b) Spies may be convoyed by fleets of any power during any of the
%four movement seasons for spies.  The convoy orders for fleets in these
%seasons must be ordered by their owner in the usual fashion or else the spy
%convoy movement fails of execution.  Fleet convoy orders for spies may be made
%in addition to regular Spring and Fall moves (note, however, that the fleets
%themselves never move during spy movement seasons).
%
%          c) Spies may also be "picked up" and carried by fleets of any
%power. Embarkation and debarkation are moves that must be made during a
%spy movement season and "permission to board" is not required.  Embarkation
%consists of a movement from a land province to an adjacent sea province
%containing a fleet.  Debarkation consists of a movement from a sea province
%containing a fleet to an adjacent land province.  A spy may not "switch
%fleets in midstream".  Once boarded, a spy may only get off by debarking.
%After boarding a fleet, the spy moves with the fleet during regular movement.
%A spy may not debark from a fleet awaiting retreat (e.g. if a fleet carrying
%a spy is dislodged in Spring, the spy may not debark until the spy movement
%season following the standard Summer retreat season).
%
%6) Spy Mortality
%
%     A) This rule will outline the circumstances under which spies may be
%captured or killed.  Spies may be disbanded in Winter seasons at the same
%time as other units to meet the requirement that a power may not have more
%spies than the number of currently held home supply centers and spies are
%annihilated when they are on board a fleet that retreats off the board.
%Otherwise, spies may only be removed from the board (there is no difference
%in the game between capturing and killing a spy, but players should feel
%free to delineate between the two states in writing press) immediately
%following the four spy movement seasons.
%
%     B) Spies killed or captured in a given season do not submit written
%spy reports for that season, though their final movement may have been
%made conditional on that spy report.  Players may never know for sure how
%a spy was lost, just as in real life.
%
%     C) Spies are "killed" by being assassinated by other spies.  When a
%spy moves, he or she may attempt an assassination, specifying the nationality
%of spies to be executed if discovered.  Each spy may hunt for only one
%nationality in each of the four seasons.  The following rules and examples
%will govern the adjudication of assassinations:
%
%          a) A spy may attempt an assassination without moving (for instance
%if the target is in the same province).  In this case, any spies of the target
%nationality that end the spy movement phase in that province are assassinated
%with one exception.  If the spy attempting the stationary assassination is
%himself or herself assassinated by a moving assassin then that spy
%assassinates no one in that season (not even a potential target other than the
%one that assassinates that spy).
%
%          b) A spy attempting a moving assassination (may include a move of
%embarkation or debarkation from a fleet) is always successful in assassinating
%spies of the target nationality that finish the spy movement phase in the
%province that the spy moves to.  This makes "mutual assassinations" possible.
%
%          c) Example: French spy is on board a French fleet in the Channel.
%An English spy is in London.  Both powers specify assassination attempts
%against the spies of the other.  If the English spy embarks on the French
%fleet in the channel (remember that embarkation does not require the
%permission of the fleet being boarded) and the French spy doesn't move, the
%French spy is killed, but the English spy isn't (he may be immediateIy
%captured, however, see part D).  If a German spy is also on board and the
%French spy tried to assassinate the German spy, that operation would fail
%as well. If the French spy debarks to London at the same time, the two spies
%"pass in the night" and neither is killed.
%
%     D) Spies are "captured" by opposing armies and fleets.  Players may
%attempt to capture spies, specifying the nationality of spies to be captured
%if discovered.  Each army and fleet on the board may search for spies of one
%nationality in each of the four seasons.  The following rules and examples
%will govern the adjudication of attempts to capture spies:
%
%          a) Players may specify a nationality to be hunted separately for
%each unit or they may issue blanket searches to be applied to all units.
%
%          b) At the end of the spy movement phase, any spies of the
%nationality specified in the same province are captured (for example, if
%the French player specifies a hunt for English spies on their Channel fleet
%in the above example, then the English spy is captured).
%
%          c) Players are informed when they successfully capture an opposing
%spy.  Note that the "owner" of the spy, however, is not informed of the
%capture.  Communication just is cut.  This rule is the only exception to the
%generaI rule that armies and fleets are blind.  It is possible to play the
%game without allowing capture of spies by armies and fleets if one wishes
%to allow freer movement of spies (i.e. RuIe D may be ignored).
%
%7) It is suggested that the game be adjudicated in four separate seasons
%in the following order:
%
%     A) Spring: (for Spring 1901 this sequence is preceded by a spy movement
%phase (no spy reports are necessary) followed by assassinations or captures)
%
%          a) Standard movement by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     B) Summer:
%
%          a) Standard retreats by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     C) Fall:
%
%          a) Standard movement by fleets and armies, adjudication reported
%only for one's own units
%
%          b) Spy report phase, spies collect information
%
%          c) Spy movement phase, spies move according to Rule 4
%
%          d) Spy assassination and capture phase
%
%     D) Winter:
%
%          a) Standard Autumn retreats by fleets and armies, adjudication
%reported only for one's own units
%
%          b) Standard Winter builds and removals, also applies to spies
%
%          c) Spy report phase, spies collect information
%
%          d) Spy movement phase, spies move according to Rule 4
%
%          e) Spy assassination and capture phase
%
%\medskip
%
%These rules have been produced by Jim Burgess (with helpful comments from
%Bernie Oaklyn and Dick Martin).  Permission is granted to reproduce and use
%these rules without restrictions.  The author would be interested to hear
%any comments and criticisms regarding any aspect of the play of this variant.
%The rules have been deposited with the North American Variant Bank.  They are
%also available from the author for the cost of postage or free by E-Mail.
%
%\bigskip
%
%\centerline{Wing Rules} 
%
%1.A wing unit can move over both land and water spaces. 
%  
%2.A wing unit can support actions in any space adjacent to the one it occupies. 
%   
%3.A wing can give, receive and cut support in the same way as armies and fleets. 
%   
%4.A wing unit cannot convoy or be convoyed. 
%
%5.A wing unit cannot capture an SC, but instead blockades it: 
%        
%\indent\indent 5.1.A blockade occurs when a wing unit occupies the SC of 
%another player in a fall season. 
%        
%\indent\indent 5.2.The player who owns a blockaded SC does not count 
%it when counting his total number of SCs. 
%        
%\indent\indent 5.3.A blockade ends as soon as the wing unit no longer occupies the SC. 
%        
%\indent\indent 5.4.Builds only take place in the winter phase, just as in games without wings. 


\vfill\eject

\centerline{\bf {\it THE ABYSSINIAN PRINCE} GAMES SECTION}

\smallskip

``So I called up George and he called up Jim, I said let's make a deal.

He said he'd talk to him.  Gonna start a church where you can save yourself,

You can make some noise, When you've got no choice...

You told me useful things, what people think of me, I guess I should thank you.

It's true, then I agree... I'm all alone, I've got no choice,

I'm all alone, I've got no choice."

From ``Got No Choice" by the incomparable Mark Cutler, from the CD
{\it Mark Cutler and Useful Things}.

\smallskip

\indent If you want to submit orders, press, or letters by E-Mail,
you can find me through the Internet system at
``burgess of world.std.com''.
If anyone has an interest in having an E-Mail address listed so people
can negotiate with you by computer, just let me know.
FAX orders to (401) 277-9904 if you let me know in advance to be sure
the fax machine is set up. 

I am continuing to note cut or failed support orders with a 
small ``s'' instead of a capital ``S''.
This will make it easier on the E-Mailed version of the szine to see
what happened, since the italics don't show there.
The italics DO show on the web page just fine.

\indent Standby lists:

Mike Barno, Dick Martin, Brad Wilson, Jack McHugh, Glenn
Petroski, Steve Emmert, Mark Kinney, Vince Lutterbie, Eric Brosius,
Paul Rauterberg, Bob Osuch, Doug Kent, Sean O'Donnell, Vern Parker,
Heath Gardner, Paul Kenny, and Jeff O'Donnell
stand by for regular Diplomacy.
%I am willing to take over for NMR or start new-Diplomacy.
%Vern Parker
%337 Winter Hill Pl.
%Powell, OH 43065
%VSParker of aol.com
%614-402-5139

Let me know if you want on or off these lists, especially OFF.
Standbies get the szine for free and receive my personal thanks.

\bigskip

\centerline{GAME OPENING INFORMATION} 

\smallskip

We've got lots of openings in the subszines, check them out!!!
Contact Rip Gooch directly at xyropedes of canada.com and try to entice him to return.
Rip has been a bit missing in action lately, but I am assured that he
SHALL return.

Breaking Away starts in this issue!!! 

I am willing to open another new game of REGULAR Diplomacy if there is enough interest!!!
Fred Wiedemeyer, %e,f,r,i,g,t,a
Brad Wilson, and Shaun Thompson start the list, who would like to join them???

Also, is there any interest in another game of Nuclear Yuppie Evil Empire 
7x7 Dip?
I know it may be getting tired, but I really like it.
We have Karl Schmit on the list, let's get seven!!
It's FREE!!!
I may drop this one shortly if we still have no interest.

I also am starting a game of the variant I designed, Spy Diplomacy.
Signups for that are now open.
Bruce Edwards and Eric Ozog are signed up.
The rules were published recently, ask to see them if you missed them!!!

John Harrington is offering to guest GM a game of Office Politics.
Any interest in that??
Let me or John know!
Jody McCullough and Bruce Edwards are interested, anyone else?
I think I'm going to drop this one as having no interest.

And since Colonia is over, Harold Reynolds is looking to start something else.

Also, I am going to design some postal rules for Devil Take the Hindmost,
and we have an opening here:
Bruce Edwards, Mike Barno, and Eoghan Barry are signed up.
Postal rules from me will be forthcoming shortly, on my never ending to-do list.
I will get them in SOON!
I'm more likely to get these things started if I see some interest.....
I've GOT to do this now,
Eoghan is getting tired of waiting....

Right now, the other thing going is the Modern
Diplomacy game with Wings.
Sean O'Donnell, Jeff O'Donnell, Steve Koehler, Art Schleinkofer,
Bob Holt, Rick Desper, Alexander Woo, and Dave Partridge are signed up for that.
I will start it when I get a full complement of players, we only need TWO more!
%Sean's list: Britain, Spain, Germany, France, Egypt, Turkey, Russia, Ukraine, Italy, and Poland.

\bigskip

\centerline{\bf TAKING OVER ISHKIBIBBLE'S REGULAR DIPLOMACY GAMES ((NOT))}

\smallskip

Last chance for anyone who was a subber to {\it Ishkibibble} to join any new
game for free, but this is a ONE TIME only offer, get your request in now.
It is going to expire VERY shortly.
Marc Ellinger and Fred Wiedemeyer already have taken us up on this request.
Come on, let me call by name who qualifies
for this deal..... Karl Schmit, John Power, Tim Snyder,
Dave Partridge, Graham Wilson, and Kevin Wilson.
I especially would like to fill the Modern Diplomacy game that Dave Partridge
already is in.
As soon as one more game fills (I'm not counting the new Breaking Away game), 
I'm going to pull this offer.

\bigskip

\centerline{\bf THE PHIL REYNOLDS MEMORIAL: 2006B, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SPRING 1902 IS APRIL 21ST, 2007}

\smallskip

\indent {\it Pre-Spring 1902}

\noindent AUSTRIA (Burgess): has a VIE, f TRI, a SER, a BUD, f GRE. 
%a vie-tri, a ser-gre, a bud-ser, f gre-aeg, f tri-alb

\noindent ENGLAND (James): has f LON, f LVP, a BRE, f ENG, f NWY.
%F English Channel - Irish Sea, F Norway - North Sea, F London - English Channel
%F Liverpool - North Atlantic Ocean, A Brest - Paris

\noindent FRANCE (Williams): has a PAR, f POR, a BUR, a SPA.

\noindent GERMANY (Ellinger): has a KIE, a BER, f BEL, 
a DEN.
%a KIE to Munich
%a BER S A Kie to Munich
%f BEL to Holland
%a DEN to Kiel

\noindent ITALY (Crow): has a VEN, f NAP, a MUN, a TUN, f ION.
%a Tun-Apu  f Ion C a Tun-Apu  a Mun s a Ven-Tyrolia  a Ven-Tyrolia   f Naples-Tyr

\noindent RUSSIA (O'Donnell): has f SEV, a WAR, a UKR, 
f BUL(EC), a MOS, f SWE.
%fleet bul east coast- rum supported by army uk and fleet sev
%army mos supports fleet sev  
%fleet sweden- golf of bothnia
%army war-liv

\noindent TURKEY (Wiedemeyer): has f BLA, a CON, 
a ARM.

\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Burgess):&TRI,VIE,BUD,ser,gre&(has 3, bld 2)\cr
%\+ ENGLAND (James):&EDI,LVP,LON,nwy,bre&(has 3, bld 2)\cr
%\+ FRANCE (Williams):&PAR,MAR,spa,por&(has 3, bld 1)\cr
%\+ GERMANY (Ellinger):&KIE,BER,den,bel,&(has 2 or 3, bld 2(r:otb) or 1)\cr
%\+ ITALY (Crow):&ROM,NAP,VEN,tun,mun&(has 3, bld 2)\cr
%\+ RUSSIA (O'Donnell):&WAR,STP,SEV,MOS,bul,swe&(has 4, bld 2)\cr
%\+ TURKEY (Wiedemeyer):&ANK,SMY,CON&(has 2 or 3, bld 1(r:otb) or even)\cr
%\+ Neutral:&hol,rum&(Total=34)\cr
%
%\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: David Burgess, 101 Laurel Lane, Queensbury, NY  12804

(518) 761-6687, dburgess of glensfallshosp.org

\noindent ENGLAND: Drew James, 3644 Whispering Woods Terrace,
Baldwinsville, NY  13027

(315) 652-1956, kjames01 of twcny.rr.com 

\noindent FRANCE: Don Williams, 27505 Artine Drive, Saugus, CA 91350, 
(661) 297-3947, 

wllmsfmly of earthlink.net or dwilliams of fontana.org (\$5)

\noindent GERMANY: Marc Ellinger, 751 Turnberry Drive,
Jefferson City, MO 65109

ellingermc of aol.com

\noindent ITALY: John Crow, 824 Kinwest Parkway \#101,
Irving, TX  75063, (214) 532-1418

\noindent RUSSIA: Jeff O'Donnell, 1345 Simpson Drive, Hurst, TX  76053
%402 Middle Ave., Elyria, OH  44035-5728,

(440) 322-2920 or (440) 225-9203 (cell, as late as midnight Eastern),
unclestaush of yahoo.com

\noindent TURKEY: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  

CANADA  T6T 1N1, (780) 465-6432, wiedem of planet.eon.net 
%cell 780-497-8283; fax 780-468-6432

\bigskip

{\it Game Notes:}

1) Spring 1902's deadline is delayed to April 21st to be sure everyone is on board.
We have one anonymous press item to fill the time.
I actually had all the sets of orders but one
(you should know who you are!!!), but at least one of the sets I had was questioning time to deadline, 
so I held it.

2) Note that Jeff O'Donnell now has an E-Mail address.

\bigskip
 
{\it Press:}

(RED KINGS): 
Damn, this is tedious, I looked at the page I was on. 
``What good is a szine without risque stories, dubious plot themes, 
and full frontal nudity?"   
I was trying to remember what szine I was in, what the continuity was, 
or if I had paid this month's rent.  Way too many details, and I have 
always found that details can be; let's say ``emulsified" with a little brandy.  
But the Cheater's was out, so it was time to head downstairs to McGillicutty's and freshen up.
``Okay, moving the theme forward can wait, at least long enough 
to grab a cold shower and a hot beer", so McGillicutty's it was.  
Simone was still out so I headed toward the door. 
 
There was a rattling banging knock on the office door.  
I immediately knew that it was not a client.  Ah, the deductive mind.  
Often there is the tentative tap, of someone who is embarrassed to hire a private eye, 
or the imbroglio pound of a fist on the door of someone who is 
angry that they have to hire a private eye... or that their wife had. 
Even the ambivalent knock of someone who is passing the pizza menus from 
the local pie shop and doesn't really care if you get one or not.  
But no, this was Burgess's rattle, snap, knuckle that denoted that the 
rent was late and he had had enough.
I debated with ignoring the knock, but quite frankly that would leave us 
with half a page of knocking, escalating to pounding and me either 
cowering under the desk (not likely) or gazing out the window (boring).  
Either way, you ``gentle reader" would be subjected to uninspired 
space-filling narrative.
I flung the door wide,  ``Burgess, my goodness I've missed you. 
Where have you been keeping yourself?"

``I'll have none of that," said the short, squat landlord, ``You're late.  
You're incredibly late. Oh, Hell your deadline is past. 
It's come and gone. Long past. Much, much too late.   
I lease you a good eight paragraphs (excluding dialogue), 
I keep the margins crisp and the font clean.  
I expect you to pay your rent on time!"  
He pulled a folded over calendar from his waistcoat and waved 
it in front of my eyes.  I could see where the months had been ``exed" out. 
I could see where he had erased his deadlines and written in newer, 
later ones, but nevertheless it was still clear I was behind.

``Well, one of my questions is answered…"  he looked perplexed... 
``I haven't paid my rent."

``You're two issues behind!" he blurted.

``Not to worry."

``Not to worry!!??"

``No, I have a case!"

``You have a case?" he echoed.

``Are you going to repeat everything I say?"

``Dialog is not included in the rent... I'm helping you stretch it out."

``I appreciate the contribution; but seriously, don't help me."

``You said you had a case..."

I didn't have a case, but I could hardly see being evicted 
over a small technicality such as that, so I decided to ``embellish".
``Yeah...it's a missing persons case." I said, pulling a cigar from my pocket.  

``Wow, a missing persons case!"  (There's a reason he doesn't charge for dialog.)

``Yeah, yeah that's the ticket!  
A well to do family, a young girl asleep by a stream, 
a secluded location for a picnic, and ``poof" she disappears... yeah, that's it."

``A young girl, or a young lad?"

``Whatever, I'm not into questioning lifestyles...  
I just know the family is concerned, and I have been retained.  
The rent cannot be far away," I lit the cigar, 
pulling to get the ember going.  I knew I had him.

``Well, it sounds most urgent.  I won't stand in your way.  
I assume I can count on your rent."

``Oh, certainly.  
You'll have it by Issue 310, I promise. 311 at the latest, or my name isn't...

\bigskip

\centerline{\bf SPIRALS OF PARANOIA: 2005A, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SPRING 1906 IS APRIL 21ST, 2007}

\smallskip

\indent {\it Winter 1905}

\noindent AUSTRIA (Rauterberg): has a RUM, a SER, 
a ROM, a TRI, f NAP.

\noindent ENGLAND (Wiedemeyer): R f spa(sc)-POR; has f por.
% f por-mid

\noindent FRANCE (Tretick): bld f bre; has f BRE, a GAS, f MID, 
f LON, a SPA, f IRI.

\noindent GERMANY (Ozog for Tallman): has a MUN, a SIL, 
a BOH,
 
a RUH, a TYO, f SKA, a PIE, a MAR, f ENG.

\noindent ITALY (O'Donnell): rem a ven; has a VIE, f APU.

\noindent RUSSIA (Sundstrom): bld a war; has a WAR, a SEV, a ARM, a BUD, a MOS.
%a arm-smy, a sev-rum, a bud-tri, a war-ukr, a mos S a war-ukr

\noindent TURKEY (Biehl): bld a ank, f smy; has a ANK, f SMY,
f BUL(EC), f ION, f GRE, f TUN.

\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Rauterberg):&TRI,ser,rum,nap,rom&(has 5, even)\cr
%\+ ENGLAND (Wiedemeyer):&por?&(has 1, even or out)\cr
%\+ FRANCE (Tretick):&PAR,BRE,spa,por?,lvp,edi,lon&(has 5, bld 1 (or 2 if ENG out))\cr
%\+ GERMANY (Ozog/Tallman):&KIE,BER,MUN,hol,den,bel,swe,&(has 9, even)\cr
%\+ &\enskip mar,nwy \cr
%\+ ITALY (O'Donnell):&VEN,vie&(has 3, rem 1)\cr
%\+ RUSSIA (Sundstrom):&WAR,STP,SEV,MOS,bud&(has 4, bld 1)\cr
%\+ TURKEY (Biehl):&ANK,SMY,CON,gre,tun,bul&(has 4, bld 2)\cr
%\+ Neutral:&none&(Total=34)\cr
%
%\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Paul Rauterberg, 3116 W.~American Dr., 
Greenfield, WI  53221, 

(414) 281-2339 (E-Mail)  trauterberg of wi.rr.com

\noindent ENGLAND: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  CANADA  T6T 1N1, 

(780) 465-6432, wiedem of planet.eon.net 
%cell 780-497-8283; fax 780-468-6432

\noindent FRANCE: Buddy Tretick, 5023 Sewell's Pointe Way,
Fredericksburg, VA  22407, (540) 898-3386

cell (540) 226-5571 (E-Mail) berniebuddy32 of aol.com

\noindent GERMANY: Terry Tallman, PO Box 782, Clinton, WA  98236,
(360) 331-5698 (\$2) 

terryt of whidbey.net

\noindent GERMANY: Temporary Standby is Eric Ozog, PO Box 1138, Granite Falls, WA  
98252-1138,

(360) 691-4264, ElfEric of Juno.com

\noindent ITALY: Jeff O'Donnell, 1345 Simpson Drive, Hurst, TX  76053
%402 Middle Ave., Elyria, OH  44035-5728,

(440) 322-2920 or (440) 225-9203 (cell, as late as midnight Eastern),
unclestaush of yahoo.com

\noindent RUSSIA: Matt Sundstrom, 1760 Robincrest Lane South, Glenview, IL  60025, 
(847) 729-1882, 

Matt.Sundstrom of bbdoch.com or mattandzoe of earthlink.net

\noindent TURKEY: John Biehl, \#8 -- 11530 84th Avenue, Delta, BRITISH COLUMBIA,
V4C 2M1  CANADA, 

(604) 816-0460 (cell) (\$7); jrb of dccnet.com

\bigskip

{\it Game Notes:}

1) Terry is still having some medical problems, 
Eric Ozog is continuing to
negotiate and submit orders for Terry.
Eric originally brought Terry into the Diplomacy hobby all those many
years ago, and so I'm glad he's agreed to do this.

2) Note that Jeff O'Donnell now has an E-Mail address.

\bigskip
 
{\it Press:}

(CONSTANTINOPLE (DEC 31, 1905)): Sultan Hatas I surveyed the 
latest military reports then mumbled out loud, ``The Czar is a madman -- 
what can he possibly gain by this perfidy?"

(BOOB to STAR TREK FANS): In a MAJOR boon to me getting this issue out, Star Trek Press is now
submitted on line, rather than postally, so I don't have to type it in.
In the translation, the Federation computer seems to have lost its capital key.
No problem. 
We'll just Mark Lew/Dick Martinize it with lower case all the way....

(STAR TREK PRESS, 7 OF 9'S LOG): down but not out! 
``i thought it was over so much so that i had made calculations to escape 
to my last reality with captain kirk. things are still pretty bleak here. 
earth and mars are occupied by the cardassians and vulcan is under siege. 
on top of that i've been forced to decommission a troop transport. 
on the other hand thru my diplomatic effort i have received help from 
of all people the grand negus (good thing he is not holding a grudge) 
and the andorians. together we managed to blow up a cardassian transport 
with the loss of all hands (die cardassian scum...) , 
defend vulcan (barley) and as a result of the battle one of our transports  
occupies a cardassian world called thesness 3. in addition,  
the andorians are occupieing cardassia prime. i don't know what 
makes gul dukat more nauseating, the fact that he can't be trusted 
or his bumbling incompetence. of course i can't talk after i ran 
the federation in this universe into the dirt but i can at least 
try to take down the cardassians with me, 7 out".......

\bigskip

\centerline{\bf FLIP FLOP: 2003G, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SPRING 1909 IS APRIL 21ST, 2007}

\smallskip

\indent {\it Pre-Spring 1909}

\noindent AUSTRIA (Wiedemeyer): has f VEN, a BUD, a WAR,  
a UKR, a MOS, a TRI.

\noindent ENGLAND (Schmit): has a BEL, a HOL, a RUH,
f NTH, f NWG, f HEL.

\noindent FRANCE (Jeff O'Donnell): has a BUR, a PIC, f SPA(SC), a GAS.
%army burgandy-belgium supported by army pickerty
%army gascony-spain
%fleet spain south coast- mid atlantic ocean 

\noindent GERMANY (Sundstrom): CORRECTED bld f ber; has f BER, a KIE,
f SWE, a DEN,
 
a NWY, a MUN, f SKA.
%a mun-ruh, a kie-hol, a den-kie, f ber s den-kie, f ska-nth, a nwy-stp, f swe-nwy

\noindent TURKEY (Levinson): has f SMY, a SEV, f ION, a BUL, f APU, 
f NAP, a ALB, 

f ADR, f BLA, a RUM, a SER.

\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Wiedemeyer):&TRI,VIE,BUD,ven,mos,war&(has 5 or 6, bld 1(r:otb) or even)\cr 
%\+ ENGLAND (Schmit):&EDI,LVP,LON,por,bel,hol&(has 7, rem 1)\cr
%\+ FRANCE (Jeff O'Donnell):&PAR,MAR,BRE,spa&(has 4, even)\cr
%\+ GERMANY (Sundstrom):&KIE,BER,MUN,den,swe,stp,nwy&(has 6, bld 1)\cr
%\+ TURKEY (Levinson):&ANK,SMY,CON,bul,sev,ser,gre,&(has 10, bld 1)\cr
%\+ &\enskip tun,rom,rum,nap \cr
%\+ Neutral:&none&(Total=34)\cr
%
%\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Fred Wiedemeyer, Box 92010-Meadowbrook RPO, 
Edmonton, ALBERTA  CANADA  T6T 1N1, 

(780) 465-6432, wiedem of planet.eon.net 
%cell 780-497-8283; fax 780-468-6432

\noindent ENGLAND: Karl Schmit, 1509 O'Keefe Road, DePere, WI  54115, (920) 338-8402, 

diplomacy of new.rr.com (\$3)

\noindent FRANCE: Jeff O'Donnell, 1345 Simpson Drive, Hurst, TX  76053
%402 Middle Ave., Elyria, OH  44035-5728,

(440) 322-2920 or (440) 225-9203 (cell, as late as midnight Eastern),
unclestaush of yahoo.com

\noindent GERMANY: Matt Sundstrom, 1760 Robincrest Lane South, Glenview, IL  60025, 
(847) 729-1882, 

Matt.Sundstrom of bbdoch.com or mattandzoe of earthlink.net

\noindent ITALY: Don Williams, 27505 Artine Drive, Saugus, CA 91350, 
(661) 297-3947, 

wllmsfmly of earthlink.net or dwilliams of fontana.org

\noindent RUSSIA: Sean O'Donnell, 1044 Wellfleet Drive, Grafton, OH  44044,
(440) 926-0230, 

sean\_o\_donnell of hotmail.com

\noindent TURKEY: Alexandre Levinson, Beeklaan 504, 2562BP Den Haag
THE NETHERLANDS, don't need phone, 

levinson7 of hotmail.com (\$5)

\bigskip

{\it Game Notes:}

1) We're pushing off to April 21 for spring deadline.
Also, I looked at Matt's order of FLEET Berlin and wrote ARMY Berlin.
Sorry about that, this is corrected here.
Then I had saved the file as Sundstrom.309 instead of sundstrom.309 and that made it 
initially difficult to re-find.
Sorry, Matt!!!

2) Note that Jeff O'Donnell now has an E-Mail address.

\bigskip

{\it Press:}

(BOOB to WORLD): See item above on other Star Trek press....

(STAR TREK PRESS): ``breathing room", a conversation: kirk K, spock S, and lt. uhura U,
spock on the bridge looking at his sensor monitor not believing his eyes...

S captain,this is curious, i can't pick up any sign of the romulans in the neutral zone. 

K is it possible that our tachion scans are no longer effective at detecting a cloaked ship?

S i don't think so. we can still detect 3 birds of prey in the andorian neutral zone 
although we have no idea as to there exact location or destination. 
they are there. also they have abandoned deep space 2. 

K what do you make of it?

S it can mean only one thing captain. our gorn allies have put up a briiliant fight 
but they are losing badly to the tomarians. also the tomarians have  
2 galaxy class starships 3 light years from mars and deep space one. 
they are no longer needed to defeat the gorn. the romulans are either very stupid 
or they have made a deal with the tomarians and as you know captain the romulans are 
many things but stupid isn't one of them. they have fought us too hard to just quit  
(suddenly lt. uhura's station starts beeping, kirk and spock look at the lieutenant)

U captain i'm getting a message from commander worf from his hiding place in exile 
on the planet grafton.
he's sending us data for a new and improved communications array and tactical 
suggestions as how to deal best with the romulan/tomarian threat.

S fascinating, apparently mr. worf has been monitoring our situation to kill time during his exile.

K any chance the data will help?

S the array will probably help us to communicate more efficiently with everyone 
and may even help us talk to Q.

K why would we want to? 

S good point. 

{\it ((Maybe Kirk and Spock don't want to, but ***I*** might want them to, 
so says Q.))}

K maybe his tactical ideas will help.

S they better because as it stands right now the tomarians are projected to 
take over this universe and if what's left of the gorn are forced to join them then...

K we better learn to speak tomarian!!!

S considering that their language is not comprehendable by the universal 
translator i'd say that's not likely.
(as the bad trek music starts playing kirk and spock just sit there contemplating)

\bigskip

\centerline{\bf I CAN'T FIND MY MONEY!: 2001F, Regular Diplomacy}

\smallskip

\noindent {\bf TWO WAY DRAW BETWEEN AUSTRIA AND GERMANY WAS DECLARED!}

%\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ AUSTRIA (Parker):&TRI,BUD,VIE,ser,rum,nap,&(has 15, bld 1)\cr
%\+ &\enskip war,mos,sev,ven,rom,bul,gre,smy,con,tun\cr
%\+ FRANCE (Kent):&PAR,BRE&(has 4, rem 2)\cr
%\+ GERMANY (Wilson):&KIE,BER,hol,den,bel,MUN,swe,&(has 12, bld 2 (PLAYS ONE SHORT))\cr
%\+ &\enskip nwy,mar,edi,lon,spa,por,stp,lvp\cr
%\+ TURKEY (Miller):&ANK&(has 2, rem 1)\cr
%\+ Neutral:&none&(Total=34)\cr
% 
\bigskip

\indent {\it Addresses of the Participants}

\noindent AUSTRIA: Vern Parker, 337 Winter Hill Place, Powell, OH 43065,
(614) 402-5139

VernDip of aol.com is preferred

\noindent ENGLAND: Mark Kinney, 4830 Westport Road, Apt D,
Louisville KY  40222

alberich of iglou.com

\noindent FRANCE: Doug Kent, 11111 Woodmeadow Pkwy \#2327, Dallas, TX  75228

dougray30 of yahoo.com 

\noindent GERMANY: Kevin Wilson, 18623 Santa Maria Drive, Baton Rouge, LA  70809,
225-751-3857,

ckevinw1 of cox.net

\noindent ITALY: Formerly was Heath Gardner, metaphorman of gmail.com

\noindent ITALY: Mike Barno, 634 Dawson Hill Road, 
Spencer, NY 14883 

mpbarno of lightlink.com 

\noindent RUSSIA: Rick Desper, 

rick\_desper of yahoo.com

\noindent TURKEY: Tim Miller, 258 New Mark Esplanade, Rockville, MD 20850,

tim of webjudge.net

\noindent GM: Jim-Bob Burgess, 664 Smith Street, Providence, RI  02908-4327,
$+$1 401-351-0287

burgess of world.std.com

\bigskip

{\it Game Notes:}

1) I have some comments in hand from Kevin Wilson that he wrote three or four months ago
which I will use next issue.
Thanks to everyone who played!

\bigskip

{\it Press:}


\bigskip

\centerline{\bf SECRETS: 1999D, Regular Diplomacy}

\smallskip

\noindent {\bf THE DUE DATE FOR SPRING 1923 IS APRIL 21ST, 2007}

\smallskip

\indent {\it Winter 1922}

\noindent ENGLAND (Kent): rem f nth; has f ENG, a GAS, 
a BEL, f MID, f POR.

\noindent FRANCE (Sasseville): has f MAR, f SPA(SC), a BUR.     
%standing orders, yes to ANY draw
                                             
\noindent GERMANY (Barno): has a SER.
%votes yes to FREGT, no to EFRT 
%vote YES to FREGT draw

\noindent RUSSIA (Parker): bld f stp(nc), a mos; has f STP(NC), a MOS,
f NWY, f EDI, a WAR, 

a DEN, a KIE, f HEL, a HOL, a LVN.

\noindent TURKEY (Linsey): bld a ank; has a ANK, a CON, f ION, a BUL, 
a BOH, 

a SIL, f WES, a GAL, f GOL, a RUH, a TRI, 
f NAF, a TYO, f PIE, a MUN.
%F NAf - Mid, F Wes S F NAf - Mid, F Pie - Mar, F Lyo S F Pie-Mar, A Ruh - Bel
%A Mun - Ruh, A Tyo - Ven, A Sil H, A Boh -Mun, A Tri H, A Bul - Rum
%A Gal - Boh, F Ion - Tyrr, A Con - Bul, A Ank - Arm

\bigskip
%
%\indent {\it Supply Center Chart}
%
%\+ ENGLAND (Kent):&LON,LVP,bre,por,bel&(has 6, rem 1)\cr
%\+ FRANCE (Sasseville):&PAR,MAR,spa&(has 3, even)\cr
%\+ GERMANY (Barno):&ser&(has 1, even)\cr
%\+ RUSSIA (Parker):&MOS,STP,nwy,swe,den,ber,WAR,kie,&(has 8, bld 2)\cr
%\+ &\enskip edi,hol   \cr
%\+ TURKEY (Linsey):&CON,ANK,SMY,rum,gre,bul,&(has 14, bld 1)\cr
%\+ &\enskip bud,nap,ven,tun,sev,rom,tri,vie,mun \cr
%\+ Neutral:&none&(Total=34)\cr
%
%\bigskip

\indent {\it Addresses of the Participants}

\noindent ENGLAND: Doug Kent, 11111 Woodmeadow Pkwy \#2327, Dallas, TX  75228

dougray30 of yahoo.com 

\noindent FRANCE: Roland Sasseville, Jr., 38 Bucklin Street, Pawtucket,
RI 02861, (401) 481-4280 (\$0)

roland6 of cox.net  

\noindent GERMANY: Mike Barno, 634 Dawson Hill Road, 
Spencer, NY 14883, (607) 589-4906 

mpbarno of lightlink.com 

\noindent RUSSIA: Vern Parker, 337 Winter Hill Place, Powell, OH 43065,
(614) 402-5139

VernDip of aol.com is preferred

\noindent TURKEY: Bruce Linsey, PO Box 234, Kinderhook, NY
12106

GonzoHQ of aol.com

\bigskip

{\it Game Notes:}

1) The RT draw and REFT draw fail.

\bigskip

{\it Press:}
 


\bigskip

\centerline{\bf CAST NO SHADOWS: Breaking Away, Designer's Rules}

\smallskip

Rules are at:

\noindent http://devel.diplom.org/DipPouch/Postal/Zines/TAP/Tinamou/rules/BreakingAway.htm

\noindent Note the special rules for replenishments on the first turn, and double check everyone's math below.  I checked, but someone might still have requested too much card.

\smallskip

\noindent {\bf NEW GAME START -- DUE DATE FOR TURN 1 IS APRIL 21ST, 2007}

\smallskip

%--F--I--N--A--L-- --F--I--N--I--S--H-- --L--I--N--E--
%--S--P--R--I--N--T-- --F--I--N--I--S--H-- --L--I--N--E--
%
\centerline{\it Turn 0}

\smallskip

%\+ 120 (replenish with a 3) &Spades  \cr
%\+ 119 (no replenishment)   &Empty   \cr
%\+ 118 (replenish with a 3) &Clay, El Vez   \cr
%\+ 117 (replenish with a 5) &Carl Sagan, James   \cr
%\+ 116 (replenish with a 7) &Sand, Paige  \cr
%\+ 115 (replenish with a 9) &Hearts, Geri Lee Lewis, Johnny Peso   \cr
%\+ 114 (replenish with a 12)&Marge   \cr
%\+ 113 (replenish with a 13)&Franklin  \cr
%\+ 112 (replenish with a 14)&Wade, Diamonds   \cr
%\+ 111 (no replenishment)   &Empty     \cr
%\+ 110 (replenish with a 3) &Frederick, Clubs, Edmond   \cr

\bigskip
%Sprint Points: 10,8,6,5,4,3,2,1 (final are just double these)
%Movement Order: A/B/C/D; highest card played that turn; highest card in hand

\indent {\it Addresses of the Participants -- Their Team and Their Cards}

\smallskip

\noindent TEAM 1 (Rick Desper): rick\_desper of yahoo.com (0 points)

Team Name: The Turtle Moves; Captained by Cut-My-Own-Throat Dibbler

\+ A: Rincewind the Wizzard &&14 12 3 1 \cr
\+ B: Granny Weatherwax     &&12 11 2   \cr
\+ C: Captain Carrot        &&15 3 2    \cr
\+ D: Death                 &&13 2 1    \cr

(note, Rincewind is accompanied by the Luggage, Granny is on Her Broom, 
Carrot is of the City Watch, and Death is just DEATH!)

Total Replenishments: $0 = 0$
                
\smallskip

\noindent TEAM 2 (Tom Howell): off-the-shelf of olympus.net (0 points)

Team Name: Never Ending Worry Source; Manager: Rumour; Team Captain: Ye Olde Manager

\+ A: Water    &&15 11 3 1 \cr
\+ B: Kyoto    &&14 7 4 \cr
\+ C: Mideast  &&11 6 3 \cr
\+ D: Drugs    &&9 5 2 \cr

Total Replenishments: $0 = 0$        
   
\smallskip

\noindent TEAM 3 ((David Partridge): rebhuhn of rocketmail.com (0 points)
%360-928-9698

Team Name: Famous Four  

\+ A: Krstajic      &&1 6 8 15\cr
\+ B: Vidic         &&4 8 13  \cr
\+ C: Gavrancic     &&3 8 9   \cr
\+ D: Dragutinovic  &&2 6 8   \cr

Total Replenishments: $0 = 0$   
               
\smallskip

\noindent TEAM 4 (Brendan Whyte): obiwonfive of hotmail.com (0 points)

Team Name: The Reverse Alphabeticists

\+ A: Zorro    && 3 10 17 \cr
\+ B: Yorrick  && 3 10 12 \cr
\+ C: Xavier   && 3 7 10  \cr
\+ D: Wally    && 3 3 10  \cr

Total Replenishments: $0 = 0$
%play the 3 for all riders

\smallskip

\noindent TEAM 5 (Alexander Woo): aswoo of yahoo.com (0 points) %awoo@math.ucdavis.edu

Team Name: Just Ordinary; Manager: Credo

\+ A: Agnus     && 15 12 2 1 \cr
\+ B: Sanctus   && 13 8 4    \cr
\+ C: Kyrie     && 10 7 3    \cr  
\+ D: Gloria    && 12 3 1    \cr
           
Total Replenishments: $0 = 0$ 

\smallskip 

\noindent TEAM 6 (Andy York): wandrew of compuserve.com (0 points)

Team Name: Alamo

\+ A: Crockett      && 20 7 3 \cr
\+ B: Travis        && 15 7 3 \cr
\+ C: Bowie         && 10 7 3 \cr
\+ D: Bonham        && 10 3 3 \cr

Total Replenishments: $0 = 0$

\bigskip

{\it Game Notes:}

1) The rules are on the {\it TAP} website in the {\it Tinamou} section.
Ask if you have any questions.
%Up above in parentheses is the card you played to get to where you are
%in the field.  The replenishment card is the last card in your list.
%Be careful to note that the card you played (the one in parentheses) is
%not available for you, for next turn.
%Just for fun, I'm going to keep track of total replenishment, by turn, which is a 
%rough measure of how the teams are doing.
%Of course, it is lining up to get across the sprint and final lines in the
%right places that really counts.
%We can calculate an ``efficiency score" later, which will be the ratio
%of scoring points per replenishment.
%If I'm predicting how the future of this will come out, a 10\% score will
%be really tremendous for this measure.

\bigskip

{\it Press:}

(JUST ORDINARY): Sorry for the delay.  Oops -- we're
starting during Lent?
{\it ((We are, I'm finishing this up on Palm Sunday after church and
singing ``The Palms''; so let me lay the palms in front of you and
have the pelaton strike out!))}

(JIM-BOB to THE END OF THE ALPHABET TEAM): Did you mean that to be
spelled ``Yorick", as from {\it Hamlet}???  I'm not sure who ``Yorrick"
is, but you may mean it as someone else.

\bigskip

{\it Personal Note to You:}

\vfill\eject
\end
